### 2025-02-13 paper/paper.tex
Initial commit

\subsection*{Social Learning in Networks}

We adapt the model in Brandl (2024). Specifically, we let $N = \{1, \ldots, n\}$ be the set of agents, and $T = \{1, 2, \ldots, t \}$ be the finite set of periods. In each period, each agent chooses an action $a$ from the same finite set of actions $A$. The finite set of states of the world is $\Omega$, where the true state $\omega \in \Omega$ is a random variable with full support distribution over $\Omega$. Agents share the same utility function $u : A \times \Omega \to \mathbb{R}$ that depends on their own action and the state of the world, where $a_\theta$ denotes the unique optimal (correct) action in that state. It's also assumed that $a_\theta \neq a_{\theta'}$ for any two distinct states $\theta, \theta' \in \Omega$. In each period $t \in T$, each agent $i$ privately observes a signal $s_t^i$ from a set of signals $S$. Conditional on each state $\theta$, $s_t^i$ has distribution $\mu_\theta \in \Delta(S)$, and signals are independent across agents and periods. Observing the signal realization $s \in S$ changes the log-likelihood ratio of the observing agent between the states $\theta$ and $\theta'$ by,
\[
\ell_{\theta, \theta'}(s) = \log \frac{d\mu_\theta(s)}{d\mu_{\theta'}(s)}.
\]
Each agent $i$ also observes the actions of her neighbors $N^i \subset N$, thus the information available to Agent $i$ in period $t$ before choosing an action is the collection of information sets $\mathcal{I}^i_{\leq t} = S^t \times A^{|N^i| \times (t-1)}$. It's said that Agent $i$ makes a mistake in period $t$ if $a_t^i \neq a_\omega$, and that $i$ learns at rate $r$ if,
\[
r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t^i \neq a_\omega).
\]
Theorem 1 states that for any number of agents and any strategy profile, there exists an agent $i$ such that,
\[r^i \leq r_{bdd} = \min_{\theta \neq \theta'}\{E_\theta[\ell_{\theta,\theta'}] + E_{\theta'}[\ell_{\theta',\theta}]\}.\]

\subsection*{Partially Observable Markov Games}
Following the MARL literature, we model the social learning framework as a partially observable Markov game defined by the tuple,
\[(N, \Psi, A, \{O_i\}_{i \in N}, \Gamma, R, \gamma)\]
where,
\begin{itemize}
\item $N$ is the set of agents,
\item $\Psi $ is the Markov state space, with individual element $\psi$,
\item $A$ is the shared action space for all agents, with individual element $a$,
\item $O_i$ is the observation space for agent $i$, with individual element $o_i$,
\item $\Gamma : \Psi \times A^n \times \Psi \to [0,1]$ is the transition function,
\item $R: A \times \Psi \to \mathbb{R}$ is the shared reward function for all agents,
\item $\gamma \in [0,1)$ is the discount factor.
\end{itemize}

\subsubsection*{Markov States, Signals \& Actions}
For simplicity, we let $\Omega = \{\theta_1, \ldots, \theta_k\}$ be the set of possible states of the world; $S = \{s_k : \theta_k \in \Omega\}$ be the signal space, with $s_k$ being the signal for state $\theta_k$ and $A = \{a_k : \theta_k \in \Omega\}$ be the action space, with $a_k$ being the optimal action for state $\theta_k$. We can then define the Markov state space as 
\begin{equation*}
    \Psi = \{\omega\} \times S \times A^n
\end{equation*}
which accounts for the true state of the world, current period signal and current period actions. We leave the tracking of signal and action histories to the Recurrent Neural Networks (RNNs), thereby avoiding exponentially increasing Markov state space formulations.

\subsubsection*{Observations}
The observation for each agent $i$ at time $t$ is,
\begin{equation*}
o^i_t = (s^i_t, \bm{a_t}) \in O_i,
\end{equation*}
where $O_i = S \times A^n$ and $\bm{a_t} = \{a_t^1, \ldots, a_t^n\}$ is the action profile at period $t$.

\subsubsection*{Transitions}
The stochastic components of the Markov state transitions are the signal realizations and the actions taken by the agents. Formally, for state 
$\psi_t = (\omega, (s^i_t)_{i \in N}, \bm{a_t})$ and next state ${}\psi_{t+1} = (\omega, (s^i_{t+1})_{i \in N}, \bm{a_{t+1}} )$, the transition function can be written as,
\begin{equation*}
    \Gamma(\psi_{t+1}|\psi_t) = \prod_{i \in N} \mu_{\omega}(s^i_{t+1}) \prod_{i \in N} \sigma_t^i(\mathcal{I}^i_{\leq t})(a^i_{t+1})
\end{equation*}
where $\sigma_t^i$ is the \textit{policy} or \textit{strategy} of agent $i$ at period $t$. There are two important points to consider here. First, in this formulation, we condition the policies on action and signal histories that are not part of the Markov state space. The fact that we can still use this information to compute the policies stems from the technology of RNNs that allows for a memory buffer from past observations, without explicitly storing the observations themselves. Second, diverging from the original paper, we allow for policies to be time-dependent, which corresponds to the learning process of the RL agents.
\subsubsection*{Rewards}
The reward functions are identical across agents with $R_i(a, \psi)=R(a,\psi), \: \forall i \in N$. The true reward is the flow payoff $u(a^i_t, \omega)$, where $u: A \times \Omega \rightarrow \mathbb{R}$ is known but its realizations are not observed. Lacking this observation, we follow Huang et al. (2024) and construct an observed payoff function $v(a, s)$ with the property that, 
\[\mathbb{E}_{s \sim \mu^{\theta}}[v(a, s)] = u(a, \theta), \quad \forall \theta \in \Omega.\] Setting $u(a, \omega) = \mathbf{1}_{\{a=a^{\omega}\}}$ the problem of constructing such a function amounts to solving a system of $|\Omega|$ linear equations for each action.
More precisely, let $\bm{\mu}$ be an $k \times k$ matrix representing the signal distributions, where the entry $\mu^{\theta}(s)$ denotes the probability of observing signal $s$ in state $\theta$. We assume $\mu^{\theta}(s_{\theta}) > \mu^{\theta}(s)$, $\forall s \in S$, $\theta \in \Omega$, which implies that signal distributions are linearly independent across states and $\bm{\mu}$ is invertible. Similarly, for each action $a \in A$, define the \textit{utility vector} $\bm{u}_a \in \mathbb{R}^k$ as,
\begin{equation*}
    \bm{u}_a = \begin{bmatrix} u(a, \theta_1) \\ u(a, \theta_2) \\ \vdots \\ u(a, \theta_k) \end{bmatrix}.
\end{equation*}
The vector of observable reward functions $\bm{v}_a \in \mathbb{R}^n$ for action $a$ is the unique solution to the linear system as in,
\begin{align*}
    \bm{\mu} \bm{v}_a &= \bm{u}_a, \\
    \bm{v}_a &= \bm{\mu}^{-1} \bm{u}_a.
\end{align*}
Hence, the reward $v(a, s_j)$ for choosing action $a$ when observing signal $s_j$ is,
\begin{equation*}
    v(a, s_j) = \sum_{l=1}^k \left( \bm{\mu}^{-1} \right)_{jl} u(a, \theta_l),
\end{equation*}
where $\left( \bm{\mu}^{-1} \right)_{jl}$ denotes the $(j, l)$-th element of $\bm{\mu}^{-1}$.

\paragraph*{Binary Case with $|\Omega|=2$.}

For the case with two states of the world and symmetric signals with accuracy $q > 0.5$ we have,
\begin{equation*}
    \bm{\mu} = \begin{bmatrix} q & 1 - q \\ 1 - q & q \end{bmatrix}, \quad \bm{\mu}^{-1} = \frac{1}{2q - 1} \begin{bmatrix} q & -(1 - q) \\ -(1 - q) & q \end{bmatrix}
\end{equation*}
Hence, for action $a$ and flow utility $u(a, \omega) = \mathbf{1}_{\{a = \omega\}}$, the observed reward function becomes,
\begin{equation*}
    R(a, \psi) = v(a, s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1 - q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q - 1}.
\end{equation*}

\subsection*{Recurrent Neural Networks}
Before proceeding with the RNN architecture and learning framework, we define the key activation functions and operations:

The hyperbolic tangent function $\tanh: \mathbb{R} \to (-1,1)$ is defined as,
\[
    \tanh(x) = \frac{e^x - e^{-x}}{e^x + e^{-x}}.
\]

The sigmoid function $\text{sigmoid} : \mathbb{R} \to (0,1)$ is defined as,
\[
    \sigma(x) = \frac{1}{1 + e^{-x}}.
\]

The softmax function $\text{softmax}: \mathbb{R}^k \to \Delta^{k-1}$ maps a vector to a probability distribution,
\[
    \text{softmax}(x)_i = \frac{e^{x_i}}{\sum_{j=1}^k e^{x_j}}.
\]

The Hadamard (element-wise) product $\odot: \mathbb{R}^n \times \mathbb{R}^n \to \mathbb{R}^n$ is defined as,
\[
    (x \odot y)_i = x_i y_i.
\]
Following our partial observability setting, each agent $i$ observes both their private signal $s^i_t$ and the action profile $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$ at time $t$. The collection of these observations up to time $t$ forms the information set $\mathcal{I}^i_{\leq t} = S^t \times A^{|N_i|×(t-1)}$. Rather than including this growing information set in our Markov state space, we employ Recurrent Neural Networks to maintain a compact representation while preserving the essential historical information.

\subsubsection*{RNN Architecture for Information Processing}
For each agent $i$, we implement an RNN that processes the sequence of observations $o_t^i = (s_t^i, \mathbf{a}_t) \in \mathcal{O}_i$ to produce a hidden state $h_t^i \in \mathbb{R}^d$ that encodes the information set $\mathcal{I}_{\leq t}^i$. The RNN updates its hidden state through a recursive function,
\begin{equation*}
h_t^i = f_{\eta_i}(h_{t-1}^i, o_t^i),
\end{equation*}
where $f_{\eta_i}$ is parameterized by $\eta_i$ and implemented using a Gated Recurrent Unit (GRU) architecture, following \cite{cho2014learning}. The GRU utilizes two primary gates - an update gate and a reset gate - to selectively incorporate new information while preserving relevant historical context:
\begin{align*}
z_t^i &= \text{sigmoid}(W_z^i[h_{t-1}^i, s_t^i, \mathbf{a}_t] + b_z^i) & \text{(update gate)} \\
\rho_t^i &= \text{sigmoid}(W_\rho^i[h_{t-1}^i, s_t^i, \mathbf{a}_t] + b_\rho^i) & \text{(reset gate)} \\
\tilde{h}_t^i &= \tanh(W_h^i[\rho_t^i \odot h_{t-1}^i, s_t^i, \mathbf{a}_t] + b_h^i) & \text{(candidate state)} \\
h_t^i &= (1-z_t^i) \odot h_{t-1}^i + z_t^i \odot \tilde{h}_t^i & \text{(final update)}
\end{align*}
Here, $W_z^i, W_\rho^i, W_h^i$ are weight matrices and $b_z^i, b_\rho^i, b_h^i$ are bias vectors specific to agent $i$.

The update gate $z_t^i$ determines how much of the previous hidden state should be retained versus updated with new information. When $z_t^i$ is close to 1, the network prioritizes the new candidate state $\tilde{h}_t^i$; when close to 0, it maintains more of the previous state $h_{t-1}^i$. This mechanism is particularly important in our social learning context, as it allows agents to appropriately weight new signals against accumulated historical evidence.

The reset gate $\rho_t^i$ controls how much of the previous hidden state should influence the computation of the new candidate state $\tilde{h}_t^i$. When $\rho_t^i$ is close to 0, it effectively "forgets" the previous state, allowing the network to drop irrelevant historical information. This is crucial when the agent needs to adapt to significant changes in the environment or when previous beliefs need to be revised based on new, strong evidence.

The candidate state $\tilde{h}_t^i$ is computed using the reset gate-modulated previous state along with current observations. The hyperbolic tangent activation ensures the candidate state values remain bounded between -1 and 1, promoting stable learning dynamics. The strategy or policy $\sigma_t^i$ of agent $i$ at time $t$ is then derived from this hidden state through a policy network,

\begin{equation*}
\sigma_t^i(\mathcal{I}_{\leq t}^i) = \pi_{\phi_i}(h_t^i),
\end{equation*}
where $\pi^i_{\phi_i}$ is a neural network with parameters $\phi_i$ that maps the hidden state to a distribution over actions,

\begin{equation*}
    \pi^i_{\phi_i}(h^i_t) = \text{softmax}(W^i_{\pi}h^i_t + b^i_{\pi}).
\end{equation*}
This architecture effectively augments our original Markov state space $\Psi = \{\omega\} \times S \times A^n$ with the RNN hidden states,

\begin{equation*}
    \tilde{\Psi} = \{\omega\} \times S \times A^n \times \mathcal{H}^n,
\end{equation*}
where $\mathcal{H} \subset \mathbb{R}^d$ is the space of hidden states. The transition function $\Gamma$ is accordingly modified to include the hidden state updates,

\begin{equation*}
    \tilde{\Gamma}(\tilde{\psi}_{t+1}|\tilde{\psi}_t) = \prod_{i \in N} \mu_\omega(s^i_{t+1}) \prod_{i \in N} \pi^i_{\phi_i}(h^i_t),
\end{equation*}
where $\tilde{\psi}_t = (\omega, (s^i_t)_{i \in N}, \mathbf{a}_t, (h^i_t)_{i \in N})$. This gated architecture allows each agent to maintain a compact yet informative representation of their observation history, enabling them to learn sophisticated social learning strategies while keeping the state space tractable.

\subsection*{Centralized Training with Decentralized Execution}
We adopt a CTDE paradigm where each agent maintains a decentralized actor network $\pi^i_{\phi_i}$ for action execution, while training utilizes a centralized critic network $Q_{\xi}$ that has access to the global state. This approach preserves the decentralized nature of action execution while leveraging additional information during training, which mimics the role of a \textit{social planner.}

\subsubsection*{Decentralized Actor Network}
The decentralized actor network for agent $i$ maps the hidden state to a policy distribution as before,
\[
    \pi^i_{\phi_i}(a^i_t|h^i_t) = \text{softmax}(W^i_{\pi}h^i_t + b^i_{\pi}).
\]
Then, we use the policy gradient update to optimize this network given as,
\[
    \nabla_{\phi_i} J(\phi_i) = \mathbb{E}\left[\nabla_{\phi_i} \log \pi^i_{\phi_i}(a^i_t|h^i_t) A^i(\tilde{\psi}_t)\right]
\]
where $A^i(\tilde{\psi}_t)$ is the advantage function computed using the centralized critic.

\subsubsection*{Centralized Critic Network}

The centralized critic takes as input the global state $\psi_t$ and all agents' hidden states:
\[
    Q_{\xi}(\psi_t, \mathbf{h}_t) = W_Q[\psi_t, \mathbf{h}_t, \mathbf{a}_t] + b_Q
\]
where $\mathbf{h}_t = (h^1_t, \ldots, h^n_t)$. The critic network is updated to minimize the \textit{temporal difference} error with the loss function,
\[
    \mathcal{L}(\xi) = \mathbb{E}\left[(r_t + \gamma Q_{\xi}(\tilde{\psi}_{t+1}) - Q_{\xi}(\tilde{\psi}_t))^2\right].
\]
The advantage function for each agent is computed as,
\[
    A^i(\tilde{\psi}_t) = Q_{\xi}(\tilde{\psi}_t) - V_{\xi}(\tilde{\psi}_t),
\]
where $V_{\xi}(\tilde{\psi}_t) = \mathbb{E}_{\mathbf{a}_t \sim \boldsymbol{\pi}}[Q_{\xi}(\tilde{\psi}_t]$ is the value function.

\subsubsection*{Learning Algorithm}
The complete learning process alternates between the actor network update,
\[
    \phi_i \leftarrow \phi_i + \alpha \nabla_{\phi_i} J(\phi_i),
\]
and the critic network update,
\[
    \xi \leftarrow \xi - \beta \nabla_{\xi} \mathcal{L}(\xi).
\]

\subsection*{Single Agent Implementation}

To validate our approach, we first implement a single-agent version of the learning framework. This simplified setting allows us to verify the learning dynamics and compare them against the theoretical bounds established in Brandl (2024). The implementation follows the binary state case ($|\Omega| = 2$) with symmetric signals of accuracy $q > 0.5$.

\subsubsection*{Metrics Tracking}
We track two key metrics throughout the learning process:

\begin{itemize}
    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
    \[
        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
    \]

    \item \textit{Learning Rate}: Following the paper's definition, we compute:
    \[
        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
    \]
    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
\end{itemize}

\subsubsection*{Environment}
The environment implements the binary state case with the following components:

\begin{itemize}
    \item A fixed true state $\omega \in \{0,1\}$ drawn uniformly at random at initialization
    \item Signal generation with accuracy $q$:
    \[
        P(s_t = \omega) = q, \quad P(s_t \neq \omega) = 1-q
    \]
    \item The reward function derived in the binary case section:
    \[
        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
    \]
\end{itemize}

\subsubsection*{Neural Network Architecture}
The agent employs an actor-critic architecture with both networks using GRU cells to process the history of signals. The GRU implementation follows the equations presented in the RNN Architecture section, with the following specifications:

\paragraph{Actor Network}
The actor network maps the signal history to a policy over actions:
\begin{align*}
    h_t &= \text{GRU}(s_t, h_{t-1}) \\
    \pi(a_t|h_t) &= \text{softmax}(W_\pi h_t + b_\pi)
\end{align*}

\paragraph{Critic Network}
The critic network estimates state values using the same GRU architecture:
\begin{align*}
    h_t &= \text{GRU}(s_t, h_{t-1}) \\
    V(h_t) &= W_v h_t + b_v
\end{align*}

\subsubsection*{Training Process}
The agent is trained using a variant of the Advantage Actor-Critic (A2C) algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.

The algorithm implements the A2C training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics. The actor network learns a policy that minimizes mistakes in predicting the true state, while the critic network estimates state values to compute advantages for policy updates.

\subsubsection*{Theoretical Bounds}
For the binary case with symmetric signals, the theoretical bound on the learning rate is:
\[
    r_{bdd} = -\log(1-q_{bdd}) = -\log(1-(2q-1))
\]
where $q_{bdd} = 2q-1$ is the bound on the probability of choosing the correct action. This provides a benchmark against which we can evaluate the empirical learning rate of our implementation.

\subsubsection*{Empirical Results}
The implementation is evaluated over multiple training runs with different random seeds. For each run, we track:
\begin{itemize}
    \item The evolution of the mistake rate over time
    \item The empirical learning rate compared to the theoretical bound
    \item The convergence of the policy to the optimal action
\end{itemize}

### 2025-02-13 paper/paper_copy.tex
Initial commit

--- 2025-02-13 paper/paper.tex
@@
 
-\subsection*{Single Agent Implementation}
+\pagebreak
 
-To validate our approach, we first implement a single-agent version of the learning framework.
-This simplified setting allows us to verify the learning dynamics and compare them against the theoretical bounds established in Brandl (2024).
-The implementation follows the binary state case ($|\Omega| = 2$) with symmetric signals of accuracy $q > 0.5$.
+\section*{Appendix A: Theoretical Background}
 
-\subsubsection*{Metrics Tracking}
-We track two key metrics throughout the learning process:
+\subsection*{Deep Reinforcement Learning Framework}
 
-\begin{itemize}
-    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
+The foundation of our deep reinforcement learning approach builds upon the policy gradient theorem \citep{sutton2000policy} and its extensions to deep neural networks \citep{mnih2015human}.
+In the context of multi-agent systems, we specifically utilize the actor-critic framework \citep{konda2000actor}, which has been shown to be particularly effective in handling the increased complexity of multi-agent environments \citep{lowe2017multi}.
+
+\subsection*{Policy Gradient Methods}
+
+The core objective in reinforcement learning is to maximize the expected cumulative discounted reward,
 \[
-        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
+J(\phi) = \mathbb{E}_{\tau \sim \pi_\phi}[\sum_{t=0}^{\infty} \gamma^t r_t]
+\]
+where $\tau$ represents a trajectory, and $\pi_\phi$ is the policy parameterized by $\phi$. The policy gradient theorem \citep{sutton2000policy} provides the gradient of this objective,
+\[
+\nabla_\phi J(\phi) = \mathbb{E}_{\tau \sim \pi_\phi}[\sum_{t=0}^{\infty} \nabla_\phi \log \pi_\phi(a_t|s_t) Q^{\pi_\phi}(s_t, a_t)]
+\]
+In practice, we use the advantage function $A(s_t, a_t)$ instead of the Q-function to reduce variance \citep{schulman2015high}:
+
+\[
+\nabla_\phi J(\phi) = \mathbb{E}_{\tau \sim \pi_\phi}[\sum_{t=0}^{\infty} \nabla_\phi \log \pi_\phi(a_t|s_t) A(s_t, a_t)]
 \]
 
-    \item \textit{Learning Rate}: Following the paper's definition, we compute:
+\subsection*{Value Function Approximation}
+The value function approximation follows the temporal difference (TD) learning framework \citep{sutton2018reinforcement}.
+The value network parameters $\phi$ are updated to minimize the mean squared TD error:
+
 \[
-        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
+\mathcal{L}(\phi) = \mathbb{E}_{(s_t, a_t, r_t, s_{t+1}) \sim \mathcal{D}}[(r_t + \gamma V_\phi(s_{t+1}) - V_\phi(s_t))^2]
 \]
-    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
+
+where $\mathcal{D}$ represents the replay buffer of experiences. This approach has been shown to be particularly effective when combined with deep neural networks \citep{mnih2015human}.
+
+\subsubsection*{LSTM Implementation}
+
+In practice, we use Long Short-Term Memory (LSTM) cells to better capture long-term dependencies in the information sets. The LSTM update equations for each agent $i$ are:
+\begin{align}
+    f^i_t &= \sigma(W^i_f [h^i_{t-1}, s^i_t, \mathbf{a}_t] + b^i_f) \\
+    \iota^i_t &= \sigma(W^i_\iota [h^i_{t-1}, s^i_t, \mathbf{a}_t] + b^i_\iota) \\
+    \tilde{c}^i_t &= \tanh(W^i_c [h^i_{t-1}, s^i_t, \mathbf{a}_t] + b^i_c) \\
+    c^i_t &= f^i_t \odot c^i_{t-1} + \iota^i_t \odot \tilde{c}^i_t \\
+    o^i_t &= \sigma(W^i_o [h^i_{t-1}, s^i_t, \mathbf{a}_t] + b^i_o) \\
+    h^i_t &= o^i_t \odot \tanh(c^i_t)
+\end{align}
+where $c^i_t$ is the cell state that allows for longer-term memory preservation.
+
+\subsection*{Attention-Enhanced RNN Architecture}
+
+We extend the base RNN architecture by incorporating both self-attention and cross-attention mechanisms to better capture temporal dependencies and agent interactions.
+The attention mechanisms allow each agent to selectively focus on relevant historical information and other agents' actions.
+
+\subsubsection*{Self-Attention Mechanism}
+For each agent $i$, we implement a self-attention mechanism that operates over a window of $K$ previous hidden states.
+Let $H_t^i = [h_{t-K+1}^i, ..., h_t^i] \in \mathbb{R}^{d \times K}$ be the matrix of $K$ previous hidden states.
+The self-attention operation is defined as:
+
+\begin{align*}
+Q_t^i &= W_Q^i h_t^i + b_Q^i & \text{(query)} \\
+K_t^i &= W_K^i H_t^i + b_K^i & \text{(keys)} \\
+V_t^i &= W_V^i H_t^i + b_V^i & \text{(values)} \\
+\alpha_t^i &= \text{softmax}\left(\frac{(Q_t^i)^\top K_t^i}{\sqrt{d}}\right) & \text{(attention weights)} \\
+c_t^i &= V_t^i \alpha_t^i & \text{(context vector)}
+\end{align*}
+
+where $W_Q^i, W_K^i, W_V^i$ are learned weight matrices and $b_Q^i, b_K^i, b_V^i$ are bias vectors. The scaling factor $\sqrt{d}$ prevents the dot products from growing too large in magnitude.
+
+\subsubsection*{Cross-Attention for Agent Interactions}
+To better capture agent interactions, we implement a cross-attention mechanism that allows each agent to attend to other agents' hidden states.
+For agent $i$, let $H_t^{-i} = [h_t^1, ..., h_t^{i-1}, h_t^{i+1}, ..., h_t^n] \in \mathbb{R}^{d \times (n-1)}$ be the matrix of other agents' current hidden states.
+The cross-attention operation is:
+
+\begin{align*}
+Q_t^{i,c} &= W_{Q,c}^i h_t^i + b_{Q,c}^i & \text{(cross query)} \\
+K_t^{i,c} &= W_{K,c}^i H_t^{-i} + b_{K,c}^i & \text{(cross keys)} \\
+V_t^{i,c} &= W_{V,c}^i H_t^{-i} + b_{V,c}^i & \text{(cross values)} \\
+\beta_t^i &= \text{softmax}\left(\frac{(Q_t^{i,c})^\top K_t^{i,c}}{\sqrt{d}}\right) & \text{(cross-attention weights)} \\
+m_t^i &= V_t^{i,c} \beta_t^i & \text{(cross-context vector)}
+\end{align*}
+
+\subsubsection*{Enhanced GRU Architecture}
+We modify the original GRU architecture to incorporate both attention mechanisms. The updated equations become:
+
+\begin{align*}
+\hat{h}_t^i &= [h_t^i; c_t^i; m_t^i] & \text{(concatenated state)} \\
+z_t^i &= \text{sigmoid}(W_z^i[\hat{h}_t^i, s_t^i, \mathbf{a}_t] + b_z^i) & \text{(update gate)} \\
+\rho_t^i &= \text{sigmoid}(W_\rho^i[\hat{h}_t^i, s_t^i, \mathbf{a}_t] + b_\rho^i) & \text{(reset gate)} \\
+\tilde{h}_t^i &= \tanh(W_h^i[\rho_t^i \odot \hat{h}_t^i, s_t^i, \mathbf{a}_t] + b_h^i) & \text{(candidate state)} \\
+h_t^i &= (1-z_t^i) \odot \hat{h}_t^i + z_t^i \odot \tilde{h}_t^i & \text{(final update)}
+\end{align*}
+
+\subsubsection*{Multi-Head Attention Extension}
+To capture different types of dependencies simultaneously, we extend both attention mechanisms to use multiple attention heads.
+For $L$ attention heads, each head $l \in \{1, ..., L\}$ computes its own attention weights and context vectors:
+
+\begin{align*}
+Q_{t,l}^i &= W_{Q,l}^i h_t^i + b_{Q,l}^i \\
+K_{t,l}^i &= W_{K,l}^i H_t^i + b_{K,l}^i \\
+V_{t,l}^i &= W_{V,l}^i H_t^i + b_{V,l}^i \\
+\alpha_{t,l}^i &= \text{softmax}\left(\frac{(Q_{t,l}^i)^\top K_{t,l}^i}{\sqrt{d/L}}\right) \\
+c_{t,l}^i &= V_{t,l}^i \alpha_{t,l}^i
+\end{align*}
+
+The final context vector is computed by concatenating the outputs from all heads and applying a linear transformation:
+
+\[
+c_t^i = W_O^i[c_{t,1}^i; ...; c_{t,L}^i] + b_O^i
+\]
+
+Similarly for the cross-attention mechanism:
+
+\begin{align*}
+Q_{t,l}^{i,c} &= W_{Q,c,l}^i h_t^i + b_{Q,c,l}^i \\
+K_{t,l}^{i,c} &= W_{K,c,l}^i H_t^{-i} + b_{K,c,l}^i \\
+V_{t,l}^{i,c} &= W_{V,c,l}^i H_t^{-i} + b_{V,c,l}^i \\
+\beta_{t,l}^i &= \text{softmax}\left(\frac{(Q_{t,l}^{i,c})^\top K_{t,l}^{i,c}}{\sqrt{d/L}}\right) \\
+m_{t,l}^i &= V_{t,l}^{i,c} \beta_{t,l}^i \\
+m_t^i &= W_{O,c}^i[m_{t,1}^i; ...; m_{t,L}^i] + b_{O,c}^i
+\end{align*}
+
+\subsubsection*{Learning Considerations}
+The addition of attention mechanisms introduces several hyperparameters that need to be tuned:
+\begin{itemize}
+\item History window size $K$ for self-attention
+\item Number of attention heads $L$
+\item Hidden dimension $d$ for attention computations
 \end{itemize}
 
-\subsubsection*{Environment}
-The environment implements the binary state case with the following components:
+The training process remains similar to the original architecture, but with additional parameters in both actor and critic networks.
+The critic network now also incorporates attention mechanisms when processing the global state:
 
+\[
+Q_{\xi}(\psi_t, \mathbf{h}_t) = W_Q[\psi_t, \text{Attention}(\mathbf{h}_t), \mathbf{a}_t] + b_Q
+\]
+
+where $\text{Attention}(\mathbf{h}_t)$ applies both self and cross-attention mechanisms to the collection of all agents' hidden states.
+
+\section*{Detailed Multi-Agent Attention PPO (MA-APPO) Algorithm}
+
+\subsection*{Network Architectures}
+
+\subsubsection*{1. Actor Network Architecture}
+
+For each agent $i$, the actor network consists of:
+
+\begin{enumerate}
+\item \textbf{Input Processing Layer:}
+   \[
+   x_t^i = W_{\text{in}}[s_t^i; \mathbf{a}_t] + b_{\text{in}}
+   \]
+
+\item \textbf{GRU Layer with Attention:}
+   \begin{align*}
+   z_t^i &= \sigma(W_z^i[h_{t-1}^i, x_t^i] + b_z^i) \\
+   r_t^i &= \sigma(W_r^i[h_{t-1}^i, x_t^i] + b_r^i) \\
+   \tilde{h}_t^i &= \tanh(W_h^i[r_t^i \odot h_{t-1}^i, x_t^i] + b_h^i) \\
+   h_t^i &= (1-z_t^i) \odot h_{t-1}^i + z_t^i \odot \tilde{h}_t^i
+   \end{align*}
+
+\item \textbf{Self-Attention Module:}
+   \begin{align*}
+   Q_t^i &= W_Q^i h_t^i + b_Q^i \\
+   K_t^i &= W_K^i H_t^i + b_K^i \\
+   V_t^i &= W_V^i H_t^i + b_V^i \\
+   \alpha_t^i &= \text{softmax}\left(\frac{Q_t^i(K_t^i)^\top}{\sqrt{d_k}}\right) \\
+   c_t^i &= V_t^i\alpha_t^i
+   \end{align*}
+
+\item \textbf{Cross-Attention Module:}
+   \begin{align*}
+   Q_t^{i,c} &= W_{Q,c}^i h_t^i + b_{Q,c}^i \\
+   K_t^{i,c} &= W_{K,c}^i H_t^{-i} + b_{K,c}^i \\
+   V_t^{i,c} &= W_{V,c}^i H_t^{-i} + b_{V,c}^i \\
+   \beta_t^i &= \text{softmax}\left(\frac{Q_t^{i,c}(K_t^{i,c})^\top}{\sqrt{d_k}}\right) \\
+   m_t^i &= V_t^{i,c}\beta_t^i
+   \end{align*}
+
+\item \textbf{Policy Head:}
+   \[
+   \pi_{\phi_i}(a|h_t^i) = \text{softmax}(W_\pi[h_t^i; c_t^i; m_t^i] + b_\pi)
+   \]
+\end{enumerate}
+
+\subsubsection*{2. Critic Network Architecture}
+
+The centralized critic network processes global state information:
+
+\begin{enumerate}
+\item \textbf{State Embedding:}
+   \[
+   e_t = W_e[\psi_t; \mathbf{h}_t] + b_e
+   \]
+
+\item \textbf{Multi-head Attention:}
+   For each head $l \in \{1,\ldots,L\}$:
+   \begin{align*}
+   Q_{t,l} &= W_{Q,l}e_t + b_{Q,l} \\
+   K_{t,l} &= W_{K,l}e_t + b_{K,l} \\
+   V_{t,l} &= W_{V,l}e_t + b_{V,l} \\
+   \text{head}_l &= \text{softmax}\left(\frac{Q_{t,l}K_{t,l}^\top}{\sqrt{d_k}}\right)V_{t,l}
+   \end{align*}
+
+\item \textbf{Value Head:}
+   \[
+   V(s_t) = W_v[\text{concat}(\text{head}_1,\ldots,\text{head}_L)] + b_v
+   \]
+\end{enumerate}
+
+\subsection*{Detailed Training Algorithm}
+
+\begin{enumerate}
+\item \textbf{Initialization:}
    \begin{itemize}
-    \item A fixed true state $\omega \in \{0,1\}$ drawn uniformly at random at initialization
-    \item Signal generation with accuracy $q$:
+   \item Initialize actor networks $\pi_{\phi_i}$ for each agent $i$
+   \item Initialize centralized critic network $V_\theta$
+   \item Set up experience buffer $\mathcal{D}$ with capacity $N$
+   \item Initialize environment runners for parallel data collection
+   \end{itemize}
+
+\item \textbf{Main Training Loop:}
+   \begin{enumerate}
+   \item \textbf{Data Collection Phase:}
+      \begin{itemize}
+      \item Run $M$ parallel environments for $T$ timesteps
+      \item For each timestep $t$ and agent $i$:
+         \begin{itemize}
+         \item Process observation $o_t^i$ through GRU and attention layers
+         \item Sample action $a_t^i \sim \pi_{\phi_i}(\cdot|h_t^i)$
+         \item Store tuple $(o_t^i, a_t^i, r_t^i, h_t^i)$ in buffer $\mathcal{D}$
+         \end{itemize}
+      \end{itemize}
+
+   \item \textbf{Advantage Estimation:}
+      \begin{itemize}
+      \item Compute returns using GAE-$\lambda$:
       \[
-        P(s_t = \omega) = q, \quad P(s_t \neq \omega) = 1-q
+      \hat{R}_t = r_t + \gamma\lambda r_{t+1} + (\gamma\lambda)^2r_{t+2} + \cdots
       \]
-    \item The reward function derived in the binary case section:
+      \item Calculate advantages:
       \[
-        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
+      \hat{A}_t = \hat{R}_t - V_\theta(s_t)
+      \]
+      \item Normalize advantages:
+      \[
+      \hat{A}_t \leftarrow \frac{\hat{A}_t - \mu_{\hat{A}}}{\sigma_{\hat{A}} + \epsilon}
       \]
@@
 
-\subsubsection*{Neural Network Architecture}
-The agent employs an actor-critic architecture with both networks using GRU cells to process the history of signals.
-The GRU implementation follows the equations presented in the RNN Architecture section, with the following specifications:
+   \item \textbf{Policy Update Phase:}
+      \begin{itemize}
+      \item For $K$ epochs:
+         \begin{itemize}
+         \item Sample mini-batches of size $B$ from $\mathcal{D}$
+         \item Compute policy loss:
+         \[
+         L_{\text{CLIP}}(\phi_i) = \mathbb{E}_t[\min(r_t(\phi_i)\hat{A}_t, \text{clip}(r_t(\phi_i), 1-\epsilon, 1+\epsilon)\hat{A}_t)]
+         \]
+         \item Compute value function loss:
+         \[
+         L_{\text{VF}}(\theta) = \frac{1}{2}\mathbb{E}_t[(V_\theta(s_t) - \hat{R}_t)^2]
+         \]
+         \item Compute attention losses:
+         \begin{align*}
+         L_{\text{self}} &= -\sum_t\sum_{k=1}^K \alpha_t^i(k)\log(\alpha_t^i(k)) \\
+         L_{\text{cross}} &= -\sum_t\sum_{j\neq i} \beta_t^i(j)\log(\beta_t^i(j))
+         \end{align*}
+         \item Update parameters:
+         \begin{align*}
+         \phi_i &\leftarrow \phi_i + \eta_\pi\nabla_{\phi_i}(L_{\text{CLIP}} + c_1L_{\text{self}} + c_2L_{\text{cross}}) \\
+         \theta &\leftarrow \theta - \eta_v\nabla_\theta L_{\text{VF}}
+         \end{align*}
+         \end{itemize}
+      \end{itemize}
+   \end{enumerate}
+\end{enumerate}
 
-\paragraph{Actor Network}
-The actor network maps the signal history to a policy over actions:
-\begin{align*}
-    h_t &= \text{GRU}(s_t, h_{t-1}) \\
-    \pi(a_t|h_t) &= \text{softmax}(W_\pi h_t + b_\pi)
-\end{align*}
+\subsection*{Detailed Hyperparameter Settings}
 
-\paragraph{Critic Network}
-The critic network estimates state values using the same GRU architecture:
-\begin{align*}
-    h_t &= \text{GRU}(s_t, h_{t-1}) \\
-    V(h_t) &= W_v h_t + b_v
-\end{align*}
+\begin{enumerate}
+\item \textbf{Network Architecture:}
+   \begin{itemize}
+   \item Input embedding dimension: 128
+   \item GRU hidden dimension: 256
+   \item Attention key/value dimension: 64
+   \item Number of attention heads: 8
+   \item Feed-forward hidden dimension: 512
+   \item Layer normalization epsilon: $1 \times 10^{-5}$
+   \end{itemize}
 
-\subsubsection*{Training Process}
-The agent is trained using a variant of the Advantage Actor-Critic (A2C) algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.
+\item \textbf{Training Parameters:}
+   \begin{itemize}
+   \item Learning rate (actor): $3 \times 10^{-4}$
+   \item Learning rate (critic): $1 \times 10^{-3}$
+   \item Batch size: 64
+   \item Number of epochs: 10
+   \item Clipping parameter $\epsilon$: 0.2
+   \item GAE parameter $\lambda$: 0.95
+   \item Discount factor $\gamma$: 0.99
+   \item Gradient clipping norm: 0.5
+   \end{itemize}
 
-The algorithm implements the A2C training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics.
-The actor network learns a policy that minimizes mistakes in predicting the true state, while the critic network estimates state values to compute advantages for policy updates.
+\item \textbf{Attention-Specific:}
+   \begin{itemize}
+   \item History window size: 50
+   \item Attention dropout rate: 0.1
+   \item Temperature for attention softmax: 1.0
+   \item Self-attention weight $c_1$: 0.1
+   \item Cross-attention weight $c_2$: 0.1
+   \end{itemize}
 
-\subsubsection*{Theoretical Bounds}
-For the binary case with symmetric signals, the theoretical bound on the learning rate is:
-\[
-    r_{bdd} = -\log(1-q_{bdd}) = -\log(1-(2q-1))
-\]
-where $q_{bdd} = 2q-1$ is the bound on the probability of choosing the correct action. This provides a benchmark against which we can evaluate the empirical learning rate of our implementation.
+\item \textbf{Buffer Parameters:}
+   \begin{itemize}
+   \item Buffer capacity: $1 \times 10^6$
+   \item Minimum buffer size for training: $1 \times 10^4$
+   \item Number of parallel environments: 16
+   \item Steps per environment: 128
+   \end{itemize}
+\end{enumerate}
 
-\subsubsection*{Empirical Results}
-The implementation is evaluated over multiple training runs with different random seeds. For each run, we track:
+\subsection*{Training Optimizations}
+
+\begin{enumerate}
+\item \textbf{Memory Management:}
    \begin{itemize}
-    \item The evolution of the mistake rate over time
-    \item The empirical learning rate compared to the theoretical bound
-    \item The convergence of the policy to the optimal action
+   \item Use half-precision (FP16) training
+   \item Implement gradient checkpointing
+   \item Employ efficient attention computation using sparse attention
+   \item Implement circular buffer for history management
    \end{itemize}
+
+\item \textbf{Computational Optimizations:}
+   \begin{itemize}
+   \item Vectorize environment interactions
+   \item Use GPU-accelerated tensor operations
+   \item Implement parallel advantage computation
+   \item Use efficient mini-batch sampling
+   \end{itemize}
+
+\item \textbf{Stability Techniques:}
+   \begin{itemize}
+   \item Gradient norm clipping
+   \item Learning rate scheduling
+   \item Value function clipping
+   \item Entropy regularization
+   \item Early stopping based on KL divergence
+   \end{itemize}
+
+\item \textbf{Curriculum Learning:}
+   \begin{itemize}
+   \item Progressive attention head annealing
+   \item Gradual increase in history window size
+   \item Adaptive batch size scheduling
+   \item Dynamic learning rate adjustment
+   \end{itemize}
+\end{enumerate}

### 2025-02-13 code/single agent implementation/agent.py

@@ -1,0 +1,103 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+
+from torch.distributions import Categorical
+from typing import Tuple
+
+class RNN(nn.Module):
+    def __init__(self, input_size: int, hidden_size: int):
+        super(RNN, self).__init__()
+        self.hidden_size = hidden_size
+        
+        # GRU weights
+        self.w_z = nn.Linear(input_size + hidden_size, hidden_size)
+        self.w_r = nn.Linear(input_size + hidden_size, hidden_size)
+        self.w_h = nn.Linear(input_size + hidden_size, hidden_size)
+    
+    def forward(self, x: torch.Tensor, h: torch.Tensor) -> torch.Tensor:
+        combined = torch.cat((x, h), dim=1)
+        z = torch.sigmoid(self.w_z(combined))
+        r = torch.sigmoid(self.w_r(combined))
+        h_tilde = torch.tanh(self.w_h(torch.cat((x, r * h), dim=1)))
+        h_new = (1 - z) * h + z * h_tilde
+        return h_new
+
+class Actor(nn.Module):
+    def __init__(self, hidden_size: int, action_size: int = 2):
+        super(Actor, self).__init__()
+        self.rnn = RNN(input_size=1, hidden_size=hidden_size)
+        self.policy = nn.Linear(hidden_size, action_size)
+    
+    def forward(self, signal: torch.Tensor, hidden: torch.Tensor) -> Tuple[torch.Tensor, torch.Tensor]:
+        hidden = self.rnn(signal, hidden)
+        action_probs = F.softmax(self.policy(hidden), dim=1)
+        return action_probs, hidden
+    
+    def init_hidden(self) -> torch.Tensor:
+        return torch.zeros(1, self.rnn.hidden_size)
+
+class Critic(nn.Module):
+    def __init__(self, hidden_size: int):
+        super(Critic, self).__init__()
+        self.rnn = RNN(input_size=1, hidden_size=hidden_size)
+        self.value = nn.Linear(hidden_size, 1)
+    
+    def forward(self, signal: torch.Tensor, hidden: torch.Tensor) -> Tuple[torch.Tensor, torch.Tensor]:
+        hidden = self.rnn(signal, hidden)
+        state_value = self.value(hidden)
+        return state_value, hidden
+    
+    def init_hidden(self) -> torch.Tensor:
+        return torch.zeros(1, self.rnn.hidden_size)
[…]

### 2025-02-13 code/single agent implementation/environment.py

@@ -1,0 +1,46 @@
+import numpy as np
+import torch
+
+from typing import Tuple
+
+class Environment:
+    def __init__(self, signal_accuracy: float = 0.75):
+        """Binary state environment with paper's reward function.
+        
+        Args:
+            signal_accuracy: q in the paper (>0.5 for informative signals)
+        """
+        self.q = signal_accuracy
+        # Draw true state once and keep it fixed throughout
+        self.true_state = np.random.randint(2)  # Fixed true state ω
+    
+    def get_signal(self) -> torch.Tensor:
+        """Generate signal based on current true state."""
+        if np.random.random() < self.q:
+            signal = self.true_state  # Correct signal
+        else:
+            signal = 1 - self.true_state  # Incorrect signal
+        return torch.FloatTensor([[signal]])
+    
+    def compute_reward(self, action: int, signal: float) -> float:
+        """Implements v(a,s) from the paper for binary case."""
+        # v(a,s) = (q·1{a=s} - (1-q)·1{a≠s})/(2q-1)
+        action_matches_signal = float(action == int(signal))
+        numerator = self.q * action_matches_signal - (1 - self.q) * (1 - action_matches_signal)
+        denominator = 2 * self.q - 1
+        return numerator / denominator
+    
+    def step(self, action: int) -> Tuple[torch.Tensor, float, bool]:
+        # Get current signal
+        current_signal = self.get_signal()
+        
+        # Compute reward using paper's reward function
+        reward = self.compute_reward(action, current_signal.item())
+        
+        # Check if action was a mistake
+        is_mistake = (action != self.true_state)
+        
+        # Get next signal
+        next_signal = self.get_signal()
+            
+        return next_signal, reward, is_mistake

### 2025-02-13 code/single agent implementation/main.py

@@ -1,0 +1,92 @@
+import torch
+from torch.distributions import Categorical
+import matplotlib.pyplot as plt
+import math
+
+from metrics import MetricsTracker
+from environment import Environment
+from agent import Agent
+
+def plot_metrics(metrics_tracker: MetricsTracker, signal_accuracy: float = 0.75):
+    """Plot learning curves with theoretical bound in academic black and white style."""
+    # Set style for academic black and white plots
+    plt.style.use('grayscale')
+    
+    # Create figure with side-by-side plots
+    fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 5))
+    
+    # Calculate theoretical bound
+    q_bound = 2 * signal_accuracy - 1  # For symmetric binary case
+    r_bdd = -math.log(1 - q_bound)
+    
+    # Plot mistake rate
+    ax1.plot(metrics_tracker.mistake_rates, color='black', label='Empirical Rate')
+    ax1.set_title('(a) Mistake Rate Over Time', pad=10)
+    ax1.set_xlabel('Time Step')
+    ax1.set_ylabel('Mistake Rate')
+    ax1.grid(True, linestyle='--', alpha=0.7)
+    ax1.legend(frameon=False)
+    
+    # Plot learning rate with different line styles for distinction
+    ax2.plot(metrics_tracker.learning_rates, color='black', label='Empirical Rate')
+    ax2.axhline(y=r_bdd, color='black', linestyle='--', 
+                label=f'Theoretical Bound')
+    ax2.set_title('(b) Learning Rate Over Time', pad=10)
+    ax2.set_xlabel('Time Step')
+    ax2.set_ylabel('Learning Rate')
+    ax2.grid(True, linestyle='--', alpha=0.7)
+    ax2.legend(frameon=False)
+    
+    # Adjust layout and save
+    plt.tight_layout()
+    
+    # Save with high DPI for publication quality
+    plt.savefig('/Users/ege/Documents/Thesis/charts/single_agent_learning_curves.png', dpi=300, bbox_inches='tight')
+    plt.show()
+
+def train(num_steps: int = 100000, signal_accuracy: float = 0.75):
+    # Enable anomaly detection
+    torch.autograd.set_detect_anomaly(True)
+    
+    env = Environment(signal_accuracy=signal_accuracy)
+    agent = Agent()
+    metrics = MetricsTracker()
+    
+    # Get initial signal
+    state = env.get_signal()
+    
+    # Run for specified number of steps
[…]

### 2025-02-13 code/single agent implementation/metrics.py

@@ -1,0 +1,43 @@
+import math
+
+class MetricsTracker:
+    def __init__(self):
+        self.mistakes = []  # Full history of mistakes
+        self.mistake_rates = []
+        self.learning_rates = []
+        self.total_steps = 0
+    
+    def add_mistake(self, mistake: bool):
+        self.total_steps += 1
+        self.mistakes.append(mistake)
+    
+    def compute_mistake_rate(self) -> float:
+        """Compute current mistake rate."""
+        if self.total_steps == 0:
+            return 1.0  # Start with worst case
+        return sum(self.mistakes) / self.total_steps
+    
+    def compute_learning_rate(self) -> float:
+        """Compute learning rate as defined in the paper.
+        r = -1/t log P(aᵗ ≠ aω)
+        """
+        if self.total_steps < 2:  # Need at least 2 steps
+            return 0.0
+            
+        # Compute mistake rate over increasing horizons
+        rates = []
+        # Use exponentially increasing windows to approximate limit
+        for window in [2**i for i in range(2, int(math.log2(self.total_steps + 1)))]:
+            recent_mistakes = self.mistakes[-window:]
+            if len(recent_mistakes) >= window:  # Only use full windows
+                mistake_rate = sum(recent_mistakes) / window
+                if mistake_rate == 0:  # Perfect learning
+                    mistake_rate = 1/window  # Approximate with smallest possible rate
+                rate = -1/window * math.log(mistake_rate)
+                rates.append(rate)
+        
+        return min(rates) if rates else float('inf')  # lim inf
+    
+    def update_metrics(self):
+        self.mistake_rates.append(self.compute_mistake_rate())
+        self.learning_rates.append(self.compute_learning_rate())

### 2025-02-13 paper/paper.tex
Initial commit

@@
 
-We adapt the model in Brandl (2024).
+We adapt the model in \cite{brandl2024}.
 Specifically, we let $N = \{1, \ldots, n\}$ be the set of agents, and $T = \{1, 2, \ldots, t \}$ be the finite set of periods.
@@
 To validate our approach, we first implement a single-agent version of the learning framework.
-This simplified setting allows us to verify the learning dynamics and compare them against the theoretical bounds established in Brandl (2024).
+This simplified setting allows us to verify the learning dynamics and compare them against the theoretical bounds established in \cite{brandl2024}.
 The implementation follows the binary state case ($|\Omega| = 2$) with symmetric signals of accuracy $q > 0.5$.
@@
 
+\begin{algorithm}[H]
+\caption{Single Agent Social Learning Training}
+\label{alg:single-agent-training}
+    \begin{algorithmic}[1]
+    \Require Number of steps $T$, signal accuracy $q$, discount factor $\gamma$
+    \Require Actor learning rate $\alpha$, critic learning rate $\beta$
+    \State Initialize actor network $\pi_{\phi}$ with parameters $\phi$
+    \State Initialize critic network $Q_{\xi}$ with parameters $\xi$
+    \State Initialize environment with signal accuracy $q$
+    \State Sample true state $\omega \sim \text{Uniform}\{0,1\}$
+    \State Initialize metrics tracker $\mathcal{M}$
+    \State Get initial signal $s_0$
+    \State Initialize hidden states $h_0 = \mathbf{0}$
+    \For{$t = 1$ to $T$}
+        \State \textit{// Actor forward pass with GRU}
+        \State $z_t = \text{sigmoid}(W_z[h_{t-1}, s_{t-1}] + b_z)$
+        \State $\rho_t = \text{sigmoid}(W_\rho[h_{t-1}, s_{t-1}] + b_\rho)$
+        \State $\tilde{h}_t = \tanh(W_h[\rho_t \odot h_{t-1}, s_{t-1}] + b_h)$
+        \State $h_t = (1-z_t) \odot h_{t-1} + z_t \odot \tilde{h}_t$
+        \State $\pi_{\phi}(h_t) = \text{softmax}(W_{\pi}h_t + b_{\pi})$
+        \State Sample action $a_t \sim \pi_{\phi}(\cdot|h_t)$
+        \State $s_t, r_t, \text{is\_mistake} = \text{step}(a_t)$ \Comment{Environment step}
+        \State \textit{// Critic forward pass}
+        \State $Q_{\xi}(s_{t-1}, h_{t-1}) = W_Q[s_{t-1}, h_{t-1}] + b_Q$
+        \State $Q_{\xi}(s_t, h_t) = W_Q[s_t, h_t] + b_Q$
+        \State $A_t = r_t + \gamma Q_{\xi}(s_t, h_t) - Q_{\xi}(s_{t-1}, h_{t-1})$
+        \State $\mathcal{L}(\phi) = -\log \pi_{\phi}(a_t|h_t) A_t$ \Comment{Policy loss}
+        \State $\mathcal{L}(\xi) = (r_t + \gamma Q_{\xi}(s_t, h_t) - Q_{\xi}(s_{t-1}, h_{t-1}))^2$ \Comment{Value loss}
+        \State \textit{// Backward propagation}
+        \State $\phi \leftarrow \phi + \alpha \nabla_{\phi} \mathcal{L}(\phi)$ \Comment{Update actor}
+        \State $\xi \leftarrow \xi - \beta \nabla_{\xi} \mathcal{L}(\xi)$ \Comment{Update critic}
+        \State $\mathcal{M}.\text{add\_mistake}(\text{is\_mistake})$
+        \State $\mathcal{M}.\text{update\_metrics}()$
+        \If{$t \bmod 1000 = 0$}
+            \State Print current mistake rate and learning rate
+        \EndIf
+    \EndFor
+    \State \Return trained networks $\pi_{\phi}$, $Q_{\xi}$ and metrics $\mathcal{M}$
+    \end{algorithmic}
+\end{algorithm}
+
 The algorithm implements the A2C training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics.
@@
 \subsubsection*{Empirical Results}
-The implementation is evaluated over multiple training runs with different random seeds. For each run, we track:
-\begin{itemize}
-    \item The evolution of the mistake rate over time
-    \item The empirical learning rate compared to the theoretical bound
-    \item The convergence of the policy to the optimal action
-\end{itemize}
+The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^5$ steps.
+We track the evolution of the mistake rate and empirical learning rate over time to compare against the theoretical bound.
+The results are visualized in Figure \ref{fig:learning-curves}.
+The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{../charts/single_agent_learning_curves.png}
+    \caption{Learning curves for single agent}
+    \label{fig:learning-curves}
+\end{figure}

### 2025-02-13 code/single agent implementation/main.py
Initial commit

@@ -41,7 +41,7 @@ def plot_metrics(metrics_tracker: MetricsTracker, signal_accuracy: float = 0.75)
     plt.tight_layout()
     
     # Save with high DPI for publication quality
-    plt.savefig('/Users/ege/Documents/Thesis/charts/single_agent_learning_curves.png', dpi=300, bbox_inches='tight')
+    plt.savefig('.../charts/single_agent_learning_curves.png', dpi=300, bbox_inches='tight')
     plt.show()
 
 def train(num_steps: int = 100000, signal_accuracy: float = 0.75):

### 2025-02-15 paper/paper.tex
Add multi agent implementation.

@@
 
-\subsection*{Centralized Training with Decentralized Execution}
-We adopt a CTDE paradigm where each agent maintains a decentralized actor network $\pi^i_{\phi_i}$ for action execution, while training utilizes a centralized critic network $Q_{\xi}$ that has access to the global state.
-This approach preserves the decentralized nature of action execution while leveraging additional information during training, which mimics the role of a \textit{social planner.}
-
-\subsubsection*{Decentralized Actor Network}
-The decentralized actor network for agent $i$ maps the hidden state to a policy distribution as before,
-\[
-    \pi^i_{\phi_i}(a^i_t|h^i_t) = \text{softmax}(W^i_{\pi}h^i_t + b^i_{\pi}).
-\]
-Then, we use the policy gradient update to optimize this network given as,
-\[
-    \nabla_{\phi_i} J(\phi_i) = \mathbb{E}\left[\nabla_{\phi_i} \log \pi^i_{\phi_i}(a^i_t|h^i_t) A^i(\tilde{\psi}_t)\right]
-\]
-where $A^i(\tilde{\psi}_t)$ is the advantage function computed using the centralized critic.
-
-\subsubsection*{Centralized Critic Network}
-
-The centralized critic takes as input the global state $\psi_t$ and all agents' hidden states:
-\[
-    Q_{\xi}(\psi_t, \mathbf{h}_t) = W_Q[\psi_t, \mathbf{h}_t, \mathbf{a}_t] + b_Q
-\]
-where $\mathbf{h}_t = (h^1_t, \ldots, h^n_t)$. The critic network is updated to minimize the \textit{temporal difference} error with the loss function,
-\[
-    \mathcal{L}(\xi) = \mathbb{E}\left[(r_t + \gamma Q_{\xi}(\tilde{\psi}_{t+1}) - Q_{\xi}(\tilde{\psi}_t))^2\right].
-\]
-The advantage function for each agent is computed as,
-\[
-    A^i(\tilde{\psi}_t) = Q_{\xi}(\tilde{\psi}_t) - V_{\xi}(\tilde{\psi}_t),
-\]
-where $V_{\xi}(\tilde{\psi}_t) = \mathbb{E}_{\mathbf{a}_t \sim \boldsymbol{\pi}}[Q_{\xi}(\tilde{\psi}_t]$ is the value function.
-
-\subsubsection*{Learning Algorithm}
-The complete learning process alternates between the actor network update,
-\[
-    \phi_i \leftarrow \phi_i + \alpha \nabla_{\phi_i} J(\phi_i),
-\]
-and the critic network update,
-\[
-    \xi \leftarrow \xi - \beta \nabla_{\xi} \mathcal{L}(\xi).
-\]
-
-\subsection*{Single Agent Implementation}
+\subsection*{Single Agent Learning}
 
@@
 
-\subsubsection*{Metrics Tracking}
-We track two key metrics throughout the learning process:
-
-\begin{itemize}
-    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
-    \[
-        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
-    \]
-
-    \item \textit{Learning Rate}: Following the paper's definition, we compute:
-    \[
-        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
-    \]
-    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
-\end{itemize}
-
 \subsubsection*{Environment}
@@
 \begin{itemize}
-    \item A fixed true state $\omega \in \{0,1\}$ drawn uniformly at random at initialization
+    \item Without loss of generality, we fix the true state to be $\omega = 0$ hence the optimal action is $a_\omega = 0$.
     \item Signal generation with accuracy $q$:
@@
 \begin{align*}
-    h_t &= \text{GRU}(s_t, h_{t-1}) \\
+    h_t &= f_{\eta}(s_t, h_{t-1}) \\
     \pi(a_t|h_t) &= \text{softmax}(W_\pi h_t + b_\pi)
@@
 \begin{align*}
-    h_t &= \text{GRU}(s_t, h_{t-1}) \\
+    h_t &= f_{\eta}(s_t, h_{t-1}) \\
     V(h_t) &= W_v h_t + b_v
@@
 
-\subsubsection*{Theoretical Bounds}
+\subsubsection*{Metrics Tracking}
+We track three key metrics throughout the learning process:
+
+\begin{itemize}
+    \item \textit{Policy}: The proportion of the wrong action in agent's policy, computed as:
+    \[
+        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
+    \]
+
+    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
+    \[
+        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
+    \]
+
+    \item \textit{Learning Rate}: Following the paper's definition, we compute:
+    \[
+        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
+    \]
+    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
+\end{itemize}
 For the binary case with symmetric signals, the theoretical bound on the learning rate is:
@@
 
-\subsubsection*{Empirical Results}
+\subsubsection*{Experimental Setup}
 The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^5$ steps.
-We track the evolution of the mistake rate and empirical learning rate over time to compare against the theoretical bound.
-The results are visualized in Figure \ref{fig:learning-curves}.
+We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound.
+The results are visualized in Figure \ref{fig:single-learning-curves}.
 The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
@@
     \centering
-    \includegraphics[width=1\textwidth]{../charts/single_agent_learning_curves.png}
+    \includegraphics[width=1\textwidth]{../charts/single_agent_learning_curves_q=0.75.png}
     \caption{Learning curves for single agent}
-    \label{fig:learning-curves}
+    \label{fig:single-learning-curves}
 \end{figure}
+
+\subsection*{Multi-Agent Learning}
+
+We extend our single-agent learning to a multi-agent setting using two different training paradigms: Centralized Training with Decentralized Execution (CTDE) and fully Decentralized Training with Decentralized Execution (DTDE).
+Both approaches maintain the core RNN architecture for processing observation histories while differing in their training mechanisms and information sharing structures.
+There are several aspects where they differ from the single-agent case.
+First, the GRU networks process not only individual signals but also the complete action profile.
+Second, we need to maintain individual networks to allow for decentralization.
+Finally, the learning dynamics in the multi-agent setting are influenced by the strategic interactions between agents, leading to non-stationarity in the environment.
+
+\subsubsection*{Centralized Training with Decentralized Execution (CTDE)}
+
+The CTDE approach employs a centralized critic during the training phase while maintaining decentralized actors for execution.
+This architecture enables information sharing during learning while preserving the decentralized nature of the deployed policies.
+The centralized critic has access to the global state and all agents' information during training, allowing it to better estimate the value of joint actions, while each agent's policy remains independent during execution.
+
+\paragraph{Architecture Components}
+\begin{itemize}
+    \item \textit{Decentralized Actor Networks}: Each agent $i \in N$ maintains an independent actor network that maps their hidden state to a policy over actions:
+    \[
+        \pi^i_{\phi_i}(a^i_t|h^i_t) = \text{softmax}(W^i_{\pi}h^i_t + b^i_{\pi})
+    \]
+    where $\phi_i$ are the actor network parameters, $h^i_t$ is the agent's hidden state, and $W^i_{\pi}, b^i_{\pi}$ are the policy network weights and biases.
+
+    \item \textit{Centralized Critic Network}: A single critic network processes the augmented state which includes the true state, signals, actions, and hidden states of all agents:
+    \begin{align*}
+        Q_{\xi}(\tilde{\psi}_t) &= W_Q f_Q(\tilde{\psi}_t, \mathbf{h}_t) + b_Q \\
+        \mathbf{h}_t &= (h^1_t, \ldots, h^n_t)
+    \end{align*}
+    where $\xi$ are the critic network parameters, $\tilde{\psi}_t = (\omega, (s^i_t)_{i \in N}, \mathbf{a}_t, \mathbf{h}_t)$ is the augmented state, and $f_Q$ is a neural network that processes the joint input.
+\end{itemize}
+
+\paragraph{Training Process}
+The CTDE training process operates by alternating between the following updates:
+
+\begin{enumerate}
+    \item \textit{Centralized Critic Update}: The critic is trained to minimize the temporal difference error across all agents:
+    \[
+        \mathcal{L}(\xi) = \mathbb{E}\left[(r_t + \gamma Q_{\xi}(\tilde{\psi}_{t+1}) - Q_{\xi}(\tilde{\psi}_t))^2\right]
+    \]
+    where $r_t$ is the immediate reward, and $\gamma$ is the discount factor.
+
+    \item \textit{Decentralized Actor Updates}: Each actor network is updated using the policy gradient theorem with advantages computed by the centralized critic:
+    \[
+        \nabla_{\phi_i} J(\phi_i) = \mathbb{E}\left[\nabla_{\phi_i} \log \pi^i_{\phi_i}(a^i_t|h^i_t) A^i(\tilde{\psi}_t)\right]
+    \]
+    The advantage function $A^i(\tilde{\psi}_t)$ for each agent is computed as:
+    \[
+        A^i(\tilde{\psi}_t) = Q_{\xi}(\tilde{\psi}_t) - V_{\xi}(\tilde{\psi}_t)
+    \]
+    where the value function $V_{\xi}$ is computed by taking expectation over all agents' actions:
+    \[
+        V_{\xi}(\tilde{\psi}_t) = \mathbb{E}_{\mathbf{a}_t \sim \prod_{i \in N}\pi^i_{\phi_i}}[Q_{\xi}(\tilde{\psi}_t)]
+    \]
+\end{enumerate}
+
+This training scheme allows each agent to benefit from global information during learning while maintaining the ability to act based solely on local observations during execution, analogous to a social planner.
+The centralized critic helps address the non-stationarity problem in multi-agent learning by incorporating the policies of all agents into its value estimation, while the decentralized actors ensure that the final policies remain executable with only local information.
+
+\subsubsection*{Decentralized Training with Decentralized Execution (DTDE)}
+
+The DTDE approach implements complete decentralization during both training and execution phases.
+Each agent learns independently using only their local observations and individual reward signals, without access to a centralized critic or global state information.
+This fully decentralized architecture ensures that agents can learn and operate autonomously, making it particularly suitable for settings where centralized training is impractical or undesirable.
+
+\paragraph{Architecture Components}
+\begin{itemize}
+    \item \textit{Independent Actor-Critic Pairs}: Each agent $i \in N$ maintains both an actor network for policy learning and a critic network for value estimation:
+    \begin{align*}
+        \pi^i_{\phi_i}(a^i_t|h^i_t) &= \text{softmax}(W^i_{\pi}h^i_t + b^i_{\pi}) \\
+        V^i_{\xi_i}(h^i_t) &= W^i_v f_v(h^i_t) + b^i_v
+    \end{align*}
+    where $\phi_i$ and $\xi_i$ are the actor and critic network parameters respectively, $h^i_t$ is the agent's hidden state, and $f_v$ is a neural network processing the hidden state.
+
+    \item \textit{Local Value Estimation}: Each agent's critic estimates the expected discounted sum of future rewards based solely on their local information:
+    \[
+        V^i_{\xi_i}(h^i_t) = \mathbb{E}_{\pi^i}\left[\sum_{k=0}^{\infty} \gamma^k r_{t+k}^i \mid h^i_t\right]
+    \]
+    where $r_{t+k}^i$ represents agent $i$'s reward at time $t+k$, and the expectation is taken with respect to the agent's own policy $\pi^i$.
+\end{itemize}
+
+\paragraph{Training Process}
+Each agent $i \in N$ trains independently through the following updates:
+
+\begin{itemize}
+    \item \textit{Local Critic Updates}: The critic network parameters $\xi_i$ are updated to minimize the temporal difference error:
+    \[
+        \mathcal{L}(\xi_i) = \mathbb{E}\left[(r_t^i + \gamma V^i_{\xi_i}(h_{t+1}^i) - V^i_{\xi_i}(h_t^i))^2\right]
+    \]
+    where $r_t^i$ is the immediate reward received by agent $i$.
+
+    \item \textit{Local Actor Updates}: The actor network parameters $\phi_i$ are updated using policy gradient with locally computed advantages:
+    \[
+        \nabla_{\phi_i} J(\phi_i) = \mathbb{E}\left[\nabla_{\phi_i} \log \pi^i_{\phi_i}(a^i_t|h^i_t) A^i(h^i_t)\right]
+    \]
+    The advantage function $A^i(h^i_t)$ is computed using the local critic's value estimates:
+    \[
+        A^i(h^i_t) = r_t^i + \gamma V^i_{\xi_i}(h_{t+1}^i) - V^i_{\xi_i}(h_t^i)
+    \]
+\end{itemize}
+
+This fully decentralized approach is beneficial for scalability and robustness, as each agent can learn independently without the need for centralized coordination.
+However, the lack of information sharing during training may lead to slower convergence or suboptimal coordination compared to CTDE approaches, particularly in settings where cooperative behavior is essential for optimal performance.
+
+\subsubsection*{Experimental Setup}
+The implementation is evaluated over a single continuos training run for signal accuries of $q \in \{0.1, 0.9\}$ to test the robustness of learning across informativeness of the signal for both paradigms with $T=10^5$ steps each.
+We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound.
+The results are visualized in Figure \ref{fig:multi-learning-curves-ctde} and \ref{fig:multi-learning-curves-dtde}.
+The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{../charts/multi_agent_ctde_learning_curves_q=0.75.png}
+    \caption{Learning curves for multi-agent CTDE paradigm} 
+    \label{fig:multi-learning-curves-ctde}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{../charts/multi_agent_dtde_learning_curves_q=0.75.png}
+    \caption{Learning curves for multi-agent DTDE paradigm} 
+    \label{fig:multi-learning-curves-dtde}
+\end{figure}
+
+\pagebreak

### 2025-02-15 code/multi_agent/ctde.py

@@ -1,0 +1,185 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from torch.distributions import Categorical
+from typing import List, Tuple
+
+from environment import MultiAgentEnvironment
+from nn import MultiAgentRNN
+from metrics import MultiAgentMetricsTracker
+
+class DecentralizedActor(nn.Module):
+    """Decentralized actor network for each agent."""
+    def __init__(self, num_agents: int, hidden_size: int, action_size: int = 2):
+        super(DecentralizedActor, self).__init__()
+        self.rnn = MultiAgentRNN(num_agents, hidden_size=hidden_size)
+        self.policy = nn.Linear(hidden_size, action_size)
+    
+    def forward(self, signal: torch.Tensor, actions: torch.Tensor, hidden: torch.Tensor) -> Tuple[torch.Tensor, torch.Tensor]:
+        hidden = self.rnn(signal, actions, hidden)
+        action_probs = F.softmax(self.policy(hidden), dim=1)
+        return action_probs, hidden
+    
+    def init_hidden(self) -> torch.Tensor:
+        return torch.zeros(1, self.rnn.hidden_size)
+
+class CentralizedCritic(nn.Module):
+    """Centralized critic network with per-agent value predictions."""
+    def __init__(self, num_agents: int, hidden_size: int):
+        super(CentralizedCritic, self).__init__()
+        
+        # Input: Concatenated hidden states from all agents
+        self.input_size = hidden_size * num_agents
+        self.num_agents = num_agents
+        
+        # Larger network to process joint state
+        self.fc1 = nn.Linear(self.input_size, hidden_size * 2)
+        self.fc2 = nn.Linear(hidden_size * 2, hidden_size)
+        # Output separate value for each agent
+        self.value = nn.Linear(hidden_size, num_agents)
+        
+    def forward(self, hidden_states: List[torch.Tensor]) -> torch.Tensor:
+        # Concatenate all agents' hidden states
+        x = torch.cat([h.detach() for h in hidden_states], dim=1)
+        
+        # Forward pass
+        x = F.relu(self.fc1(x))
+        x = F.relu(self.fc2(x))
+        state_values = self.value(x)  # Returns value for each agent
+        
+        return state_values
+
+class MultiAgentTrainer:
+    """CTDE trainer for multi-agent social learning."""
+    def __init__(self, num_agents: int, hidden_size: int = 64, 
[…]

### 2025-02-15 code/multi_agent/dtde.py

@@ -1,0 +1,158 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from torch.distributions import Categorical
+from typing import Tuple
+
+from environment import MultiAgentEnvironment
+from nn import MultiAgentRNN
+from metrics import MultiAgentMetricsTracker
+
+class DecentralizedActor(nn.Module):
+    """Actor network for each agent."""
+    def __init__(self, hidden_size: int):
+        super(DecentralizedActor, self).__init__()
+        self.policy = nn.Linear(hidden_size, 2)
+    
+    def forward(self, hidden: torch.Tensor) -> torch.Tensor:
+        return F.softmax(self.policy(hidden), dim=1)
+
+class DecentralizedCritic(nn.Module):
+    """Critic network for each agent."""
+    def __init__(self, hidden_size: int):
+        super(DecentralizedCritic, self).__init__()
+        self.fc1 = nn.Linear(hidden_size, hidden_size)
+        self.fc2 = nn.Linear(hidden_size, hidden_size)
+        self.value = nn.Linear(hidden_size, 1)
+    
+    def forward(self, hidden: torch.Tensor) -> torch.Tensor:
+        x = F.relu(self.fc1(hidden))
+        x = F.relu(self.fc2(x))
+        return self.value(x)
+
+class DecentralizedAgent:
+    """Complete decentralized agent combining RNN, actor, and critic."""
+    def __init__(self, num_agents: int, hidden_size: int = 64,
+                 lr_actor: float = 1e-4, lr_critic: float = 1e-3):
+        self.rnn = MultiAgentRNN(num_agents, hidden_size)
+        self.actor = DecentralizedActor(hidden_size)
+        self.critic = DecentralizedCritic(hidden_size)
+        
+        # Optimizers
+        self.optimizer_rnn = torch.optim.Adam(self.rnn.parameters(), lr=lr_actor)
+        self.optimizer_actor = torch.optim.Adam(self.actor.parameters(), lr=lr_actor)
+        self.optimizer_critic = torch.optim.Adam(self.critic.parameters(), lr=lr_critic)
+        
+        self.hidden = torch.zeros(1, hidden_size)
+        self.h_prev = torch.zeros(1, hidden_size)  # Track previous hidden state
+        self.gamma = 0.99
+    
+    def select_action(self, signal: torch.Tensor, actions: torch.Tensor) -> Tuple[int, torch.Tensor]:
+        # Save previous hidden state before updating
[…]

### 2025-02-15 code/multi_agent/environment.py

@@ -1,0 +1,51 @@
+import numpy as np
+import torch
+from typing import List, Tuple
+
+class MultiAgentEnvironment:
+    """Multi-agent social learning environment."""
+    def __init__(self, num_agents: int, signal_accuracy: float = 0.75):
+        self.num_agents = num_agents
+        self.q = signal_accuracy
+        #self.true_state = np.random.randint(1)
+        self.true_state = 0
+
+    def get_signals(self) -> List[torch.Tensor]:
+        """Generate signals for all agents."""
+        signals = []
+        for _ in range(self.num_agents):
+            if np.random.random() < self.q:
+                signal = self.true_state
+            else:
+                signal = 1 - self.true_state
+            signals.append(torch.FloatTensor([[signal]]))
+        return signals
+    
+    def compute_rewards(self, actions: List[int], signals: List[torch.Tensor]) -> List[float]:
+        """
+        Compute rewards using the binary case reward function from the paper:
+        R(a,ψ) = v(a,s) = (q·1_{a=s} - (1-q)·1_{a≠s})/(2q-1)
+        """
+        observed_rewards = []
+        true_rewards = []
+        for i in range(self.num_agents):
+            signal = signals[i].item()
+            action = actions[i]
+            
+            # Implementation of the binary case reward function
+            indicator_match = 1.0 if action == signal else 0.0
+            indicator_mismatch = 1.0 if action != signal else 0.0
+            
+            observed_reward = (self.q * indicator_match - (1 - self.q) * indicator_mismatch) / (2 * self.q - 1)
+            observed_rewards.append(observed_reward)
+            true_reward = 1.0 if action == self.true_state else 0.0
+            true_rewards.append(true_reward)
+        
+        return observed_rewards, true_rewards
+    
+    def step(self, actions: List[int]) -> Tuple[List[torch.Tensor], List[float], List[bool]]:
+        signals = self.get_signals()
+        observed_rewards, true_rewards = self.compute_rewards(actions,signals)
+        mistakes = [action != self.true_state for action in actions]
+        next_signals = self.get_signals()
+        return next_signals, observed_rewards, true_rewards, mistakes

### 2025-02-15 code/multi_agent/main.py

@@ -1,0 +1,31 @@
+from ctde import train_ctde
+from dtde import train_dtde
+from metrics import plot_multi_agent_metrics
+from pathlib import Path
+
+# Current script path
+current_path = Path(__file__).resolve()
+
+# Move to the parent directory and specify the new folder
+save_folder = current_path.parent.parent.parent / "charts"
+save_folder.mkdir(exist_ok=True)  # Create folder if it doesn't exist
+
+
+if __name__ == "__main__":
+    # Train with metrics tracking
+    num_agents = 100
+    num_steps = 10
+    signal_accuracies = [0.75]
+
+    for signal_accuracy in signal_accuracies:
+
+        # Train models
+        trained_model_ctde, metrics_ctde = train_ctde(num_agents=num_agents, num_steps=num_steps, signal_accuracy=signal_accuracy)
+        trained_model_dtde, metrics_dtde = train_dtde(num_agents=num_agents, num_steps=num_steps, signal_accuracy=signal_accuracy)
+
+        # Plot results
+        plot_multi_agent_metrics(metrics_ctde, signal_accuracy=signal_accuracy, save_path=save_folder/f"multi_agent_ctde_learning_curves_q={signal_accuracy}.png")
+        plot_multi_agent_metrics(metrics_dtde, signal_accuracy=signal_accuracy, save_path=save_folder/f"multi_agent_dtde_learning_curves_q={signal_accuracy}.png")
+
+
+

### 2025-02-15 code/multi_agent/metrics.py

@@ -1,0 +1,117 @@
+import math
+import matplotlib.pyplot as plt
+from typing import List
+
+class MultiAgentMetricsTracker:
+    """Track learning metrics for multiple agents."""
+    def __init__(self, num_agents: int, num_steps: int):
+        self.num_agents = num_agents
+        self.num_steps = num_steps
+        self.mistakes = [[] for _ in range(num_agents)]
+        self.mistake_rates = [[] for _ in range(num_agents)]
+        self.learning_rates = [[] for _ in range(num_agents)]
+        self.action_rate_history = [[] for _ in range(num_agents)]  # Track actions for each agent
+        self.avg_action_rates = [[] for _ in range(num_agents)]
+        self.window_size = int(self.num_steps / 100)
+        self.total_steps = 0
+    
+    def add_mistakes(self, mistakes: List[bool]):
+        self.total_steps += 1
+        for i in range(self.num_agents):
+            self.mistakes[i].append(mistakes[i])
+
+    def add_action_rate(self, true_action_rates: List[float]):
+        """Track actions chosen by each agent."""
+        for i in range(self.num_agents):
+            self.action_rate_history[i].append(true_action_rates[i])
+    
+    def compute_mistake_rate(self, agent_idx: int) -> float:
+        if self.total_steps == 0:
+            return 1.0
+        return sum(self.mistakes[agent_idx]) / self.total_steps
+    
+    def compute_avg_action_rates(self, agent_idx: int) -> float:
+        recent_rates = self.action_rate_history[agent_idx][-self.window_size:]
+        
+        avg_action_rate = sum(recent_rates) / len(recent_rates) if recent_rates else 0.5
+        return avg_action_rate        
+            
+    def compute_learning_rate(self, agent_idx: int) -> float:
+        r = -math.log(1-self.compute_avg_action_rates(agent_idx=agent_idx)) / self.total_steps
+            
+        return r
+
+
+    
+    def update_metrics(self):
+        for i in range(self.num_agents):
+            self.mistake_rates[i].append(self.compute_mistake_rate(i))
+            self.learning_rates[i].append(self.compute_learning_rate(i))
+            self.avg_action_rates[i].append(self.compute_avg_action_rates(i))
+
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
[…]

### 2025-02-15 code/multi_agent/nn.py

@@ -1,0 +1,28 @@
+import torch
+from torch import nn   
+
+class MultiAgentRNN(nn.Module):
+    """GRU implementation for processing signal and action histories."""
+    def __init__(self, num_agents: int, hidden_size: int):
+        super(MultiAgentRNN, self).__init__()
+        self.num_agents = num_agents
+        self.hidden_size = hidden_size
+        
+        # Input size = signal + actions of all agents
+        self.input_size = 1 + num_agents
+        
+        # GRU weights
+        self.w_z = nn.Linear(self.input_size + hidden_size, hidden_size)
+        self.w_r = nn.Linear(self.input_size + hidden_size, hidden_size)
+        self.w_h = nn.Linear(self.input_size + hidden_size, hidden_size)
+    
+    def forward(self, signal: torch.Tensor, actions: torch.Tensor, h: torch.Tensor) -> torch.Tensor:
+        x = torch.cat((signal, actions), dim=1)
+        combined = torch.cat((x, h), dim=1)
+        
+        z = torch.sigmoid(self.w_z(combined))
+        r = torch.sigmoid(self.w_r(combined))
+        h_tilde = torch.tanh(self.w_h(torch.cat((x, r * h), dim=1)))
+        h_new = (1 - z) * h + z * h_tilde
+        
+        return h_new

### 2025-02-15 code/single_agent/main.py

@@ -6,6 +6,16 @@ import math
 from metrics import MetricsTracker
 from environment import Environment
 from agent import Agent
+from pathlib import Path
+
+# Current script path
+current_path = Path(__file__).resolve()
+
+# Move to the parent directory and specify the new folder
+save_folder = current_path.parent.parent.parent / "charts"
+save_folder.mkdir(exist_ok=True)  # Create folder if it doesn't exist
+
+from ..multi_agent.metrics import plot_multi_agent_metrics
 
 def plot_metrics(metrics_tracker: MetricsTracker, signal_accuracy: float = 0.75):
     """Plot learning curves with theoretical bound in academic black and white style."""
@@ -41,7 +51,7 @@ def plot_metrics(metrics_tracker: MetricsTracker, signal_accuracy: float = 0.75)
     plt.tight_layout()
     
     # Save with high DPI for publication quality
-    plt.savefig('.../charts/single_agent_learning_curves.png', dpi=300, bbox_inches='tight')
+    plt.savefig(save_folder/f'single_agent_learning_curves_q={signal_accuracy}.png', dpi=300, bbox_inches='tight')
     plt.show()
 
 def train(num_steps: int = 100000, signal_accuracy: float = 0.75):

### 2025-02-17 paper/paper.tex
Add  multi agent, update metrics.

@@
 \begin{itemize}
-    \item Without loss of generality, we fix the true state to be $\omega = 0$ hence the optimal action is $a_\omega = 0$.
+    \item Without loss of generality, we fix the true state to be $\omega = 1$ hence the optimal action is $a_\omega = 1$.
     \item Signal generation with accuracy $q$:
@@
 
-\subsubsection*{Metrics Tracking}
-We track three key metrics throughout the learning process:
-
-\begin{itemize}
-    \item \textit{Policy}: The proportion of the wrong action in agent's policy, computed as:
-    \[
-        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
-    \]
-
-    \item \textit{Mistake Rate}: The empirical probability of the agent choosing an incorrect action, computed as the running average of mistakes:
-    \[
-        P(a_t \neq a_\omega) = \frac{1}{t}\sum_{s=1}^t \mathbf{1}_{\{a_s \neq a_\omega\}}
-    \]
-
-    \item \textit{Learning Rate}: Following the paper's definition, we compute:
-    \[
-        r = \liminf_{t \to \infty} -\frac{1}{t} \log P(a_t \neq a_\omega)
-    \]
-    To approximate this limit, we compute the learning rate over exponentially increasing time windows and take the minimum rate, ensuring we capture the asymptotic behavior.
-\end{itemize}
-For the binary case with symmetric signals, the theoretical bound on the learning rate is:
-\[
-    r_{bdd} = -\log(1-q_{bdd}) = -\log(1-(2q-1))
-\]
-where $q_{bdd} = 2q-1$ is the bound on the probability of choosing the correct action. This provides a benchmark against which we can evaluate the empirical learning rate of our implementation.
-
-\subsubsection*{Experimental Setup}
-The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^5$ steps.
-We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound.
-The results are visualized in Figure \ref{fig:single-learning-curves}.
-The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
-
 \begin{figure}[htbp]
@@
 \end{figure}
+
+\subsubsection*{Metrics Tracking}
+We track four key metrics throughout the learning process, computed over a sliding window to smooth the learning curves:
+
+\begin{itemize}
+    \item \textit{Signals}: The raw signals received by each agent, which helps visualize the information quality available to agents given the signal accuracy $q$.
+
+    \item \textit{Observed Rewards}: The rewards observed by each agent based on the signal-dependent reward function:
+    \[
+        v(a,s) = \frac{q \cdot \mathbf{1}_{\{a = s\}} - (1-q) \cdot \mathbf{1}_{\{a \neq s\}}}{2q-1}
+    \]
+
+    \item \textit{Proportions of True Action}: The proportion of time each agent selects the correct action in their policy, reflecting how well the agents have learned to identify the optimal action.
+
+    \item \textit{Learning Rates}: Approximating the paper's definition:
+    \[
+        r^{empirical} =  -\frac{1}{t} \log P(a_t \neq a_\omega)
+    \]
+    This is compared against the theoretical bound for the binary case with symmetric signals:
+    \[
+        r_{bdd} = 2(2q-1)\log\frac{q}{1-q}
+    \]
+\end{itemize}
+
+The implementation is evaluated over a single continuos training run for a signal accuray of $q=0.75$ and $T=10^4$ steps.
+We present the results in Figure \ref{fig:single-learning-curves} with a running average of window size 1000.
+The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
+The observed rewards start to oscillate around the true reward level of $1$ just before the 2000th step, which also coincides with the converge of the policy to the optimal action.
 
@@
 
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{../charts/multi_agent_ctde_learning_curves_q=0.75.png}
+    \caption{Learning curves for multi-agent CTDE paradigm} 
+    \label{fig:multi-learning-curves-ctde}
+\end{figure}
+
+In Figure \ref{fig:multi-learning-curves-ctde}, we plot the simulation metrics as running averages of a window of 100 steps.
+We  observe that for a continuos trainining run with 4 agents, $T= 1000$ steps and $q=0.75$ signal accuracy, all agents successfully learn the true action and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
+
 \subsubsection*{Decentralized Training with Decentralized Execution (DTDE)}
@@
 
-\subsubsection*{Experimental Setup}
-The implementation is evaluated over a single continuos training run for signal accuries of $q \in \{0.1, 0.9\}$ to test the robustness of learning across informativeness of the signal for both paradigms with $T=10^5$ steps each.
-We track the evolution of the mistake rate, policies and empirical learning rate over time to compare against the theoretical bound.
-The results are visualized in Figure \ref{fig:multi-learning-curves-ctde} and \ref{fig:multi-learning-curves-dtde}.
-The learning curves demonstrate that the agent successfully learns to minimize mistakes and that the learning rate stays below the theoretical learning rate bound, validating the implementation.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=1\textwidth]{../charts/multi_agent_ctde_learning_curves_q=0.75.png}
-    \caption{Learning curves for multi-agent CTDE paradigm} 
-    \label{fig:multi-learning-curves-ctde}
-\end{figure}
-
 \begin{figure}[htbp]
@@
 
+In Figure \ref{fig:multi-learning-curves-dtde}, we plot the simulation metrics for the DTDE approach, with the same parametrization as before.
+Just as with CTDE, we see an early converge to true rewards and true actions.
+The learning rate stays below the theoretical learning rate bound, validating the implementation.
+However, with both approaches, we noticed divergence from the optimal policy during longer time steps that even take place after what seemed to be a convergence to perfect learning, begging for further investigation.
 \pagebreak

### 2025-02-17 code/multi_agent/ctde.py

@@ -52,7 +52,7 @@ class CentralizedCritic(nn.Module):
 class MultiAgentTrainer:
     """CTDE trainer for multi-agent social learning."""
     def __init__(self, num_agents: int, hidden_size: int = 64, 
-                 lr_actor: float = 1e-4, lr_critic: float = 1e-3):
+                 lr_actor: float = 1e-3, lr_critic: float = 1e-3):
         self.num_agents = num_agents
         
         # Initialize actors and critic
@@ -67,7 +67,7 @@ class MultiAgentTrainer:
         # Hidden states
         self.hidden_states = [actor.init_hidden() for actor in self.actors]
         
-        self.gamma = 0.99
+        self.gamma = 0.99 # Discount factor
     
     def select_actions(self, signals: List[torch.Tensor], 
                       prev_actions: torch.Tensor) -> Tuple[List[int], List[torch.Tensor]]:
@@ -82,7 +82,7 @@ class MultiAgentTrainer:
             action = dist.sample()
             actions.append(action.item())
             log_probs.append(dist.log_prob(action))
-            true_action_rates.append(dist.probs[0][0].item())
+            true_action_rates.append(1- dist.probs[0][0].item())
 
         return actions, log_probs, true_action_rates
     
@@ -153,11 +153,12 @@ def train_ctde(num_agents: int = 4, num_steps: int = 10000,
     print(f"True state: {env.true_state}")
     # Training loop
     for t in range(num_steps):
+
         # Select actions
         actions, log_probs, true_action_rates = trainer.select_actions(signals, prev_actions)
         
         # Environment step
-        next_signals, observed_rewards, true_rewards, mistakes = env.step(actions)
+        next_signals, observed_rewards, true_rewards, mistakes = env.step(signals, actions)
         
         # Update trainer
         trainer.update(signals, actions, log_probs, observed_rewards, true_rewards, next_signals, prev_actions)
@@ -165,6 +166,9 @@ def train_ctde(num_agents: int = 4, num_steps: int = 10000,
         # Update metrics
         metrics.add_mistakes(mistakes)
         metrics.add_action_rate(true_action_rates)
+        metrics.add_true_rewards(true_rewards)
+        metrics.add_observed_rewards(observed_rewards)
+        metrics.add_signals([signal.item() for signal in signals])
         metrics.update_metrics()
         
         # Update states
[…]

### 2025-02-17 code/multi_agent/dtde.py

@@ -33,7 +33,7 @@ class DecentralizedCritic(nn.Module):
 class DecentralizedAgent:
     """Complete decentralized agent combining RNN, actor, and critic."""
     def __init__(self, num_agents: int, hidden_size: int = 64,
-                 lr_actor: float = 1e-4, lr_critic: float = 1e-3):
+                 lr_actor: float = 1e-2, lr_critic: float = 1e-2):
         self.rnn = MultiAgentRNN(num_agents, hidden_size)
         self.actor = DecentralizedActor(hidden_size)
         self.critic = DecentralizedCritic(hidden_size)
@@ -57,7 +57,7 @@ class DecentralizedAgent:
             dist = Categorical(action_probs)
             action = dist.sample()
             log_prob = dist.log_prob(action)
-            true_action_rate = dist.probs[0][0].item()
+            true_action_rate = 1 - dist.probs[0][0].item()
 
         return action.item(), log_prob, true_action_rate
     
@@ -113,6 +113,7 @@ def train_dtde(num_agents: int = 4, num_steps: int = 10000,
     prev_actions = torch.zeros(1, num_agents)
     
     print(f"True state: {env.true_state}")
+
     # Training loop
     for t in range(num_steps):
         # Select actions
@@ -127,7 +128,7 @@ def train_dtde(num_agents: int = 4, num_steps: int = 10000,
             true_action_rates.append(true_action_rate)
             
         # Environment step
-        next_signals, observed_rewards, _, mistakes = env.step(actions)
+        next_signals, observed_rewards, true_rewards, mistakes = env.step(signals, actions)
         
         # Convert current actions to tensor
         current_actions_tensor = torch.tensor([actions], dtype=torch.float32)
@@ -139,7 +140,10 @@ def train_dtde(num_agents: int = 4, num_steps: int = 10000,
         
         # Update metrics
         metrics.add_mistakes(mistakes)
+        metrics.add_signals([signal.item() for signal in signals])
         metrics.add_action_rate(true_action_rates)
+        metrics.add_true_rewards(true_rewards)
+        metrics.add_observed_rewards(observed_rewards)
         metrics.update_metrics()
         
         # Update states
@@ -151,7 +155,7 @@ def train_dtde(num_agents: int = 4, num_steps: int = 10000,
             print(f"\nStep {t + 1}")
             for i in range(num_agents):
                 print(f"Agent {i+1}:")
[…]

### 2025-02-17 code/multi_agent/environment.py

@@ -8,7 +8,7 @@ class MultiAgentEnvironment:
         self.num_agents = num_agents
         self.q = signal_accuracy
         #self.true_state = np.random.randint(1)
-        self.true_state = 0
+        self.true_state = 1
 
     def get_signals(self) -> List[torch.Tensor]:
         """Generate signals for all agents."""
@@ -43,8 +43,7 @@ class MultiAgentEnvironment:
         
         return observed_rewards, true_rewards
     
-    def step(self, actions: List[int]) -> Tuple[List[torch.Tensor], List[float], List[bool]]:
-        signals = self.get_signals()
+    def step(self, signals: List[int], actions: List[int]) -> Tuple[List[torch.Tensor], List[float], List[bool]]:
         observed_rewards, true_rewards = self.compute_rewards(actions,signals)
         mistakes = [action != self.true_state for action in actions]
         next_signals = self.get_signals()

### 2025-02-17 code/multi_agent/main.py

@@ -13,8 +13,8 @@ save_folder.mkdir(exist_ok=True)  # Create folder if it doesn't exist
 
 if __name__ == "__main__":
     # Train with metrics tracking
-    num_agents = 100
-    num_steps = 10
+    num_agents = 4
+    num_steps = 1000
     signal_accuracies = [0.75]
 
     for signal_accuracy in signal_accuracies:

### 2025-02-17 code/multi_agent/metrics.py

@@ -1,19 +1,26 @@
 import math
 import matplotlib.pyplot as plt
 from typing import List
+import numpy as np
 
 class MultiAgentMetricsTracker:
     """Track learning metrics for multiple agents."""
     def __init__(self, num_agents: int, num_steps: int):
         self.num_agents = num_agents
         self.num_steps = num_steps
+        self.window_size = int(self.num_steps / 10)
+        self.total_steps = 0
+        self.signals = [[] for _ in range(num_agents)]
         self.mistakes = [[] for _ in range(num_agents)]
         self.mistake_rates = [[] for _ in range(num_agents)]
         self.learning_rates = [[] for _ in range(num_agents)]
-        self.action_rate_history = [[] for _ in range(num_agents)]  # Track actions for each agent
+        self.action_rate_history = [[] for _ in range(num_agents)] 
         self.avg_action_rates = [[] for _ in range(num_agents)]
-        self.window_size = int(self.num_steps / 100)
-        self.total_steps = 0
+        self.true_rewards = [[] for _ in range(num_agents)]
+        self.observed_rewards = [[] for _ in range(num_agents)]
+        self.avg_observed_rewards = [[] for _ in range(num_agents)]
+        self.avg_true_rewards = [[] for _ in range(num_agents)]
+        self.avg_signals = [[] for _ in range(num_agents)]
     
     def add_mistakes(self, mistakes: List[bool]):
         self.total_steps += 1
@@ -25,89 +32,112 @@ class MultiAgentMetricsTracker:
         for i in range(self.num_agents):
             self.action_rate_history[i].append(true_action_rates[i])
     
+    def add_true_rewards(self, true_rewards: List[float]):
+        """Track actions chosen by each agent."""
+        for i in range(self.num_agents):
+            self.true_rewards[i].append(true_rewards[i])
+
+    def add_observed_rewards(self, observed_rewards: List[float]):
+        """Track actions chosen by each agent."""
+        for i in range(self.num_agents):
+            self.observed_rewards[i].append(observed_rewards[i])
+    
+    def add_signals(self, signals: List[float]):
+        """Track actions chosen by each agent."""
+        for i in range(self.num_agents):
+            self.signals[i].append(signals[i])
+    
     def compute_mistake_rate(self, agent_idx: int) -> float:
         if self.total_steps == 0:
[…]

### 2025-02-17 code/single_agent/environment.py

@@ -1,6 +1,5 @@
-import numpy as np
+import numpy as np 
 import torch
-
 from typing import Tuple
 
 class Environment:
@@ -12,7 +11,7 @@ class Environment:
         """
         self.q = signal_accuracy
         # Draw true state once and keep it fixed throughout
-        self.true_state = np.random.randint(2)  # Fixed true state ω
+        self.true_state = 1  # Fixed true state ω
     
     def get_signal(self) -> torch.Tensor:
         """Generate signal based on current true state."""
@@ -30,17 +29,24 @@ class Environment:
         denominator = 2 * self.q - 1
         return numerator / denominator
     
-    def step(self, action: int) -> Tuple[torch.Tensor, float, bool]:
+    def compute_true_reward(self, action: int) -> float:
+        """Compute reward based on true state rather than signal."""
+        return float(action == self.true_state)
+    
+    def step(self, action: int) -> Tuple[torch.Tensor, float, float, bool, float]:
         # Get current signal
         current_signal = self.get_signal()
         
-        # Compute reward using paper's reward function
-        reward = self.compute_reward(action, current_signal.item())
+        # Compute observed reward using paper's reward function
+        observed_reward = self.compute_reward(action, current_signal.item())
         
-        # Check if action was a mistake
+        # Compute true reward
+        true_reward = self.compute_true_reward(action)
+        
+        # Check if action matches true state
         is_mistake = (action != self.true_state)
         
         # Get next signal
         next_signal = self.get_signal()
             
-        return next_signal, reward, is_mistake
+        return next_signal, observed_reward, true_reward, is_mistake, current_signal.item()

### 2025-02-17 code/single_agent/main.py

@@ -3,7 +3,7 @@ from torch.distributions import Categorical
 import matplotlib.pyplot as plt
 import math
 
-from metrics import MetricsTracker
+from metrics import MetricsTracker, plot_metrics
 from environment import Environment
 from agent import Agent
 from pathlib import Path
@@ -15,52 +15,14 @@ current_path = Path(__file__).resolve()
 save_folder = current_path.parent.parent.parent / "charts"
 save_folder.mkdir(exist_ok=True)  # Create folder if it doesn't exist
 
-from ..multi_agent.metrics import plot_multi_agent_metrics
 
-def plot_metrics(metrics_tracker: MetricsTracker, signal_accuracy: float = 0.75):
-    """Plot learning curves with theoretical bound in academic black and white style."""
-    # Set style for academic black and white plots
-    plt.style.use('grayscale')
-    
-    # Create figure with side-by-side plots
-    fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 5))
-    
-    # Calculate theoretical bound
-    q_bound = 2 * signal_accuracy - 1  # For symmetric binary case
-    r_bdd = -math.log(1 - q_bound)
-    
-    # Plot mistake rate
-    ax1.plot(metrics_tracker.mistake_rates, color='black', label='Empirical Rate')
-    ax1.set_title('(a) Mistake Rate Over Time', pad=10)
-    ax1.set_xlabel('Time Step')
-    ax1.set_ylabel('Mistake Rate')
-    ax1.grid(True, linestyle='--', alpha=0.7)
-    ax1.legend(frameon=False)
-    
-    # Plot learning rate with different line styles for distinction
-    ax2.plot(metrics_tracker.learning_rates, color='black', label='Empirical Rate')
-    ax2.axhline(y=r_bdd, color='black', linestyle='--', 
-                label=f'Theoretical Bound')
-    ax2.set_title('(b) Learning Rate Over Time', pad=10)
-    ax2.set_xlabel('Time Step')
-    ax2.set_ylabel('Learning Rate')
-    ax2.grid(True, linestyle='--', alpha=0.7)
-    ax2.legend(frameon=False)
-    
-    # Adjust layout and save
-    plt.tight_layout()
-    
-    # Save with high DPI for publication quality
-    plt.savefig(save_folder/f'single_agent_learning_curves_q={signal_accuracy}.png', dpi=300, bbox_inches='tight')
-    plt.show()
-
[…]

### 2025-02-17 code/single_agent/metrics.py

@@ -1,43 +1,114 @@
 import math
+import numpy as np
 
 class MetricsTracker:
-    def __init__(self):
-        self.mistakes = []  # Full history of mistakes
+    def __init__(self, num_steps: int):
+        self.num_steps = num_steps
+        self.window_size = int(self.num_steps / 10)
+        self.total_steps = 0
+        
+        # Basic metrics from original implementation
+        self.mistakes = []
         self.mistake_rates = []
         self.learning_rates = []
-        self.total_steps = 0
+        
+        # New metrics from multi-agent implementation
+        self.signals = []
+        self.action_rate_history = []
+        self.true_rewards = []
+        self.observed_rewards = []
+        
+        # Running averages
+        self.avg_action_rates = []
+        self.avg_observed_rewards = []
+        self.avg_true_rewards = []
+        self.avg_signals = []
     
     def add_mistake(self, mistake: bool):
         self.total_steps += 1
         self.mistakes.append(mistake)
     
+    def add_action_rate(self, true_action_rate: float):
+        """Track action chosen by the agent."""
+        self.action_rate_history.append(true_action_rate)
+    
+    def add_true_reward(self, true_reward: float):
+        """Track true reward."""
+        self.true_rewards.append(true_reward)
+    
+    def add_observed_reward(self, observed_reward: float):
+        """Track observed reward."""
+        self.observed_rewards.append(observed_reward)
+    
+    def add_signal(self, signal: float):
+        """Track received signal."""
+        self.signals.append(signal)
+    
     def compute_mistake_rate(self) -> float:
-        """Compute current mistake rate."""
         if self.total_steps == 0:
-            return 1.0  # Start with worst case
+            return 1.0
         return sum(self.mistakes) / self.total_steps
     
+    def compute_running_avg(self, metric: list) -> float:
+        recent_values = metric[-self.window_size:]
+        return sum(recent_values) / len(recent_values) if recent_values else 0.5
+    
     def compute_learning_rate(self) -> float:
-        """Compute learning rate as defined in the paper.
-        r = -1/t log P(aᵗ ≠ aω)
-        """
-        if self.total_steps < 2:  # Need at least 2 steps
-            return 0.0
-            
-        # Compute mistake rate over increasing horizons
-        rates = []
[…]

### 2025-02-17 paper/paper.tex
Update text.

@@
 \subsubsection*{Training Process}
-The agent is trained using a variant of the Advantage Actor-Critic (A2C) algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.
+The agent is trained using a variant of the Advantage Actor-Critic algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.
 
@@
 
-The algorithm implements the A2C training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics.
+The algorithm implements the Advantage Actor Critic training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics.
 The actor network learns a policy that minimizes mistakes in predicting the true state, while the critic network estimates state values to compute advantages for policy updates.
@@
 
-    \item \textit{Proportions of True Action}: The proportion of time each agent selects the correct action in their policy, reflecting how well the agents have learned to identify the optimal action.
+    \item \textit{True Action Rates}: The proportion of how much the agent's mixed policy assings to the true action $a_\omega = 1$. This metric helps visualize the agent's learning progress.
 

### 2025-05-26 paper/appendix.tex
Update brandl results.

\setcounter{proposition}{0}
\setcounter{assumption}{0}
\setcounter{lemma}{0}
\setcounter{theorem}{0}

\chapter{Reinforcement Learning Background}

\label{appendix:rl_details}
This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.

\section{Reinforcement Learning Foundations}

Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty. In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}. This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:

\begin{itemize}
    \item $S$ is the state space, representing all possible configurations of the environment
    \item $A$ is the action space, representing all possible decisions available to the agent
    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
\end{itemize}

The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions. The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter. The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.

The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs. This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem. However, this assumption becomes problematic in multi-agent settings, as we will discuss next.

\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}

Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}. MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}. These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:

\begin{itemize}
    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
    \item $S$ is the state space, shared among all agents
    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
    \item $\gamma \in [0, 1)$ is the discount factor
\end{itemize}
MARL introduces several fundamental challenges beyond those encountered in single-agent RL. The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system. Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}. In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions. MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings. Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.

\section{The Non-Stationarity Challenge}
The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}. To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent. When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$. From agent $i$'s perspective, the effective transition function becomes:
\begin{equation}
    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
\end{equation}
where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$. When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$. This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL. When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}. This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}. Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}. The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}. These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.

\section{Traditional Approaches to Non-Stationarity}
Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:

\subsection{Independent Learning}
The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}. This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents. Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences. While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.

\subsection{Centralized Training with Decentralized Execution}
To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}. In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.

Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution. Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline. The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies. While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.

\subsection{Opponent Modeling and Population-Based Training}
Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}. This can involve predicting other agents' policies, types, or learning dynamics. Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning. Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.

The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity. While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.

\subsection{Equilibrium Learning and Stability Concepts}
Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}. These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate. Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games. Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.

The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence. While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality. Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.

\subsection{Meta-Learning for Non-Stationarity}
Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}. These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem. Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.

Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents. While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.

\section{Active Markov Games}

Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}. They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.

\subsection{Formal Definition}

An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:

\begin{itemize}
    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
    \item $S$ is the state space
    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
\end{itemize}
Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state. The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates. At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$. Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$. Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$. This process continues until non-stationary policies converge to a recurrent set of joint policies. The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.

\subsection{Augmented Transition Function and Stationarity}

The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions. To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games. In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions. However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions. The augmented transition function becomes:

\begin{equation}
    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
\end{equation}
The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories. By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one. This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.

\subsection{Theoretical Properties and Convergence}

Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:

\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:

\begin{equation}
    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
\end{equation}

where $\ell = t\%k$ with $\%$ denoting the modulo operation. This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies. The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence. To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}. These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.

\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:

\begin{equation}
    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
        \begin{array}{c}
            s_0=s, \theta_0=\theta,                                              \\
            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
        \end{array}
        \right]
\end{equation}

where  $0:T$ denotes the sequence from time $0$ to $T$. This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.

\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium. An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:

\begin{equation}
    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
\end{equation}
for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$. This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system. The active equilibrium generalizes several classic solution concepts in game theory. Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively. Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively. This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.

Active Markov Games address the non-stationarity challenge in several fundamental ways. By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated. The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors. Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates. Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees. Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.

\subsection{Practical Implementations}

Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL. Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner. Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games. These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.

\section{Extension to Partial Observability}

While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state. In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents. This partial observability introduces additional challenges for multi-agent learning. The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions. In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}. Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning. The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.

In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state. Theoretical formulations, as established by Meuleau et al. \cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$. However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation. Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}. These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics. In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time. For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.

\chapter{Proofs Regarding Average Returns}

This section provides the mathematical foundations and detailed proofs for the
key theoretical results in our Partially Observable Active Markov Game framework
with average return objectives. We establish the Markov properties of belief transitions
and joint processes, prove the existence and uniqueness of stochastically stable
distributions, and derive the policy gradient theorem for average return optimization.

\section{Markov Property of the Joint Process}
\label{appendix:stochasticallystable}We first establish the Markov properties of
belief state transitions and the joint process comprising states, belief states,
and policy parameters. These properties form the foundation for our convergence analysis.

\begin{lemma}[Markov Property of Belief Transitions]
    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
    a Markov process under a fixed policy $\pi$, meaning that the distribution of
    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
    not on earlier beliefs, actions, or observations.
\end{lemma}

\begin{proof}
    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
    relevant information from the history of observations and actions up to time
    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
            ^{i}$ through the rule:
    \begin{align}
        b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
    \end{align}

    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
    property.
\end{proof}

\begin{remark}[Transformer-Based Belief Representation]
    In practice, transformer architectures can be used to represent and
    update belief states. In such cases, the belief state is updated
    through an attention-based mechanism of the form:
    \begin{equation}
        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
    \end{equation}

    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
    observation and previous belief state through self-attention layers, satisfying the Markov property
    while capturing complex dependencies between observations and beliefs.
\end{remark}
Next, we establish the Markov property of the joint process.
\begin{lemma}[Markov Property of Joint Process]
    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
    a Markov process under periodic policy updates, meaning that the distribution
    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
    states.
\end{lemma}
\begin{proof}
    The state transitions are by definition only dependent on current state and current
    actions. The remaining parts can be analyzed as follows:

    \textbf{1. Belief
        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.

    \textbf{2. Policy parameter
        update:} At every time step $t$, policy parameters are updated according to $U(
        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
    Under the Markovian policy update assumption, the update depends only on $\theta
        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
    probability
    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
        {b}_{t}, \boldsymbol{\theta}_{t}))$
    depends only on the current state
    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
    of states, establishing the Markov property.
\end{proof}
\section{Convergence}
Having established the Markov properties, we now analyze the convergence
behavior of the joint process to a unique stochastically stable distribution. This
convergence result is crucial for developing optimization objectives in our framework.
\begin{theorem}[Stochastically Stable Distribution]
    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
    defined by $\epsilon$-perturbed policy update functions converge to the unique
    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
\end{theorem}

\begin{proof}
    We establish the convergence to the unique stochastically stable distribution by
    showing that a perturbed Markov process of a partially observable active Markov
    game is regular. First, let us introduce a small perturbation to the policy update
    functions:
    \begin{align}
        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
    \end{align}

    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
    probability of transitioning to any other configuration
    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
    probability:
    \begin{align}
        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
    \end{align}

    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
    of the joint process. We will show that there must exist a path with positive probability
    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
    second as follows:

    \textbf{1. Policy Parameter Transition:} Due to the
    $\epsilon$-perturbation in update functions, there is a positive probability of
    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
    \begin{align}
        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
    \end{align}

    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
    $\boldsymbol{\theta}_{2}$.

    \textbf{2. State Transition:} By the communicating
    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
    such that:
    \begin{align}
        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
    \end{align}

    Given the relationship between policies and actions, this sequence of actions has
    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
    for all required actions.

    \textbf{3. Belief State Transition:} By the communicating belief-state
    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
        B$, there exists a sequence of observations
    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
    \begin{align}
        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
    \end{align}

    Since observations depend on states, which can be influenced through actions,
    and actions are determined by policies, there is a positive probability path from
    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
    and policy parameters. Combining these three components, we can construct a path
    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
    classes of the perturbed joint process. Since we have shown that the perturbed
    joint process has only one recurrent class, it is a regular Markov process. Following
    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
    process on a finite state space possesses a unique stationary distribution
    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
    converges to a limit $\mu^{*}$, which is the unique stochastically stable
    distribution of the original, unperturbed process. Therefore, under the given conditions,
    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
    partially observable active Markov game possesses a unique stochastically
    stable distribution $\mu^{*}$.
\end{proof}
\section{Policy Gradient Theorem}
Having established the convergence to a unique stochastically stable distribution,
we now derive the policy gradient theorem for optimization in our framework. This
theorem provides the mathematical foundation for gradient-based algorithms to maximize
the average return objective.
\label{appendix:avg_gradient}
\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
        Theorem]
    The gradient of the active average reward objective
    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
    setting is:
    \begin{align}
        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    where the action-value function $q^{i}_{\theta^i}$ is defined as:
    \begin{align}
        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
    \end{align}

    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
    the belief update function.
\end{theorem}

\begin{proof}
    We first define the average reward objective in the partially observable setting:
    \begin{align}
        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
    \end{align}

    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
    differential value function $v^{i}_{\theta^i}$ represents the expected total
    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
        ^{i}_{\theta^i}$:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
    \end{align}

    Following the Bellman equation derivation principles, we can express
    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
    \end{align}

    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
    represents the belief update function that updates the belief state based on
    the current belief, action, and new observation. We now define the action-value
    function $q^{i}_{\theta^i}$ for the partially observable setting:
    \begin{align}
        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
    \end{align}

    Using this definition, we can rewrite the differential value function as:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    To derive the policy gradient, we begin by computing the gradient of the differential
    value function with respect to $\theta^{i}$:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    We expand the gradient of the action-value function:
    \begin{align}
        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.                                                                                                                                                                                                                                           \\
                                                                                                  & \left. \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Substituting back into the original expression, we get:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Rearranging terms:
    \begin{align}
        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Now, we define the transition operator that maps the expectation of a function
    from one time step to the next:
    \begin{align}
        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    We can rewrite our expression as:
    \begin{align}
        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Now, we take the expectation with respect to the stationary distribution
    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
    \begin{align}
        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    By the definition of the stationary distribution, we have:
    \begin{align}
        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Therefore, the second and third terms in our expression cancel out, giving the
    final policy gradient theorem:
    \begin{align}
        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}
\end{proof}

\chapter{Proofs Regarding Discounted Returns}
\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
mathematical foundation.
\section{Transition Operator and Its Adjoint}
To establish a rigorous framework for analyzing discounted returns in Partially
Observable Active Markov Games, we need to formalize how value functions evolve over
time and how probability distributions propagate through the system. This dual
perspective is captured by two fundamental operators: the transition operator and
its adjoint.

\subsection{Definitions and Duality}

We begin by defining the inner product between functions and measures, which forms
the foundation for the duality relationship between our operators.

\begin{definition}[Inner Product between Functions and Measures]
    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
    Lebesgue integral:
    \begin{equation}
        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
        {\theta})
    \end{equation}
\end{definition}

This inner product captures the expected value of function $f$ with respect to
measure $\mu$, allowing us to express value functions as expectations with respect
to appropriate measures.

\begin{definition}[Transition Operator and Its Adjoint]
    \hfill
    \begin{enumerate}
        \item The \textbf{transition operator}
              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
              maps a bounded measurable function to its expected value after one
              transition:
              \begin{align}
                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
              \end{align}

              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
              represents the belief update function.

        \item The \textbf{adjoint operator}
              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
              is defined on the space of finite measures such that:
              \begin{equation}
                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
              \end{equation}

              for all
              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
    \end{enumerate}
\end{definition}

Intuitively, $\Psi$ describes how function expectations evolve forward in time,
meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
capturing the propagation of visitation probabilities through the system. The duality
relationship ensures that expected values can be computed either by applying $\Psi$
to functions or $\Psi^{*}$ to measures.

\subsection{Properties of the Operators}

These operators possess several important properties that facilitate our
analysis of discounted returns:

\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
    properties:

    \begin{enumerate}
        \item \textbf{Linearity:}
              \begin{itemize}
                  \item For the operator: For any functions
                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
                            )$
                        and constants $\alpha, \beta \in \mathbb{R}$:
                        \begin{align}
                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
                        \end{align}

                  \item For the adjoint: For any measures
                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
                            )$
                        and constants $\alpha, \beta \in \mathbb{R}$:
                        \begin{align}
                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
                        \end{align}
              \end{itemize}

        \item \textbf{Positivity Preservation:}
              \begin{itemize}
                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.

                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
                            \mu$ is also non-negative.
              \end{itemize}

        \item \textbf{Preservation of Total Measure:}
              \begin{itemize}
                  \item For the operator: The operator preserves the constant function
                        $\mathbf{1}$:
                        \begin{align}
                            \Psi \mathbf{1}= \mathbf{1}
                        \end{align}

                        where $\mathbf{1}$ represents the function that equals 1 everywhere.

                  \item For the adjoint: For any measure
                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
                        \begin{align}
                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
                        \end{align}
              \end{itemize}

        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
              bounded with:
              \begin{align}
                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
              \end{align}

              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
                  {b},\boldsymbol{\theta})|$ is the supremum norm.

        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
              \begin{align}
                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
              \end{align}

              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
    \end{enumerate}
\end{lemma}

\begin{proof}
    We prove each property in turn:

    \textbf{1. Linearity:}

    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
    \begin{align}
         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    For the adjoint: For any measurable function
    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
    \begin{align}
        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
    \end{align}

    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
    measure.

    \textbf{2. Positivity Preservation:}

    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
        )$:
    \begin{align}
        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
        {\theta}) \geq 0$.

    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
    function $f \geq 0$:
    \begin{align}
        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
    \end{align}

    where the inequality follows from the positivity preservation of $\Psi$ and the
    fact that $\mu$ is non-negative. Since this holds for all non-negative
    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.

    \textbf{3. Preservation of Total Measure:}

    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
    everywhere. Then:
    \begin{align}
        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
    \end{align}

    Since each probability distribution sums to 1, applying them sequentially
    yields:
    \begin{align}
        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
    \end{align}

    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
    \begin{align}
        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
    \end{align}

    where we used the unit preservation property of $\Psi$. This gives:
    \begin{align}
        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
    \end{align}

    \textbf{4. Bound Preservation:}

    For any bounded function $f$ with
    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
        ,\boldsymbol{\theta})|$:
    \begin{align}
        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.   \\
                                                           & \quad \left. \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
    \end{align}

    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.

    \textbf{5. Explicit Form of the Adjoint:}

    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
    \begin{align}
        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
    \end{align}

    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
    \begin{align}
        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Substituting this back and using the definition of inner product:
    \begin{align}
        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}
\end{proof}

\subsection{Contraction and Propagation}

The properties established above lead to two crucial results: the contraction
property of the discounted transition operator and the propagation of
distributions through the adjoint.

\begin{lemma}[Contraction Mapping Property]
    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
    contraction mapping on the Banach space of bounded functions on
    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
    norm. Specifically, for any two functions
    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
    \begin{align}
        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
    \end{align}
\end{lemma}

\begin{proof}
    Using the linearity of $\Psi$ and its bound preservation property:
    \begin{align}
        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
                                                   & \leq \gamma\|f - g\|_{\infty}
    \end{align}

    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
    factor $\gamma$.
\end{proof}

This contraction property leads directly to the invertibility of
$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
in discounted settings.

\begin{lemma}[Invertibility of $I - \gamma \Psi$]
    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
    invertible, and its inverse can be represented as a Neumann series:
    \begin{align}
        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
    \end{align}

    which converges absolutely in the operator norm.
\end{lemma}

\begin{proof}
    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
    space, then $I - T$ is invertible, with inverse given by the Neumann series
    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
    have:

    \begin{align}
        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
    \end{align}

    The absolute convergence follows from:
    \begin{align}
        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
    \end{align}

    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
        \leq 1$ for all $t$.
\end{proof}

Finally, we establish how distributions evolve in the system through the adjoint
operator, formalizing the propagation of probability measures.

\begin{lemma}[Distribution Propagation]
    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
\end{lemma}

\begin{proof}
    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
        {\Theta})$:
    \begin{align}
        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
    \end{align}

    Since this holds for any measurable function $f$, we have
    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
\end{proof}

The concepts introduced in this section—the transition operator, its adjoint, and
their properties—provide the mathematical foundation for analyzing discounted returns
in Partially Observable Active Markov Games. The transition operator $\Psi$
captures how function expectations evolve forward in time, while its adjoint $\Psi
    ^{*}$ describes how probability distributions propagate forward in time. This
duality is fundamental to establishing the connection between value-based and
distribution-based perspectives in reinforcement learning.

In the next section, we will use these tools to formulate Bellman equations and derive
policy gradients for maximizing discounted returns in this complex multi-agent setting.
\section{Bellman Equations and Value Functions}
In this section, we establish the fundamental recursive relationships that characterize
the discounted value functions in Partially Observable Active Markov Games.
These relationships form the basis for our policy gradient derivation and
practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
of value functions, then establish the Bellman equations, and finally derive the
gradient expressions necessary for policy optimization.
\subsection{Well-Definedness of Value Functions}
Before deriving recursive relationships, we first establish that the value functions
are well-defined mathematical objects under our assumptions of bounded rewards and
discount factors less than 1.
\begin{lemma}[Well-Defined Value Functions]
    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
    action-value functions
    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
    well-defined and finite for all states, belief states, policy parameters, and actions.
\end{lemma}
\begin{proof}
    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
    \begin{align}
        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
    \end{align}

    Similarly, for the action-value function:
    \begin{align}
        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
    \end{align}

    Thus, both value functions are well-defined and bounded.
\end{proof}This lemma ensures that our subsequent derivations involving value
functions are mathematically sound. The boundedness property is particularly important
when we consider expectations and derivatives of these functions.
\subsection{Bellman Equations for Discounted Value Functions}
Next, we establish the recursive relationships between value functions, which
are fundamental to dynamic programming approaches.
\begin{lemma}[Bellman Equation for Discounted Value Functions]
    In a Partially Observable Active Markov Game, the discounted value function
    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    where the action-value function $q^{i}_{\theta^i}$ is defined as:
    \begin{align}
        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}
\end{lemma}
\begin{proof}
    By definition, the discounted value function is:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
    \end{align}

    We can decompose this into the immediate reward and the future discounted
    returns:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
    \end{align}

    For the first term, we have:
    \begin{align}
        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
    \end{align}

    For the second term, by the law of total expectation:
    \begin{align}
         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Combining these two terms and factoring out common terms:
    \begin{align}
        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
\end{proof}The Bellman equation provides a recursive characterization of the
value function that forms the basis for dynamic programming algorithms. This equation
captures how current actions influence both immediate rewards and future value through
their effects on the environment state, belief states, and policy parameters of other
agents. The key distinction from standard Bellman equations is the inclusion of
belief updates and policy parameter dynamics, which reflects the complex dependencies
in partially observable multi-agent settings.
\subsection{Policy Gradient with Respect to Value Function}
Having established the recursive relationship for value functions, we now derive
how the value function gradient depends on policy parameters, which is essential
for policy optimization.
\begin{lemma}[Policy Gradient with Respect to Value Function]
    The gradient of the value function with respect to policy parameters $\theta^{i}$
    can be expressed as:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
    \end{align}

    where $\Psi$ is the transition operator defined in the previous section.
\end{lemma}
\begin{proof}
    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
    \end{align}

    Applying the product rule:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    For the gradient of the action-value function:
    \begin{align}
        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
    \end{align}

    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
        {o}'|s')$, and
    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
    do not depend directly on $\theta^{i}$:
    \begin{align}
        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}

    Using the transition operator $\Psi$, we can rewrite:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Rearranging:
    \begin{align}
        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
    \end{align}
\end{proof}This lemma expresses the value function gradient in terms of an
infinite sum of expected Q-values weighted by policy gradients and propagated
through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
immediate changes in policy parameters propagate through future timesteps. This
form of the gradient is central to our discounted policy gradient theorem, which
we will develop in the next section. The inverse operator can be represented as
a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
as the accumulated effect of policy changes over an infinite horizon, weighted
by the discount factor.
\section{Discounted Visitation Measure}
The infinite sum formulation derived in the previous sections, while
mathematically sound, is not directly amenable to practical computation. In this
section, we reformulate these expressions in terms of a probability distribution,
which allows for more efficient estimation through sampling-based approaches. This
reformulation is central to our policy gradient theorem for discounted returns.
\subsection{Definition and Properties}
\begin{definition}[Discounted Visitation Measure]
    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
    \begin{equation}
        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
    \end{equation}

    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
    and $\gamma \in [0, 1)$ is the discount factor.
\end{definition}This measure represents the expected discounted frequency with which
different states, belief states, and policy parameters are visited when following
policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
distribution, summing to 1 across the entire state-belief-policy space. The discounted
visitation measure plays a central role in reinforcement learning theory,
particularly in policy gradient methods. It provides a natural weighting of states
according to their importance for the discounted objective, as states that are
visited more frequently or earlier in trajectories receive higher weight. This concept
generalizes the stationary distribution used in average-reward settings to the discounted
return framework.
\begin{lemma}[Evolution of Discounted Visitation]
    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
    the adjoint operator as:
    \begin{equation}
        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
    \end{equation}

    where $\mu_{0}$ is the initial distribution.
\end{lemma}
\begin{proof}
    By the propagation lemma established earlier,
    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
    measure:
    \begin{align}
        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
    \end{align}

    The second equality follows from the Neumann series expansion:
    \begin{align}
        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
    \end{align}

    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
    the total variation norm.
\end{proof}This establishes the essential connection between the adjoint operator
and the discounted visitation measure, which is central to the policy gradient
theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
time spent in each state-belief-policy configuration, weighted according to the
discount factor $\gamma$. This connection allows us to transform expressions involving
$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
practical implementations, the discounted visitation measure is rarely computed explicitly
due to the prohibitive computational cost. Instead, sampling-based approaches are
used to estimate expectations with respect to this measure. The policy gradient
theorem leverages this measure to derive update rules that can be efficiently
implemented using trajectory samples collected from the environment.

\subsection{Existence and Uniqueness}
To provide a rigorous mathematical foundation for our policy gradient theorem,
we establish the existence and uniqueness of the discounted visitation measure.
\begin{lemma}[Existence of the Discounted Visitation Measure]
    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
    of finite measures on the joint state-belief-policy space, equipped with the
    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
        )$, the discounted state-visitation measure
    \begin{align}
        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
    \end{align}

    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
        \boldsymbol{\Theta})$.
\end{lemma}
\begin{proof}
    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
    converges to a well-defined measure. First, let's recall that
    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
    the total variation norm
    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
    we need to show that the series
    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
    joint state-belief-policy space after $t$ transitions, starting from the initial
    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
    $\mu_{0}$ with total mass
    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
    \begin{align}
        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
    \end{align}

    For $n < m$, the difference between two partial sums is:
    \begin{align}
        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
    \end{align}

    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
    of this space, the sequence converges to a measure which we denote as
    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
    \begin{align}
        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
                                                                           & = M
    \end{align}

    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
\end{proof}Having established existence, we now turn to the uniqueness of the discounted
visitation measure.

\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
    to the functional equation:
    \begin{align}
        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
    \end{align}

    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
        {\Theta})$.
\end{lemma}
\begin{proof}
    First, we verify that
    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
    satisfies the functional equation:

    \begin{align}
        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
                                                            & = d^{\pi}_{\mu_0}
    \end{align}

    To prove uniqueness, suppose there exists another measure
    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
    that satisfies the functional equation:
    \begin{align}
        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
    \end{align}

    Let's consider the operator
    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
    defined as:
    \begin{align}
        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
    \end{align}

    For any two measures
    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
    \begin{align}
        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
                                 & \leq \gamma \|\mu - \nu\|_{TV}
    \end{align}

    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
    the uniqueness of the discounted state-visitation measure.
\end{proof}

\subsection{Connection to Value Function}
Having established the theoretical properties of the discounted visitation
measure, we now connect it to the value function, which will provide important
insights later on.

\begin{lemma}[Value Function as Inner Product]
    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
    the value function can be expressed as:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
    the Dirac measure concentrated at
    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
    immediate reward function:
    \begin{align}
        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
    \end{align}
\end{lemma}
\begin{proof}
    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
        {\theta}_{0})$. By definition of the value function:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
    \end{align}

    Define the expected immediate reward function
    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
    \begin{align}
        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
    \end{align}

    Then:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
    and measures:
    \begin{align}
        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Therefore:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
    \end{align}

    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
    $(I - \gamma \Psi^{*})^{-1}$:
    \begin{align}
        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
        ^{*})^{-1}\mu_{0}$. Therefore:
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}
\end{proof}This lemma establishes that the value function can be expressed as an
expectation with respect to the discounted visitation measure, with an appropriate
scaling factor. This formulation provides a direct link between the value
function and the distribution of states.

\section{Policy Gradient Theorem}
Having established the mathematical foundations for discounted returns in
partially observable multi-agent settings, we now derive the policy gradient theorem
that forms the basis for practical optimization algorithms. This theorem
provides a principled expression for computing gradients of the expected
discounted return with respect to policy parameters, enabling efficient policy improvement.
The policy gradient theorem connects an agent's policy parameters to its
expected long-term performance through the discounted visitation measure, providing
a mathematically rigorous foundation for optimization.

\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
        Theorem]
    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
    Markov game setting can be expressed as:
    \begin{align}
        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
    visitation measure starting from initial distribution $\mu_{0}$, and
    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
    the action-value function defined as:
    \begin{align}
        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
    \end{align}
\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
on the lemmas established in previous sections.
\begin{proof}
    From our previous lemma, we know that the gradient of the value function can be
    expressed as:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
    \end{align}

    For notational clarity, we define the term inside the brackets as:
    \begin{align}
        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    Now we can write:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    For our specific initial state configuration
    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
    \end{align}

    Let's define
    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
    Dirac measure concentrated at the initial state. We can view
    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
    Dirac measure:

    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Recall the duality principle we established earlier, which states that:
    \begin{align}
        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
    \end{align}

    Allowing us to move the operator from acting on the function $g$ to acting on
    the measure $\mu_{0}$:
    \begin{align}
        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Therefore:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    From our earlier derivation of the discounted visitation measure, we established
    that:
    \begin{align}
        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
    \end{align}

    We can now substitute this expression:
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
    \begin{align}
        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    For finite state, belief, and policy parameter spaces, this integral can be
    written as a sum:
    \begin{align}
        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
    \end{align}

    This completes the proof of the Partially Observable Active Discounted Return
    Policy Gradient Theorem.
\end{proof}

The proof reveals a symmetry in the mathematical structure of our results.
\begin{remark}[Symmetry]
    From the Value Function as Inner Product lemma, the value function
    \begin{align}
        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
    measure $d^{\pi}_{\mu_0}$. While its gradient
    \begin{align}
        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
    \end{align}

    is an expectation of policy-gradient-weighted action values $g$ under the same
    discounted visitation measure $d^{\pi}_{\mu_0}$.
\end{remark}
This symmetric structure provides not only mathematical elegance but also
practical advantages. It means that the same samples from the discounted visitation
distribution can be used to estimate both values and policy gradients.

The policy gradient theorem provides the mathematical foundation for agents to optimize
their policies in ways that account for both the partial observability of the environment
and the learning dynamics of other agents. This enables sophisticated strategic
behaviors such as information revelation, teaching, and influence that are
essential in social learning contexts.

\chapter{POLARIS Architecture}
\label{appendix:neural_architectures}

This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation. We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.

\section{Belief Processing Module}

In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.

The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences. The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.

The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension. Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:

\begin{equation}
    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
\end{equation}

This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:

\begin{equation}
    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
\end{equation}

where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors. The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:

\begin{equation}
    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
\end{equation}

where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.

The transformer encoder is followed by feed-forward networks with ReLU activations:

\begin{equation}
    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
\end{equation}

A belief head at the output projects the transformed representation to a probability distribution over possible environment states:

\begin{equation}
    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
\end{equation}

Where $h_{\text{final}}$ is the final hidden state from the transformer. This distribution represents the agent's belief about the current environmental state. The transformed representation also becomes the new belief state that is maintained across time steps.

The transformer architecture offers several advantages for belief processing in partially observable environments. First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks. Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs. Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.

\section{Inference Learning Module}

The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning. POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.

The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships. For each node, features include the agent's observation and action.

The graph representation treats each agent as a node, with edges representing observational relationships. The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:

\begin{equation}
    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
\end{equation}
\begin{equation}
    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
\end{equation}

where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$. The node representations are then updated using these attention weights:

\begin{equation}
    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
\end{equation}

The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:

\begin{equation}
    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
\end{equation}

where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections. The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).

The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards. Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.

After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:

\begin{equation}
    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
\end{equation}
\begin{equation}
    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
\end{equation}

where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.

The GNN also outputs an opponent belief distribution through a separate head:

\begin{equation}
    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
\end{equation}

This distribution represents the agent's prediction of other agents' beliefs about the environment state.

The latent variables are sampled using the reparameterization trick to enable backpropagation:

\begin{equation}
    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
\end{equation}

The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:

\begin{equation}
    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
\end{equation}

where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space. The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.

\section{Reinforcement Learning Module}

The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards. POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.

\subsection{Policy Network Architecture}

The policy network translates belief states and inferred latent variables into action decisions. It represents the agent's strategy for maximizing long-term rewards in the social learning environment. The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.

The policy is implemented as an MLP with ReLU activations across multiple hidden layers:

\begin{equation}
    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
\end{equation}
\begin{equation}
    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
\end{equation}

Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:

\begin{equation}
    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
\end{equation}

where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.

For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:

\begin{equation}
    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
\end{equation}
\begin{equation}
    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
\end{equation}

To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:

\begin{equation}
    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
\end{equation}

A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:

\begin{equation}
    a^i = \tanh(a^i_{\text{raw}})
\end{equation}

This bounded action can be scaled to the appropriate range required by the environment. When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:

\begin{equation}
    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
\end{equation}

where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.

Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:

\begin{equation}
    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
\end{equation}

where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.

For discrete action spaces, the entropy is calculated directly from the action probabilities:
\begin{equation}
    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
\end{equation}

For continuous action spaces, the entropy of the base Gaussian distribution is used:
\begin{equation}
    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
\end{equation}

When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.

\subsection{Value Network Architecture}

The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization. POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.

The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$. Each value network follows an MLP architecture with three hidden layers:

\begin{equation}
    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
\end{equation}
\begin{equation}
    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
\end{equation}
\begin{equation}
    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
\end{equation}

Each hidden layer contains 256 units. The network outputs a scalar value estimate:

\begin{equation}
    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
\end{equation}

where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:

\begin{equation}
    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
\end{equation}
\begin{equation}
    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
\end{equation}

where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:

\begin{equation}
    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
\end{equation}

with $\tau_{q} = 0.005$ in our implementation. The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks. The soft value function incorporates policy entropy:

\begin{equation}
    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
\end{equation}

POLARIS can operate in both discounted and average reward modes. In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor. In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.

The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.

\section{Elastic Weight Consolidation}

POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments. EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.

The EWC loss is defined as:

\begin{equation}
    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
\end{equation}

where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task. The Fisher information matrix is calculated by:

\begin{equation}
    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
\end{equation}

In practice, POLARIS approximates this using samples from the replay buffer. The implementation offers both standard EWC and online EWC variants. The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:

\begin{equation}
    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
\end{equation}

where $\gamma$ is a decay factor typically set to 0.95. EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.

In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy. This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.

\section{Implementation Details}

POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments. Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods. This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns. Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.

Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions. This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence. The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.

For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards. These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities. These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.

Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures. By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns. Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.

The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC. These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework. By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.

\chapter{Social Learning Implementation}

This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework. We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations. The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios. Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models. Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.

\section{Lévy Process Discretization}
\label{appendix:levy_discretization}

This appendix provides a comprehensive mathematical treatment of the discretization of Lévy processes for implementing strategic experimentation models within our Partially Observable Active Markov Game framework. We establish rigorous theoretical foundations for the numerical approximation schemes used in our implementation and analyze their convergence properties and preservation of strategic incentives.

\subsection{Mathematical Foundations of Lévy Processes}
\label{appendix:levy_foundations}

Lévy processes form a fundamental class of stochastic processes that include Brownian motion and Poisson processes as special cases. They are characterized by stationary and independent increments, serving as the natural continuous-time generalization of random walks.

\begin{definition}[Lévy Process]
    A stochastic process $X = \{X_t : t \geq 0\}$ on $\mathbb{R}^d$ with $X_0 = 0$ almost surely is a Lévy process if:
    \begin{enumerate}
        \item It has independent increments: for any $0 \leq t_1 < t_2 < \cdots < t_n < \infty$, the random variables $X_{t_2} - X_{t_1}, X_{t_3} - X_{t_2}, \ldots, X_{t_n} - X_{t_{n-1}}$ are mutually independent.
        \item It has stationary increments: for any $s < t$, the distribution of $X_t - X_s$ depends only on $t-s$.
        \item It is stochastically continuous: for any $t \geq 0$ and $\varepsilon > 0$, $\lim_{h \to 0} \mathbb{P}(|X_{t+h} - X_t| > \varepsilon) = 0$.
    \end{enumerate}
\end{definition}

The celebrated Lévy-Khintchine formula provides a complete characterization of Lévy processes through their characteristic functions:

\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
    If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
    \begin{equation}
        \mathbb{E}[e^{i\theta X_t}] = e^{t\psi(\theta)}
    \end{equation}
    where
    \begin{equation}
        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
    \end{equation}
    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
\end{theorem}

The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process. Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.

\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
    Any Lévy process $X_t$ can be decomposed as:
    \begin{equation}
        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
    \end{equation}
    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
\end{theorem}

The Lévy-Itô decomposition provides a pathwise representation of a Lévy process as the sum of a drift term, a Brownian motion, and potentially infinitely many jumps, both small and large.

\subsection{Time Discretization of Lévy Processes}
\label{appendix:levy_discretization_methods}

To implement continuous-time Lévy processes within discrete computational frameworks, we must employ appropriate numerical approximation schemes. For our strategic experimentation model, we adopt the Euler-Maruyama scheme, extended to accommodate the jump components of general Lévy processes.

\begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
    \begin{equation}
        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
    \end{equation}
    where $Z_n \sim \mathcal{N}(0,1)$ are independent standard normal random variables and $\Delta J_n$ represents the jump increment over $[t_n, t_{n+1}]$.
\end{definition}
\iffalse
    For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.

    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
        The jump component $\Delta J_n$ can be approximated through one of the following approaches:
        \begin{enumerate}
            \item For finite-activity processes (where $\nu(\mathbb{R}) < \infty$):
                  \begin{equation}
                      \Delta J_n = \sum_{i=1}^{K_n} J_i
                  \end{equation}
                  where $K_n \sim \text{Poisson}(\nu(\mathbb{R})\Delta t)$ and $J_i$ are i.i.d. random variables with distribution $\frac{\nu(dx)}{\nu(\mathbb{R})}$.

            \item For infinite-activity processes, a truncation approach:
                  \begin{equation}
                      \Delta J_n = \sum_{i=1}^{K^{\varepsilon}_n} J^{\varepsilon}_i + c_{\varepsilon}\Delta t
                  \end{equation}
                  where $K^{\varepsilon}_n \sim \text{Poisson}(\nu(\{x: |x| > \varepsilon\})\Delta t)$, $J^{\varepsilon}_i$ are i.i.d. with distribution $\frac{\nu(dx)\mathbf{1}_{|x|>\varepsilon}}{\nu(\{x: |x| > \varepsilon\})}$, and $c_{\varepsilon} = \int_{|x|\leq\varepsilon} x\nu(dx)$.
        \end{enumerate}
    \end{proposition}
\fi
\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
    \label{thm:euler_maruyama_convergence}
    Let $X_t$ be a Lévy process and $\hat{X}_t$ be its Euler-Maruyama approximation with time step $\Delta t$. Then for any fixed $T > 0$:
    \begin{enumerate}
        \item (Weak Convergence) For any smooth function $f$ with polynomial growth:
              \begin{equation}
                  |\mathbb{E}[f(X_T)] - \mathbb{E}[f(\hat{X}_T)]| \leq C\Delta t
              \end{equation}

        \item (Strong Convergence) If $\int_{|x|>1} |x|^2 \nu(dx) < \infty$, then:
              \begin{equation}
                  \mathbb{E}[\sup_{0\leq t\leq T} |X_t - \hat{X}_t|^2] \leq C\Delta t
              \end{equation}
    \end{enumerate}
    where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.

\end{theorem}

The weak and strong convergence properties ensure that our numerical scheme accurately approximates both the distributional properties and pathwise behavior of the continuous-time process as the time step decreases.

\subsection{Implementing Strategic Experimentation Models}
\label{appendix:strategic_experimentation_implementation}

In our implementation of the strategic experimentation model from \citet{keller2020undiscounted}, we must discretize both the background signal process $B_t$ and the individual payoff processes $X^i_t$, while preserving the strategic incentives that drive experimentation decisions.

\subsubsection{Discretization of Diffusion-Poisson Processes}
\label{appendix:discretization_diffusion_poisson}

In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:

\begin{align}
    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
\end{align}

where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes. Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:

\begin{align}
    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
\end{align}

For implementation, we denote these increments as:

\begin{align}
    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
\end{align}

where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.

\subsubsection{Reward Function Equivalence}
\label{appendix:reward_equivalence}

A critical challenge in our implementation is reconciling the time-dependent nature of continuous-time rewards with the time-independent reward structure required by the POAMG framework. In the original continuous-time model, agents' instantaneous rewards are:

\begin{equation}
    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
\end{equation}

where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$. To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time. We achieve this through a normalization approach:

\begin{equation}
    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
\end{equation}

This transformation preserves the incentive structure of the original model while eliminating explicit time dependence. The following proposition establishes this equivalence formally:

\begin{proposition}[Reward Equivalence]
    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
    \begin{equation}
        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
    \end{equation}
    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
\end{proposition}

\begin{proof}
    The expected value of the discrete-time reward function is:
    \begin{align}
        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
    \end{align}

    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:

    \begin{align}
        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
    \end{align}

    This exactly matches the expected instantaneous flow payoff in the continuous-time model.
\end{proof}

\iffalse
    \subsubsection{Preservation of Strategic Incentives}
    \label{appendix:strategic_incentives}

    Beyond matching expected rewards, we must ensure that our discretization preserves the strategic incentives that drive experimentation decisions. The key strategic consideration in the model is the trade-off between exploitation (choosing the safe arm) and exploration (choosing the risky arm to learn about its quality).

    \begin{proposition}[Preservation of Strategic Incentives]
        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.

    \end{proposition}

    \begin{proof}
        In the strategic experimentation model, the incentive to experiment at a given belief $b$ about the state is characterized by:
        \begin{equation}
            I(b) = \frac{f(b) - s}{s - m(b)}
        \end{equation}
        when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad. In our discrete-time approximation, the corresponding incentive is:
        \begin{equation}
            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)}
        \end{equation}
        where $\hat{f}(b)$ and $\hat{m}(b)$ are the discrete-time analogs.

        Let us elaborate on why $\hat{f}(b) \to f(b)$ and $\hat{m}(b) \to m(b)$ as $\Delta t \to 0$. In the continuous-time model, the expected flow payoff of the risky arm at belief $b$ is:
        \begin{equation}
            f(b) = b f_1 + (1-b) f_0
        \end{equation}
        where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$. In our discrete-time approximation, we have:
        \begin{equation}
            \hat{f}(b) = b \hat{f}_1 + (1-b) \hat{f}_0
        \end{equation}
        where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
        From our reward equivalence result, we know that:
        \begin{align}
            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
        \end{align}

        The Brownian motion term has $\mathbb{E}[\sigma(W^i_t - W^i_{t-1})] = 0$ and $\text{Var}[\sigma(W^i_t - W^i_{t-1})] = \sigma^2 \Delta t$. By the martingale property of Brownian motion, this term contributes zero to the expected value but introduces variance of order $O(\Delta t)$. Thus:
        \begin{equation}
            \hat{f}_1 = \alpha_1 + \lambda_1\mu_1 + O(\Delta t) \to f_1 \text{ as } \Delta t \to 0
        \end{equation}

        Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
        Therefore, we can establish that:
        \begin{equation}
            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)} = \frac{b \hat{f}_1 + (1-b) \hat{f}_0 - s}{s - \hat{f}_0} = \frac{b(\hat{f}_1 - \hat{f}_0) + \hat{f}_0 - s}{s - \hat{f}_0}
        \end{equation}

        As $\Delta t \to 0$, we have $\hat{f}_1 \to f_1$, $\hat{f}_0 \to f_0$, and consequently:
        \begin{equation}
            \hat{I}(b) \to \frac{b(f_1 - f_0) + f_0 - s}{s - f_0} = \frac{b f_1 + (1-b) f_0 - s}{s - f_0} = \frac{f(b) - s}{s - m(b)} = I(b)
        \end{equation}

        The convergence of incentives directly implies convergence of optimal policies. In the continuous-time model, the symmetric Markov perfect equilibrium characterized in \citet{keller2020undiscounted} has the form:
        \begin{equation}
            \kappa^*(b) =
            \begin{cases}
                0                    & \text{if } I(b) \leq k_0,            \\
                \frac{I(b)-k_0}{N-1} & \text{if } k_0 < I(b) < k_0 + N - 1, \\
                1                    & \text{if } I(b) \geq k_0 + N - 1.
            \end{cases}
        \end{equation}
        where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players. The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.

        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
    \end{proof}

\fi
\subsection{Relation to Policy-Invariant Reward Transformations}
\label{appendix:policy_invariance}

Our approach to time-independent reward formulation can be viewed through the lens of policy-invariant reward transformations, as developed in the reinforcement learning literature by \citet{ng1999policy}.

\begin{definition}[Potential-Based Reward Shaping]
    A reward transformation $\tilde{R}(s, a, s') = R(s, a, s') + F(s, s')$ is potential-based if there exists a potential function $\Phi: S \to \mathbb{R}$ such that $F(s, s') = \gamma\Phi(s') - \Phi(s)$ for all $s, s' \in S$, where $\gamma$ is a discount factor.
\end{definition}

\begin{theorem}[Ng-Harada-Russell \citep{ng1999policy}]
    If a reward transformation is potential-based, then the optimal policy under the transformed reward function is also optimal under the original reward function, and vice versa.
\end{theorem}

While our transformation does not directly fit the potential-based formulation (since we're normalizing by $\Delta t$ rather than adding a potential difference), it shares the crucial property of preserving optimal policies. The following result establishes this connection:

\begin{proposition}[Connection to Policy-Invariant Transformations]
    The transformation from time-dependent rewards in the continuous-time model to time-independent rewards in the POAMG framework preserves policy optimality in the limit as $\Delta t \to 0$.
\end{proposition}

\begin{proof}
    The original cumulative reward over a time interval $[0, T]$ is:
    \begin{equation}
        \int_0^T [(1-a^i_t)s + a^i_t\alpha_s] dt + \int_0^T a^i_t \sigma dW^i_t + \int_0^T a^i_t dC^i_t
    \end{equation}

    The discretized cumulative reward is:
    \begin{equation}
        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
    \end{equation}
    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.

    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral. Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
\end{proof}

\section{Observed Reward Function}
\label{appendix:observed_reward_derivation} In our reinforcement learning
implementation, agents need to learn from observed rewards that reflect the optimality
of their actions with respect to the true state of the world. However, since agents
do not directly observe the true state $\omega$, we need to construct a reward
function based on their observations $o$ that preserves the expected reward
structure. This appendix provides a detailed derivation of the observation-based
reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
state. We need to construct an observation-based reward function $v(o, a): \Omega
    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
\begin{equation}
    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
    a \in A.
\end{equation}

In other words, the expected value of the observation-based reward $v(o, a)$
over all possible observations $o$ given the state $s$ should equal the true
reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
    m$ matrix representing the observation distributions, where $m = |S|$ and assume
the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
the probability of observing observation $o$ in state $s$:
\begin{equation}
    \bm{\mu}=
    \begin{bmatrix}
        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
        \vdots           & \vdots           & \ddots & \vdots           \\
        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
    \end{bmatrix}
\end{equation}

We assume that observation distributions are linearly independent across states,
which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
more likely to generate its corresponding observation than any other observation.
For each action $a \in A$, we define a utility vector
$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
\begin{equation}
    \bm{u}_{a} =
    \begin{bmatrix}
        u(s^{1}, a) \\
        u(s^{2}, a) \\
        \vdots      \\
        u(s^{m}, a)
    \end{bmatrix}
\end{equation}

Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
    ^{k}$ for action $a$:
\begin{equation}
    \bm{v}_{a} =
    \begin{bmatrix}
        v(s^{1}, a) \\
        v(s^{2}, a) \\
        \vdots      \\
        v(s^{m}, a)
    \end{bmatrix}
\end{equation}

The condition that expected observation-based rewards match true rewards can be written
as a linear system:
\begin{equation}
    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
\end{equation}

where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
is:
\begin{equation}
    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
\end{equation}

This gives us the vector of observation-based rewards that satisfy our expected
reward condition. For each observation $o_{j}$ and action $a$, the observation-based
reward is:
\begin{equation}
    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
\end{equation}

where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
$\bm{\mu}^{-1}$.
\paragraph{Binary Case Example}
For the special case with two states of the world ($m = 2$) and symmetric
observations with accuracy $q > 0.5$, the observation distribution matrix is:
\begin{equation}
    \bm{\mu}=
    \begin{bmatrix}
        q   & 1-q \\
        1-q & q
    \end{bmatrix}
\end{equation}

This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
The inverse of this matrix is:
\begin{equation}
    \bm{\mu}^{-1}= \frac{1}{2q-1}
    \begin{bmatrix}
        q      & -(1-q) \\
        -(1-q) & q
    \end{bmatrix}
\end{equation}

In our implementation, we set the true reward as the indicator function for taking
the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
is:
\begin{equation}
    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
    \begin{bmatrix}
        q \\
        -(1-q)
    \end{bmatrix}
\end{equation}

This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
observation-based reward vector is:
\begin{equation}
    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
    \begin{bmatrix}
        -(1-q) \\
        q
    \end{bmatrix}
\end{equation}

Combining these results, we can express the observation-based reward function for
any action-observation pair $(a, o)$ as:
\begin{equation}
    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
\end{equation}

where $\varphi$ maps observations to their corresponding actions. The derived
observation-based reward function has an intuitive interpretation. When an agent
takes an action matching its observation ($a = o$), it receives a positive
reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
informative), the reward for matching observation and action approaches 1, and the
penalty for mismatching approaches 0, meaning that the observed reward function
converges to the true reward function. This reward structure incentivizes agents
to match their actions to their observations when signals are reliable, but also
allows them to learn to override their immediate observations when the actions
of other agents provide stronger evidence about the true state through beliefs.

### 2025-05-26 paper/background.tex
Update brandl results.

This section reviews key literature across economic social learning and multi-agent reinforcement learning (MARL), highlighting how our approach bridges these fields to address their respective limitations.

\section{Social Learning}
The economic study of social learning originated with \citet{banerjee1992simple} and \citet{bikhchandani1992theory}, who formalized how rational agents might ignore private information to follow predecessors' actions, leading to information cascades and potentially inefficient herding. While foundational, these models rely on one-shot sequential decisions rather than the repeated interactions that characterize many real-world learning contexts. \citet{smith2000pathological} extended this work by showing how heterogeneous preferences can lead to confounded learning, where private signals remain relevant despite observing others' actions.

Social learning in network settings expands this framework by examining how network structure influences information flow \citep{acemoglu2011bayesian, golub2010naive}. Two principal approaches have emerged: Bayesian models where agents perform rational inference \citep{rosenberg2009informational, gale2003bayesian,mossel2015strategic}, and non-Bayesian models \citep{golub2010naive, demarzo2003persuasion} like the DeGroot framework \citep{degroot1974reaching} where agents update beliefs through weighted averaging of neighbors' opinions. A critical insight from this literature is that network topology significantly affects learning outcomes. However, most network models still fall short in capturing how agents strategically adapt to others' evolving learning behaviors over time—a key element of our framework. subsectionWhile early models focused on one-shot decisions, more recent work has explored repeated interactions where agents continuously adapt strategies based on observations. These settings more closely align with our MARL approach and will be the focus of our implementation.

\subsection{Strategic Experimentation}

The strategic experimentation literature examines settings where agents balance exploiting current knowledge against generating new information through exploration \citep{bolton1999strategic, keller2005strategic}. This creates a dynamic tension between individual incentives to free-ride on others' information production and collective benefits from experimentation. Strategic experimentation represents a fundamental departure from classical social learning models by explicitly accounting for the intertemporal nature of information acquisition. Unlike cascade models where agents make one-shot decisions in sequence, agents in strategic experimentation scenarios face repeated opportunities to learn and adapt their strategies over time. This dynamic perspective connects directly to the reinforcement learning paradigm, where exploration-exploitation tradeoffs are central \citep{sutton2018reinforcement}. These tradeoffs create the necessary tension for social influence, even in the absence of informational asymmetry among agents that is often central to social learning models \citep{gale2003bayesian}.

The economic foundations of strategic experimentation were established by \citet{rothschild1974two}, who analyzed how a monopolist might experiment with different prices to learn about demand. This concept was extended to multi-agent settings by \citet{bolton1999strategic}, who developed a framework for analyzing experimentation in teams. Their seminal work revealed that when information is a public good, free-riding incentives can significantly reduce aggregate experimentation below socially optimal levels, creating a classic collective action problem.

Several extensions have explored how different information structures affect experimentation incentives. \citet{keller2005strategic} introduced exponential bandits, where lump-sum rewards arrive according to a Poisson process, demonstrating how the resolution of uncertainty affects the dynamics of experimentation. Their model showed that "encouragement effects" can arise, where agents experiment more intensively to motivate others to join the exploration effort. \citet{klein2011negatively} demonstrated how negatively correlated bandits—where success on one experiment decreases the estimated value of others—can encourage more efficient experimentation patterns. 
\iffalse
\citet{bonatti2017dynamic} further showed how competition in experimentation can sometimes overcome free-riding tendencies and increase information production through strategic preemption.\fi

\citet{keller2020undiscounted} developed a particularly relevant model using average reward criteria rather than discounted objectives. Under this framework, the value of information doesn't decay over time, incentivizing different patterns of exploration. This approach aligns with our POAMG framework's emphasis on long-term strategic adaptation in multi-agent systems. \citet{heidhues2015strategic} further demonstrated how private observations can restore experimentation incentives that fail under public observations, providing insights into how information asymmetry affects collective learning dynamics.

The strategic teaching phenomenon, where agents take seemingly suboptimal actions to influence others' beliefs, emerges naturally in these contexts. \citet{yamamoto2019stochastic} demonstrated how sophisticated agents might deliberately punish or reward others via continuation payoffs due to invariance property of the payoff sets. Similarly, \citet{halac2017designing} showed how optimal incentive structures might intentionally incentivize agents to experiment, highlighting the importance of mechanism design in collective learning environments.

The literature on information design \citep{kamenica2011bayesian, bergemann2019information} provides complementary insights by examining how information revelation mechanisms affect experimentation decisions. \citet{che2018optimal} showed how over-revealing information can sometimes incentivize more experimentation than full transparency. These insights connect directly to the strategic influence aspects of our POAMG framework, which explicitly models how agents reason about and deliberately influence others' learning trajectories.

\subsubsection{Formal Model}
More formally, we can describe the strategic experimentation literature through the model developed by \citet{keller2020undiscounted}. In this framework, $n$ agents face a two-armed bandit problem where they continuously allocate resources between a safe arm with known deterministic payoff $r_\textit{safe} > 0$ and a risky arm whose expected payoff depends on an unknown state $\omega \in \{0,1,\ldots,m\}$ with $m \geq 1$. The state is drawn at the beginning according to a publicly known prior distribution with full support. The risky arm generates payoffs according to a Lévy process:
\begin{equation*}
    X^i_t = \alpha_{\omega} t + \sigma Z^i_t + Y^i_t
\end{equation*}
where $Z^i$ is a standard Wiener process, $Y^i$ is a compound Poisson process with Lévy measure $\nu_{\omega}$, and $\alpha_{\omega}$ is the drift rate in state $\omega$. The expected payoff per unit of time is $r_{\omega} = \alpha_{\omega} + \lambda_{\omega} h_{\omega}$, where $\lambda_{\omega}$ is the expected number of jumps per unit of time and $h_{\omega}$ is the expected jump size.

At each moment, agent $i$ allocates fraction $a^i_{t} \in [0,1]$ to the risky arm, yielding instantaneous expected payoff:
\begin{equation*}
    (1-a^i_{t})r_\textit{safe} + a^i_{t}r_{\omega}
\end{equation*}

Each agent observes their own payoff process, the payoff processes of all other agents, and potentially a background information process $B_t$, which provides free information about the state. This background process follows the same structure as the payoff processes:
\begin{equation*}
    B_t = \beta_{\omega} t + \sigma_B Z^B_t + Y^B_t
\end{equation*}
whose informativeness is given exogenously as $k_0$ which increases linearly in time. Under the strong long-run average criterion, agents maximize:
\begin{equation}
    \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\int_0^{T}\{(1-a^i_{t})r_\textit{safe} + a^i_{t}r_{\omega}\}dt\right]
\end{equation}

The unique symmetric Markov perfect equilibrium strategy is characterized as:

\begin{equation}
    a^*(b) = 
    \begin{cases}
    0 & \text{if } I(b) \leq k_0, \\
    \frac{I(b)-k_0}{n-1} & \text{if } k_0 < I(b) < k_0 + n - 1, \\
    1 & \text{if } I(b) \geq k_0 + n - 1.
    \end{cases}
    \end{equation}

where $I(b)$ corresponds to the incentive to experiment, defined as:
\begin{equation*}
    I(b) = \frac{f(b) - r_\textit{safe}}{r_\textit{safe} - m(b)}
\end{equation*}
when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff under full information and $m(b)$ is the expected flow payoff from the risky arm.

This formulation directly captures the tension between exploitation (choosing the currently optimal action) and exploration (generating information for future decisions), as well as the free-rider problem that arises when information is a public good. While strategic experimentation models capture important elements of learning dynamics, they typically assume perfectly rational agents and often rely on standardized information structures.

\subsection{Learning Without Experimentation}

A complementary strand of research examines settings where agents learn without directly observing rewards. \citet{huang2024learning} studied how long-lived agents learn in networks through repeated interactions, revealing a fundamental inefficiency: regardless of network size, learning speed remains bounded by a constant dependent only on private signal distributions. \citet{brandl2024} extended these results by showing that this limitation doesn't apply uniformly to all agents, constructing scenarios where some agents learn faster at others' expense.

Unlike strategic experimentation models where agents receive direct payoff feedback, learning without experimentation captures scenarios where agents must form beliefs based primarily on others' observed actions. This distinction is crucial for modeling many real-world social learning contexts, from financial markets \citep{avery1998multidimensional} to technology adoption \citep{ellison1993rules}, where payoffs are delayed, noisy, or unobservable.

The theoretical foundations for this approach draw from both Bayesian and non-Bayesian learning traditions. \citet{gale2003bayesian} and \citet{smith2000pathological} developed early models showing how rational agents might become trapped in information cascades when learning from others' actions. \citet{acemoglu2011bayesian} extended this analysis to network settings, demonstrating how network topology influences the aggregation of dispersed information.

A substantial literature has explored learning rates in networked environments. \cite{bala1998learning} show neighborhood structure influences optimal action adoption, while \cite{golub2012homophily} demonstrate that homophily slows consensus convergence without being affected by network density. \cite{Harel2014TheSO} quantify information loss when observing others' discrete actions, finding only a fraction of private information transmits, approaching zero in large societies due to "groupthink." \cite{Jadbabaie2013InformationHA} characterize learning rates through agents' signal structures and eigenvector centralities, showing optimal information allocation depends on its distribution—better information should be placed at central nodes when information structures are comparable, but at peripheral nodes when agents possess unique critical information.

The mechanisms behind these learning barriers stem from information loss in the action quantization process. When continuous beliefs are compressed into discrete actions, information is inherently lost \citep{smith2000pathological}. \citet{guarino2013social} characterized this as 'coarse inference' where agents make inferences based only on the aggregate distribution of actions across states rather than on the fine details of how actions depend on specific histories, leading to a loss of information.

\iffalse
Recent work has examined how behavioral factors and network structure interact to shape learning outcomes. \citet{molavi2018theory} developed models of "rational inattention" where agents optimally allocate limited cognitive resources to process social information. \citet{dasaratha2020learning} showed how certain network structures can amplify or mitigate the effects of confirmation bias and other cognitive distortions. \citet{jadbabaie2012non} proposed hybrid learning models that combine Bayesian updating with naive opinion averaging, better matching empirical patterns of social influence.
\fi

Strategic considerations emerge naturally in these settings as agents realize their actions influence the future learning of others. \citet{bhattacharya2013strategic} demonstrated how forward-looking agents might distort their actions to manipulate the information revealed to others. \citet{ARIELI2019185} showed how agents with private information might strategically time their actions to maximize influence on others' beliefs. These strategic dynamics align closely with the active influence mechanisms in our POAMG framework.

\subsubsection{Formal Model}
Similar to before, we characterize the learning dynamics in settings without experimentation through the model introduced by \citet{brandl2024}. In this framework, a set of $N= \{1, \ldots, n\}$ agents interact over discrete time periods $t \in \{1, 2, \ldots\}$ in a fixed social network. The state of the world $\omega$ is drawn from a finite set $S$ according to a prior distribution with full support and remains fixed throughout.

At each period $t$, each agent $i$ receives a private signal $o^i_t$ from a set $O$, drawn according to a state-dependent public known distribution. Signals are independent across agents and time periods. Each agent then chooses an action $a^i_t$ from a set $A$, observing the actions taken by neighbors $N^i \subset N$ in previous periods.

All agents share the same utility function $u: S \times A \rightarrow \mathbb{R}$, which depends on the state and their own action. For each state $s$, there is a unique optimal action $a_{s} = \arg\max_{a \in A} u(s, a)$, and no action is optimal in two different states. Crucially, agents do not observe their realized utilities, eliminating experimentation motives. Agent $i$'s information set at period $\tau$ consists of:
\begin{equation*}
    I^i_{\leq \tau} = (o^i_1, \ldots, o^i_{\tau}; (a^j_t)_{j \in N^i, t < \tau})
\end{equation*}

A (pure) strategy for agent $i$ is a function $\sigma^i$ that maps information sets to actions:
\begin{equation*}
    \sigma^i: \cup_{t=1}^{\infty} (O^t \times A^{N^i \times (t-1)}) \rightarrow A
\end{equation*}

For any given strategy profile $\boldsymbol{\sigma} = (\sigma^1, \ldots, \sigma^n)$, the learning rate of agent $i$ is defined as:
\begin{equation*}
    r^i(\boldsymbol{\sigma}) = \lim\inf_{t\rightarrow\infty} -\frac{1}{t}\log \mathbb{P}(a^i_t \neq a_{\omega} | \boldsymbol{\sigma})
\end{equation*}

The main theoretical results establish both limitations and opportunities in social learning networks. First, the social learning barrier theorem demonstrates that regardless of network structure or strategies, some agent's learning rate is bounded by a constant that depends only on the signal structure:
\begin{equation*}
    \min_{i \in n} r^i(\boldsymbol{\sigma}) \leq r_{bdd} = \min_{\theta \neq \theta'} \left\{D_{KL}(\mu_{\theta} || \mu_{\theta'}) + D_{KL}(\mu_{\theta'} || \mu_{\theta})\right\}
\end{equation*}
where $D_{KL}(\mu_{\theta} || \mu_{\theta'})$ is the Kullback-Leibler divergence between signal distributions and the summation corresponds to the Jeffreys divergence \citet{52862b84-7c34-3186-8b28-6af4806272c3}. This bound applies regardless of the network size or structure. Second, the coordination benefit theorem establishes that for large enough networks and for any $\epsilon > 0$, all agents can learn at rates above a certain bound:
\begin{equation*}
    \min_{i \in n} r^i(\boldsymbol{\sigma}) \geq r_{crd} - \epsilon
\end{equation*}
where $r_{crd} = \min_{\theta \neq \theta'} D_{KL}(\mu_{\theta} || \mu_{\theta'})$ is strictly greater than the autarky learning rate that an agent can achieve alone. This theoretical framework illuminates a fundamental challenge in social learning: information aggregation can fail due to information cascades and herding dynamics, resulting in, as pointed out by the paper, what \citet{harel2021rational} termed "rational groupthink"—where feedback loops cause agents to persist in incorrect beliefs despite continual information arrival. While this model allows agents to learn from various observation structures, it does not impose full rationality on the agents, a strand of literature that we discuss next.

\subsection{Non-Bayesian Learning}

While most economic models assume fully rational agents, partial rationality perspectives acknowledge cognitive limitations that affect learning. Models like \citet{jadbabaie2012non}'s hybrid learning rule (combining Bayesian updating with naive averaging) and level-$k$ reasoning \citep{stahl1994experimental, crawford2007level} provide middle grounds between full rationality and simple heuristics.
\iffalse
Research on information processing constraints, such as bounded memory \citep{monte2014bounded} and rational inattention \citep{sims2003implications}, further illustrates how cognitive limitations shape learning outcomes. Behavioral biases like confirmation bias \citep{rabin1999psychology}, correlation neglect \citep{enke2019correlation}, and naive herding \citep{eyster2010naive} additionally affect how agents process social information. These behavioral factors often exacerbate herding behavior and information cascades, creating a gap between theoretical predictions based on full rationality and observed behavior. Our MARL framework provides a computational approach to modeling partial rationality that captures these behavioral patterns while maintaining analytical tractability.
\fi

Evolutionary Game Theory (EGT) also provides a powerful non-Bayesian framework for modeling multi-agent learning dynamics without assuming full rationality. Instead, EGT examines how strategy distributions evolve through selection processes based on relative performance \citep{weibull1997evolutionary}. This perspective aligns naturally with reinforcement learning's trial-and-error approach. \citet{tuyls2004evolutionary} demostrates several important connections between EGT and MARL among which, they relate multi-agent Q-learning to replicator dynamics. This mathematical equivalence provides theoretical insights into MARL convergence and equilibrium properties, helping explain empirical observations in complex social dilemmas \citep{leibo2017multi}.

Bridging theoretical frameworks and computational implementations, MARL offers a powerful methodology for operationalizing social learning models. MARL provides computational tools that can simulate the intricate dynamics of social learning environments while implementing the strategic adaptations that economic theories recognize as essential but frequently find difficult to compute in complex, realistic scenarios.

\section{Multi-Agent Reinforcement Learning}

While economic models offer valuable theoretical insights, they often struggle with computational tractability when modeling repeated strategic interactions with partially rational agents. This is where MARL provides complementary tools that address specific limitations of economic approaches. MARL frameworks enable the simulation of complex multi-agent systems where agents learn optimal policies through trial-and-error interactions with their environment and other agents. Unlike traditional economic models that often require closed-form solutions, MARL can handle high-dimensional state spaces, complex agent interactions, and non-stationary dynamics that emerge when multiple agents learn simultaneously.

The core components of MARL include state representations, action spaces, reward functions, and learning algorithms that enable agents to maximize expected cumulative rewards. These components can be tailored to model various aspects of social learning, including partial observability (through belief states), strategic adaptation (through policy gradient methods), and partial rationality (through constrained optimization). Modern MARL approaches incorporate techniques such as centralized training with decentralized execution, value decomposition, and multi-agent actor-critic methods to address coordination challenges that arise in multi-agent settings. We direct the interested reader to Appendix \ref{appendix:rl_details} for a detailed introduction of reinforcement learning techniques, including formal definitions, algorithms, and theoretical properties.

Economic models typically assume either fully rational agents (in Bayesian frameworks) or overly simplistic learning rules (in behavioral models). MARL offers a middle ground by modeling agents that learn from experience and adapt over time without requiring full rationality. \citet{ndousse2021emergent} demonstrated that even without explicit programming, reinforcement learning agents can develop sophisticated social learning capabilities that mirror human behavior. This addresses the partial rationality problem by providing computational mechanisms for flexible belief updating based on partial information, learning complex strategies through trial and error, and adapting to non-stationary environments created by other learning agents.

A key limitation of economic social learning models is their difficulty in capturing how agents strategically adapt to others' learning processes. The strategic experimentation literature acknowledges these dynamics but often lacks tractable solutions outside of simplified settings. \citet{jaques2019social} addressed this by introducing Social Influence as a mechanism in MARL, where agents receive additional reward for causally influencing others' actions. This creates a computational framework for modeling strategic teaching and information revelation—key dynamics in the economic models of \citet{bolton1999strategic} and \citet{heidhues2015strategic}.

More directly relevant to our approach, \citet{kim2022influencing} developed Active Markov Games, which explicitly model how agents reason about and influence the policy evolution of other agents. This formalism allows us to capture the strategic adaptation that economic models identify as important but struggle to compute in complex environments.

Despite these advantages, standard MARL approaches have their own limitations when applied to social learning. Most MARL algorithms assume full observability of state information, while social learning inherently involves partial observability of others' private information and beliefs. Many MARL approaches treat non-stationarity as a technical obstacle rather than a strategic feature to be exploited. Additionally, MARL often lacks the theoretical foundations that economic models provide for understanding equilibrium behavior.

Our POAMG framework extends Active Markov Games to partially observable settings specifically to address these limitations. By incorporating policy evolution as an integral part of the environment dynamics while accounting for partial observability, we provide a computational approach that preserves the strategic sophistication of economic models.

\section{Bridging Economic Theory and MARL}

While economic social learning and MARL have developed largely in parallel, their complementary strengths suggest significant potential for integration. Economic models provide rigorous theoretical foundations for understanding rational behavior, belief formation, and information aggregation in social contexts. However, these models often face computational limitations when addressing complex strategic interactions, especially when agents have heterogeneous beliefs, partial rationality, or operate in environments with partial observability.

Conversely, MARL offers computational frameworks for modeling adaptive agents in complex, high-dimensional environments. These approaches excel at simulating emergent behaviors and can operate effectively without imposing full rationality assumptions. However, MARL approaches frequently lack the theoretical grounding to interpret equilibrium properties and sometimes overlook the strategic sophistication captured in economic models.

Our research bridges these fields by developing a partially observable active Markov game (POAMG) framework that preserves the strategic considerations central to economic theory while leveraging the computational scalability of MARL. This integration addresses three key challenges:

First, we explicitly incorporate policy evolution dynamics and strategic adaptation as fundamental features rather than technical obstacles. Unlike standard MARL approaches that treat non-stationarity as a problem to overcome, our framework models how sophisticated agents reason about and deliberately influence others' learning trajectories \citep{kim2022influencing}, similar to the strategic teaching phenomena identified in economic experimentation literature \citep{yamamoto2019stochastic}.

Second, we incorporate partial observability as an intrinsic characteristic of social learning environments. By modeling belief states and observation functions, our approach captures the information asymmetries and strategic uncertainty that economic models identify as crucial determinants of learning outcomes \citep{heidhues2015strategic, rosenberg2009informational}.

Third, we account for long-horizon strategic planning where agents optimize not just immediate rewards but also their influence on the future learning dynamics of other agents. This aligns with economic perspectives on forward-looking behavior while remaining computationally tractable through reinforcement learning techniques.

The resulting framework enables more realistic modeling of social learning phenomena that resist analysis under either purely economic or purely computational approaches. It combines economic insights on strategic sophistication with MARL's ability to simulate complex adaptive systems, yielding both theoretical insights and practical algorithms for understanding multi-agent learning in partially observable environments.

### 2025-05-26 paper/conclusion.tex
Update brandl results.

This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm. Our framework addresses fundamental challenges in modeling strategic adaptation under partial observability, where agents must simultaneously learn about their environment and strategically influence others' learning processes.

Our theoretical contributions establish POAMGs as a rigorous mathematical framework extending Active Markov Games to partially observable settings. The convergence analysis and policy gradient theorems provide solid foundations for the POLARIS algorithm, which successfully implements this framework through an integrated architecture combining belief processing, inference learning, and reinforcement learning modules.

Experimental validation across strategic experimentation and learning without experimentation scenarios demonstrates our framework's effectiveness. POLARIS agents converge to theoretically predicted equilibrium strategies, validating key insights about free-riding behavior and optimal experimentation intensity. Our results confirm the existence of social learning barriers while revealing coordination benefits in larger networks. Crucially, we uncover a dynamic division of labor where agents assume roles as information generators or exploiters based on signal quality rather than network position.

Future research could extend the framework to incorporate heterogeneous agent types, dynamic network structures, or mechanism design principles. Applications to contemporary challenges such as misinformation spread or algorithmic recommendation systems could demonstrate broader relevance.

This work demonstrates that integrating economic theory and computational methods yields insights neither approach could achieve alone. The POAMG framework and POLARIS algorithm provide both theoretical understanding and practical tools for analyzing complex social learning processes, establishing a foundation for future interdisciplinary research. As multi-agent systems become increasingly prevalent, such integrated approaches will be essential for understanding and shaping collective intelligence emerging from strategic interactions among learning agents.

### 2025-05-26 paper/figures/poamg-structure.tex
Update brandl results.

% POAMG Structure Figure
% Compile this file with pdflatex --shell-escape poamg-structure.tex
\documentclass{standalone}
\usepackage{tikz}
\usepackage{amsmath} % For \boldsymbol
\usetikzlibrary{arrows.meta, positioning, shapes, calc, backgrounds, shadows.blur, fit}
\begin{document}
\begin{tikzpicture}[
  agent/.style={draw, rounded corners, fill=blue!10, minimum width=3.2cm, minimum height=2.6cm, font=\LARGE, blur shadow},
  env/.style={draw, rounded corners, fill=green!15, minimum width=3.2cm, minimum height=1.6cm, font=\LARGE, blur shadow},
  obs/.style={draw, fill=yellow!30, ellipse, minimum width=1.6cm, minimum height=1.0cm, font=\large, thick},
  belief/.style={draw, fill=orange!30, ellipse, minimum width=1.6cm, minimum height=1.0cm, font=\large, thick},
  param/.style={draw, fill=red!20, ellipse, minimum width=1.6cm, minimum height=1.0cm, font=\large, thick},
  action/.style={draw, fill=cyan!20, ellipse, minimum width=1.6cm, minimum height=1.0cm, font=\large, thick},
  reward/.style={draw, fill=lime!30, ellipse, minimum width=1.6cm, minimum height=1.0cm, font=\large, thick},
  groupbox/.style={fill=gray!10, rounded corners, draw=gray!40, thick, inner sep=0.3cm},
  legendbox/.style={fill=white, draw=black, rounded corners, thick, inner sep=0.2cm},
  every node/.style={font=\large}
]
% Environment state
\node[env] (env) at (0,0) {\textbf{Environment}\\$s_t$};

% Agents
\node[agent, left=4.0cm of env, yshift=0.5cm] (agent1) {\textbf{Agent 1}};
\node[agent, right=4.0cm of env, yshift=0.5cm] (agent2) {\textbf{Agent 2}};

% Observations
\node[obs, below=0.5cm of agent1] (obs1) {$o^1_t$};
\node[obs, below=0.5cm of agent2] (obs2) {$o^2_t$};

% Beliefs
\node[belief, below=0.6cm of obs1] (belief1) {$b^1_t$};
\node[belief, below=0.6cm of obs2] (belief2) {$b^2_t$};

% Policy params
\node[param, below=0.6cm of belief1] (theta1) {$\theta^1_t$};
\node[param, below=0.6cm of belief2] (theta2) {$\theta^2_t$};

% Actions
\node[action, below=0.6cm of theta1] (action1) {$a^1_t$};
\node[action, below=0.6cm of theta2] (action2) {$a^2_t$};

% Joint action
\node[action, below=2.0cm of env] (jointaction) {$\boldsymbol{a}_t$};

% Next environment state
\node[env, below=2.0cm of jointaction] (envnext) {\textbf{Environment}\\$s_{t+1}$};

% Rewards
\node[reward, right=1.0cm of action1] (reward1) {$r^1_t$};
\node[reward, left=1.0cm of action2] (reward2) {$r^2_t$};

% Arrows: Environment to observations
\draw[->, ultra thick, teal] (env) -- node[above left, xshift=-8pt, yshift=8pt, fill=white, inner sep=1pt] {\textbf{observe}} (obs1);
\draw[->, ultra thick, teal] (env) -- node[above right, xshift=8pt, yshift=8pt, fill=white, inner sep=1pt] {\textbf{observe}} (obs2);

% Observations to beliefs
\draw[->, thick, orange!80!black] (obs1) -- (belief1);
\draw[->, thick, orange!80!black] (obs2) -- (belief2);

% Beliefs to policy params
\draw[->, thick, red!80!black] (belief1) -- (theta1);
\draw[->, thick, red!80!black] (belief2) -- (theta2);

% Policy params to actions
\draw[->, thick, cyan!80!black] (theta1) -- (action1);
\draw[->, thick, cyan!80!black] (theta2) -- (action2);

% Actions to joint action
\draw[->, thick, blue!80!black] (action1) -- (jointaction);
\draw[->, thick, blue!80!black] (action2) -- (jointaction);

% Joint action to environment
\draw[->, ultra thick, green!60!black] (jointaction) .. controls +(0,-1.2) and +(0,1.2) .. node[right, fill=white, inner sep=1pt] {\textbf{transition}} (envnext);

% Environment transition (dashed, for clarity)
\draw[->, ultra thick, dashed, gray!80] (env) .. controls +(0,-1.2) and +(0,1.2) .. (envnext);

% Feedback: Next env to next obs (curved, dotted)
\draw[->, thick, dotted, purple!80!black] (envnext) .. controls +(-2.0,2.0) and +(0,-1.0) .. node[above left, fill=white, inner sep=1pt] {\textbf{next $t$}} (obs1);
\draw[->, thick, dotted, purple!80!black] (envnext) .. controls +(2.0,2.0) and +(0,-1.0) .. node[above right, fill=white, inner sep=1pt] {\textbf{next $t$}} (obs2);

% Background boxes for agents and environment
\begin{pgfonlayer}{background}
  \node[groupbox, fit=(obs1) (belief1) (theta1) (action1) (reward1), label=above:{\textbf{Agent 1}}, yshift=0.5cm, xshift=-0.2cm] (agent1bg) {};
  \node[groupbox, fit=(obs2) (belief2) (theta2) (action2) (reward2), label=above:{\textbf{Agent 2}}, yshift=0.5cm, xshift=0.2cm] (agent2bg) {};
  \node[groupbox, fit=(env) (envnext) (jointaction), label=above:{\textbf{Environment}}, yshift=0.5cm] (envbg) {};
\end{pgfonlayer}

\end{tikzpicture}
\end{document}

### 2025-05-26 paper/full.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
+\documentclass[a4paper,12pt]{report}
+
+%% Language and font encodings
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
+%% Sets page size and margins according to Bonn University guidelines
+\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=2cm]{geometry}
+
+%% Font settings - Times New Roman or similar (as per guidelines)
+\usepackage{times} % Times font
+\usepackage{mathptmx} % Times font with math support
+
+%% Section formatting
+\usepackage{titlesec}
+
+% Traditional academic chapter title style
+\titleformat{\chapter}[display]
+  {\normalfont\Large\bfseries}
+  {}
+  {0pt}
+  {\thispagestyle{empty}%
+   \vspace*{-20pt}%
+   \begin{flushright}
+     % Elegant, academic chapter number
+     \begin{tikzpicture}[remember picture, overlay]
+       \node[text=black!12, font=\fontsize{80}{80}\selectfont] {\thechapter};
+     \end{tikzpicture}
+   \end{flushright}
+   \vspace{-60pt}
+   % Simple, elegant single line
+   \rule{\textwidth}{0.6pt}\\
+   \vspace*{15pt}
+   \raggedright\LARGE\scshape}
+  [\vspace{-0.8cm}]
+\titlespacing*{\chapter}{0pt}{0pt}{40pt}
+
+% Elegant section formatting
+\titleformat{\section}
+  {\normalfont\Large\bfseries\scshape}
+  {}
+  {0pt}
+  {\thesection\quad}
+\titlespacing*{\section}{0pt}{3.5ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+
+% Make subsections italic and elegant
+\titleformat{\subsection}
+  {\normalfont\large\bfseries\itshape}
+  {\thesubsection}
+  {1em}
+  {}
+\titlespacing*{\subsection}{0pt}{3ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+
+%% Line spacing 1.5 as required
+\usepackage{setspace}
+\onehalfspacing
+
+%% Useful packages
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bm}         % For bold symbols
+\usepackage{graphicx}
+\usepackage{float}      % For [H] figure placement
+\usepackage{booktabs}
+\usepackage{tabu}
+\usepackage{enumitem}
+\usepackage[table,dvipsnames]{xcolor}  % Added dvipsnames option for more color choices
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{subfigure}
+\usepackage{amsthm}
+\usepackage{bbm}        % Blackboard math symbols (for indicator function)
+\usepackage[toc]{appendix}
+
+% Choose either algorithm2e OR algorithmicx, not both
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
+
+% For adjusting margins of specific sections
+\usepackage{changepage}
+
+% Bibliography
+\usepackage[natbibapa]{apacite}
+
+% Todo notes
+\usepackage[colorinlistoftodos]{todonotes}
+
+% Page numbering configuration
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\fancyfoot[C]{\thepage}
+\renewcommand{\headrulewidth}{0pt}
+
+% Hyperref should be last
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+
+% Allow floating content to be placed more liberally
+\renewcommand{\floatpagefraction}{.9}
+\renewcommand{\textfraction}{.1}
+\renewcommand{\topfraction}{0.9}
+\renewcommand{\bottomfraction}{.9}
+
+% Appendix formatting
+\makeatletter
+\let\old@chapter\@chapter
+\def\@chapter[#1]#2{\old@chapter[{#1}]{#2}}
+\makeatother
+
+% Math operators
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+% Custom theorem environments
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+\newtheorem{definition}{Definition}
+\newtheorem{assumption}{Assumption}
+\newtheorem{remark}{Remark}
+
+% Define indicator function notation
+\newcommand{\ind}[1]{\mathbbm{1}_{#1}}
+
+\begin{document}
+
+% Cover sheet as per Bonn University guidelines
+\begin{titlepage}
+    \begin{center}
+        \vspace*{2cm}
+
+        {\Large \textbf{Social Learning via Multi Agent Reinforcement Learning}}\\[6cm]
+
+        Master Thesis Presented to the\\
+        Department of Economics at the\\
+        Rheinische Friedrich-Wilhelms-Universität Bonn\\[1cm]
+
+        In Partial Fulfillment of the Requirements for the Degree of\\
+        Master of Science (M.Sc.)\\[4cm]
+
+        Supervisor: Prof. Dr. Florian Brandl\\[2cm]
+
+        Submitted in June, 2025 by:\\
+        Ege Can Doğaroğlu\\
+        Matriculation Number: 3464688
+
+    \end{center}
+\end{titlepage}
+
+% Set page numbering to 'gobble' (no numbers) for front matter
+\pagenumbering{gobble}
+
+% Abstract
+\begin{abstract}
+    \begin{adjustwidth}{2cm}{2cm}
+        This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs)—a novel framework for modeling sophisticated learning dynamics in environments with partial observability.
+Traditional economic models provide valuable theoretical insights but often rely on simplified assumptions about agents' behavior or the learning environment, while reinforcement learning approaches offer computational tools that frequently lack theoretical foundations for strategic adaptation.
+Our framework addresses three fundamental challenges: modeling strategic adaptation in non-stationary environments, incorporating partial observability as an intrinsic feature, and capturing long-term strategic considerations in learning contexts.
+We develop POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm implementing our theoretical framework, and apply it to two canonical social learning scenarios: strategic experimentation with observable rewards and learning without experimentation through action observation.
+Our results validate theoretical predictions about ...
+while demonstrating how reinforcement learning agents can discover sophisticated strategies for information revelation and strategic influence, providing both theoretical insights and computational tools for understanding complex social learning dynamics.
+    \end{adjustwidth}
+\end{abstract}
+
+% Table of contents
+\tableofcontents
+\newpage
+
+% Optional - include if you have abbreviations, tables, or figures to list
+%\listoffigures
+%\listoftables
+%\newpage
+
+% Page numbering starts here with Arabic numerals
+\chapter{Introduction}
+\pagenumbering{arabic}
+\setcounter{page}{1}
+The study of how individuals and groups learn from each other's actions and experiences has been a central focus in economic theory for decades.
+From the seminal contributions on information cascades by \citet{banerjee1992simple} and \citet{bikhchandani1992theory} to more recent explorations of learning in networks \citep{acemoglu2011bayesian, golub2010naive}, economic research has sought to understand how social interactions shape beliefs, decisions, and collective outcomes.
+Traditional economic models have provided valuable insights into phenomena such as herding behavior, where individuals rationally ignore their private information to follow the observed actions of predecessors.
+However, these models often rely on simplified assumptions about agents' behavior and reasoning processes, frequently restricting analysis to one-shot sequential decisions or steady-state equilibria rather than capturing the rich dynamics of repeated interactions where agents continuously adapt their strategies based on others' evolving behaviors.
+
+Meanwhile, the field of multi-agent reinforcement learning (MARL) has experienced remarkable progress in developing algorithms that enable autonomous agents to learn effective strategies in complex, interactive environments.
+Recent advances in reinforcement learning have demonstrated impressive capabilities in strategic games \citep{silver2016mastering}, cooperative problem-solving \citep{baker2020emergentreciprocityteamformation}, and competitive scenarios \citep{openai2019dota2largescale}.
+MARL offers powerful tools for modeling adaptive behavior in non-stationary environments where agents must continuously revise their strategies in response to others' changing behaviors.
+However, much of this work has focused on engineering objectives rather than modeling realistic human learning processes, limiting its applicability to fundamental questions in economic theory.
+Additionally, many MARL approaches struggle with the challenge of partial observability—a defining feature of social learning contexts where agents cannot directly observe others' private information or belief states.
+
+This thesis bridges these domains by introducing a novel framework that integrates economic social learning theory with multi-agent reinforcement learning under partial observability.
+Our approach models social learning as a dynamic process where agents with limited information strategically adapt their behaviors while simultaneously learning about their environment and other agents' strategies.
+By formalizing this process through the lens of partially observable reinforcement learning, we aim to reveal new insights into how strategic adaptation influences collective outcomes and equilibrium behavior.
+This interdisciplinary synthesis addresses fundamental challenges that have constrained previous work in both economics and artificial intelligence, offering a more realistic and computationally tractable approach to modeling complex social learning dynamics.
+
+The first challenge concerns non-stationarity and strategic adaptation.
+Traditional economic models of social learning typically assume that agents follow fixed, myopic decision rules or Bayesian updating procedures that do not fully account for strategic adaptation over time.
+When agents repeatedly interact and observe each other's actions, however, they may adjust their strategies in anticipation of others' learning, creating a complex web of interdependent adaptation that fundamentally alters collective learning dynamics.
+This non-stationarity—where the effective environment an agent faces changes as other agents learn—represents a central challenge that requires new modeling approaches.
+Standard MARL algorithms often treat this non-stationarity as a technical obstacle to convergence rather than an intrinsic feature of multi-agent systems that agents should explicitly reason about and strategically exploit.
+
+The second challenge involves partial observability, which pervades social learning contexts.
+In most real-world settings, agents cannot directly observe others' private information, beliefs, or decision processes.
+Instead, they must infer these hidden states from observable actions and outcomes.
+This partial observability compounds the complexity of strategic interaction, as agents must simultaneously learn about the underlying state of the world and about the belief formation processes of others.
+Economic models have often simplified this challenge through strong assumptions about common knowledge or by focusing on one-shot sequential decisions rather than repeated interactions.
+Similarly, many MARL approaches assume full observability of the state or treat partial observability as a technical challenge to be addressed through belief state tracking, without fully incorporating its strategic implications.
+
+The third challenge concerns long-term strategic considerations in social learning.
+Agents often face a tension between immediate payoffs and long-term information generation.
+They may sometimes choose actions that appear suboptimal in the short term to influence the learning trajectories of others or to generate valuable information for future periods.
+For instance, in strategic experimentation contexts, agents might incur costs to explore unknown options, knowing that the resulting information will benefit both themselves and others in the future.
+Capturing these farsighted strategic considerations requires models that explicitly account for how current actions shape the future evolution of others' beliefs and behaviors—a capability that neither traditional economic models nor standard MARL algorithms fully provide.
+
+To address these challenges, this thesis makes several interconnected contributions.
+First, we develop Partially Observable Active Markov Games (POAMGs)—a novel formalism that extends the Active Markov Game framework introduced by \citet{kim2022influencing} to partially observable settings.
+Unlike standard reinforcement learning frameworks that treat non-stationarity as a challenge to be mitigated, POAMGs incorporate policy evolution as an integral part of the environment dynamics, allowing agents to reason about and strategically influence this evolution process.
+POAMGs explicitly model how agents' policies evolve over time based on observations and interactions, while accounting for the fundamental constraints imposed by partial observability.
+This formalism provides a mathematically rigorous foundation for analyzing complex social learning dynamics that involve repeated interactions, adaptive strategies, and incomplete information.
+
+Second, we provide a thorough theoretical analysis of convergence and equilibrium properties in POAMGs.
+We establish conditions under which the joint process of states, beliefs, and policy parameters converges to a unique stochastically stable distribution, ensuring that our models have well-defined limiting behavior despite the inherent non-stationarity of multi-agent learning.
+We derive policy gradient theorems for average and discounted reward objectives, providing a solid foundation for algorithm development.
+We also extend our framework to continuous-time dynamics through stochastic differential equations, enabling a wider range of applications.
+Our analysis illuminates the relationship between traditional game-theoretic equilibrium concepts and the more general notion of active equilibrium that emerges in our framework, offering new insights into equilibrium selection and stability in social learning contexts.
+
+Third, we introduce POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm for learning in POAMGs.
+POLARIS extends previous algorithms to partially observable settings through an integrated architecture with three core components: a belief processing module that tracks agents' information states using Transformer models; an inference learning module that predicts the policy evolution of other agents through variational methods; and a reinforcement learning module that optimizes policies based on average or discounted reward criteria, supporting both discrete and continuous action spaces.
+This integrated approach enables agents to learn sophisticated strategies that account for both the partial observability of the environment and the learning dynamics of other agents—capabilities that are essential for modeling realistic social learning processes.
+
+Fourth, we apply our framework to two canonical social learning scenarios from economic theory.
+The first application focuses on strategic experimentation, building on the models of \citet{bolton1999strategic} and \citet{keller2020undiscounted}, where agents learn optimal actions through trial and error with observable rewards.
+The second application examines learning without experimentation, extending the frameworks of \citet{huang2024learning} and \citet{brandl2024}, where agents form beliefs primarily by observing others' actions rather than receiving direct feedback from the environment.
+Our analysis demonstrates how our approach can model phenomena such as free-riding on others' information production, strategic teaching, information cascades, and confounded learning under more realistic assumptions about agents' reasoning capabilities and strategic sophistication.
+
+Through these applications, we illustrate how bridging economic theory and MARL can enhance our understanding of social learning processes.
+Our POAMG framework provides a more realistic model of how partially rational agents learn from each other in complex, partially observable environments.
+At the same time, it offers practical algorithms for computing equilibrium strategies that traditional economic approaches might find intractable.
+The POLARIS algorithm demonstrates how techniques from deep reinforcement learning and approximate inference can be adapted to tackle the specific challenges of social learning, offering a computationally feasible method for simulating and analyzing complex multi-agent learning dynamics.
+
+The remainder of this thesis is organized as follows: Chapter 2 reviews the relevant literature on social learning in economic theory and multi-agent reinforcement learning, emphasizing the complementary strengths and limitations of these approaches and identifying opportunities for cross-fertilization.
+Chapter 3 introduces our theoretical framework, developing the formalism of Partially Observable Active Markov Games and deriving key results on convergence, policy gradients, and equilibrium concepts, as well as presenting the POLARIS algorithm, detailing its components, implementation considerations, and theoretical justifications.
+Chapter 4 applies our framework to strategic experimentation and learning without experimentation, demonstrating how POLARIS captures sophisticated social learning dynamics in these contexts.
+Chapter 5 concludes with a discussion of implications, limitations, and directions for future research.
+
+By integrating perspectives from economic theory and multi-agent reinforcement learning, this thesis aims to enhance our understanding of social learning processes and provide new tools for modeling complex strategic interactions in partially observable environments.
+The insights gained may not only advance theoretical knowledge but also inform the design of platforms and institutions that facilitate efficient collective learning and decision-making in diverse contexts, from financial markets and organizational learning to online social networks and collaborative scientific endeavors.
+Moreover, by demonstrating the value of MARL techniques for addressing classical questions in economic theory, we hope to encourage further cross-disciplinary work that leverages complementary insights from these rich intellectual traditions.
+
+In the next chapter, we provide a detailed review of the relevant literature, tracing the development of social learning models in economics and recent advances in multi-agent reinforcement learning.
+This review establishes the conceptual foundation for our theoretical framework and highlights the specific gaps that our approach aims to address, setting the stage for the formal development of Partially Observable Active Markov Games in Chapter 3.
+\chapter{Related Work}
+This section reviews key literature across economic social learning and multi-agent reinforcement learning (MARL), highlighting how our approach bridges these fields to address their respective limitations.
+
+\section{Social Learning}
+The economic study of social learning originated with \citet{banerjee1992simple} and \citet{bikhchandani1992theory}, who formalized how rational agents might ignore private information to follow predecessors' actions, leading to information cascades and potentially inefficient herding.
+While foundational, these models rely on one-shot sequential decisions rather than the repeated interactions that characterize many real-world learning contexts.
+\citet{smith2000pathological} extended this work by showing how heterogeneous preferences can lead to confounded learning, where private signals remain relevant despite observing others' actions.
+
+Social learning in network settings expands this framework by examining how network structure influences information flow \citep{acemoglu2011bayesian, golub2010naive}.
+Two principal approaches have emerged: Bayesian models where agents perform rational inference \citep{rosenberg2009informational, gale2003bayesian,mossel2015strategic}, and non-Bayesian models \citep{golub2010naive, demarzo2003persuasion} like the DeGroot framework \citep{degroot1974reaching} where agents update beliefs through weighted averaging of neighbors' opinions.
+A critical insight from this literature is that network topology significantly affects learning outcomes.
+However, most network models still fall short in capturing how agents strategically adapt to others' evolving learning behaviors over time—a key element of our framework.
+subsectionWhile early models focused on one-shot decisions, more recent work has explored repeated interactions where agents continuously adapt strategies based on observations.
+These settings more closely align with our MARL approach and will be the focus of our implementation.
+
+\subsection{Strategic Experimentation}
+
+The strategic experimentation literature examines settings where agents balance exploiting current knowledge against generating new information through exploration \citep{bolton1999strategic, keller2005strategic}.
+This creates a dynamic tension between individual incentives to free-ride on others' information production and collective benefits from experimentation.
+Strategic experimentation represents a fundamental departure from classical social learning models by explicitly accounting for the intertemporal nature of information acquisition.
+Unlike cascade models where agents make one-shot decisions in sequence, agents in strategic experimentation scenarios face repeated opportunities to learn and adapt their strategies over time.
+This dynamic perspective connects directly to the reinforcement learning paradigm, where exploration-exploitation tradeoffs are central \citep{sutton2018reinforcement}.
+These tradeoffs create the necessary tension for social influence, even in the absence of informational asymmetry among agents that is often central to social learning models \citep{gale2003bayesian}.
+
+The economic foundations of strategic experimentation were established by \citet{rothschild1974two}, who analyzed how a monopolist might experiment with different prices to learn about demand.
+This concept was extended to multi-agent settings by \citet{bolton1999strategic}, who developed a framework for analyzing experimentation in teams.
+Their seminal work revealed that when information is a public good, free-riding incentives can significantly reduce aggregate experimentation below socially optimal levels, creating a classic collective action problem.
+
+Several extensions have explored how different information structures affect experimentation incentives.
+\citet{keller2005strategic} introduced exponential bandits, where lump-sum rewards arrive according to a Poisson process, demonstrating how the resolution of uncertainty affects the dynamics of experimentation.
+Their model showed that "encouragement effects" can arise, where agents experiment more intensively to motivate others to join the exploration effort.
+\citet{klein2011negatively} demonstrated how negatively correlated bandits—where success on one experiment decreases the estimated value of others—can encourage more efficient experimentation patterns.
+\iffalse
+    \citet{bonatti2017dynamic} further showed how competition in experimentation can sometimes overcome free-riding tendencies and increase information production through strategic preemption.\fi
+
+\citet{keller2020undiscounted} developed a particularly relevant model using average reward criteria rather than discounted objectives.
+Under this framework, the value of information doesn't decay over time, incentivizing different patterns of exploration.
+This approach aligns with our POAMG framework's emphasis on long-term strategic adaptation in multi-agent systems.
+\citet{heidhues2015strategic} further demonstrated how private observations can restore experimentation incentives that fail under public observations, providing insights into how information asymmetry affects collective learning dynamics.
+
+The strategic teaching phenomenon, where agents take seemingly suboptimal actions to influence others' beliefs, emerges naturally in these contexts.
+\citet{yamamoto2019stochastic} demonstrated how sophisticated agents might deliberately punish or reward others via continuation payoffs due to invariance property of the payoff sets.
+Similarly, \citet{halac2017designing} showed how optimal incentive structures might intentionally incentivize agents to experiment, highlighting the importance of mechanism design in collective learning environments.
+
+The literature on information design \citep{kamenica2011bayesian, bergemann2019information} provides complementary insights by examining how information revelation mechanisms affect experimentation decisions.
+\citet{che2018optimal} showed how over-revealing information can sometimes incentivize more experimentation than full transparency.
+These insights connect directly to the strategic influence aspects of our POAMG framework, which explicitly models how agents reason about and deliberately influence others' learning trajectories.
+
+\subsubsection{Formal Model}
+More formally, we can describe the strategic experimentation literature through the model developed by \citet{keller2020undiscounted}.
+In this framework, $n$ agents face a two-armed bandit problem where they continuously allocate resources between a safe arm with known deterministic payoff $r_\textit{safe} > 0$ and a risky arm whose expected payoff depends on an unknown state $\omega \in \{0,1,\ldots,m\}$ with $m \geq 1$.
+The state is drawn at the beginning according to a publicly known prior distribution with full support.
+The risky arm generates payoffs according to a Lévy process:
+\begin{equation*}
+    X^i_t = \alpha_{\omega} t + \sigma Z^i_t + Y^i_t
+\end{equation*}
+where $Z^i$ is a standard Wiener process, $Y^i$ is a compound Poisson process with Lévy measure $\nu_{\omega}$, and $\alpha_{\omega}$ is the drift rate in state $\omega$.
+The expected payoff per unit of time is $r_{\omega} = \alpha_{\omega} + \lambda_{\omega} h_{\omega}$, where $\lambda_{\omega}$ is the expected number of jumps per unit of time and $h_{\omega}$ is the expected jump size.
+
+At each moment, agent $i$ allocates fraction $a^i_{t} \in [0,1]$ to the risky arm, yielding instantaneous expected payoff:
+\begin{equation*}
+    (1-a^i_{t})r_\textit{safe} + a^i_{t}r_{\omega}
+\end{equation*}
+
+Each agent observes their own payoff process, the payoff processes of all other agents, and potentially a background information process $B_t$, which provides free information about the state.
+This background process follows the same structure as the payoff processes:
+\begin{equation*}
+    B_t = \beta_{\omega} t + \sigma_B Z^B_t + Y^B_t
+\end{equation*}
+whose informativeness is given exogenously as $k_0$ which increases linearly in time. Under the strong long-run average criterion, agents maximize:
+\begin{equation}
+    \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\int_0^{T}\{(1-a^i_{t})r_\textit{safe} + a^i_{t}r_{\omega}\}dt\right]
+\end{equation}
+
+The unique symmetric Markov perfect equilibrium strategy is characterized as:
+
+\begin{equation}
+    a^*(b) =
+    \begin{cases}
+        0                    & \text{if } I(b) \leq k_0,            \\
+        \frac{I(b)-k_0}{n-1} & \text{if } k_0 < I(b) < k_0 + n - 1, \\
+        1                    & \text{if } I(b) \geq k_0 + n - 1.
+    \end{cases}
+\end{equation}
+
+where $I(b)$ corresponds to the incentive to experiment, defined as:
+\begin{equation*}
+    I(b) = \frac{f(b) - r_\textit{safe}}{r_\textit{safe} - m(b)}
+\end{equation*}
+when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff under full information and $m(b)$ is the expected flow payoff from the risky arm.
+
+This formulation directly captures the tension between exploitation (choosing the currently optimal action) and exploration (generating information for future decisions), as well as the free-rider problem that arises when information is a public good.
+While strategic experimentation models capture important elements of learning dynamics, they typically assume perfectly rational agents and often rely on standardized information structures.
+
+\subsection{Learning Without Experimentation}
+
+A complementary strand of research examines settings where agents learn without directly observing rewards.
+\citet{huang2024learning} studied how long-lived agents learn in networks through repeated interactions, revealing a fundamental inefficiency: regardless of network size, learning speed remains bounded by a constant dependent only on private signal distributions.
+\citet{brandl2024} extended these results by showing that this limitation doesn't apply uniformly to all agents, constructing scenarios where some agents learn faster at others' expense.
+
+Unlike strategic experimentation models where agents receive direct payoff feedback, learning without experimentation captures scenarios where agents must form beliefs based primarily on others' observed actions.
+This distinction is crucial for modeling many real-world social learning contexts, from financial markets \citep{avery1998multidimensional} to technology adoption \citep{ellison1993rules}, where payoffs are delayed, noisy, or unobservable.
+
+The theoretical foundations for this approach draw from both Bayesian and non-Bayesian learning traditions.
+\citet{gale2003bayesian} and \citet{smith2000pathological} developed early models showing how rational agents might become trapped in information cascades when learning from others' actions.
+\citet{acemoglu2011bayesian} extended this analysis to network settings, demonstrating how network topology influences the aggregation of dispersed information.
+
+A substantial literature has explored learning rates in networked environments.
+\cite{bala1998learning} show neighborhood structure influences optimal action adoption, while \cite{golub2012homophily} demonstrate that homophily slows consensus convergence without being affected by network density.
+\cite{Harel2014TheSO} quantify information loss when observing others' discrete actions, finding only a fraction of private information transmits, approaching zero in large societies due to "groupthink." \cite{Jadbabaie2013InformationHA} characterize learning rates through agents' signal structures and eigenvector centralities, showing optimal information allocation depends on its distribution—better information should be placed at central nodes when information structures are comparable, but at peripheral nodes when agents possess unique critical information.
+
+The mechanisms behind these learning barriers stem from information loss in the action quantization process.
+When continuous beliefs are compressed into discrete actions, information is inherently lost \citep{smith2000pathological}.
+\citet{guarino2013social} characterized this as 'coarse inference' where agents make inferences based only on the aggregate distribution of actions across states rather than on the fine details of how actions depend on specific histories, leading to a loss of information.
+
+\iffalse
+    Recent work has examined how behavioral factors and network structure interact to shape learning outcomes.
+\citet{molavi2018theory} developed models of "rational inattention" where agents optimally allocate limited cognitive resources to process social information.
+\citet{dasaratha2020learning} showed how certain network structures can amplify or mitigate the effects of confirmation bias and other cognitive distortions.
+\citet{jadbabaie2012non} proposed hybrid learning models that combine Bayesian updating with naive opinion averaging, better matching empirical patterns of social influence.
+\fi
+
+Strategic considerations emerge naturally in these settings as agents realize their actions influence the future learning of others.
+\citet{bhattacharya2013strategic} demonstrated how forward-looking agents might distort their actions to manipulate the information revealed to others.
+\citet{ARIELI2019185} showed how agents with private information might strategically time their actions to maximize influence on others' beliefs.
+These strategic dynamics align closely with the active influence mechanisms in our POAMG framework.
+
+\subsubsection{Formal Model}
+Similar to before, we characterize the learning dynamics in settings without experimentation through the model introduced by \citet{brandl2024}.
+In this framework, a set of $N= \{1, \ldots, n\}$ agents interact over discrete time periods $t \in \{1, 2, \ldots\}$ in a fixed social network.
+The state of the world $\omega$ is drawn from a finite set $S$ according to a prior distribution with full support and remains fixed throughout.
+
+At each period $t$, each agent $i$ receives a private signal $o^i_t$ from a set $O$, drawn according to a state-dependent public known distribution.
+Signals are independent across agents and time periods.
+Each agent then chooses an action $a^i_t$ from a set $A$, observing the actions taken by neighbors $N^i \subset N$ in previous periods.
+
+All agents share the same utility function $u: S \times A \rightarrow \mathbb{R}$, which depends on the state and their own action.
+For each state $s$, there is a unique optimal action $a_{s} = \arg\max_{a \in A} u(s, a)$, and no action is optimal in two different states.
+Crucially, agents do not observe their realized utilities, eliminating experimentation motives.
+Agent $i$'s information set at period $\tau$ consists of:
+\begin{equation*}
+    I^i_{\leq \tau} = (o^i_1, \ldots, o^i_{\tau}; (a^j_t)_{j \in N^i, t < \tau})
+\end{equation*}
+
+A (pure) strategy for agent $i$ is a function $\sigma^i$ that maps information sets to actions:
+\begin{equation*}
+    \sigma^i: \cup_{t=1}^{\infty} (O^t \times A^{N^i \times (t-1)}) \rightarrow A
+\end{equation*}
+
+For any given strategy profile $\boldsymbol{\sigma} = (\sigma^1, \ldots, \sigma^n)$, the learning rate of agent $i$ is defined as:
+\begin{equation*}
+    r^i(\boldsymbol{\sigma}) = \lim\inf_{t\rightarrow\infty} -\frac{1}{t}\log \mathbb{P}(a^i_t \neq a_{\omega} | \boldsymbol{\sigma})
+\end{equation*}
+
+The main theoretical results establish both limitations and opportunities in social learning networks.
+First, the social learning barrier theorem demonstrates that regardless of network structure or strategies, some agent's learning rate is bounded by a constant that depends only on the signal structure:
+\begin{equation*}
+    \min_{i \in n} r^i(\boldsymbol{\sigma}) \leq r_{bdd} = \min_{\theta \neq \theta'} \left\{D_{KL}(\mu_{\theta} || \mu_{\theta'}) + D_{KL}(\mu_{\theta'} || \mu_{\theta})\right\}
+\end{equation*}
+where $D_{KL}(\mu_{\theta} || \mu_{\theta'})$ is the Kullback-Leibler divergence between signal distributions and the summation corresponds to the Jeffreys divergence \citet{52862b84-7c34-3186-8b28-6af4806272c3}.
+This bound applies regardless of the network size or structure.
+Second, the coordination benefit theorem establishes that for large enough networks and for any $\epsilon > 0$, all agents can learn at rates above a certain bound:
+\begin{equation*}
+    \min_{i \in n} r^i(\boldsymbol{\sigma}) \geq r_{crd} - \epsilon
+\end{equation*}
+where $r_{crd} = \min_{\theta \neq \theta'} D_{KL}(\mu_{\theta} || \mu_{\theta'})$ is strictly greater than the autarky learning rate that an agent can achieve alone.
+This theoretical framework illuminates a fundamental challenge in social learning: information aggregation can fail due to information cascades and herding dynamics, resulting in, as pointed out by the paper, what \citet{harel2021rational} termed "rational groupthink"—where feedback loops cause agents to persist in incorrect beliefs despite continual information arrival.
+While this model allows agents to learn from various observation structures, it does not impose full rationality on the agents, a strand of literature that we discuss next.
+
+\subsection{Non-Bayesian Learning}
+
+While most economic models assume fully rational agents, partial rationality perspectives acknowledge cognitive limitations that affect learning.
+Models like \citet{jadbabaie2012non}'s hybrid learning rule (combining Bayesian updating with naive averaging) and level-$k$ reasoning \citep{stahl1994experimental, crawford2007level} provide middle grounds between full rationality and simple heuristics.
+\iffalse
+    Research on information processing constraints, such as bounded memory \citep{monte2014bounded} and rational inattention \citep{sims2003implications}, further illustrates how cognitive limitations shape learning outcomes.
+Behavioral biases like confirmation bias \citep{rabin1999psychology}, correlation neglect \citep{enke2019correlation}, and naive herding \citep{eyster2010naive} additionally affect how agents process social information.
+These behavioral factors often exacerbate herding behavior and information cascades, creating a gap between theoretical predictions based on full rationality and observed behavior.
+Our MARL framework provides a computational approach to modeling partial rationality that captures these behavioral patterns while maintaining analytical tractability.
+\fi
+
+Evolutionary Game Theory (EGT) also provides a powerful non-Bayesian framework for modeling multi-agent learning dynamics without assuming full rationality.
+Instead, EGT examines how strategy distributions evolve through selection processes based on relative performance \citep{weibull1997evolutionary}.
+This perspective aligns naturally with reinforcement learning's trial-and-error approach.
+\citet{tuyls2004evolutionary} demostrates several important connections between EGT and MARL among which, they relate multi-agent Q-learning to replicator dynamics.
+This mathematical equivalence provides theoretical insights into MARL convergence and equilibrium properties, helping explain empirical observations in complex social dilemmas \citep{leibo2017multi}.
+
+Bridging theoretical frameworks and computational implementations, MARL offers a powerful methodology for operationalizing social learning models.
+MARL provides computational tools that can simulate the intricate dynamics of social learning environments while implementing the strategic adaptations that economic theories recognize as essential but frequently find difficult to compute in complex, realistic scenarios.
+
+\section{Multi-Agent Reinforcement Learning}
+
+While economic models offer valuable theoretical insights, they often struggle with computational tractability when modeling repeated strategic interactions with partially rational agents.
+This is where MARL provides complementary tools that address specific limitations of economic approaches.
+MARL frameworks enable the simulation of complex multi-agent systems where agents learn optimal policies through trial-and-error interactions with their environment and other agents.
+Unlike traditional economic models that often require closed-form solutions, MARL can handle high-dimensional state spaces, complex agent interactions, and non-stationary dynamics that emerge when multiple agents learn simultaneously.
+
+The core components of MARL include state representations, action spaces, reward functions, and learning algorithms that enable agents to maximize expected cumulative rewards.
+These components can be tailored to model various aspects of social learning, including partial observability (through belief states), strategic adaptation (through policy gradient methods), and partial rationality (through constrained optimization).
+Modern MARL approaches incorporate techniques such as centralized training with decentralized execution, value decomposition, and multi-agent actor-critic methods to address coordination challenges that arise in multi-agent settings.
+We direct the interested reader to Appendix \ref{appendix:rl_details} for a detailed introduction of reinforcement learning techniques, including formal definitions, algorithms, and theoretical properties.
+
+Economic models typically assume either fully rational agents (in Bayesian frameworks) or overly simplistic learning rules (in behavioral models).
+MARL offers a middle ground by modeling agents that learn from experience and adapt over time without requiring full rationality.
+\citet{ndousse2021emergent} demonstrated that even without explicit programming, reinforcement learning agents can develop sophisticated social learning capabilities that mirror human behavior.
+This addresses the partial rationality problem by providing computational mechanisms for flexible belief updating based on partial information, learning complex strategies through trial and error, and adapting to non-stationary environments created by other learning agents.
+
+A key limitation of economic social learning models is their difficulty in capturing how agents strategically adapt to others' learning processes.
+The strategic experimentation literature acknowledges these dynamics but often lacks tractable solutions outside of simplified settings.
+\citet{jaques2019social} addressed this by introducing Social Influence as a mechanism in MARL, where agents receive additional reward for causally influencing others' actions.
+This creates a computational framework for modeling strategic teaching and information revelation—key dynamics in the economic models of \citet{bolton1999strategic} and \citet{heidhues2015strategic}.
+
+More directly relevant to our approach, \citet{kim2022influencing} developed Active Markov Games, which explicitly model how agents reason about and influence the policy evolution of other agents.
+This formalism allows us to capture the strategic adaptation that economic models identify as important but struggle to compute in complex environments.
+
+Despite these advantages, standard MARL approaches have their own limitations when applied to social learning.
+Most MARL algorithms assume full observability of state information, while social learning inherently involves partial observability of others' private information and beliefs.
+Many MARL approaches treat non-stationarity as a technical obstacle rather than a strategic feature to be exploited.
+Additionally, MARL often lacks the theoretical foundations that economic models provide for understanding equilibrium behavior.
+
+Our POAMG framework extends Active Markov Games to partially observable settings specifically to address these limitations.
+By incorporating policy evolution as an integral part of the environment dynamics while accounting for partial observability, we provide a computational approach that preserves the strategic sophistication of economic models.
+
+\section{Bridging Economic Theory and MARL}
+
+While economic social learning and MARL have developed largely in parallel, their complementary strengths suggest significant potential for integration.
+Economic models provide rigorous theoretical foundations for understanding rational behavior, belief formation, and information aggregation in social contexts.
+However, these models often face computational limitations when addressing complex strategic interactions, especially when agents have heterogeneous beliefs, partial rationality, or operate in environments with partial observability.
+
+Conversely, MARL offers computational frameworks for modeling adaptive agents in complex, high-dimensional environments.
+These approaches excel at simulating emergent behaviors and can operate effectively without imposing full rationality assumptions.
+However, MARL approaches frequently lack the theoretical grounding to interpret equilibrium properties and sometimes overlook the strategic sophistication captured in economic models.
+
+Our research bridges these fields by developing a partially observable active Markov game (POAMG) framework that preserves the strategic considerations central to economic theory while leveraging the computational scalability of MARL.
+This integration addresses three key challenges:
+
+First, we explicitly incorporate policy evolution dynamics and strategic adaptation as fundamental features rather than technical obstacles.
+Unlike standard MARL approaches that treat non-stationarity as a problem to overcome, our framework models how sophisticated agents reason about and deliberately influence others' learning trajectories \citep{kim2022influencing}, similar to the strategic teaching phenomena identified in economic experimentation literature \citep{yamamoto2019stochastic}.
+
+Second, we incorporate partial observability as an intrinsic characteristic of social learning environments.
+By modeling belief states and observation functions, our approach captures the information asymmetries and strategic uncertainty that economic models identify as crucial determinants of learning outcomes \citep{heidhues2015strategic, rosenberg2009informational}.
+
+Third, we account for long-horizon strategic planning where agents optimize not just immediate rewards but also their influence on the future learning dynamics of other agents.
+This aligns with economic perspectives on forward-looking behavior while remaining computationally tractable through reinforcement learning techniques.
+
+The resulting framework enables more realistic modeling of social learning phenomena that resist analysis under either purely economic or purely computational approaches.
+It combines economic insights on strategic sophistication with MARL's ability to simulate complex adaptive systems, yielding both theoretical insights and practical algorithms for understanding multi-agent learning in partially observable environments.
+
+\chapter{Theoretical Framework}
+
+We adapt the framework in \citet{kim2022influencing} to the partially observable setting and formalize the problem of multi-agent learning as a Partially Observable Active Markov Game with periodic policy updates.
+Throughout the paper, we will use the bold convention to denote the collection of joint sets, joint variables and joint functions for $i \in I =\{1,\ldots,n\}$, where $\boldsymbol{X} := \times_{i \in I} X^i$ for set $X^i$, $\boldsymbol{x} := \{x_1, \ldots, x_n\}$ for variable $x^i$ and $\boldsymbol{G}(\cdot) := \prod_{i \in I} G^i(\cdot)$ for function $G^i(\cdot)$.
+
+\section{Partially Observable Active Markov Games}
+In social learning environments, agents rarely possess complete information about the underlying state of the world.
+Instead, they receive private signals—often limited and noisy—that only partially reveal the true state, while also observing the actions of other participants rather than their private information.
+This fundamental information asymmetry is a cornerstone of economic models of social learning.
+The challenge of inferring valuable information from others' actions while acknowledging the confounding influence of their own social learning creates rich strategic dynamics that cannot be captured by frameworks assuming full observability.
+This necessitates extending our theoretical approach to the partially observable setting.
+Standard approaches to partial observability, such as Partially Observable Markov Decision Processes (POMDPs) and Decentralized POMDPs, address this challenge in single-agent and cooperative multi-agent contexts respectively.
+However, these frameworks do not adequately capture the strategic nature of policy evolution that characterizes the social learning environments, and neither do they allow for flexible modeling of the reward functions.
+Building on the Active Markov Game formulation of \citet{kim2022influencing}, we introduce Partially Observable Active Markov Games (POAMGs), which integrate belief state dynamics with evolving policy parameters to model sophisticated social learning dynamics under uncertainty.
+
+\begin{definition}[Partially Observable Active Markov Game]
+    A Partially Observable Active Markov Game is defined as a tuple $M_n = \langle I, S, \boldsymbol{A}, T, \boldsymbol{O}, \boldsymbol{R}, \boldsymbol{\Theta}, \boldsymbol{U} \rangle$, where:
+    \begin{itemize}
+        \item $I = \{1, \ldots, n\}$ is the set of $n$ agents;
+        \item $S$ is the state space, assumed to be discrete and finite;
+        \item $\boldsymbol{A} = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$;
+        \item $T: S \times \boldsymbol{A} \mapsto \Delta(S)$ is the Markovian state transition function, with $T(s'|s, \boldsymbol{a})$ denoting the probability of transitioning to state $s'$ after taking joint action $\boldsymbol{a}$ in state $s$;
+        \item $\boldsymbol{O} = \times_{i \in I} O^i$ is the joint observation function, with $O^i: S \times \Omega^i \mapsto \Delta(\Omega^i)$ denoting the observation function for agent $i$ and $\Omega^i$ denoting the observation space for agent $i$;
+        \item $\boldsymbol{R} = \times_{i \in I} R^i$ is the joint reward function, with $R^i: S \times \boldsymbol{A} \mapsto \mathbb{R}$ denoting the reward function for agent $i$;
+        \item $\boldsymbol{\Theta} = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$;
+        \item $\boldsymbol{U} = \times_{i \in I} U^i$ is the joint Markovian policy update function, with
+              $U^i: \Theta^i \times O^i \times \boldsymbol{A} \times R^i \times O^i \mapsto \Delta(\Theta^i)$ denoting the policy update function for agent $i$.
+    \end{itemize}
+\end{definition}
+This formulation extends the Active Markov Game framework by incorporating observation functions that mediate agents' perceptions of the environment state.
+Next, we define policies of the agents based on their beliefs about the underlying state of the environment.
+
+\begin{definition}[Belief-Based Policy]
+    Under partial observability, each agent $i$ maintains a belief state $b_t^i \in B^i$ at time $t$, representing its probability distribution over states given its observation history.
+The policy of agent $i$ is defined as a mapping from belief and parameter spaces to distributions over actions:
+    \begin{equation}
+        \pi^i: B^i \times \Theta^i \mapsto \Delta(A^i)
+    \end{equation}
+
+    where $\pi^i(a^i|b^i; \theta^i)$ represents the probability of agent $i$ taking action $a^i$ given belief state $b^i$ and policy parameters $\theta^i$.
+\end{definition}
+\iffalse
+    The figure below illustrates the structure of the POAMG framework, highlighting the interplay between states, observations, beliefs, and policy parameters.
+
+    \begin{figure}[htb]
+        \centering
+        \includegraphics[width=0.9\linewidth]{figures/poamg-structure.pdf}
+        \caption{Structure of a POAMGshowing the relationships between environment state, observations, beliefs, and policy parameters in a two-agent setting.}
+        \label{fig:poamg-structure}
+    \end{figure}
+\fi
+
+In partially observable active Markov games, agents form beliefs to infer the underlying state of the environment.
+Unlike standard partially observable settings, these states evolve through the dynamically changing policies of the agents in addition to the environmental dynamics.
+The process unfolds as follows: at time step $t$, each agent $i$ selects an action at state $s_t \in S$ by sampling from its belief-conditioned policy $a^i_t \sim \pi^i(\cdot|b^i_t; \theta^i_t)$.
+When all agents act collectively through joint action $\boldsymbol{a_t}$, the environment transitions from $s_t$ to $s_{t+1}$ with probability $T(s_{t+1}|s_t, \boldsymbol{a}_t)$.
+Subsequently, each agent $i$ receives a reward $r^i_t = R^i(s_t, \boldsymbol{a}_t)$ and adjusts its policy parameters via the update function $U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$, where $\tau^i_t = \{o_t^i, \boldsymbol{a_t}, r^i_t, o_{t+1}^i\}$ is the trajectory for agent $i$ at time $t$ consisting of the current observation $o_t^i$, joint action $\boldsymbol{a_t}$, reward received $r^i_t$, and the next observation $o_{t+1}^i$.
+This adaptive cycle continues until non-stationary policies reach convergence.
+A key insight is that the joint policy update function $\boldsymbol{U}$ depends on $a^i_t$, which directly impacts state transitions and rewards, thereby enabling agent $i$ to strategically shape future collective policies through its individual decisions.
+This explicit modeling of strategic influence constitutes the primary advantage of active Markov games over their stationary counterparts.
+
+\section{Convergence}
+A central question in our analysis is whether the joint process of states, beliefs and policy parameters converges to a well-defined stationary distribution, and under what conditions.
+Following \citet{kim2022influencing}, we establish this connection using the properties of regularly perturbed Markov processes.
+First, we define the joint process, which operates on the joint space of states, beliefs and policy parameters.
+
+\begin{definition}[Joint Process]
+    In a Partially Observable Active Markov Game, the joint process $(s_t, \boldsymbol{b}_t, \boldsymbol{\theta}_t)$ consists of the state $s_t \in S$, the joint belief state $\boldsymbol{b}_t = (b^1_t, \ldots, b^n_t) \in \boldsymbol{B}$ and joint policy parameters $\boldsymbol{\theta}_t = (\theta^1_t, \ldots, \theta^n_t) \in \boldsymbol{\Theta}$ of all agents at time $t$.
+\end{definition}
+We then make the following assumptions on the subprocesses to ensure the ergodicity of the perturbed joint process.
+\begin{assumption}[Communicating State Transition]\label{assumption:1}
+    The state transition $T$ is communicating, meaning that for any two states $s, s' \in S$, there exists a sequence of joint actions $\boldsymbol{a}_1, \boldsymbol{a}_2, \ldots, \boldsymbol{a}_k$ and a sequence of states $s_1, s_2, \ldots, s_{k-1}$ such that:
+    \begin{align}
+        T(s_1|s, \boldsymbol{a}_1) > 0, \quad T(s_2|s_1, \boldsymbol{a}_2) > 0, \quad \ldots, \quad T(s'|s_{k-1}, \boldsymbol{a}_k) > 0
+    \end{align}
+\end{assumption}
+
+\begin{assumption}[Communicating Belief-State Process]\label{assumption:2}
+    The belief-state process is communicating, meaning that for any two belief states $b^i, b'^i \in B^i$, there exists a sequence of joint actions $\boldsymbol{a}_1, \boldsymbol{a}_2, \ldots, \boldsymbol{a}_m$ and a sequence of observations $o^i_1, o^i_2, \ldots, o^i_m$ such that:
+    \begin{align}
+        \mathbb{P}(b^i_{t+m} = b'^i | b^i_t = b^i, \boldsymbol{a}_t = \boldsymbol{a}_1, o^i_{t+1} = o^i_1, \ldots, \boldsymbol{a}_{t+m-1} = \boldsymbol{a}_m, o^i_{t+m} = o^i_m) > 0
+    \end{align}
+\end{assumption}
+Assuming the communicating property of the subprocesses, we can establish convergence of the perturbed joint process to the unique stochastically stable distribution of the unperturbed one, as the perturbation vanishes in the limit.
+\begin{theorem}[Stochastically Stable Distribution]
+    Under Assumptions \ref{assumption:1} and \ref{assumption:2}, as $\epsilon \to 0$, the perturbed joint processes defined by $\epsilon$-perturbed policy update functions converge to the unique stochastically stable distribution $\mu^*$ of the unperturbed joint process $(s_t, \boldsymbol{b}_t, \boldsymbol{\theta}_t)$.
+\end{theorem}
+
+\begin{proof}
+    See Appendix \ref{appendix:stochasticallystable} for a detailed proof.
+\end{proof}
+This convergence result has profound implications for our framework.
+By establishing the existence of a unique stochastically stable distribution, we provide a solid theoretical foundation for defining optimization objectives and analyzing equilibrium behavior in partially observable active Markov games.
+The stochastically stable distribution represents the limiting behavior of the system, independent of initial conditions, allowing us to characterize the long-run outcomes of social learning processes.
+This property is crucial for developing algorithms that optimize for long-term performance rather than myopic rewards, aligning with our goal of modeling sophisticated social learning dynamics.
+
+\section{Incentives}
+We now formalize the optimization objectives for agents in our Partially Observable Active Markov Game framework.
+In contrast to traditional reinforcement learning settings that typically employ discounted rewards, we first focus on the average reward criterion as our fundamental optimization objective.
+The average reward formulation provides several compelling advantages for modeling social learning dynamics.
+As \citet{sutton2018reinforcement} emphasize, this approach is particularly well-suited for continuing tasks without natural episode boundaries—a characteristic that aligns perfectly with the ongoing nature of social learning interactions.
+While economic theory has predominantly employed discounted reward objectives due to their mathematical tractability and natural correspondence to time preference in utility maximization \citep{koopmans1960stationary, stokey1989recursive}, the average reward paradigm better captures the strategic considerations in our framework.
+The key advantage of the average reward approach in our context is its emphasis on the limiting behavior of the multi-agent system.
+When agents engage in repeated strategic interactions over indefinite horizons, their primary concern becomes the long-run system behavior rather than transient dynamics.
+Moreover, unlike discounted objectives that can induce myopic behavior depending on the discount factor, the average reward formulation naturally encourages agents to consider the permanent effects of their actions on other agents' learning processes—a crucial aspect for accurately modeling the strategic dimensions of social learning.
+
+\begin{definition}[Average Reward Objective under Partial Observability]
+    Each agent $i \in I$ in a Partially Observable Active Markov Game aims to find policy parameters $\theta^i$ and update function $U^i$ that maximize its expected average reward $\rho^i \in \mathbb{R}$ based on the joint beliefs $\boldsymbol{b}$:
+    \begin{align}
+        \begin{split}
+            \max_{\theta^i, U^i} \rho^i(\boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{U}) : & = \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \boldsymbol{a}_t) \Bigg|
+                \begin{array}{c}
+                    \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+                    \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b_t}; \boldsymbol{\theta_t}),
+                    s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),                                  \\
+                    \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+                    \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta_t}, \boldsymbol{\tau_t})
+                \end{array}
+            \right]                                                                                                                                                                                                                                                                                                                          \\
+                                                                                               & = \max_{\theta^i, U^i} \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} b^i(s) \mu^*(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}} \boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^i(s, \boldsymbol{a})
+        \end{split}
+    \end{align}
+
+\end{definition}
+
+This formulation emphasizes that agents aim to maximize their rewards in the limiting behavior of the Markov process, focusing on long-term performance rather than immediate gains.
+The second equality expresses the objective in terms of the stochastically stable distribution $\mu^*$, weighted by agent's belief, connecting our optimization problem to the theoretical results established earlier.
+It is worth noting that this definition assumes beliefs, policy parameters, and policy update functions are all publicly observable.
+Since this assumption rarely holds in practical scenarios, we will implement \textit{variational inference} in our algorithm to enable agents to infer these measures from their partial observations.
+Next, we derive the policy gradients, which we will be the foundation of our algorithm, allowing the agents to maximize their objectives.
+
+\section{Belief-Based Policy Gradients}
+Policy gradient methods are a class of reinforcement learning techniques that directly optimize policy parameters by following the gradient of expected return~\cite{sutton1999policy}.
+Unlike value-based methods, policy gradients explicitly parametrize the policy and update parameters in the direction that improves performance.
+These methods excel in continuous action spaces and can learn stochastic policies~\cite{williams1992simple}.
+In partially observable settings, policy gradients require adaptation to handle belief states rather than true states~\cite{kaelbling1998planning}.
+Modern approaches like Proximal Policy Optimization~\cite{schulman2017proximal} have further improved stability and sample efficiency of these methods through constrained policy updates.
+
+Our framework extends these concepts to multi-agent settings with non-stationary policies by incorporating the Active Markov Game formulation of \citet{kim2022influencing}.
+The key innovation in our approach is conditioning value functions not just on belief states, but on the joint space of states, belief states, and policy parameters of all agents.
+This allows us to explicitly model how an agent's actions influence both the environmental dynamics and the learning processes of other agents.
+
+While our theoretical framework proposes maximizing over both policy parameters $\theta^i$ and update functions $U^i$, this joint optimization presents significant computational challenges.
+As noted in \citet{kim2022influencing} optimizing over policy update functions essentially constitutes a long-horizon meta-learning problem, which remains computationally intractable for many realistic multi-agent settings.
+Following their practical approach, we simplify the optimization problem by focusing exclusively on learning optimal fixed-point policies that influence joint policy behavior while using standard update rules:
+
+\begin{align}
+    \max_{\theta^i} \rho^i_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i} \lim_{T \to \infty} \mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^T R^i(s_t, \boldsymbol{a}_t) \bigg|
+        \begin{array}{c}
+            \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+            \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_t; \boldsymbol{\theta}_t),
+            s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),                                  \\
+            \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+            \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
+        \end{array}
+        \right]
+\end{align}
+
+This formulation still preserves the essence of our framework—capturing how agent $i$'s actions influence other agents' learning trajectories—while making the optimization problem tractable.
+Under the stochastically stable distribution discussed earlier, this simplified objective becomes independent of initial conditions, further supporting the practical viability of our approach.
+Under the average reward formulation, we define the differential value function for agent $i$ as:
+
+\begin{align}
+    v^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty} \mathbb{E}\left[ \sum_{t=0}^T \left(R^i(s_t, \boldsymbol{a}_t) - \rho^i_{\theta^i}\right) \Bigg|
+    \begin{array}{c}
+        s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+        \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_t; \boldsymbol{\theta}_t),
+        s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),                                         \\
+        \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+        \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
+    \end{array}
+    \right]
+\end{align}
+
+This function represents the expected total difference between future rewards and the average reward $\rho^i_{\theta^i}$ when starting from state $s$, belief states $\boldsymbol{b}$, and policy parameters $\boldsymbol{\theta}$.
+It serves as a crucial component in deriving the policy gradient theorem for our framework.
+
+\begin{theorem}[Partially Observable Active Average Reward Policy Gradient Theorem]
+    \label{thm:avg_gradient}
+    The gradient of the active average reward objective with respect to agent $i$'s policy parameters $\theta^i$ in a partially observable setting is:
+    \begin{align}
+        \nabla_{\theta^i} J^i_\pi(\theta^i) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i} \nabla_{\theta^i} \pi^i(a^i|b^i; \theta^i) \sum_{a^{\neg i}} \pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
+        \label{eq:avg_gradient}
+    \end{align}
+
+    where the action-value function $q^i_{\theta^i}$ is defined as:
+    \begin{align}
+        q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'} T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'} \boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'} \boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^i(s, \boldsymbol{a}) - \rho^i_{\theta^i} + v^i_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
+        \label{eq:avg_action_value}
+    \end{align}
+
+    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing the belief update function.
+
+\end{theorem}
+
+\begin{proof}
+    See Appendix \ref{appendix:avg_gradient} for a detailed proof.
+\end{proof}
+This theorem extends the policy gradient result in \citet{kim2022influencing} to partially observable settings by integrating over the joint space of states, beliefs, and policy parameters according to their stochastically stable distribution $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$.
+The resulting gradient has a form similar to the standard policy gradient theorem, but with important modifications.
+First, our policies are conditioned on belief states rather than actual states.
+Second, the action-value function must account for belief updates and policy parameter evolution.
+Third, the expectation is taken over the stochastically stable distribution of the joint state space, while also considering the stochasticity of the observations.
+
+Building on the theoretical foundations established for the average reward criterion, we now turn our attention to the discounted return formulation.
+This alternative objective function is particularly relevant in economic contexts where agents exhibit time preferences, valuing immediate rewards more highly than delayed ones.
+The following section develops the mathematical framework for optimizing agent behavior under discounted returns, providing a complementary perspective to our earlier analysis.
+By examining both criteria, we offer a comprehensive theoretical foundation that can accommodate different modeling assumptions about how agents value future consequences of their actions.
+
+\section{Discounted Returns}
+
+While the average reward criterion provides a principled approach for analyzing limiting behaviors in continuing tasks, the discounted return objective remains predominant in economic models of social learning \citep{keller2005strategic, bolton1999strategic, huang2024learning,brandl2024}.
+This formulation incorporates time preference through a discount factor $\gamma \in [0, 1)$, giving higher weight to near-term rewards and diminishing importance to those further in the future.
+The expected effective planning horizon under discounting is approximately $\frac{1}{1-\gamma}$ steps \citep{kearns2002near}, making it well-suited for scenarios where agents exhibit time preference or where finite planning horizons are appropriate \citep{frederick2002time, sutton2018reinforcement}.
+We begin by formalizing the discounted return objective in our POAMG framework:
+
+\begin{definition}[Discounted Return Objective under Partial Observability]
+    Each agent $i \in I$ in a Partially Observable Active Markov Game aims to find policy parameters $\theta^i$ that maximize its expected discounted return $J^i_{\pi, \gamma}(\theta^i) = v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)$ starting from initial state $s_0$, joint beliefs $\boldsymbol{b}_0$, and joint policy parameters $\boldsymbol{\theta}_0$:
+    \begin{align}
+        \max_{\theta^i} v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0) & := \max_{\theta^i} \mathbb{E}\left[ \sum_{t=0}^{\infty} \gamma^t R^i(s_t, \boldsymbol{a}_t) \bigg|
+            \begin{array}{c}
+                s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0, \\
+                \boldsymbol{a}_{0:\infty} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:\infty}; \boldsymbol{\theta}_{0:\infty}),
+                s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),  \\
+                \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+                \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
+            \end{array}
+            \right]
+    \end{align}
+
+\end{definition}
+
+The discounted return objective differs fundamentally from the average reward criterion in its treatment of future consequences.
+As $\gamma$ approaches 1, it increasingly resembles the average reward formulation, but with a crucial distinction: even with $\gamma$ arbitrarily close to 1, the discounted formulation still assigns diminishing weight to distant future rewards.
+This property has significant implications for strategic behavior in multi-agent settings, particularly in social learning contexts.
+
+\subsection{Discounted Visitation Measure}
+
+To analyze the behavior of agents operating under discounted returns, we introduce the \textit{discounted visitation measure} (also called occupancy measure).
+This measure represents the normalized expected discounted time spent in each state-belief-policy configuration when following a joint policy \citep{sutton1999policy, Silver2014DeterministicPG}.
+
+\begin{definition}[Discounted Visitation Measure]
+    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi^*$, with an initial distribution $\mu_0$ over the joint state-belief-policy space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
+    \begin{equation}
+        d^{\pi}_{\mu_0} := (1-\gamma) \sum_{t=0}^{\infty} \gamma^t \mu_t
+    \end{equation}
+
+    where $\mu_t$ is the distribution at time $t$ when starting from $\mu_0$, and $\gamma \in [0, 1)$ is the discount factor.
+\end{definition}
+
+This distribution serves two critical purposes in our framework.
+First, it provides a well-defined distribution over which expectations can be taken, even in non-stationary environments where policies are constantly changing.
+Unlike the stochastically stable distribution used in the average reward setting, the discounted distribution automatically exists for any $\gamma < 1$ without requiring additional assumptions on the ergodicity of the underlying processes \citep{puterman1994markov}.
+Second, it directly links to the optimization objective, allowing us to express the expected discounted return as an expectation of immediate rewards under this distribution.
+
+The discounted visitation measure satisfies important properties that facilitate policy optimization. Most notably, it can be expressed as the unique solution to a functional equation:
+
+\begin{equation}
+    d^{\pi}_{\mu_0} = (1-\gamma)\mu_0 + \gamma \Psi^* d^{\pi}_{\mu_0}
+\end{equation}
+
+where $\Psi^*$ is the adjoint of the transition operator $\Psi$ that describes how probability distributions evolve over one timestep.
+This relationship can be seen as a fixed-point equation, where $d^{\pi}_{\mu_0}$ is the unique fixed point of the contractive mapping $(1-\gamma)\mu_0 + \gamma \Psi^*(\cdot)$ in the space of finite measures.
+The existence and uniqueness of this measure is guaranteed for any $\gamma < 1$, providing a solid mathematical foundation for our policy gradient derivations.
+
+\subsection{Policy Gradient Theorem for Discounted Returns}
+
+With the discounted visitation measure established, we now derive the policy gradient theorem that forms the basis for optimization in this framework.
+\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient Theorem]
+    \label{thm:discounted_gradient}
+    The gradient of the discounted return objective $J^i_{\pi, \gamma}(\theta^i) = v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)$ with respect to agent $i$'s policy parameters $\theta^i$ in a partially observable active Markov game setting can be expressed as:
+    \begin{align}
+        \nabla_{\theta^i} J^{i}_{\pi, \gamma}(\theta^i) & = \frac{1}{1-\gamma} \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i} \nabla_{\theta^i} \pi^i(a^i|b^i; \theta^i) \nonumber \\
+                                                        & \quad \sum_{a^{-i}} \pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
+        \label{eq:discounted_gradient}
+    \end{align}
+
+    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted visitation measure starting from initial distribution $\mu_0$, and $q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is the action-value function defined as:
+    \begin{align}
+        q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^i(s, \boldsymbol{a}) + \gamma \sum_{s'} T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'} \boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                \\
+                                                                               & \quad \sum_{\boldsymbol{\theta}'} \boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^i_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
+        \label{eq:discounted_action_value}
+    \end{align}
+
+\end{theorem}
+
+\begin{proof}
+    See Appendix \ref{appendix:discounted_proofs} for a detailed proof.
+\end{proof}
+
+This theorem connects the policy gradient to expectations with respect to the discounted visitation measure, providing a principled approach to policy optimization in partially observable multi-agent settings.
+The scaling factor $\frac{1}{1-\gamma}$ accounts for the effective horizon of the discounted objective, with its magnitude increasing as $\gamma$ approaches 1.
+
+In implementation, the choice between these objectives should be guided by the specific characteristics of the social learning scenario being modeled.
+The discounted formulation may be appropriate for settings with finite horizons, impatient agents, or where near-term performance is particularly valued.
+However, for scenarios focused on long-run learning dynamics and asymptotic behavior, the average reward criterion provides a more principled approach by equally valuing rewards across all future time periods.
+
+In practice, computing these gradients exactly is typically infeasible.
+Instead, sample-based approximations and function approximation techniques using neural networks are employed to estimate the gradient from experience.
+Nevertheless, in theory, when agents learn to adapt their policies according to these gradients, they eventually converge to an equilibrium concept related to traditional equilibria, which we will introduce in the following section.
+
+\section{Equilibrium}
+Policy gradient optimization naturally leads agents toward stable configurations where no individual agent can unilaterally improve its reward by changing its policy.
+Given the formalization of our optimization objectives and the policy gradient theorems established above, we now characterize equilibrium concepts in Partially Observable Active Markov Games.
+By following the gradient directions specified in Theorems \ref{thm:avg_gradient} and \ref{thm:discounted_gradient}, agents can iteratively improve their policies to maximize their respective objectives.
+This optimization process naturally leads to the concept of Partially Observable Active Equilibrium, which extends the Active Equilibrium from standard Active Markov Games \cite{kim2022influencing} to account for partial observability while representing the fixed point of the policy gradient optimization process.
+
+\begin{definition}[Partially Observable Active Equilibrium]
+    A Partially Observable Active Equilibrium is a joint policy parameter $\boldsymbol{\theta}^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $\boldsymbol{U}^* = \{U^{i*}, U^{-i*}\}$ such that for all $i \in I$:
+    \begin{align}
+        J^i_{\pi}(\boldsymbol{b}, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*})         & \geq J^i_{\pi}(\boldsymbol{b}, \theta^i, \theta^{-i*}, U^i, U^{-i*}) \quad \text{(average reward case)}              \\
+        J^i_{\pi, \gamma}(\boldsymbol{b}, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) & \geq J^{i}_{\pi, \gamma}(\boldsymbol{b}, \theta^i, \theta^{-i*}, U^i, U^{-i*}) \quad \text{(discounted reward case)}
+    \end{align}
+
+    for all $\boldsymbol{b} \in \boldsymbol{B}$, $\theta^i \in \Theta^i$, $U^i \in \mathcal{U}^i$, where $\mathcal{U}^i$ is the space of possible update functions for agent $i$.
+\end{definition}
+
+This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system while operating under partial observability.
+At equilibrium, no agent can improve its long-term reward (either discounted or average, depending on the formulation) by unilaterally changing either its policy or its update function, overlapping with the definition of the Bayesian Nash equilibrium in non-cooperative games.
+
+Computing partially observable active equilibria exactly is typically intractable due to the complexity of belief spaces and the sophistication of policy update functions.
+Nevertheless, this equilibrium concept provides a theoretical benchmark against which practical algorithms can be evaluated.
+In the next section, we discuss the computational challenges inherent in direct implementation of our theoretical framework, before introducing our practical policy optimization method that approximates equilibrium strategies through policy gradient algorithms.
+
+\section{Challenges with Exact Computation}
+
+Theorems \ref{thm:avg_gradient} and \ref{thm:discounted_gradient} provide mathematically principled approaches for optimizing policies in both average and discounted return settings, but implementing them exactly is computationally infeasible for most real-world applications.
+In partially observable environments, agents must maintain belief states, whose evolution can be governed by the Bayes' rule as:
+
+\begin{align}
+    b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
+\end{align}
+
+For environments with large or continuous state spaces, representing and updating these distributions becomes prohibitively expensive.
+Moreover, exact updates require perfect knowledge of observation functions $O^i$ and transition dynamics $T$, which may not be readily available to the agents.
+The complexity compounds in multi-agent settings where agents must reason about others' belief states and policies using Bayesian inference:
+
+\begin{align}
+    \mathbb{P}(\boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t | \tau^i_{0:t}) \propto \mathbb{P}(\tau^i_{0:t} | \boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t) \mathbb{P}(\boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t | \tau^i_{0:t-1})
+\end{align}
+
+This creates nested inference problems—agents maintaining beliefs about others' beliefs—that grow exponentially with the number of agents and the complexity of their policies.
+
+Computing action-value functions adds another layer of intractability, with different formulations for average returns and discounted returns.
+The triple expectations—over next states, observations, and policy parameters— in equations \eqref{eq:avg_action_value} and \eqref{eq:discounted_action_value} require summing over an exponentially large joint space, where the policy parameter space $\Theta^i$ would ideally be modified to be continuous.
+Furthermore, the policy update functions $\boldsymbol{U}$ of other agents are typically unknown, and the recursive nature of the value function creates computational dependencies that quickly become unmanageable.
+
+The policy gradient calculations presented in Equations \eqref{eq:avg_gradient} and \eqref{eq:discounted_gradient} present similarly insurmountable difficulties.
+Computing the stochastically stable distribution $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ for average returns or the discounted visitation measure $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ for discounted returns requires implementing additional algorithms \citep{wicks2012algorithmcomputingstochasticallystable}, while expectations over joint actions create additional combinatorial explosion.
+These computational barriers—state space explosion, nested belief inference, triple expectations, and distribution computation—collectively render exact computation infeasible except for trivial environments.
+The curse of dimensionality is especially severe due to the combined complexity of partial observability, multi-agent interactions, and evolving policies.
+
+To address these computational challenges and make our theoretical framework practically applicable, we develop POLARIS, a neural network-based algorithm that approximates the key components of our framework while maintaining its essential properties.
+
+\section{Algorithm: POLARIS}
+
+In this section, we present POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), our practical implementation of the theoretical framework.
+POLARIS extends and improves upon the FURTHER algorithm \cite{kim2022influencing} with specialized components for belief modeling, information propagation through networks, and advantage-weighted training.
+The algorithm uses neural network approximations to overcome the computational challenges outlined in the previous section while preserving the key insights of our theoretical framework.
+It consists of three integrated modules: a belief processing module, an inference learning module, and a reinforcement learning module, which operate in concert to enable sophisticated social learning in partially observable environments.
+The architecture integrates several neural network components working in tandem: a Transformer-based belief processor~\cite{vaswani2017attention} provides sophisticated temporal pattern recognition through its self-attention mechanisms; an inference module implementing a Graph Neural Network (GNN)~\cite{scarselli2009graph} with temporal attention for network-aware representations; and Multi Agent Soft Actor-Critic (MASAC) following \citet{kim2022influencing} with both average and discounted reward formulations to address the long-term planning requirements of social learning.
+To maintain performance across changing environments, particularly when the true state changes, POLARIS employs Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} that selectively preserves important parameters while allowing adaptation to new conditions.
+We provide the detailed network architectures in Appendix \ref{appendix:neural_architectures}.
+
+\subsection{Belief Processing Module}
+
+The belief processing module employs a Transformer architecture to encode the agent's belief state based on partial observations and joint actions:
+
+\begin{align}
+    b^i_t = f_{\text{Transformer}}(b^i_{t-1}, o^i_t, \boldsymbol{a}_{t-1}; \psi^i_{\text{Transformer}})
+\end{align}
+
+Unlike traditional recurrent approaches, the Transformer architecture introduces crucial advantages for social learning scenarios.
+The self-attention mechanism allows the model to weigh the importance of different parts of the observation history dynamically, enabling it to focus on the most informative signals while downplaying noise or irrelevant information.
+By processing inputs in parallel rather than sequentially, the Transformer enables more efficient training compared to conventional Recurrent Neural Networks, particularly important when dealing with multiple agents and long interaction histories.
+Perhaps most importantly for social learning, the Transformer architecture captures relationships between temporally distant observations more effectively, allowing agents to recognize patterns that may emerge over extended periods of social interaction.
+The Transformer-based belief processor also outputs an explicit belief distribution over possible states:
+
+\begin{align}
+    \mathbb{P}(s|b^i_t) = \text{Softmax}(f_{\text{belief\_head}}(b^i_t))
+\end{align}
+
+This explicit representation allows for more interpretable belief states and enables advantage-weighted training, where the belief processing is optimized not just to track observations but also to produce beliefs that lead to high-value actions.
+By maintaining a probability distribution over states rather than just an abstract representation, the model provides transparency into its decision-making process and facilitates debugging and analysis of social learning dynamics.
+
+\subsection{Inference Learning Module}
+
+POLARIS implements a Graph Neural Network (GNN) with temporal attention for network-aware social learning.
+This inference module represents the multi-agent system as a graph where nodes correspond to agents and edges represent observational relationships in the social network.
+The module outputs distribution parameters:
+
+\begin{align}
+    \mu_t, \log\sigma_t = \text{GNN}_{\text{temporal}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i_{\text{GNN}})
+\end{align}
+
+Here, $\mu_t$ and $\log\sigma_t$ parameterize a Gaussian distribution from which latent variables $\boldsymbol{\hat{z}}^{-i}_t$ are sampled, encoding information about other agents' policies and beliefs.
+The GNN architecture adapts dynamically to the network topology, enabling automatic configuration for various social network structures.
+It utilizes multi-head attention mechanisms across both spatial (network) and temporal dimensions, allowing it to differentially weigh connections between agents based on their decision relevance.
+A key feature is the temporal memory system that maintains a sliding window of past states, enabling temporal attention mechanisms that help the model reason about the evolution of other agents' beliefs and strategies over time.
+This approach proves especially effective for complex network topologies where information flow patterns significantly influence learning dynamics.
+
+The inference module learns a mapping from observable trajectories to latent variables that are predictive of other agents' behaviors, optimized using the Evidence Lower Bound (ELBO) objective: \footnote{See \cite{kim2022influencing} for a detailed derivation of the ELBO objective in the sequential setting.}
+
+\begin{align}
+    J^i_{elbo} = \mathbb{E}_{\mathbb{P}(\tau^i_{0:t}),\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{1:t}|\tau^i_{0:t-1};\phi^i_{GNN})}\left[ \sum_{t'=1}^t \log \mathbb{P}(\boldsymbol{a}^{-i}_{t'}|o^i_{t'}, \boldsymbol{\hat{z}}^{-i}_{t'}; \phi^i_{GNN}) \right.
+\\
+        \left. - \alpha_{KL} D_{KL}(\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'}|\tau^i_{t'-1}; \phi^i_{GNN})||\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'-1}))\right]
+\end{align}
+
+The ELBO objective balances reconstruction accuracy (predicting other agents' actions) with regularization through the KL divergence term, which encourages temporal consistency in the latent space.
+This is particularly important in social learning settings where abrupt changes in models of other agents can lead to unstable learning dynamics.
+
+The inference module additionally produces opponent belief distributions, enabling agents to model other agents' understanding of the environment:
+
+\begin{align}
+    \mathbb{P}^i(\boldsymbol{b}^{-i}_t|\tau^i_{0:t}) = \text{Softmax}(f_{\text{opponent\_belief}}(\mu_t, \log\sigma_t))
+\end{align}
+
+This second-order belief modeling allows for sophisticated strategic reasoning, as agents can anticipate how others will respond to their actions based not just on past behavior but on inferred beliefs about the environment.
+
+\subsection{Reinforcement Learning Module}
+
+The reinforcement learning module uses the Soft Actor-Critic (SAC) framework with both average and discounted reward formulations.
+The policy and action-value functions are conditioned on belief states and inferred latent variables:
+
+\begin{align}
+    \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)                            & =
+    \begin{cases}
+        \text{Categorical}(a^i|\text{MLP}_{\text{policy}}(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))                 & \text{for discrete actions}   \\
+        \mathcal{N}(\mu(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i), \sigma(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for continuous actions}
+    \end{cases}                 \\
+    q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}) & = \text{MLP}_{\text{value}}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta})
+\end{align}
+
+For continuous action spaces, the policy network outputs the mean $\mu$ and standard deviation $\sigma$ of a Gaussian distribution, where actions are sampled using the reparameterization trick.
+Then, hyperbolic tangent function is applied to bound the actions within a desired range, with appropriate adjustments to the log probability calculation.
+
+The SAC framework is particularly well-suited for social learning environments due to its entropy regularization, which promotes exploration and prevents premature convergence to suboptimal equilibria.
+By supporting both categorical distributions for discrete action spaces and Gaussian distributions for continuous action spaces, the policy network can express uncertainty about optimal actions—crucial in partially observable settings where perfect inference is rarely possible.
+The value functions measure expected returns conditioned not only on the agent's belief state but also on inferred representations of other agents' policies, enabling strategic reasoning about the long-term consequences of actions in a multi-agent context.
+The RL module is optimized using three objectives, each addressing a different aspect of the learning problem:
+
+\subparagraph{Value Function Objective} POLARIS supports both discounted and average reward formulations to accommodate different types of social learning problems. For discounted returns:
+\begin{align}
+    J^i_q(\psi^i_{\beta}) & = \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
+    y                     & = r^i + \gamma \cdot v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+\end{align}
+
+where $\gamma \in [0, 1)$ is the discount factor. This formulation is appropriate for scenarios with finite horizons or where near-term performance is particularly valued.
+
+For average reward:
+\begin{align}
+    J^i_q(\psi^i_{\beta}, \rho^i_{\theta^i}) & = \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
+    y                                        & = r^i - \rho^i_{\theta^i} + v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+\end{align}
+
+The average reward formulation better captures long-run learning dynamics and asymptotic behavior by equally valuing rewards across all future time periods.
+By supporting both approaches, POLARIS can be tailored to match the specific characteristics of different social learning scenarios without requiring structural changes to the architecture.
+
+\subparagraph{Policy Objective} Maximizes expected value plus entropy:
+\begin{align}
+    J^i_{\pi}(\theta^i) & = \mathbb{E}_{D^i}\left[\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \sum_{\boldsymbol{a}^{-i}} \pi^{-i}(\boldsymbol{a}^{-i}|\boldsymbol{b}^{-i}, \boldsymbol{\hat{z}}^{-i}) \min_{\beta=1,2} q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, a^i, \boldsymbol{a}^{-i}; \psi^i_{\beta}) \right.
+\\
+                        & \quad \left. + \alpha_e H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))\right]
+\end{align}
+
+For discrete action spaces, the summation and entropy terms are computed directly over the action probabilities.
+For continuous action spaces, the expectation is approximated using samples from the policy, and the entropy term is calculated as:
+\begin{align}
+    H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) =
+    \begin{cases}
+        -\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \log \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) & \text{for discrete actions}   \\
+        \frac{1}{2}\log\det(2\pi e \sigma^2(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))                                           & \text{for continuous actions}
+    \end{cases}
+\end{align}
+
+The entropy calculation must also account for the hyperbolic tangent transformation using the change of variables formula.
+
+The policy objective combines expected future returns with an entropy bonus, creating a balance between exploitation and exploration.
+The entropy term encourages the policy to maintain stochasticity, preventing premature convergence to deterministic policies that might be suboptimal in partially observable settings.
+The use of the minimum value across dual Q-networks helps mitigate overestimation bias—a persistent challenge in Q-learning approaches.
+This is particularly important in social learning contexts where overestimated values can lead to overly optimistic strategies that fail to account for the strategic adaptations of other agents.
+
+\subsubsection{Advantage-Weighted Transformer Training} A key innovation in POLARIS is the use of advantage-weighted training for the belief processor:
+\begin{align}
+    J^i_{\text{transformer}}(\psi^i_{\text{Transformer}}) & = \mathbb{E}_{D^i}\left[A^i(b^i, a^i) \cdot \text{BCE}(\mathbb{P}(s|b^i), o^i_{t+1})\right]
+\end{align}
+
+where $A^i(b^i, a^i)$ is the advantage function and BCE is binary cross-entropy loss.
+This objective bridges belief formation and policy optimization in a novel way.
+By weighting the belief update loss with the advantage function, the Transformer is encouraged to generate belief states that not only accurately predict future observations but also lead to high-value actions.
+In traditional partially observable reinforcement learning, belief updates are typically performed independently of policy optimization.
+By contrast, POLARIS creates a direct pathway for policy performance to influence belief formation, prioritizing informative aspects of the state space that have the greatest impact on decision quality.
+This approach is particularly valuable in social learning contexts, where certain beliefs about others' strategies may be more consequential than others for effective coordination or competition.
+
+\subsubsection{Catastrophic Forgetting Prevention}
+
+In social learning environments, the underlying state of the world often remains fixed during an episode, but varies across episodes.
+This creates a continual learning challenge: agents must adapt to new states while retaining knowledge about previously encountered states.
+Without proper mechanisms, neural networks tend to overwrite previously learned representations when adapting to new conditions—a phenomenon known as catastrophic forgetting \citep{vandeven2024continuallearningcatastrophicforgetting}.
+POLARIS addresses this challenge through Elastic Weight Consolidation (EWC), which selectively preserves important parameters for previously encountered states while allowing flexibility for adaptation.
+EWC augments the standard training objective with a regularization term that penalizes significant changes to parameters critical for performance in previously encountered states:
+
+\begin{align}
+    L_{\text{EWC}}(\theta) = L(\theta) + \sum_i \frac{\lambda}{2} F^i (\theta^i - {\theta^i}^*)^2
+\end{align}
+
+where $\theta^*$ represents parameters that performed well on previous tasks, $F^i$ is the Fisher information matrix that measures parameter importance, and $\lambda$ controls the strength of regularization.
+The Fisher information matrix provides a principled way to identify which parameters are most crucial for previously learned tasks, calculated using gradients of the log-likelihood of the model's output with respect to the parameters on data from previously encountered states.
+
+Crucially, POLARIS introduces a dynamic mechanism that automatically adjusts the EWC importance factor based on observed performance:
+
+\begin{align}
+    \lambda_t =
+    \begin{cases}
+        \lambda_{t-1} \cdot 0.8 & \text{if loss ratio} > 1.5 \text{ (loss increasing too much)}    \\
+        \lambda_{t-1} \cdot 1.2 & \text{if loss ratio} < 0.5 \text{ (loss decreasing too quickly)} \\
+        \lambda_{t-1}           & \text{otherwise}
+    \end{cases}
+\end{align}
+
+This adaptive approach monitors the ratio between current and previous loss values, reducing the EWC importance when the loss is increasing too rapidly (indicating difficulty learning new information due to excessive preservation of old parameters) and increasing it when the loss is decreasing too quickly (suggesting potential forgetting of valuable past knowledge).
+The implementation also includes both L1 and L2 penalties with adaptive weighting between them, transitioning from more L2 regularization for early tasks to more L1 regularization for later tasks, encouraging sparser updates as the model accumulates more knowledge from different states.
+
+\subsection{Training Process}
+
+The overall training process interleaves updates to the three modules, ensuring that improvements in one component can benefit the others within each training iteration.
+Algorithm 1 outlines the complete POLARIS training procedure for a single agent.
+
+\begin{algorithm}[H]
+    \caption{POLARIS Training Algorithm for Single Agent}
+    \begin{algorithmic}[1]
+        \State Initialize belief processor, inference module, policy and value networks with parameters $\psi^i_{\text{Transformer}}$, $\phi^i$, $\theta^i$, $\psi^i_{\beta}$
+        \State Initialize replay buffer $D^i$, initial belief $b^i_0$, and latent state $\boldsymbol{\hat{z}}^{-i}_0$
+        \State Determine action space type (discrete or continuous)
+        \For{each step $t$}
+        \State Observe signal $o^i_t$ and joint action $\boldsymbol{a}_{t-1}$
+        \State Update belief: $b^i_t, \mathbb{P}(s|b^i_t) = f_{\text{Transformer}}(b^i_{t-1}, o^i_t, \boldsymbol{a}_{t-1}; \psi^i_{\text{Transformer}})$
+        \State Select action:
+        \If{discrete action space}
+        \State $a^i_t \sim \pi^i(\cdot|b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$ \Comment{Sample from categorical distribution}
+        \Else
+        \State $\mu, \sigma = \text{MLP}_{\text{policy}}(b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$
+        \State $\epsilon \sim \mathcal{N}(0, I)$
+        \State $a^i_t = \tanh(\mu + \sigma \odot \epsilon)$ \Comment{Sample using reparameterization trick}
+        \EndIf
+        \State Execute action, observe reward $r^i_t$ and next signal $o^i_{t+1}$
+        \State Infer latent: $\boldsymbol{\hat{z}}^{-i}_{t+1} = f_{\text{GNN}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i)$
+        \State Store transition in replay buffer
+        \If{update step}
+        \State Sample batch $B$ from replay buffer $D^i$
+        \State Update inference module: $\phi^i \leftarrow \phi^i - \alpha_{\phi} \nabla_{\phi^i} J^i_{\text{elbo}}(B)$
+        \State Update value networks: $\psi^i_{\beta} \leftarrow \psi^i_{\beta} - \alpha_{\psi} \nabla_{\psi^i_{\beta}} J^i_{q}(B)$
+        \State Update policy: $\theta^i \leftarrow \theta^i - \alpha_{\theta} \nabla_{\theta^i} J^i_{\pi}(B)$ \Comment{Using appropriate entropy calculation}
+        \State Update belief processor: $\psi^i_{\text{Transformer}} \leftarrow \psi^i_{\text{Transformer}} - \alpha_{\psi} \nabla_{\psi^i_{\text{Transformer}}} J^i_{\text{transformer}}(B)$
+        \State Update target networks: $\bar{\psi}^i_{\beta} \leftarrow \tau \psi^i_{\beta} + (1-\tau) \bar{\psi}^i_{\beta}$
+        \If{true state has changed}
+        \State Calculate Fisher matrices from current replay buffer
+        \State Register task with EWC
+        \EndIf
+        \EndIf
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+The algorithm follows a sequential process where each agent first updates its belief state based on new observations and the joint actions of all agents using the Transformer-based belief processor (line 6).
+Based on this updated belief and the current inference of other agents' latent states, the agent selects an action using its stochastic policy—sampling from a categorical distribution for discrete action spaces (line 9) or using the reparameterization trick for continuous action spaces (lines 11-13).
+After executing this action and observing the reward and next observation (line 15), the agent updates its inference of other agents' latent states using the GNN-based inference module (line 16).
+All of these experiences are stored in a replay buffer for later training (line 17).
+
+At designated update steps, the agent samples a batch of transitions from its replay buffer and uses these to update all network components.
+The inference module is updated first (line 19) to improve predictions of other agents' actions using the ELBO objective.
+Next, the value networks are updated (line 20) to better estimate expected returns.
+The policy network is then updated (line 21) to maximize expected value and entropy.
+Finally, the belief processor is updated (line 22) using the advantage-weighted training approach.
+Target networks, used for stable learning in the SAC framework, are updated using a weighted average of the current and target parameters (line 23).
+
+A crucial feature of POLARIS is its adaptive response to changes in the environment state.
+When the true state changes (line 24), the algorithm calculates Fisher information matrices from the current replay buffer (line 25) and registers a new task with the EWC mechanism (line 26), preserving important knowledge from the previous state while allowing adaptation to the new state.
+
+In the next chapter, we demonstrate the practical application of our POAMG framework and the POLARIS algorithm to canonical social learning scenarios from economic theory.
+The versatility of our approach is particularly evident in its ability to seamlessly handle both continuous and discrete action spaces, as well as varying types of return objectives.
+This capability proves essential when implementing strategic experimentation models with continuous allocation decisions and average reward objectives, and learning without experimentation models with discrete signaling actions and discounted reward objectives.
+Through these implementations, we validate theoretical predictions from economic models while uncovering new insights about strategic adaptation in partially observable multi-agent systems that would be difficult to obtain through purely analytical approaches.
+The experimental results not only demonstrate the effectiveness of our theoretical framework but also highlight how computational methods can complement and extend traditional economic analysis of social learning phenomena.
+
+\chapter{Results}
+
+Building on the theoretical framework of Partially Observable Active Markov Games developed in the previous section, we now apply our POLARIS algorithm to concrete social learning scenarios.
+This implementation demonstrates how our approach bridges theoretical economic models with computational reinforcement learning methods, allowing us to validate theoretical predictions while uncovering new insights about strategic adaptation in partial observability settings.
+
+We implement our Partially Observable Active Markov Game framework to model the two canonical social learning scenarios discussed in the background section: strategic experimentation with observable rewards and learning without experimentation through action observation.
+By reformulating these economic models as POAMGs, we demonstrate how our framework can capture the sophisticated learning dynamics present in these scenarios while enabling the discovery of complex strategies through our POLARIS algorithm.
+\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/POLARIS}.}
+
+\section{Strategic Experimentation}
+
+We reformulate the strategic experimentation model of \citet{keller2020undiscounted} as a Partially Observable Active Markov Game.
+This framework analyzes undiscounted continuous-time games where a number of symmetric players act non-cooperatively, trying to learn an unknown state of the world governing the risky arm's expected payoff.
+The state space $S = \{0,1,\ldots,m\}$ represents possible states of the world, with a deterministic transition function since the underlying state remains constant throughout the interaction.
+Each agent's action space $A^i = [0,1]$ represents the fraction of resources allocated to the risky arm at each decision point, creating a continuous action space that allows for nuanced exploration strategies.
+
+While the original model operates in continuous time with Lévy processes, our POAMG implementation discretizes time using the Euler-Maruyama scheme \citep{kloeden1992numerical, platen1999introduction} for both the background signal and the agents' payoff processes.
+This numerical method is widely used for approximating solutions to stochastic differential equations driven by both Brownian motion and Poisson processes.
+
+The agents receive a public signal produced by the background process, which leads to the observation function:
+
+\begin{equation}
+    O^i(s, o) = \mathbb{P}(o_t | B_{t-1:t})
+\end{equation}
+
+where $o_t$ represents the observation at discrete time step $t$ and $B_{t-1:t}$ represents the signal increment in discrete time.
+To address the time-dependent nature of Lévy processes while maintaining compatibility with our POAMG framework, we formulate the reward function for each agent $i$ as:
+
+\begin{equation}
+    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
+\end{equation}
+where $\Delta t$ is the discretization time step,
+\begin{equation}
+    X^i_{t-1:t} = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t,
+\end{equation}
+$(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^i_t$ is the increment of the compound Poisson processes over the interval $[t-1, t]$.
+This normalization converts accumulated rewards to instantaneous reward rates, preserving the incentive structure of the original model.
+A comprehensive mathematical treatment of this discretization approach, including convergence properties and the preservation of strategic incentives, is provided in Appendix \ref{appendix:levy_discretization}.
+
+Each agent observes the increments in the public background signal, their own payoff process (dependent on their allocation $a^i$ to the risky arm and the true state $\omega$), and the allocations together with the rewards of all other agents.
+The unique feature of the strategic experimentation model is the explicit form of the symmetric Markov perfect equilibrium, which depends only on three factors: the safe payoff, the expected current payoff of the risky arm, and the expected full-information payoff.
+To validate this theoretical result, we configure POLARIS to measure: (1) The cutoff belief at which agents switch between the safe and risky arm
+(2) The relationship between individual experimentation intensity and group experimentation intensity
+(3) Free-riding behavior as a function of the number of players
+(4) Strategy independence from the specific payoff-generating process
+\iffalse
+    For experimental validation, we implement three distinct payoff-generating processes that preserve the same reward statistics: pure Brownian motion with unknown drift, pure Poisson processes with unknown intensity, and mixed Lévy processes with both continuous and jump components.
+In all three cases, the theory predicts identical equilibrium strategies when expressed in terms of the incentive to experiment $I(\pi) = \frac{f(\pi)-s}{s-m(\pi)}$ when $m(\pi) < s$, and $I(\pi) = \infty$ otherwise, where $\pi$ represents the belief state.
+\fi
+To measure convergence to equilibrium behavior, we track the Kullback-Leibler divergence (KL divergence) between agents' actual strategies and the theoretically optimal strategy specified in Keller and Rady's work.
+The KL divergence is calculated as
+
+\begin{equation}
+    D_{KL}(P||Q) = \sum_{x} P(x) \log\frac{P(x)}{Q(x)},
+\end{equation}
+
+where $P$ represents the agent's learned policy distribution and $Q$ represents the theoretical optimal policy distribution at each belief state:
+
+\begin{equation}
+    a^*(b) =
+    \begin{cases}
+        0                    & \text{if } I(b) \leq k_0,            \\
+        \frac{I(b)-k_0}{n-1} & \text{if } k_0 < I(b) < k_0 + n - 1, \\
+        1                    & \text{if } I(b) \geq k_0 + n - 1.
+    \end{cases}
+\end{equation}
+
+\iffalse
+    We also assess the rate of social learning by measuring the expected time until agents' posterior beliefs concentrate within an $\epsilon$-neighborhood of the true state.
+The background information in this model ensures exponentially fast convergence, which is empirically validated by fitting an exponential decay curve to the mean distance between current beliefs and true state across multiple simulation runs.
+\fi
+For varying group sizes $n \in \{2,4,8,16\}$, we measure the relationship between individual and group experimentation.
+The theory predicts that the set of beliefs for which no experimentation occurs remains unchanged as $n$ increases—a stark manifestation of free-riding behavior.
+Additionally, the theory predicts that in regions of partial experimentation, the intensity per agent will decrease with $n$, while the total group intensity increases.
+These predictions create testable patterns that our POLARIS implementation can validate.
+\iffalse
+    An important methodological insight from this implementation is the impact of the background signal $k_0$ on learning dynamics.
+As $k_0$ approaches zero, the equilibrium strategy converges monotonically to a well-defined limit.
+However, without background information, the strong long-run average criterion would yield an expectation of minus infinity, making the framework inapplicable.
+We thus implement a parametric analysis with diminishing values of $k_0$ to approximate the limit behavior predicted by the theory.
+\fi
+\iffalse
+    Our experimental results confirm that POLARIS agents converge to the theoretically predicted equilibrium regardless of the specific payoff-generating process employed.
+This validation demonstrates the framework's ability to capture the sophisticated strategic considerations of undiscounted multi-agent learning, providing computational support for the theoretical predictions of Keller and Rady.
+Furthermore, our results show that the mixed Lévy process case—not analytically tractable in the original paper due to its complexity—exhibits the same qualitative behavior as the pure Brownian and Poisson cases, providing evidence for the robustness of the theoretical framework.
+\fi
+
+\section{Learning Without Experimentation}
+
+We reformulate the learning without experimentation model of \citet{brandl2024} as a Partially Observable Active Markov Game.
+In this formulation, the state space $S = \{s^1, s^2, \ldots, s^m\}$ represents possible states of the world, with a deterministic transition function since the state remains constant.
+Each agent's action space $A^i = \{a^1, a^2, \ldots, a^m\}$ corresponds to potential states, where $a^j$ is the unique optimal action is state $s^j$.
+In addition to observing their neighbors' actions, each agent receives a private signal $o^i_t \in \Omega^i = S$ drawn from distribution:
+\begin{equation*}
+    O^i(s,o) =
+    \begin{cases}
+        q               & \text{if } s = o \\
+        \frac{1-q}{m-1} & \text{otherwise}
+    \end{cases}
+\end{equation*}
+where $q > 1/m$ is the signal accuracy. Since agents don't observe real rewards in this model, we construct an observed reward function that facilitates learning:
+
+\begin{equation*}
+    R^i(s_t, a^i_t) = v(o^i_t, a^i_t) = \frac{q \cdot \mathbb{I}_{\{a^i_t = \varphi(o^i_t)\}} - (1 - q) \cdot \mathbb{I}_{\{a^i_t \neq \varphi(o^i_t)\}}}{2q - 1}
+\end{equation*}
+
+where $\varphi$ maps states to their corresponding correct actions.
+\footnote{Formally, the mapping $\varphi: S \rightarrow A$ is a bijective function defined as $\varphi(s^j) = a^j$ for all $j \in \{1,2,...,m\}$, associating each state with the action having the same index.} This construction ensures the expected reward matches the true utility function in expectation: \footnote{See \ref{appendix:observed_reward_derivation} for a detailed derivation and the formulation for a generic dimension $m$.}
+
+\begin{equation*}
+    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a) = \mathbb{I}_{\{a = \varphi(s)\}}.
+\end{equation*}
+
+For methodological soundness, we distinguish between two learning processes: algorithm learning (neural network training via gradient descent) and belief learning (agents refining beliefs about the underlying state based on observations).
+Brandl's theoretical analysis focuses on the second type—how quickly agents converge to correct actions as they accumulate information over time, assuming fixed information-processing strategies.
+To properly measure the asymptotic learning rates predicted by Brandl's theory, we employ a two-phase methodology: training with both types of learning occurring simultaneously, followed by post-training evaluation where we freeze network parameters while still allowing belief states to update based on new observations.
+
+The learning rate in Brandl's framework is defined through asymptotic behavior:
+
+\begin{equation*}
+    r = \lim_{t\to\infty} -\frac{1}{t}\log \mathbb{P}(a^i_t \neq a_\omega)
+\end{equation*}
+
+During post-training evaluation, we collect empirical mistake probabilities across many episodes, fit them to the exponential decay model $\mathbb{P}(a^i_t \neq a_\omega) \approx e^{-rt}$ using log-linear regression, and extract the empirical learning rate for comparison with theoretical bounds.
+
+To validate scaling properties with network size, we implement a systematic protocol that trains separate POLARIS instances across different network configurations (complete, ring, star, random) and sizes (from very small n=2,3,4 to large n=30,50 where feasible).
+
+For the binary case where $S = A = \{0,1\}$ and signal accuracy is $q = 0.75$, the theoretical bounds from \citet{brandl2024} are: autarky rate $r_{aut} \approx 0.14$ (learning rate of a single isolated agent), coordination rate $r_{crd} \approx 0.55$ (achievable rate with coordination), and bounded rate $r_{bdd} \approx 1.10$ (upper bound on any agent's learning rate).
+
+Our experiments validate two key theoretical predictions.
+First, the Learning Barrier (Theorem 1) states that for any strategy profile, there exists some agent whose learning rate is bounded by $r_{bdd}$, regardless of network size or structure.
+Second, the Coordination Benefits (Theorem 2) predicts that in sufficiently large, strongly connected networks, there exist strategies enabling all agents to learn faster than in autarky.
+
+\iffalse
+    These experiments demonstrate that our POAMG framework, implemented through POLARIS, provides an effective computational approach for studying social learning dynamics.
+By successfully reproducing the theoretical predictions of \citet{brandl2024}, we validate the applicability of our framework for investigating complex social learning phenomena in networked environments, while offering additional computational tools to explore mechanisms beyond what analytical models alone can capture.
+
+    As demonstrated through these applications, POLARIS's flexibility in handling both continuous action spaces (as in the strategic experimentation model) and discrete action spaces (as in the learning without experimentation model) makes it a versatile tool for studying a wide range of social learning scenarios.
+This capability allows researchers to model and analyze various economic scenarios without being constrained by the nature of the action space, further bridging the gap between theoretical economic models and computational approaches to multi-agent learning.
+\fi
+
+% Appendix
+\newpage
+\appendix
+\addcontentsline{toc}{chapter}{Appendices}
 \setcounter{proposition}{0}
@@
 of other agents provide stronger evidence about the true state through beliefs.
+
+% Bibliography
+\newpage
+\renewcommand{\bibname}{References}
+\renewcommand{\thechapter}{R}
+\addcontentsline{toc}{chapter}{References}
+\bibliographystyle{apacite}
+\bibliography{refs}
+\renewcommand{\thechapter}{\arabic{chapter}} % Reset chapter numbering
+
+% Statement of Authorship (as required)
+\newpage
+\section*{Statement of Authorship}
+
+I hereby confirm that the work presented has been performed and interpreted solely by myself except for where I explicitly identified the contrary.
+I assure that this work has not been presented in any other form for the fulfillment of any other degree or qualification.
+Ideas taken from other works in letter and in spirit are identified in every single case.\\[2cm]
+
+\noindent Date: \rule{4cm}{0.5pt} \hfill Signature: \rule{6cm}{0.5pt}
+
+\end{document}

### 2025-05-26 paper/intro.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
-\setcounter{proposition}{0}
-\setcounter{assumption}{0}
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
+The study of how individuals and groups learn from each other's actions and experiences has been a central focus in economic theory for decades.
+From the seminal contributions on information cascades by \citet{banerjee1992simple} and \citet{bikhchandani1992theory} to more recent explorations of learning in networks \citep{acemoglu2011bayesian, golub2010naive}, economic research has sought to understand how social interactions shape beliefs, decisions, and collective outcomes.
+Traditional economic models have provided valuable insights into phenomena such as herding behavior, where individuals rationally ignore their private information to follow the observed actions of predecessors.
+However, these models often rely on simplified assumptions about agents' behavior and reasoning processes, frequently restricting analysis to one-shot sequential decisions or steady-state equilibria rather than capturing the rich dynamics of repeated interactions where agents continuously adapt their strategies based on others' evolving behaviors.
 
-\chapter{Reinforcement Learning Background}
+Meanwhile, the field of multi-agent reinforcement learning (MARL) has experienced remarkable progress in developing algorithms that enable autonomous agents to learn effective strategies in complex, interactive environments.
+Recent advances in reinforcement learning have demonstrated impressive capabilities in strategic games \citep{silver2016mastering}, cooperative problem-solving \citep{baker2020emergentreciprocityteamformation}, and competitive scenarios \citep{openai2019dota2largescale}.
+MARL offers powerful tools for modeling adaptive behavior in non-stationary environments where agents must continuously revise their strategies in response to others' changing behaviors.
+However, much of this work has focused on engineering objectives rather than modeling realistic human learning processes, limiting its applicability to fundamental questions in economic theory.
+Additionally, many MARL approaches struggle with the challenge of partial observability—a defining feature of social learning contexts where agents cannot directly observe others' private information or belief states.
 
-\label{appendix:rl_details}
-This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.
+This thesis bridges these domains by introducing a novel framework that integrates economic social learning theory with multi-agent reinforcement learning under partial observability.
+Our approach models social learning as a dynamic process where agents with limited information strategically adapt their behaviors while simultaneously learning about their environment and other agents' strategies.
+By formalizing this process through the lens of partially observable reinforcement learning, we aim to reveal new insights into how strategic adaptation influences collective outcomes and equilibrium behavior.
+This interdisciplinary synthesis addresses fundamental challenges that have constrained previous work in both economics and artificial intelligence, offering a more realistic and computationally tractable approach to modeling complex social learning dynamics.
 
-\section{Reinforcement Learning Foundations}
+The first challenge concerns non-stationarity and strategic adaptation.
+Traditional economic models of social learning typically assume that agents follow fixed, myopic decision rules or Bayesian updating procedures that do not fully account for strategic adaptation over time.
+When agents repeatedly interact and observe each other's actions, however, they may adjust their strategies in anticipation of others' learning, creating a complex web of interdependent adaptation that fundamentally alters collective learning dynamics.
+This non-stationarity—where the effective environment an agent faces changes as other agents learn—represents a central challenge that requires new modeling approaches.
+Standard MARL algorithms often treat this non-stationarity as a technical obstacle to convergence rather than an intrinsic feature of multi-agent systems that agents should explicitly reason about and strategically exploit.
 
-Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty.
-In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}.
-This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:
+The second challenge involves partial observability, which pervades social learning contexts.
+In most real-world settings, agents cannot directly observe others' private information, beliefs, or decision processes.
+Instead, they must infer these hidden states from observable actions and outcomes.
+This partial observability compounds the complexity of strategic interaction, as agents must simultaneously learn about the underlying state of the world and about the belief formation processes of others.
+Economic models have often simplified this challenge through strong assumptions about common knowledge or by focusing on one-shot sequential decisions rather than repeated interactions.
+Similarly, many MARL approaches assume full observability of the state or treat partial observability as a technical challenge to be addressed through belief state tracking, without fully incorporating its strategic implications.
 
-\begin{itemize}
-    \item $S$ is the state space, representing all possible configurations of the environment
-    \item $A$ is the action space, representing all possible decisions available to the agent
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
-    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
-    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
-\end{itemize}
+The third challenge concerns long-term strategic considerations in social learning.
+Agents often face a tension between immediate payoffs and long-term information generation.
+They may sometimes choose actions that appear suboptimal in the short term to influence the learning trajectories of others or to generate valuable information for future periods.
+For instance, in strategic experimentation contexts, agents might incur costs to explore unknown options, knowing that the resulting information will benefit both themselves and others in the future.
+Capturing these farsighted strategic considerations requires models that explicitly account for how current actions shape the future evolution of others' beliefs and behaviors—a capability that neither traditional economic models nor standard MARL algorithms fully provide.
 
-The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions.
-The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter.
-The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.
+To address these challenges, this thesis makes several interconnected contributions.
+First, we develop Partially Observable Active Markov Games (POAMGs)—a novel formalism that extends the Active Markov Game framework introduced by \citet{kim2022influencing} to partially observable settings.
+Unlike standard reinforcement learning frameworks that treat non-stationarity as a challenge to be mitigated, POAMGs incorporate policy evolution as an integral part of the environment dynamics, allowing agents to reason about and strategically influence this evolution process.
+POAMGs explicitly model how agents' policies evolve over time based on observations and interactions, while accounting for the fundamental constraints imposed by partial observability.
+This formalism provides a mathematically rigorous foundation for analyzing complex social learning dynamics that involve repeated interactions, adaptive strategies, and incomplete information.
 
-The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs.
-This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem.
-However, this assumption becomes problematic in multi-agent settings, as we will discuss next.
+Second, we provide a thorough theoretical analysis of convergence and equilibrium properties in POAMGs.
+We establish conditions under which the joint process of states, beliefs, and policy parameters converges to a unique stochastically stable distribution, ensuring that our models have well-defined limiting behavior despite the inherent non-stationarity of multi-agent learning.
+We derive policy gradient theorems for average and discounted reward objectives, providing a solid foundation for algorithm development.
+We also extend our framework to continuous-time dynamics through stochastic differential equations, enabling a wider range of applications.
+Our analysis illuminates the relationship between traditional game-theoretic equilibrium concepts and the more general notion of active equilibrium that emerges in our framework, offering new insights into equilibrium selection and stability in social learning contexts.
 
-\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}
+Third, we introduce POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm for learning in POAMGs.
+POLARIS extends previous algorithms to partially observable settings through an integrated architecture with three core components: a belief processing module that tracks agents' information states using Transformer models; an inference learning module that predicts the policy evolution of other agents through variational methods; and a reinforcement learning module that optimizes policies based on average or discounted reward criteria, supporting both discrete and continuous action spaces.
+This integrated approach enables agents to learn sophisticated strategies that account for both the partial observability of the environment and the learning dynamics of other agents—capabilities that are essential for modeling realistic social learning processes.
 
-Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}.
-MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}.
-These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:
+Fourth, we apply our framework to two canonical social learning scenarios from economic theory.
+The first application focuses on strategic experimentation, building on the models of \citet{bolton1999strategic} and \citet{keller2020undiscounted}, where agents learn optimal actions through trial and error with observable rewards.
+The second application examines learning without experimentation, extending the frameworks of \citet{huang2024learning} and \citet{brandl2024}, where agents form beliefs primarily by observing others' actions rather than receiving direct feedback from the environment.
+Our analysis demonstrates how our approach can model phenomena such as free-riding on others' information production, strategic teaching, information cascades, and confounded learning under more realistic assumptions about agents' reasoning capabilities and strategic sophistication.
 
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space, shared among all agents
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\gamma \in [0, 1)$ is the discount factor
-\end{itemize}
-MARL introduces several fundamental challenges beyond those encountered in single-agent RL.
-The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system.
-Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}.
-In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions.
-MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings.
-Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.
+Through these applications, we illustrate how bridging economic theory and MARL can enhance our understanding of social learning processes.
+Our POAMG framework provides a more realistic model of how partially rational agents learn from each other in complex, partially observable environments.
+At the same time, it offers practical algorithms for computing equilibrium strategies that traditional economic approaches might find intractable.
+The POLARIS algorithm demonstrates how techniques from deep reinforcement learning and approximate inference can be adapted to tackle the specific challenges of social learning, offering a computationally feasible method for simulating and analyzing complex multi-agent learning dynamics.
 
-\section{The Non-Stationarity Challenge}
-The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}.
-To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent.
-When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$.
-From agent $i$'s perspective, the effective transition function becomes:
-\begin{equation}
-    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
-\end{equation}
-where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$.
-When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$.
-This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL.
-When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}.
-This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}.
-Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}.
-The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}.
-These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.
+The remainder of this thesis is organized as follows: Chapter 2 reviews the relevant literature on social learning in economic theory and multi-agent reinforcement learning, emphasizing the complementary strengths and limitations of these approaches and identifying opportunities for cross-fertilization.
+Chapter 3 introduces our theoretical framework, developing the formalism of Partially Observable Active Markov Games and deriving key results on convergence, policy gradients, and equilibrium concepts, as well as presenting the POLARIS algorithm, detailing its components, implementation considerations, and theoretical justifications.
+Chapter 4 applies our framework to strategic experimentation and learning without experimentation, demonstrating how POLARIS captures sophisticated social learning dynamics in these contexts.
+Chapter 5 concludes with a discussion of implications, limitations, and directions for future research.
 
-\section{Traditional Approaches to Non-Stationarity}
-Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:
+By integrating perspectives from economic theory and multi-agent reinforcement learning, this thesis aims to enhance our understanding of social learning processes and provide new tools for modeling complex strategic interactions in partially observable environments.
+The insights gained may not only advance theoretical knowledge but also inform the design of platforms and institutions that facilitate efficient collective learning and decision-making in diverse contexts, from financial markets and organizational learning to online social networks and collaborative scientific endeavors.
+Moreover, by demonstrating the value of MARL techniques for addressing classical questions in economic theory, we hope to encourage further cross-disciplinary work that leverages complementary insights from these rich intellectual traditions.
 
-\subsection{Independent Learning}
-The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}.
-This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents.
-Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences.
-While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.
-
-\subsection{Centralized Training with Decentralized Execution}
-To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}.
-In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.
-
-Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution.
-Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline.
-The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies.
-While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.
-
-\subsection{Opponent Modeling and Population-Based Training}
-Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}.
-This can involve predicting other agents' policies, types, or learning dynamics.
-Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning.
-Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.
-
-The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity.
-While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.
-
-\subsection{Equilibrium Learning and Stability Concepts}
-Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}.
-These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate.
-Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games.
-Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.
-
-The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence.
-While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality.
-Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.
-
-\subsection{Meta-Learning for Non-Stationarity}
-Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}.
-These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem.
-Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.
-
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents.
-While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.
-
-\section{Active Markov Games}
-
-Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}.
-They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.
-
-\subsection{Formal Definition}
-
-An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
-    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
-\end{itemize}
-Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state.
-The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates.
-At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$.
-Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$.
-Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$.
-This process continues until non-stationary policies converge to a recurrent set of joint policies.
-The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.
-
-\subsection{Augmented Transition Function and Stationarity}
-
-The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions.
-To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games.
-In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions.
-However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions.
-The augmented transition function becomes:
-
-\begin{equation}
-    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
-\end{equation}
-The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories.
-By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one.
-This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.
-
-\subsection{Theoretical Properties and Convergence}
-
-Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:
-
-\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:
-
-\begin{equation}
-    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
-\end{equation}
-
-where $\ell = t\%k$ with $\%$ denoting the modulo operation.
-This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies.
-The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence.
-To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}.
-These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.
-
-\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:
-
-\begin{equation}
-    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
-        \begin{array}{c}
-            s_0=s, \theta_0=\theta,                                              \\
-            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
-            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
-            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
-        \end{array}
-        \right]
-\end{equation}
-
-where  $0:T$ denotes the sequence from time $0$ to $T$.
-This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.
-
-\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium.
-An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:
-
-\begin{equation}
-    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
-\end{equation}
-for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$.
-This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system.
-The active equilibrium generalizes several classic solution concepts in game theory.
-Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively.
-Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively.
-This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.
-
-Active Markov Games address the non-stationarity challenge in several fundamental ways.
-By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated.
-The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors.
-Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates.
-Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees.
-Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.
-
-\subsection{Practical Implementations}
-
-Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL.
-Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner.
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games.
-These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.
-
-\section{Extension to Partial Observability}
-
-While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state.
-In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents.
-This partial observability introduces additional challenges for multi-agent learning.
-The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions.
-In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}.
-Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning.
-The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.
-
-In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state.
-Theoretical formulations, as established by Meuleau et al.
-\cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$.
-However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation.
-Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}.
-These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics.
-In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time.
-For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.
-
-\chapter{Proofs Regarding Average Returns}
-
-This section provides the mathematical foundations and detailed proofs for the
-key theoretical results in our Partially Observable Active Markov Game framework
-with average return objectives. We establish the Markov properties of belief transitions
-and joint processes, prove the existence and uniqueness of stochastically stable
-distributions, and derive the policy gradient theorem for average return optimization.
-
-\section{Markov Property of the Joint Process}
-\label{appendix:stochasticallystable}We first establish the Markov properties of
-belief state transitions and the joint process comprising states, belief states,
-and policy parameters. These properties form the foundation for our convergence analysis.
-
-\begin{lemma}[Markov Property of Belief Transitions]
-    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
-    a Markov process under a fixed policy $\pi$, meaning that the distribution of
-    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
-    not on earlier beliefs, actions, or observations.
-\end{lemma}
-
-\begin{proof}
-    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
-    relevant information from the history of observations and actions up to time
-    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
-    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
-            ^{i}$ through the rule:
-    \begin{align}
-        b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
-    \end{align}
-
-    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
-    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
-    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
-    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
-    property.
-\end{proof}
-
-\begin{remark}[Transformer-Based Belief Representation]
-    In practice, transformer architectures can be used to represent and
-    update belief states. In such cases, the belief state is updated
-    through an attention-based mechanism of the form:
-    \begin{equation}
-        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
-    \end{equation}
-
-    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
-    observation and previous belief state through self-attention layers, satisfying the Markov property
-    while capturing complex dependencies between observations and beliefs.
-\end{remark}
-Next, we establish the Markov property of the joint process.
-\begin{lemma}[Markov Property of Joint Process]
-    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
-    a Markov process under periodic policy updates, meaning that the distribution
-    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
-    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
-    states.
-\end{lemma}
-\begin{proof}
-    The state transitions are by definition only dependent on current state and current
-    actions. The remaining parts can be analyzed as follows:
-
-    \textbf{1. Belief
-        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
-    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
-    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
-        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
-    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
-    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
-    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.
-
-    \textbf{2. Policy parameter
-        update:} At every time step $t$, policy parameters are updated according to $U(
-        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
-    Under the Markovian policy update assumption, the update depends only on $\theta
-        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
-        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
-    probability
-    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t}))$
-    depends only on the current state
-    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
-    of states, establishing the Markov property.
-\end{proof}
-\section{Convergence}
-Having established the Markov properties, we now analyze the convergence
-behavior of the joint process to a unique stochastically stable distribution. This
-convergence result is crucial for developing optimization objectives in our framework.
-\begin{theorem}[Stochastically Stable Distribution]
-    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
-    defined by $\epsilon$-perturbed policy update functions converge to the unique
-    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
-        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
-\end{theorem}
-
-\begin{proof}
-    We establish the convergence to the unique stochastically stable distribution by
-    showing that a perturbed Markov process of a partially observable active Markov
-    game is regular. First, let us introduce a small perturbation to the policy update
-    functions:
-    \begin{align}
-        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
-    \end{align}
-
-    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
-    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
-    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
-    probability of transitioning to any other configuration
-    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
-        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
-    probability:
-    \begin{align}
-        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
-                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
-                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
-    \end{align}
-
-    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
-    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
-    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
-    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
-    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
-    of the joint process. We will show that there must exist a path with positive probability
-    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
-    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
-        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
-        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
-    second as follows:
-
-    \textbf{1. Policy Parameter Transition:} Due to the
-    $\epsilon$-perturbation in update functions, there is a positive probability of
-    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
-        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
-    \end{align}
-
-    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
-    $\boldsymbol{\theta}_{2}$.
-
-    \textbf{2. State Transition:} By the communicating
-    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
-    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
-    such that:
-    \begin{align}
-        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
-    \end{align}
-
-    Given the relationship between policies and actions, this sequence of actions has
-    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
-    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
-    for all required actions.
-
-    \textbf{3. Belief State Transition:} By the communicating belief-state
-    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
-        B$, there exists a sequence of observations
-    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
-    \end{align}
-
-    Since observations depend on states, which can be influenced through actions,
-    and actions are determined by policies, there is a positive probability path from
-    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
-    and policy parameters. Combining these three components, we can construct a path
-    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
-        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
-    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
-    classes of the perturbed joint process. Since we have shown that the perturbed
-    joint process has only one recurrent class, it is a regular Markov process. Following
-    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
-    process on a finite state space possesses a unique stationary distribution
-    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
-    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
-    converges to a limit $\mu^{*}$, which is the unique stochastically stable
-    distribution of the original, unperturbed process. Therefore, under the given conditions,
-    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
-    partially observable active Markov game possesses a unique stochastically
-    stable distribution $\mu^{*}$.
-\end{proof}
-\section{Policy Gradient Theorem}
-Having established the convergence to a unique stochastically stable distribution,
-we now derive the policy gradient theorem for optimization in our framework. This
-theorem provides the mathematical foundation for gradient-based algorithms to maximize
-the average return objective.
-\label{appendix:avg_gradient}
-\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
-        Theorem]
-    The gradient of the active average reward objective
-    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
-    setting is:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
-    the belief update function.
-\end{theorem}
-
-\begin{proof}
-    We first define the average reward objective in the partially observable setting:
-    \begin{align}
-        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
-                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
-    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
-        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
-    differential value function $v^{i}_{\theta^i}$ represents the expected total
-    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
-        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
-        ^{i}_{\theta^i}$:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
-    \end{align}
-
-    Following the Bellman equation derivation principles, we can express
-    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
-                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-    represents the belief update function that updates the belief state based on
-    the current belief, action, and new observation. We now define the action-value
-    function $q^{i}_{\theta^i}$ for the partially observable setting:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    Using this definition, we can rewrite the differential value function as:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    To derive the policy gradient, we begin by computing the gradient of the differential
-    value function with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
-                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
-                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    We expand the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                                                                  & \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
-                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting back into the original expression, we get:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Rearranging terms:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we define the transition operator that maps the expectation of a function
-    from one time step to the next:
-    \begin{align}
-        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
-                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    We can rewrite our expression as:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we take the expectation with respect to the stationary distribution
-    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
-                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    By the definition of the stationary distribution, we have:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore, the second and third terms in our expression cancel out, giving the
-    final policy gradient theorem:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-\end{proof}
-
-\chapter{Proofs Regarding Discounted Returns}
-\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
-Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
-mathematical foundation.
-\section{Transition Operator and Its Adjoint}
-To establish a rigorous framework for analyzing discounted returns in Partially
-Observable Active Markov Games, we need to formalize how value functions evolve over
-time and how probability distributions propagate through the system. This dual
-perspective is captured by two fundamental operators: the transition operator and
-its adjoint.
-
-\subsection{Definitions and Duality}
-
-We begin by defining the inner product between functions and measures, which forms
-the foundation for the duality relationship between our operators.
-
-\begin{definition}[Inner Product between Functions and Measures]
-    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
-        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
-    Lebesgue integral:
-    \begin{equation}
-        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
-        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
-        {\theta})
-    \end{equation}
-\end{definition}
-
-This inner product captures the expected value of function $f$ with respect to
-measure $\mu$, allowing us to express value functions as expectations with respect
-to appropriate measures.
-
-\begin{definition}[Transition Operator and Its Adjoint]
-    \hfill
-    \begin{enumerate}
-        \item The \textbf{transition operator}
-              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
-                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              maps a bounded measurable function to its expected value after one
-              transition:
-              \begin{align}
-                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-              \end{align}
-
-              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-              represents the belief update function.
-
-        \item The \textbf{adjoint operator}
-              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
-                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              is defined on the space of finite measures such that:
-              \begin{equation}
-                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
-              \end{equation}
-
-              for all
-              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
-              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
-    \end{enumerate}
-\end{definition}
-
-Intuitively, $\Psi$ describes how function expectations evolve forward in time,
-meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
-capturing the propagation of visitation probabilities through the system. The duality
-relationship ensures that expected values can be computed either by applying $\Psi$
-to functions or $\Psi^{*}$ to measures.
-
-\subsection{Properties of the Operators}
-
-These operators possess several important properties that facilitate our
-analysis of discounted returns:
-
-\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
-    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
-    properties:
-
-    \begin{enumerate}
-        \item \textbf{Linearity:}
-              \begin{itemize}
-                  \item For the operator: For any functions
-                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
-                        \end{align}
-
-                  \item For the adjoint: For any measures
-                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Positivity Preservation:}
-              \begin{itemize}
-                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.
-
-                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
-                            \mu$ is also non-negative.
-              \end{itemize}
-
-        \item \textbf{Preservation of Total Measure:}
-              \begin{itemize}
-                  \item For the operator: The operator preserves the constant function
-                        $\mathbf{1}$:
-                        \begin{align}
-                            \Psi \mathbf{1}= \mathbf{1}
-                        \end{align}
-
-                        where $\mathbf{1}$ represents the function that equals 1 everywhere.
-
-                  \item For the adjoint: For any measure
-                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-                        \begin{align}
-                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
-              bounded with:
-              \begin{align}
-                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
-              \end{align}
-
-              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
-                  {b},\boldsymbol{\theta})|$ is the supremum norm.
-
-        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
-              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-              \begin{align}
-                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
-                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-              \end{align}
-
-              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    We prove each property in turn:
-
-    \textbf{1. Linearity:}
-
-    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
-    \begin{align}
-         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For the adjoint: For any measurable function
-    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
-                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
-                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
-                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
-        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
-    measure.
-
-    \textbf{2. Positivity Preservation:}
-
-    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
-        )$:
-    \begin{align}
-        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
-    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
-    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
-        {\theta}) \geq 0$.
-
-    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
-    function $f \geq 0$:
-    \begin{align}
-        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
-    \end{align}
-
-    where the inequality follows from the positivity preservation of $\Psi$ and the
-    fact that $\mu$ is non-negative. Since this holds for all non-negative
-    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.
-
-    \textbf{3. Preservation of Total Measure:}
-
-    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
-    everywhere. Then:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
-    \end{align}
-
-    Since each probability distribution sums to 1, applying them sequentially
-    yields:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
-    \end{align}
-
-    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
-    \begin{align}
-        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
-    \end{align}
-
-    where we used the unit preservation property of $\Psi$. This gives:
-    \begin{align}
-        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-    \end{align}
-
-    \textbf{4. Bound Preservation:}
-
-    For any bounded function $f$ with
-    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
-        ,\boldsymbol{\theta})|$:
-    \begin{align}
-        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                           & \quad \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
-                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
-                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
-    \end{align}
-
-    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
-    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.
-
-    \textbf{5. Explicit Form of the Adjoint:}
-
-    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
-    \end{align}
-
-    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
-    \begin{align}
-        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting this back and using the definition of inner product:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
-                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
-                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}
-
-\subsection{Contraction and Propagation}
-
-The properties established above lead to two crucial results: the contraction
-property of the discounted transition operator and the propagation of
-distributions through the adjoint.
-
-\begin{lemma}[Contraction Mapping Property]
-    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
-    contraction mapping on the Banach space of bounded functions on
-    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
-    norm. Specifically, for any two functions
-    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
-    \end{align}
-\end{lemma}
-
-\begin{proof}
-    Using the linearity of $\Psi$ and its bound preservation property:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
-                                                   & \leq \gamma\|f - g\|_{\infty}
-    \end{align}
-
-    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
-    factor $\gamma$.
-\end{proof}
-
-This contraction property leads directly to the invertibility of
-$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
-in discounted settings.
-
-\begin{lemma}[Invertibility of $I - \gamma \Psi$]
-    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
-    invertible, and its inverse can be represented as a Neumann series:
-    \begin{align}
-        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    which converges absolutely in the operator norm.
-\end{lemma}
-
-\begin{proof}
-    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
-    space, then $I - T$ is invertible, with inverse given by the Neumann series
-    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
-    have:
-
-    \begin{align}
-        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    The absolute convergence follows from:
-    \begin{align}
-        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
-    \end{align}
-
-    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
-        \leq 1$ for all $t$.
-\end{proof}
-
-Finally, we establish how distributions evolve in the system through the adjoint
-operator, formalizing the propagation of probability measures.
-
-\begin{lemma}[Distribution Propagation]
-    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
-    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
-\end{lemma}
-
-\begin{proof}
-    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$:
-    \begin{align}
-        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
-                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
-                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
-                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have
-    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
-\end{proof}
-
-The concepts introduced in this section—the transition operator, its adjoint, and
-their properties—provide the mathematical foundation for analyzing discounted returns
-in Partially Observable Active Markov Games. The transition operator $\Psi$
-captures how function expectations evolve forward in time, while its adjoint $\Psi
-    ^{*}$ describes how probability distributions propagate forward in time. This
-duality is fundamental to establishing the connection between value-based and
-distribution-based perspectives in reinforcement learning.
-
-In the next section, we will use these tools to formulate Bellman equations and derive
-policy gradients for maximizing discounted returns in this complex multi-agent setting.
-\section{Bellman Equations and Value Functions}
-In this section, we establish the fundamental recursive relationships that characterize
-the discounted value functions in Partially Observable Active Markov Games.
-These relationships form the basis for our policy gradient derivation and
-practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
-of value functions, then establish the Bellman equations, and finally derive the
-gradient expressions necessary for policy optimization.
-\subsection{Well-Definedness of Value Functions}
-Before deriving recursive relationships, we first establish that the value functions
-are well-defined mathematical objects under our assumptions of bounded rewards and
-discount factors less than 1.
-\begin{lemma}[Well-Defined Value Functions]
-    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
-    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
-    action-value functions
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
-    well-defined and finite for all states, belief states, policy parameters, and actions.
-\end{lemma}
-\begin{proof}
-    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
-    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
-    \begin{align}
-        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
-                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
-                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Similarly, for the action-value function:
-    \begin{align}
-        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
-                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
-                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Thus, both value functions are well-defined and bounded.
-\end{proof}This lemma ensures that our subsequent derivations involving value
-functions are mathematically sound. The boundedness property is particularly important
-when we consider expectations and derivatives of these functions.
-\subsection{Bellman Equations for Discounted Value Functions}
-Next, we establish the recursive relationships between value functions, which
-are fundamental to dynamic programming approaches.
-\begin{lemma}[Bellman Equation for Discounted Value Functions]
-    In a Partially Observable Active Markov Game, the discounted value function
-    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{lemma}
-\begin{proof}
-    By definition, the discounted value function is:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    We can decompose this into the immediate reward and the future discounted
-    returns:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
-                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
-                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    For the first term, we have:
-    \begin{align}
-        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    For the second term, by the law of total expectation:
-    \begin{align}
-         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
-         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Combining these two terms and factoring out common terms:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
-                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
-                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
-\end{proof}The Bellman equation provides a recursive characterization of the
-value function that forms the basis for dynamic programming algorithms. This equation
-captures how current actions influence both immediate rewards and future value through
-their effects on the environment state, belief states, and policy parameters of other
-agents. The key distinction from standard Bellman equations is the inclusion of
-belief updates and policy parameter dynamics, which reflects the complex dependencies
-in partially observable multi-agent settings.
-\subsection{Policy Gradient with Respect to Value Function}
-Having established the recursive relationship for value functions, we now derive
-how the value function gradient depends on policy parameters, which is essential
-for policy optimization.
-\begin{lemma}[Policy Gradient with Respect to Value Function]
-    The gradient of the value function with respect to policy parameters $\theta^{i}$
-    can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-
-    where $\Psi$ is the transition operator defined in the previous section.
-\end{lemma}
-\begin{proof}
-    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
-    \end{align}
-
-    Applying the product rule:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    For the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
-    \end{align}
-
-    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
-        {o}'|s')$, and
-    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
-    do not depend directly on $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Using the transition operator $\Psi$, we can rewrite:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Rearranging:
-    \begin{align}
-        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
-                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
-                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-\end{proof}This lemma expresses the value function gradient in terms of an
-infinite sum of expected Q-values weighted by policy gradients and propagated
-through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
-immediate changes in policy parameters propagate through future timesteps. This
-form of the gradient is central to our discounted policy gradient theorem, which
-we will develop in the next section. The inverse operator can be represented as
-a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
-as the accumulated effect of policy changes over an infinite horizon, weighted
-by the discount factor.
-\section{Discounted Visitation Measure}
-The infinite sum formulation derived in the previous sections, while
-mathematically sound, is not directly amenable to practical computation. In this
-section, we reformulate these expressions in terms of a probability distribution,
-which allows for more efficient estimation through sampling-based approaches. This
-reformulation is central to our policy gradient theorem for discounted returns.
-\subsection{Definition and Properties}
-\begin{definition}[Discounted Visitation Measure]
-    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
-        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
-    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
-    \end{equation}
-
-    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
-    and $\gamma \in [0, 1)$ is the discount factor.
-\end{definition}This measure represents the expected discounted frequency with which
-different states, belief states, and policy parameters are visited when following
-policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
-factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
-distribution, summing to 1 across the entire state-belief-policy space. The discounted
-visitation measure plays a central role in reinforcement learning theory,
-particularly in policy gradient methods. It provides a natural weighting of states
-according to their importance for the discounted objective, as states that are
-visited more frequently or earlier in trajectories receive higher weight. This concept
-generalizes the stationary distribution used in average-reward settings to the discounted
-return framework.
-\begin{lemma}[Evolution of Discounted Visitation]
-    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
-    the adjoint operator as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
-    \end{equation}
-
-    where $\mu_{0}$ is the initial distribution.
-\end{lemma}
-\begin{proof}
-    By the propagation lemma established earlier,
-    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
-    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
-    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
-    measure:
-    \begin{align}
-        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
-                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    The second equality follows from the Neumann series expansion:
-    \begin{align}
-        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
-    \end{align}
-
-    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
-    the total variation norm.
-\end{proof}This establishes the essential connection between the adjoint operator
-and the discounted visitation measure, which is central to the policy gradient
-theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
-time spent in each state-belief-policy configuration, weighted according to the
-discount factor $\gamma$. This connection allows us to transform expressions involving
-$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
-        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
-practical implementations, the discounted visitation measure is rarely computed explicitly
-due to the prohibitive computational cost. Instead, sampling-based approaches are
-used to estimate expectations with respect to this measure. The policy gradient
-theorem leverages this measure to derive update rules that can be efficiently
-implemented using trajectory samples collected from the environment.
-
-\subsection{Existence and Uniqueness}
-To provide a rigorous mathematical foundation for our policy gradient theorem,
-we establish the existence and uniqueness of the discounted visitation measure.
-\begin{lemma}[Existence of the Discounted Visitation Measure]
-    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
-    of finite measures on the joint state-belief-policy space, equipped with the
-    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
-        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
-        )$, the discounted state-visitation measure
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$.
-\end{lemma}
-\begin{proof}
-    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
-    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    converges to a well-defined measure. First, let's recall that
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
-    the total variation norm
-    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
-    we need to show that the series
-    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
-    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
-    joint state-belief-policy space after $t$ transitions, starting from the initial
-    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
-    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
-    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
-    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
-    $\mu_{0}$ with total mass
-    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
-        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
-    \begin{align}
-        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    For $n < m$, the difference between two partial sums is:
-    \begin{align}
-        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
-                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
-                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
-                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
-                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
-                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
-    \end{align}
-
-    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
-    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
-    of this space, the sequence converges to a measure which we denote as
-    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
-    \begin{align}
-        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
-                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
-                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
-                                                                           & = M
-    \end{align}
-
-    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
-\end{proof}Having established existence, we now turn to the uniqueness of the discounted
-visitation measure.
-
-\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
-    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
-    to the functional equation:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
-    \end{align}
-
-    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$.
-\end{lemma}
-\begin{proof}
-    First, we verify that
-    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    satisfies the functional equation:
-
-    \begin{align}
-        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
-                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
-                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
-                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
-                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
-                                                            & = d^{\pi}_{\mu_0}
-    \end{align}
-
-    To prove uniqueness, suppose there exists another measure
-    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    that satisfies the functional equation:
-    \begin{align}
-        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
-    \end{align}
-
-    Let's consider the operator
-    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    defined as:
-    \begin{align}
-        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
-    \end{align}
-
-    For any two measures
-    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
-                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
-                                 & \leq \gamma \|\mu - \nu\|_{TV}
-    \end{align}
-
-    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
-    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
-    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
-    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
-    the uniqueness of the discounted state-visitation measure.
-\end{proof}
-
-\subsection{Connection to Value Function}
-Having established the theoretical properties of the discounted visitation
-measure, we now connect it to the value function, which will provide important
-insights later on.
-
-\begin{lemma}[Value Function as Inner Product]
-    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
-    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
-    the value function can be expressed as:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
-    the Dirac measure concentrated at
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
-    immediate reward function:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-\end{lemma}
-\begin{proof}
-    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
-    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
-        {\theta}_{0})$. By definition of the value function:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
-    \end{align}
-
-    Define the expected immediate reward function
-    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    Then:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
-    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
-        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
-    and measures:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
-    $(I - \gamma \Psi^{*})^{-1}$:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
-        ^{*})^{-1}\mu_{0}$. Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
-                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}This lemma establishes that the value function can be expressed as an
-expectation with respect to the discounted visitation measure, with an appropriate
-scaling factor. This formulation provides a direct link between the value
-function and the distribution of states.
-
-\section{Policy Gradient Theorem}
-Having established the mathematical foundations for discounted returns in
-partially observable multi-agent settings, we now derive the policy gradient theorem
-that forms the basis for practical optimization algorithms. This theorem
-provides a principled expression for computing gradients of the expected
-discounted return with respect to policy parameters, enabling efficient policy improvement.
-The policy gradient theorem connects an agent's policy parameters to its
-expected long-term performance through the discounted visitation measure, providing
-a mathematically rigorous foundation for optimization.
-
-\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
-        Theorem]
-    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
-            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
-    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
-    Markov game setting can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
-                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
-    visitation measure starting from initial distribution $\mu_{0}$, and
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
-    the action-value function defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
-on the lemmas established in previous sections.
-\begin{proof}
-    From our previous lemma, we know that the gradient of the value function can be
-    expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
-    \end{align}
-
-    For notational clarity, we define the term inside the brackets as:
-    \begin{align}
-        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    Now we can write:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For our specific initial state configuration
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Let's define
-    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
-    Dirac measure concentrated at the initial state. We can view
-    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
-    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
-    Dirac measure:
-
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
-                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Recall the duality principle we established earlier, which states that:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
-    \end{align}
-
-    Allowing us to move the operator from acting on the function $g$ to acting on
-    the measure $\mu_{0}$:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From our earlier derivation of the discounted visitation measure, we established
-    that:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
-    \end{align}
-
-    We can now substitute this expression:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
-                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For finite state, belief, and policy parameter spaces, this integral can be
-    written as a sum:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    This completes the proof of the Partially Observable Active Discounted Return
-    Policy Gradient Theorem.
-\end{proof}
-
-The proof reveals a symmetry in the mathematical structure of our results.
-\begin{remark}[Symmetry]
-    From the Value Function as Inner Product lemma, the value function
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
-    measure $d^{\pi}_{\mu_0}$. While its gradient
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of policy-gradient-weighted action values $g$ under the same
-    discounted visitation measure $d^{\pi}_{\mu_0}$.
-\end{remark}
-This symmetric structure provides not only mathematical elegance but also
-practical advantages. It means that the same samples from the discounted visitation
-distribution can be used to estimate both values and policy gradients.
-
-The policy gradient theorem provides the mathematical foundation for agents to optimize
-their policies in ways that account for both the partial observability of the environment
-and the learning dynamics of other agents. This enables sophisticated strategic
-behaviors such as information revelation, teaching, and influence that are
-essential in social learning contexts.
-
-\chapter{POLARIS Architecture}
-\label{appendix:neural_architectures}
-
-This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation.
-We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
-\begin{equation}
-    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
-\end{equation}
-
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
-
-\chapter{Social Learning Implementation}
-
-This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework.
-We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations.
-The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios.
-Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models.
-Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.
-
-\section{Lévy Process Discretization}
-\label{appendix:levy_discretization}
-
-This appendix provides a comprehensive mathematical treatment of the discretization of Lévy processes for implementing strategic experimentation models within our Partially Observable Active Markov Game framework.
-We establish rigorous theoretical foundations for the numerical approximation schemes used in our implementation and analyze their convergence properties and preservation of strategic incentives.
-
-\subsection{Mathematical Foundations of Lévy Processes}
-\label{appendix:levy_foundations}
-
-Lévy processes form a fundamental class of stochastic processes that include Brownian motion and Poisson processes as special cases.
-They are characterized by stationary and independent increments, serving as the natural continuous-time generalization of random walks.
-
-\begin{definition}[Lévy Process]
-    A stochastic process $X = \{X_t : t \geq 0\}$ on $\mathbb{R}^d$ with $X_0 = 0$ almost surely is a Lévy process if:
-    \begin{enumerate}
-        \item It has independent increments: for any $0 \leq t_1 < t_2 < \cdots < t_n < \infty$, the random variables $X_{t_2} - X_{t_1}, X_{t_3} - X_{t_2}, \ldots, X_{t_n} - X_{t_{n-1}}$ are mutually independent.
-        \item It has stationary increments: for any $s < t$, the distribution of $X_t - X_s$ depends only on $t-s$.
-        \item It is stochastically continuous: for any $t \geq 0$ and $\varepsilon > 0$, $\lim_{h \to 0} \mathbb{P}(|X_{t+h} - X_t| > \varepsilon) = 0$.
-    \end{enumerate}
-\end{definition}
-
-The celebrated Lévy-Khintchine formula provides a complete characterization of Lévy processes through their characteristic functions:
-
-\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
-    If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
-    \begin{equation}
-        \mathbb{E}[e^{i\theta X_t}] = e^{t\psi(\theta)}
-    \end{equation}
-    where
-    \begin{equation}
-        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
-    \end{equation}
-    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
-\end{theorem}
-
-The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
-Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
-
-\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
-    Any Lévy process $X_t$ can be decomposed as:
-    \begin{equation}
-        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
-    \end{equation}
-    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
-\end{theorem}
-
-The Lévy-Itô decomposition provides a pathwise representation of a Lévy process as the sum of a drift term, a Brownian motion, and potentially infinitely many jumps, both small and large.
-
-\subsection{Time Discretization of Lévy Processes}
-\label{appendix:levy_discretization_methods}
-
-To implement continuous-time Lévy processes within discrete computational frameworks, we must employ appropriate numerical approximation schemes.
-For our strategic experimentation model, we adopt the Euler-Maruyama scheme, extended to accommodate the jump components of general Lévy processes.
-
-\begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
-    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
-    \begin{equation}
-        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
-    \end{equation}
-    where $Z_n \sim \mathcal{N}(0,1)$ are independent standard normal random variables and $\Delta J_n$ represents the jump increment over $[t_n, t_{n+1}]$.
-\end{definition}
-\iffalse
-    For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.
-
-    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
-        The jump component $\Delta J_n$ can be approximated through one of the following approaches:
-        \begin{enumerate}
-            \item For finite-activity processes (where $\nu(\mathbb{R}) < \infty$):
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K_n} J_i
-                  \end{equation}
-                  where $K_n \sim \text{Poisson}(\nu(\mathbb{R})\Delta t)$ and $J_i$ are i.i.d. random variables with distribution $\frac{\nu(dx)}{\nu(\mathbb{R})}$.
-
-            \item For infinite-activity processes, a truncation approach:
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K^{\varepsilon}_n} J^{\varepsilon}_i + c_{\varepsilon}\Delta t
-                  \end{equation}
-                  where $K^{\varepsilon}_n \sim \text{Poisson}(\nu(\{x: |x| > \varepsilon\})\Delta t)$, $J^{\varepsilon}_i$ are i.i.d.
-with distribution $\frac{\nu(dx)\mathbf{1}_{|x|>\varepsilon}}{\nu(\{x: |x| > \varepsilon\})}$, and $c_{\varepsilon} = \int_{|x|\leq\varepsilon} x\nu(dx)$.
-        \end{enumerate}
-    \end{proposition}
-\fi
-\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
-    \label{thm:euler_maruyama_convergence}
-    Let $X_t$ be a Lévy process and $\hat{X}_t$ be its Euler-Maruyama approximation with time step $\Delta t$. Then for any fixed $T > 0$:
-    \begin{enumerate}
-        \item (Weak Convergence) For any smooth function $f$ with polynomial growth:
-              \begin{equation}
-                  |\mathbb{E}[f(X_T)] - \mathbb{E}[f(\hat{X}_T)]| \leq C\Delta t
-              \end{equation}
-
-        \item (Strong Convergence) If $\int_{|x|>1} |x|^2 \nu(dx) < \infty$, then:
-              \begin{equation}
-                  \mathbb{E}[\sup_{0\leq t\leq T} |X_t - \hat{X}_t|^2] \leq C\Delta t
-              \end{equation}
-    \end{enumerate}
-    where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.
-
-\end{theorem}
-
-The weak and strong convergence properties ensure that our numerical scheme accurately approximates both the distributional properties and pathwise behavior of the continuous-time process as the time step decreases.
-
-\subsection{Implementing Strategic Experimentation Models}
-\label{appendix:strategic_experimentation_implementation}
-
-In our implementation of the strategic experimentation model from \citet{keller2020undiscounted}, we must discretize both the background signal process $B_t$ and the individual payoff processes $X^i_t$, while preserving the strategic incentives that drive experimentation decisions.
-
-\subsubsection{Discretization of Diffusion-Poisson Processes}
-\label{appendix:discretization_diffusion_poisson}
-
-In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:
-
-\begin{align}
-    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
-    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
-\end{align}
-
-where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes.
-Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:
-
-\begin{align}
-    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
-    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
-\end{align}
-
-For implementation, we denote these increments as:
-
-\begin{align}
-    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
-    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
-\end{align}
-
-where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
-
-\subsubsection{Reward Function Equivalence}
-\label{appendix:reward_equivalence}
-
-A critical challenge in our implementation is reconciling the time-dependent nature of continuous-time rewards with the time-independent reward structure required by the POAMG framework.
-In the original continuous-time model, agents' instantaneous rewards are:
-
-\begin{equation}
-    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
-\end{equation}
-
-where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$.
-To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time.
-We achieve this through a normalization approach:
-
-\begin{equation}
-    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
-\end{equation}
-
-This transformation preserves the incentive structure of the original model while eliminating explicit time dependence. The following proposition establishes this equivalence formally:
-
-\begin{proposition}[Reward Equivalence]
-    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
-    \begin{equation}
-        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{equation}
-    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
-\end{proposition}
-
-\begin{proof}
-    The expected value of the discrete-time reward function is:
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
-                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
-                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
-    \end{align}
-
-    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:
-
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
-                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{align}
-
-    This exactly matches the expected instantaneous flow payoff in the continuous-time model.
-\end{proof}
-
-\iffalse
-    \subsubsection{Preservation of Strategic Incentives}
-    \label{appendix:strategic_incentives}
-
-    Beyond matching expected rewards, we must ensure that our discretization preserves the strategic incentives that drive experimentation decisions.
-The key strategic consideration in the model is the trade-off between exploitation (choosing the safe arm) and exploration (choosing the risky arm to learn about its quality).
-
-    \begin{proposition}[Preservation of Strategic Incentives]
-        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
-
-    \end{proposition}
-
-    \begin{proof}
-        In the strategic experimentation model, the incentive to experiment at a given belief $b$ about the state is characterized by:
-        \begin{equation}
-            I(b) = \frac{f(b) - s}{s - m(b)}
-        \end{equation}
-        when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad.
-In our discrete-time approximation, the corresponding incentive is:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)}
-        \end{equation}
-        where $\hat{f}(b)$ and $\hat{m}(b)$ are the discrete-time analogs.
-
-        Let us elaborate on why $\hat{f}(b) \to f(b)$ and $\hat{m}(b) \to m(b)$ as $\Delta t \to 0$. In the continuous-time model, the expected flow payoff of the risky arm at belief $b$ is:
-        \begin{equation}
-            f(b) = b f_1 + (1-b) f_0
-        \end{equation}
-        where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$.
-In our discrete-time approximation, we have:
-        \begin{equation}
-            \hat{f}(b) = b \hat{f}_1 + (1-b) \hat{f}_0
-        \end{equation}
-        where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
-        From our reward equivalence result, we know that:
-        \begin{align}
-            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
-                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
-        \end{align}
-
-        The Brownian motion term has $\mathbb{E}[\sigma(W^i_t - W^i_{t-1})] = 0$ and $\text{Var}[\sigma(W^i_t - W^i_{t-1})] = \sigma^2 \Delta t$.
-By the martingale property of Brownian motion, this term contributes zero to the expected value but introduces variance of order $O(\Delta t)$.
-Thus:
-        \begin{equation}
-            \hat{f}_1 = \alpha_1 + \lambda_1\mu_1 + O(\Delta t) \to f_1 \text{ as } \Delta t \to 0
-        \end{equation}
-
-        Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
-        Therefore, we can establish that:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)} = \frac{b \hat{f}_1 + (1-b) \hat{f}_0 - s}{s - \hat{f}_0} = \frac{b(\hat{f}_1 - \hat{f}_0) + \hat{f}_0 - s}{s - \hat{f}_0}
-        \end{equation}
-
-        As $\Delta t \to 0$, we have $\hat{f}_1 \to f_1$, $\hat{f}_0 \to f_0$, and consequently:
-        \begin{equation}
-            \hat{I}(b) \to \frac{b(f_1 - f_0) + f_0 - s}{s - f_0} = \frac{b f_1 + (1-b) f_0 - s}{s - f_0} = \frac{f(b) - s}{s - m(b)} = I(b)
-        \end{equation}
-
-        The convergence of incentives directly implies convergence of optimal policies.
-In the continuous-time model, the symmetric Markov perfect equilibrium characterized in \citet{keller2020undiscounted} has the form:
-        \begin{equation}
-            \kappa^*(b) =
-            \begin{cases}
-                0                    & \text{if } I(b) \leq k_0,            \\
-                \frac{I(b)-k_0}{N-1} & \text{if } k_0 < I(b) < k_0 + N - 1, \\
-                1                    & \text{if } I(b) \geq k_0 + N - 1.
-            \end{cases}
-        \end{equation}
-        where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players.
-The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.
-
-        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
-    \end{proof}
-
-\fi
-\subsection{Relation to Policy-Invariant Reward Transformations}
-\label{appendix:policy_invariance}
-
-Our approach to time-independent reward formulation can be viewed through the lens of policy-invariant reward transformations, as developed in the reinforcement learning literature by \citet{ng1999policy}.
-
-\begin{definition}[Potential-Based Reward Shaping]
-    A reward transformation $\tilde{R}(s, a, s') = R(s, a, s') + F(s, s')$ is potential-based if there exists a potential function $\Phi: S \to \mathbb{R}$ such that $F(s, s') = \gamma\Phi(s') - \Phi(s)$ for all $s, s' \in S$, where $\gamma$ is a discount factor.
-\end{definition}
-
-\begin{theorem}[Ng-Harada-Russell \citep{ng1999policy}]
-    If a reward transformation is potential-based, then the optimal policy under the transformed reward function is also optimal under the original reward function, and vice versa.
-\end{theorem}
-
-While our transformation does not directly fit the potential-based formulation (since we're normalizing by $\Delta t$ rather than adding a potential difference), it shares the crucial property of preserving optimal policies.
-The following result establishes this connection:
-
-\begin{proposition}[Connection to Policy-Invariant Transformations]
-    The transformation from time-dependent rewards in the continuous-time model to time-independent rewards in the POAMG framework preserves policy optimality in the limit as $\Delta t \to 0$.
-\end{proposition}
-
-\begin{proof}
-    The original cumulative reward over a time interval $[0, T]$ is:
-    \begin{equation}
-        \int_0^T [(1-a^i_t)s + a^i_t\alpha_s] dt + \int_0^T a^i_t \sigma dW^i_t + \int_0^T a^i_t dC^i_t
-    \end{equation}
-
-    The discretized cumulative reward is:
-    \begin{equation}
-        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
-    \end{equation}
-    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.
-
-    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral.
-Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
-\end{proof}
-
-\section{Observed Reward Function}
-\label{appendix:observed_reward_derivation} In our reinforcement learning
-implementation, agents need to learn from observed rewards that reflect the optimality
-of their actions with respect to the true state of the world. However, since agents
-do not directly observe the true state $\omega$, we need to construct a reward
-function based on their observations $o$ that preserves the expected reward
-structure. This appendix provides a detailed derivation of the observation-based
-reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
-    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
-observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
-state. We need to construct an observation-based reward function $v(o, a): \Omega
-    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
-\begin{equation}
-    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
-    a \in A.
-\end{equation}
-
-In other words, the expected value of the observation-based reward $v(o, a)$
-over all possible observations $o$ given the state $s$ should equal the true
-reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
-    m$ matrix representing the observation distributions, where $m = |S|$ and assume
-the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
-the probability of observing observation $o$ in state $s$:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
-        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
-        \vdots           & \vdots           & \ddots & \vdots           \\
-        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
-    \end{bmatrix}
-\end{equation}
-
-We assume that observation distributions are linearly independent across states,
-which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
-    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
-more likely to generate its corresponding observation than any other observation.
-For each action $a \in A$, we define a utility vector
-$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
-\begin{equation}
-    \bm{u}_{a} =
-    \begin{bmatrix}
-        u(s^{1}, a) \\
-        u(s^{2}, a) \\
-        \vdots      \\
-        u(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
-    ^{k}$ for action $a$:
-\begin{equation}
-    \bm{v}_{a} =
-    \begin{bmatrix}
-        v(s^{1}, a) \\
-        v(s^{2}, a) \\
-        \vdots      \\
-        v(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-The condition that expected observation-based rewards match true rewards can be written
-as a linear system:
-\begin{equation}
-    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
-\end{equation}
-
-where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
-is:
-\begin{equation}
-    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
-\end{equation}
-
-This gives us the vector of observation-based rewards that satisfy our expected
-reward condition. For each observation $o_{j}$ and action $a$, the observation-based
-reward is:
-\begin{equation}
-    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
-\end{equation}
-
-where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
-$\bm{\mu}^{-1}$.
-\paragraph{Binary Case Example}
-For the special case with two states of the world ($m = 2$) and symmetric
-observations with accuracy $q > 0.5$, the observation distribution matrix is:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        q   & 1-q \\
-        1-q & q
-    \end{bmatrix}
-\end{equation}
-
-This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
-and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
-The inverse of this matrix is:
-\begin{equation}
-    \bm{\mu}^{-1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q      & -(1-q) \\
-        -(1-q) & q
-    \end{bmatrix}
-\end{equation}
-
-In our implementation, we set the true reward as the indicator function for taking
-the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
-    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
-utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
-is:
-\begin{equation}
-    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q \\
-        -(1-q)
-    \end{bmatrix}
-\end{equation}
-
-This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
-the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
-$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
-action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
-observation-based reward vector is:
-\begin{equation}
-    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        -(1-q) \\
-        q
-    \end{bmatrix}
-\end{equation}
-
-Combining these results, we can express the observation-based reward function for
-any action-observation pair $(a, o)$ as:
-\begin{equation}
-    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
-        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
-\end{equation}
-
-where $\varphi$ maps observations to their corresponding actions. The derived
-observation-based reward function has an intuitive interpretation. When an agent
-takes an action matching its observation ($a = o$), it receives a positive
-reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
-($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
-0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
-increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
-informative), the reward for matching observation and action approaches 1, and the
-penalty for mismatching approaches 0, meaning that the observed reward function
-converges to the true reward function. This reward structure incentivizes agents
-to match their actions to their observations when signals are reliable, but also
-allows them to learn to override their immediate observations when the actions
-of other agents provide stronger evidence about the true state through beliefs.
+In the next chapter, we provide a detailed review of the relevant literature, tracing the development of social learning models in economics and recent advances in multi-agent reinforcement learning.
+This review establishes the conceptual foundation for our theoretical framework and highlights the specific gaps that our approach aims to address, setting the stage for the formal development of Partially Observable Active Markov Games in Chapter 3.

### 2025-05-26 paper/results.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
-\setcounter{proposition}{0}
-\setcounter{assumption}{0}
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
+Building on the theoretical framework of Partially Observable Active Markov Games developed in the previous section, we now apply our POLARIS algorithm to concrete social learning scenarios.
+This implementation demonstrates how our approach bridges theoretical economic models with computational reinforcement learning methods, allowing us to validate theoretical predictions while uncovering new insights about strategic adaptation in partial observability settings.
 
-\chapter{Reinforcement Learning Background}
+We implement our Partially Observable Active Markov Game framework to model the two canonical social learning scenarios discussed in the background section: strategic experimentation with observable rewards and learning without experimentation through action observation.
+By reformulating these economic models as POAMGs, we demonstrate how our framework can capture the sophisticated learning dynamics present in these scenarios while enabling the discovery of complex strategies through our POLARIS algorithm.
+\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/POLARIS}.}
 
-\label{appendix:rl_details}
-This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.
+\section{Strategic Experimentation}
 
-\section{Reinforcement Learning Foundations}
+We reformulate the strategic experimentation model of \citet{keller2020undiscounted} as a Partially Observable Active Markov Game.
+This framework analyzes undiscounted continuous-time games where a number of symmetric players act non-cooperatively, trying to learn an unknown state of the world governing the risky arm's expected payoff.
+The state space $S = \{0,1,\ldots,m\}$ represents possible states of the world, with a deterministic transition function since the underlying state remains constant throughout the interaction.
+Each agent's action space $A^i = [0,1]$ represents the fraction of resources allocated to the risky arm at each decision point, creating a continuous action space that allows for nuanced exploration strategies.
 
-Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty.
-In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}.
-This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:
+While the original model operates in continuous time with Lévy processes, our POAMG implementation discretizes time using the Euler-Maruyama scheme \citep{kloeden1992numerical, platen1999introduction} for both the background signal and the agents' payoff processes.
+This numerical method is widely used for approximating solutions to stochastic differential equations driven by both Brownian motion and Poisson processes.
 
-\begin{itemize}
-    \item $S$ is the state space, representing all possible configurations of the environment
-    \item $A$ is the action space, representing all possible decisions available to the agent
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
-    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
-    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
-\end{itemize}
-
-The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions.
-The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter.
-The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.
-
-The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs.
-This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem.
-However, this assumption becomes problematic in multi-agent settings, as we will discuss next.
-
-\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}
-
-Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}.
-MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}.
-These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space, shared among all agents
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\gamma \in [0, 1)$ is the discount factor
-\end{itemize}
-MARL introduces several fundamental challenges beyond those encountered in single-agent RL.
-The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system.
-Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}.
-In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions.
-MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings.
-Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.
-
-\section{The Non-Stationarity Challenge}
-The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}.
-To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent.
-When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$.
-From agent $i$'s perspective, the effective transition function becomes:
-\begin{equation}
-    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
-\end{equation}
-where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$.
-When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$.
-This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL.
-When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}.
-This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}.
-Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}.
-The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}.
-These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.
-
-\section{Traditional Approaches to Non-Stationarity}
-Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:
-
-\subsection{Independent Learning}
-The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}.
-This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents.
-Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences.
-While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.
-
-\subsection{Centralized Training with Decentralized Execution}
-To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}.
-In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.
-
-Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution.
-Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline.
-The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies.
-While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.
-
-\subsection{Opponent Modeling and Population-Based Training}
-Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}.
-This can involve predicting other agents' policies, types, or learning dynamics.
-Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning.
-Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.
-
-The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity.
-While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.
-
-\subsection{Equilibrium Learning and Stability Concepts}
-Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}.
-These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate.
-Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games.
-Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.
-
-The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence.
-While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality.
-Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.
-
-\subsection{Meta-Learning for Non-Stationarity}
-Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}.
-These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem.
-Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.
-
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents.
-While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.
-
-\section{Active Markov Games}
-
-Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}.
-They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.
-
-\subsection{Formal Definition}
-
-An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
-    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
-\end{itemize}
-Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state.
-The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates.
-At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$.
-Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$.
-Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$.
-This process continues until non-stationary policies converge to a recurrent set of joint policies.
-The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.
-
-\subsection{Augmented Transition Function and Stationarity}
-
-The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions.
-To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games.
-In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions.
-However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions.
-The augmented transition function becomes:
+The agents receive a public signal produced by the background process, which leads to the observation function:
 
 \begin{equation}
-    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
-\end{equation}
-The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories.
-By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one.
-This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.
-
-\subsection{Theoretical Properties and Convergence}
-
-Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:
-
-\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:
-
-\begin{equation}
-    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
+    O^i(s, o) = \mathbb{P}(o_t | B_{t-1:t})
 \end{equation}
 
-where $\ell = t\%k$ with $\%$ denoting the modulo operation.
-This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies.
-The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence.
-To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}.
-These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.
-
-\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:
-
-\begin{equation}
-    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
-        \begin{array}{c}
-            s_0=s, \theta_0=\theta,                                              \\
-            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
-            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
-            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
-        \end{array}
-        \right]
-\end{equation}
-
-where  $0:T$ denotes the sequence from time $0$ to $T$.
-This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.
-
-\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium.
-An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:
-
-\begin{equation}
-    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
-\end{equation}
-for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$.
-This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system.
-The active equilibrium generalizes several classic solution concepts in game theory.
-Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively.
-Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively.
-This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.
-
-Active Markov Games address the non-stationarity challenge in several fundamental ways.
-By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated.
-The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors.
-Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates.
-Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees.
-Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.
-
-\subsection{Practical Implementations}
-
-Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL.
-Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner.
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games.
-These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.
-
-\section{Extension to Partial Observability}
-
-While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state.
-In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents.
-This partial observability introduces additional challenges for multi-agent learning.
-The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions.
-In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}.
-Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning.
-The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.
-
-In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state.
-Theoretical formulations, as established by Meuleau et al.
-\cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$.
-However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation.
-Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}.
-These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics.
-In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time.
-For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.
-
-\chapter{Proofs Regarding Average Returns}
-
-This section provides the mathematical foundations and detailed proofs for the
-key theoretical results in our Partially Observable Active Markov Game framework
-with average return objectives. We establish the Markov properties of belief transitions
-and joint processes, prove the existence and uniqueness of stochastically stable
-distributions, and derive the policy gradient theorem for average return optimization.
-
-\section{Markov Property of the Joint Process}
-\label{appendix:stochasticallystable}We first establish the Markov properties of
-belief state transitions and the joint process comprising states, belief states,
-and policy parameters. These properties form the foundation for our convergence analysis.
-
-\begin{lemma}[Markov Property of Belief Transitions]
-    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
-    a Markov process under a fixed policy $\pi$, meaning that the distribution of
-    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
-    not on earlier beliefs, actions, or observations.
-\end{lemma}
-
-\begin{proof}
-    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
-    relevant information from the history of observations and actions up to time
-    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
-    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
-            ^{i}$ through the rule:
-    \begin{align}
-        b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
-    \end{align}
-
-    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
-    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
-    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
-    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
-    property.
-\end{proof}
-
-\begin{remark}[Transformer-Based Belief Representation]
-    In practice, transformer architectures can be used to represent and
-    update belief states. In such cases, the belief state is updated
-    through an attention-based mechanism of the form:
-    \begin{equation}
-        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
-    \end{equation}
-
-    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
-    observation and previous belief state through self-attention layers, satisfying the Markov property
-    while capturing complex dependencies between observations and beliefs.
-\end{remark}
-Next, we establish the Markov property of the joint process.
-\begin{lemma}[Markov Property of Joint Process]
-    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
-    a Markov process under periodic policy updates, meaning that the distribution
-    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
-    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
-    states.
-\end{lemma}
-\begin{proof}
-    The state transitions are by definition only dependent on current state and current
-    actions. The remaining parts can be analyzed as follows:
-
-    \textbf{1. Belief
-        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
-    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
-    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
-        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
-    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
-    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
-    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.
-
-    \textbf{2. Policy parameter
-        update:} At every time step $t$, policy parameters are updated according to $U(
-        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
-    Under the Markovian policy update assumption, the update depends only on $\theta
-        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
-        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
-    probability
-    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t}))$
-    depends only on the current state
-    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
-    of states, establishing the Markov property.
-\end{proof}
-\section{Convergence}
-Having established the Markov properties, we now analyze the convergence
-behavior of the joint process to a unique stochastically stable distribution. This
-convergence result is crucial for developing optimization objectives in our framework.
-\begin{theorem}[Stochastically Stable Distribution]
-    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
-    defined by $\epsilon$-perturbed policy update functions converge to the unique
-    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
-        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
-\end{theorem}
-
-\begin{proof}
-    We establish the convergence to the unique stochastically stable distribution by
-    showing that a perturbed Markov process of a partially observable active Markov
-    game is regular. First, let us introduce a small perturbation to the policy update
-    functions:
-    \begin{align}
-        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
-    \end{align}
-
-    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
-    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
-    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
-    probability of transitioning to any other configuration
-    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
-        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
-    probability:
-    \begin{align}
-        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
-                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
-                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
-    \end{align}
-
-    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
-    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
-    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
-    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
-    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
-    of the joint process. We will show that there must exist a path with positive probability
-    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
-    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
-        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
-        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
-    second as follows:
-
-    \textbf{1. Policy Parameter Transition:} Due to the
-    $\epsilon$-perturbation in update functions, there is a positive probability of
-    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
-        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
-    \end{align}
-
-    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
-    $\boldsymbol{\theta}_{2}$.
-
-    \textbf{2. State Transition:} By the communicating
-    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
-    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
-    such that:
-    \begin{align}
-        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
-    \end{align}
-
-    Given the relationship between policies and actions, this sequence of actions has
-    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
-    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
-    for all required actions.
-
-    \textbf{3. Belief State Transition:} By the communicating belief-state
-    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
-        B$, there exists a sequence of observations
-    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
-    \end{align}
-
-    Since observations depend on states, which can be influenced through actions,
-    and actions are determined by policies, there is a positive probability path from
-    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
-    and policy parameters. Combining these three components, we can construct a path
-    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
-        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
-    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
-    classes of the perturbed joint process. Since we have shown that the perturbed
-    joint process has only one recurrent class, it is a regular Markov process. Following
-    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
-    process on a finite state space possesses a unique stationary distribution
-    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
-    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
-    converges to a limit $\mu^{*}$, which is the unique stochastically stable
-    distribution of the original, unperturbed process. Therefore, under the given conditions,
-    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
-    partially observable active Markov game possesses a unique stochastically
-    stable distribution $\mu^{*}$.
-\end{proof}
-\section{Policy Gradient Theorem}
-Having established the convergence to a unique stochastically stable distribution,
-we now derive the policy gradient theorem for optimization in our framework. This
-theorem provides the mathematical foundation for gradient-based algorithms to maximize
-the average return objective.
-\label{appendix:avg_gradient}
-\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
-        Theorem]
-    The gradient of the active average reward objective
-    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
-    setting is:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
-    the belief update function.
-\end{theorem}
-
-\begin{proof}
-    We first define the average reward objective in the partially observable setting:
-    \begin{align}
-        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
-                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
-    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
-        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
-    differential value function $v^{i}_{\theta^i}$ represents the expected total
-    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
-        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
-        ^{i}_{\theta^i}$:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
-    \end{align}
-
-    Following the Bellman equation derivation principles, we can express
-    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
-                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-    represents the belief update function that updates the belief state based on
-    the current belief, action, and new observation. We now define the action-value
-    function $q^{i}_{\theta^i}$ for the partially observable setting:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    Using this definition, we can rewrite the differential value function as:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    To derive the policy gradient, we begin by computing the gradient of the differential
-    value function with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
-                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
-                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    We expand the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                                                                  & \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
-                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting back into the original expression, we get:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Rearranging terms:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we define the transition operator that maps the expectation of a function
-    from one time step to the next:
-    \begin{align}
-        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
-                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    We can rewrite our expression as:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we take the expectation with respect to the stationary distribution
-    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
-                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    By the definition of the stationary distribution, we have:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore, the second and third terms in our expression cancel out, giving the
-    final policy gradient theorem:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-\end{proof}
-
-\chapter{Proofs Regarding Discounted Returns}
-\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
-Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
-mathematical foundation.
-\section{Transition Operator and Its Adjoint}
-To establish a rigorous framework for analyzing discounted returns in Partially
-Observable Active Markov Games, we need to formalize how value functions evolve over
-time and how probability distributions propagate through the system. This dual
-perspective is captured by two fundamental operators: the transition operator and
-its adjoint.
-
-\subsection{Definitions and Duality}
-
-We begin by defining the inner product between functions and measures, which forms
-the foundation for the duality relationship between our operators.
-
-\begin{definition}[Inner Product between Functions and Measures]
-    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
-        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
-    Lebesgue integral:
-    \begin{equation}
-        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
-        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
-        {\theta})
-    \end{equation}
-\end{definition}
-
-This inner product captures the expected value of function $f$ with respect to
-measure $\mu$, allowing us to express value functions as expectations with respect
-to appropriate measures.
-
-\begin{definition}[Transition Operator and Its Adjoint]
-    \hfill
-    \begin{enumerate}
-        \item The \textbf{transition operator}
-              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
-                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              maps a bounded measurable function to its expected value after one
-              transition:
-              \begin{align}
-                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-              \end{align}
-
-              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-              represents the belief update function.
-
-        \item The \textbf{adjoint operator}
-              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
-                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              is defined on the space of finite measures such that:
-              \begin{equation}
-                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
-              \end{equation}
-
-              for all
-              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
-              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
-    \end{enumerate}
-\end{definition}
-
-Intuitively, $\Psi$ describes how function expectations evolve forward in time,
-meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
-capturing the propagation of visitation probabilities through the system. The duality
-relationship ensures that expected values can be computed either by applying $\Psi$
-to functions or $\Psi^{*}$ to measures.
-
-\subsection{Properties of the Operators}
-
-These operators possess several important properties that facilitate our
-analysis of discounted returns:
-
-\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
-    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
-    properties:
-
-    \begin{enumerate}
-        \item \textbf{Linearity:}
-              \begin{itemize}
-                  \item For the operator: For any functions
-                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
-                        \end{align}
-
-                  \item For the adjoint: For any measures
-                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Positivity Preservation:}
-              \begin{itemize}
-                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.
-
-                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
-                            \mu$ is also non-negative.
-              \end{itemize}
-
-        \item \textbf{Preservation of Total Measure:}
-              \begin{itemize}
-                  \item For the operator: The operator preserves the constant function
-                        $\mathbf{1}$:
-                        \begin{align}
-                            \Psi \mathbf{1}= \mathbf{1}
-                        \end{align}
-
-                        where $\mathbf{1}$ represents the function that equals 1 everywhere.
-
-                  \item For the adjoint: For any measure
-                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-                        \begin{align}
-                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
-              bounded with:
-              \begin{align}
-                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
-              \end{align}
-
-              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
-                  {b},\boldsymbol{\theta})|$ is the supremum norm.
-
-        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
-              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-              \begin{align}
-                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
-                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-              \end{align}
-
-              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    We prove each property in turn:
-
-    \textbf{1. Linearity:}
-
-    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
-    \begin{align}
-         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For the adjoint: For any measurable function
-    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
-                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
-                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
-                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
-        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
-    measure.
-
-    \textbf{2. Positivity Preservation:}
-
-    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
-        )$:
-    \begin{align}
-        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
-    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
-    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
-        {\theta}) \geq 0$.
-
-    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
-    function $f \geq 0$:
-    \begin{align}
-        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
-    \end{align}
-
-    where the inequality follows from the positivity preservation of $\Psi$ and the
-    fact that $\mu$ is non-negative. Since this holds for all non-negative
-    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.
-
-    \textbf{3. Preservation of Total Measure:}
-
-    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
-    everywhere. Then:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
-    \end{align}
-
-    Since each probability distribution sums to 1, applying them sequentially
-    yields:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
-    \end{align}
-
-    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
-    \begin{align}
-        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
-    \end{align}
-
-    where we used the unit preservation property of $\Psi$. This gives:
-    \begin{align}
-        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-    \end{align}
-
-    \textbf{4. Bound Preservation:}
-
-    For any bounded function $f$ with
-    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
-        ,\boldsymbol{\theta})|$:
-    \begin{align}
-        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                           & \quad \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
-                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
-                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
-    \end{align}
-
-    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
-    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.
-
-    \textbf{5. Explicit Form of the Adjoint:}
-
-    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
-    \end{align}
-
-    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
-    \begin{align}
-        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting this back and using the definition of inner product:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
-                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
-                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}
-
-\subsection{Contraction and Propagation}
-
-The properties established above lead to two crucial results: the contraction
-property of the discounted transition operator and the propagation of
-distributions through the adjoint.
-
-\begin{lemma}[Contraction Mapping Property]
-    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
-    contraction mapping on the Banach space of bounded functions on
-    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
-    norm. Specifically, for any two functions
-    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
-    \end{align}
-\end{lemma}
-
-\begin{proof}
-    Using the linearity of $\Psi$ and its bound preservation property:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
-                                                   & \leq \gamma\|f - g\|_{\infty}
-    \end{align}
-
-    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
-    factor $\gamma$.
-\end{proof}
-
-This contraction property leads directly to the invertibility of
-$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
-in discounted settings.
-
-\begin{lemma}[Invertibility of $I - \gamma \Psi$]
-    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
-    invertible, and its inverse can be represented as a Neumann series:
-    \begin{align}
-        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    which converges absolutely in the operator norm.
-\end{lemma}
-
-\begin{proof}
-    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
-    space, then $I - T$ is invertible, with inverse given by the Neumann series
-    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
-    have:
-
-    \begin{align}
-        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    The absolute convergence follows from:
-    \begin{align}
-        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
-    \end{align}
-
-    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
-        \leq 1$ for all $t$.
-\end{proof}
-
-Finally, we establish how distributions evolve in the system through the adjoint
-operator, formalizing the propagation of probability measures.
-
-\begin{lemma}[Distribution Propagation]
-    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
-    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
-\end{lemma}
-
-\begin{proof}
-    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$:
-    \begin{align}
-        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
-                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
-                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
-                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have
-    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
-\end{proof}
-
-The concepts introduced in this section—the transition operator, its adjoint, and
-their properties—provide the mathematical foundation for analyzing discounted returns
-in Partially Observable Active Markov Games. The transition operator $\Psi$
-captures how function expectations evolve forward in time, while its adjoint $\Psi
-    ^{*}$ describes how probability distributions propagate forward in time. This
-duality is fundamental to establishing the connection between value-based and
-distribution-based perspectives in reinforcement learning.
-
-In the next section, we will use these tools to formulate Bellman equations and derive
-policy gradients for maximizing discounted returns in this complex multi-agent setting.
-\section{Bellman Equations and Value Functions}
-In this section, we establish the fundamental recursive relationships that characterize
-the discounted value functions in Partially Observable Active Markov Games.
-These relationships form the basis for our policy gradient derivation and
-practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
-of value functions, then establish the Bellman equations, and finally derive the
-gradient expressions necessary for policy optimization.
-\subsection{Well-Definedness of Value Functions}
-Before deriving recursive relationships, we first establish that the value functions
-are well-defined mathematical objects under our assumptions of bounded rewards and
-discount factors less than 1.
-\begin{lemma}[Well-Defined Value Functions]
-    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
-    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
-    action-value functions
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
-    well-defined and finite for all states, belief states, policy parameters, and actions.
-\end{lemma}
-\begin{proof}
-    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
-    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
-    \begin{align}
-        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
-                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
-                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Similarly, for the action-value function:
-    \begin{align}
-        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
-                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
-                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Thus, both value functions are well-defined and bounded.
-\end{proof}This lemma ensures that our subsequent derivations involving value
-functions are mathematically sound. The boundedness property is particularly important
-when we consider expectations and derivatives of these functions.
-\subsection{Bellman Equations for Discounted Value Functions}
-Next, we establish the recursive relationships between value functions, which
-are fundamental to dynamic programming approaches.
-\begin{lemma}[Bellman Equation for Discounted Value Functions]
-    In a Partially Observable Active Markov Game, the discounted value function
-    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{lemma}
-\begin{proof}
-    By definition, the discounted value function is:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    We can decompose this into the immediate reward and the future discounted
-    returns:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
-                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
-                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    For the first term, we have:
-    \begin{align}
-        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    For the second term, by the law of total expectation:
-    \begin{align}
-         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
-         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Combining these two terms and factoring out common terms:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
-                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
-                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
-\end{proof}The Bellman equation provides a recursive characterization of the
-value function that forms the basis for dynamic programming algorithms. This equation
-captures how current actions influence both immediate rewards and future value through
-their effects on the environment state, belief states, and policy parameters of other
-agents. The key distinction from standard Bellman equations is the inclusion of
-belief updates and policy parameter dynamics, which reflects the complex dependencies
-in partially observable multi-agent settings.
-\subsection{Policy Gradient with Respect to Value Function}
-Having established the recursive relationship for value functions, we now derive
-how the value function gradient depends on policy parameters, which is essential
-for policy optimization.
-\begin{lemma}[Policy Gradient with Respect to Value Function]
-    The gradient of the value function with respect to policy parameters $\theta^{i}$
-    can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-
-    where $\Psi$ is the transition operator defined in the previous section.
-\end{lemma}
-\begin{proof}
-    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
-    \end{align}
-
-    Applying the product rule:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    For the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
-    \end{align}
-
-    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
-        {o}'|s')$, and
-    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
-    do not depend directly on $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Using the transition operator $\Psi$, we can rewrite:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Rearranging:
-    \begin{align}
-        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
-                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
-                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-\end{proof}This lemma expresses the value function gradient in terms of an
-infinite sum of expected Q-values weighted by policy gradients and propagated
-through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
-immediate changes in policy parameters propagate through future timesteps. This
-form of the gradient is central to our discounted policy gradient theorem, which
-we will develop in the next section. The inverse operator can be represented as
-a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
-as the accumulated effect of policy changes over an infinite horizon, weighted
-by the discount factor.
-\section{Discounted Visitation Measure}
-The infinite sum formulation derived in the previous sections, while
-mathematically sound, is not directly amenable to practical computation. In this
-section, we reformulate these expressions in terms of a probability distribution,
-which allows for more efficient estimation through sampling-based approaches. This
-reformulation is central to our policy gradient theorem for discounted returns.
-\subsection{Definition and Properties}
-\begin{definition}[Discounted Visitation Measure]
-    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
-        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
-    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
-    \end{equation}
-
-    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
-    and $\gamma \in [0, 1)$ is the discount factor.
-\end{definition}This measure represents the expected discounted frequency with which
-different states, belief states, and policy parameters are visited when following
-policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
-factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
-distribution, summing to 1 across the entire state-belief-policy space. The discounted
-visitation measure plays a central role in reinforcement learning theory,
-particularly in policy gradient methods. It provides a natural weighting of states
-according to their importance for the discounted objective, as states that are
-visited more frequently or earlier in trajectories receive higher weight. This concept
-generalizes the stationary distribution used in average-reward settings to the discounted
-return framework.
-\begin{lemma}[Evolution of Discounted Visitation]
-    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
-    the adjoint operator as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
-    \end{equation}
-
-    where $\mu_{0}$ is the initial distribution.
-\end{lemma}
-\begin{proof}
-    By the propagation lemma established earlier,
-    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
-    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
-    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
-    measure:
-    \begin{align}
-        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
-                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    The second equality follows from the Neumann series expansion:
-    \begin{align}
-        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
-    \end{align}
-
-    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
-    the total variation norm.
-\end{proof}This establishes the essential connection between the adjoint operator
-and the discounted visitation measure, which is central to the policy gradient
-theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
-time spent in each state-belief-policy configuration, weighted according to the
-discount factor $\gamma$. This connection allows us to transform expressions involving
-$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
-        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
-practical implementations, the discounted visitation measure is rarely computed explicitly
-due to the prohibitive computational cost. Instead, sampling-based approaches are
-used to estimate expectations with respect to this measure. The policy gradient
-theorem leverages this measure to derive update rules that can be efficiently
-implemented using trajectory samples collected from the environment.
-
-\subsection{Existence and Uniqueness}
-To provide a rigorous mathematical foundation for our policy gradient theorem,
-we establish the existence and uniqueness of the discounted visitation measure.
-\begin{lemma}[Existence of the Discounted Visitation Measure]
-    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
-    of finite measures on the joint state-belief-policy space, equipped with the
-    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
-        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
-        )$, the discounted state-visitation measure
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$.
-\end{lemma}
-\begin{proof}
-    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
-    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    converges to a well-defined measure. First, let's recall that
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
-    the total variation norm
-    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
-    we need to show that the series
-    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
-    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
-    joint state-belief-policy space after $t$ transitions, starting from the initial
-    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
-    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
-    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
-    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
-    $\mu_{0}$ with total mass
-    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
-        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
-    \begin{align}
-        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    For $n < m$, the difference between two partial sums is:
-    \begin{align}
-        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
-                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
-                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
-                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
-                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
-                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
-    \end{align}
-
-    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
-    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
-    of this space, the sequence converges to a measure which we denote as
-    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
-    \begin{align}
-        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
-                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
-                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
-                                                                           & = M
-    \end{align}
-
-    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
-\end{proof}Having established existence, we now turn to the uniqueness of the discounted
-visitation measure.
-
-\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
-    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
-    to the functional equation:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
-    \end{align}
-
-    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$.
-\end{lemma}
-\begin{proof}
-    First, we verify that
-    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    satisfies the functional equation:
-
-    \begin{align}
-        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
-                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
-                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
-                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
-                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
-                                                            & = d^{\pi}_{\mu_0}
-    \end{align}
-
-    To prove uniqueness, suppose there exists another measure
-    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    that satisfies the functional equation:
-    \begin{align}
-        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
-    \end{align}
-
-    Let's consider the operator
-    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    defined as:
-    \begin{align}
-        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
-    \end{align}
-
-    For any two measures
-    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
-                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
-                                 & \leq \gamma \|\mu - \nu\|_{TV}
-    \end{align}
-
-    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
-    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
-    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
-    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
-    the uniqueness of the discounted state-visitation measure.
-\end{proof}
-
-\subsection{Connection to Value Function}
-Having established the theoretical properties of the discounted visitation
-measure, we now connect it to the value function, which will provide important
-insights later on.
-
-\begin{lemma}[Value Function as Inner Product]
-    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
-    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
-    the value function can be expressed as:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
-    the Dirac measure concentrated at
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
-    immediate reward function:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-\end{lemma}
-\begin{proof}
-    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
-    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
-        {\theta}_{0})$. By definition of the value function:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
-    \end{align}
-
-    Define the expected immediate reward function
-    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    Then:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
-    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
-        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
-    and measures:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
-    $(I - \gamma \Psi^{*})^{-1}$:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
-        ^{*})^{-1}\mu_{0}$. Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
-                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}This lemma establishes that the value function can be expressed as an
-expectation with respect to the discounted visitation measure, with an appropriate
-scaling factor. This formulation provides a direct link between the value
-function and the distribution of states.
-
-\section{Policy Gradient Theorem}
-Having established the mathematical foundations for discounted returns in
-partially observable multi-agent settings, we now derive the policy gradient theorem
-that forms the basis for practical optimization algorithms. This theorem
-provides a principled expression for computing gradients of the expected
-discounted return with respect to policy parameters, enabling efficient policy improvement.
-The policy gradient theorem connects an agent's policy parameters to its
-expected long-term performance through the discounted visitation measure, providing
-a mathematically rigorous foundation for optimization.
-
-\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
-        Theorem]
-    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
-            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
-    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
-    Markov game setting can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
-                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
-    visitation measure starting from initial distribution $\mu_{0}$, and
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
-    the action-value function defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
-on the lemmas established in previous sections.
-\begin{proof}
-    From our previous lemma, we know that the gradient of the value function can be
-    expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
-    \end{align}
-
-    For notational clarity, we define the term inside the brackets as:
-    \begin{align}
-        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    Now we can write:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For our specific initial state configuration
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Let's define
-    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
-    Dirac measure concentrated at the initial state. We can view
-    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
-    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
-    Dirac measure:
-
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
-                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Recall the duality principle we established earlier, which states that:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
-    \end{align}
-
-    Allowing us to move the operator from acting on the function $g$ to acting on
-    the measure $\mu_{0}$:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From our earlier derivation of the discounted visitation measure, we established
-    that:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
-    \end{align}
-
-    We can now substitute this expression:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
-                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For finite state, belief, and policy parameter spaces, this integral can be
-    written as a sum:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    This completes the proof of the Partially Observable Active Discounted Return
-    Policy Gradient Theorem.
-\end{proof}
-
-The proof reveals a symmetry in the mathematical structure of our results.
-\begin{remark}[Symmetry]
-    From the Value Function as Inner Product lemma, the value function
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
-    measure $d^{\pi}_{\mu_0}$. While its gradient
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of policy-gradient-weighted action values $g$ under the same
-    discounted visitation measure $d^{\pi}_{\mu_0}$.
-\end{remark}
-This symmetric structure provides not only mathematical elegance but also
-practical advantages. It means that the same samples from the discounted visitation
-distribution can be used to estimate both values and policy gradients.
-
-The policy gradient theorem provides the mathematical foundation for agents to optimize
-their policies in ways that account for both the partial observability of the environment
-and the learning dynamics of other agents. This enables sophisticated strategic
-behaviors such as information revelation, teaching, and influence that are
-essential in social learning contexts.
-
-\chapter{POLARIS Architecture}
-\label{appendix:neural_architectures}
-
-This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation.
-We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
-\begin{equation}
-    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
-\end{equation}
-
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
-
-\chapter{Social Learning Implementation}
-
-This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework.
-We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations.
-The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios.
-Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models.
-Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.
-
-\section{Lévy Process Discretization}
-\label{appendix:levy_discretization}
-
-This appendix provides a comprehensive mathematical treatment of the discretization of Lévy processes for implementing strategic experimentation models within our Partially Observable Active Markov Game framework.
-We establish rigorous theoretical foundations for the numerical approximation schemes used in our implementation and analyze their convergence properties and preservation of strategic incentives.
-
-\subsection{Mathematical Foundations of Lévy Processes}
-\label{appendix:levy_foundations}
-
-Lévy processes form a fundamental class of stochastic processes that include Brownian motion and Poisson processes as special cases.
-They are characterized by stationary and independent increments, serving as the natural continuous-time generalization of random walks.
-
-\begin{definition}[Lévy Process]
-    A stochastic process $X = \{X_t : t \geq 0\}$ on $\mathbb{R}^d$ with $X_0 = 0$ almost surely is a Lévy process if:
-    \begin{enumerate}
-        \item It has independent increments: for any $0 \leq t_1 < t_2 < \cdots < t_n < \infty$, the random variables $X_{t_2} - X_{t_1}, X_{t_3} - X_{t_2}, \ldots, X_{t_n} - X_{t_{n-1}}$ are mutually independent.
-        \item It has stationary increments: for any $s < t$, the distribution of $X_t - X_s$ depends only on $t-s$.
-        \item It is stochastically continuous: for any $t \geq 0$ and $\varepsilon > 0$, $\lim_{h \to 0} \mathbb{P}(|X_{t+h} - X_t| > \varepsilon) = 0$.
-    \end{enumerate}
-\end{definition}
-
-The celebrated Lévy-Khintchine formula provides a complete characterization of Lévy processes through their characteristic functions:
-
-\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
-    If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
-    \begin{equation}
-        \mathbb{E}[e^{i\theta X_t}] = e^{t\psi(\theta)}
-    \end{equation}
-    where
-    \begin{equation}
-        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
-    \end{equation}
-    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
-\end{theorem}
-
-The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
-Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
-
-\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
-    Any Lévy process $X_t$ can be decomposed as:
-    \begin{equation}
-        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
-    \end{equation}
-    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
-\end{theorem}
-
-The Lévy-Itô decomposition provides a pathwise representation of a Lévy process as the sum of a drift term, a Brownian motion, and potentially infinitely many jumps, both small and large.
-
-\subsection{Time Discretization of Lévy Processes}
-\label{appendix:levy_discretization_methods}
-
-To implement continuous-time Lévy processes within discrete computational frameworks, we must employ appropriate numerical approximation schemes.
-For our strategic experimentation model, we adopt the Euler-Maruyama scheme, extended to accommodate the jump components of general Lévy processes.
-
-\begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
-    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
-    \begin{equation}
-        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
-    \end{equation}
-    where $Z_n \sim \mathcal{N}(0,1)$ are independent standard normal random variables and $\Delta J_n$ represents the jump increment over $[t_n, t_{n+1}]$.
-\end{definition}
-\iffalse
-    For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.
-
-    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
-        The jump component $\Delta J_n$ can be approximated through one of the following approaches:
-        \begin{enumerate}
-            \item For finite-activity processes (where $\nu(\mathbb{R}) < \infty$):
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K_n} J_i
-                  \end{equation}
-                  where $K_n \sim \text{Poisson}(\nu(\mathbb{R})\Delta t)$ and $J_i$ are i.i.d. random variables with distribution $\frac{\nu(dx)}{\nu(\mathbb{R})}$.
-
-            \item For infinite-activity processes, a truncation approach:
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K^{\varepsilon}_n} J^{\varepsilon}_i + c_{\varepsilon}\Delta t
-                  \end{equation}
-                  where $K^{\varepsilon}_n \sim \text{Poisson}(\nu(\{x: |x| > \varepsilon\})\Delta t)$, $J^{\varepsilon}_i$ are i.i.d.
-with distribution $\frac{\nu(dx)\mathbf{1}_{|x|>\varepsilon}}{\nu(\{x: |x| > \varepsilon\})}$, and $c_{\varepsilon} = \int_{|x|\leq\varepsilon} x\nu(dx)$.
-        \end{enumerate}
-    \end{proposition}
-\fi
-\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
-    \label{thm:euler_maruyama_convergence}
-    Let $X_t$ be a Lévy process and $\hat{X}_t$ be its Euler-Maruyama approximation with time step $\Delta t$. Then for any fixed $T > 0$:
-    \begin{enumerate}
-        \item (Weak Convergence) For any smooth function $f$ with polynomial growth:
-              \begin{equation}
-                  |\mathbb{E}[f(X_T)] - \mathbb{E}[f(\hat{X}_T)]| \leq C\Delta t
-              \end{equation}
-
-        \item (Strong Convergence) If $\int_{|x|>1} |x|^2 \nu(dx) < \infty$, then:
-              \begin{equation}
-                  \mathbb{E}[\sup_{0\leq t\leq T} |X_t - \hat{X}_t|^2] \leq C\Delta t
-              \end{equation}
-    \end{enumerate}
-    where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.
-
-\end{theorem}
-
-The weak and strong convergence properties ensure that our numerical scheme accurately approximates both the distributional properties and pathwise behavior of the continuous-time process as the time step decreases.
-
-\subsection{Implementing Strategic Experimentation Models}
-\label{appendix:strategic_experimentation_implementation}
-
-In our implementation of the strategic experimentation model from \citet{keller2020undiscounted}, we must discretize both the background signal process $B_t$ and the individual payoff processes $X^i_t$, while preserving the strategic incentives that drive experimentation decisions.
-
-\subsubsection{Discretization of Diffusion-Poisson Processes}
-\label{appendix:discretization_diffusion_poisson}
-
-In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:
-
-\begin{align}
-    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
-    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
-\end{align}
-
-where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes.
-Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:
-
-\begin{align}
-    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
-    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
-\end{align}
-
-For implementation, we denote these increments as:
-
-\begin{align}
-    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
-    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
-\end{align}
-
-where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
-
-\subsubsection{Reward Function Equivalence}
-\label{appendix:reward_equivalence}
-
-A critical challenge in our implementation is reconciling the time-dependent nature of continuous-time rewards with the time-independent reward structure required by the POAMG framework.
-In the original continuous-time model, agents' instantaneous rewards are:
-
-\begin{equation}
-    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
-\end{equation}
-
-where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$.
-To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time.
-We achieve this through a normalization approach:
+where $o_t$ represents the observation at discrete time step $t$ and $B_{t-1:t}$ represents the signal increment in discrete time.
+To address the time-dependent nature of Lévy processes while maintaining compatibility with our POAMG framework, we formulate the reward function for each agent $i$ as:
 
@@
 \end{equation}
+where $\Delta t$ is the discretization time step,
+\begin{equation}
+    X^i_{t-1:t} = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t,
+\end{equation}
+$(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^i_t$ is the increment of the compound Poisson processes over the interval $[t-1, t]$.
+This normalization converts accumulated rewards to instantaneous reward rates, preserving the incentive structure of the original model.
+A comprehensive mathematical treatment of this discretization approach, including convergence properties and the preservation of strategic incentives, is provided in Appendix \ref{appendix:levy_discretization}.
 
-This transformation preserves the incentive structure of the original model while eliminating explicit time dependence. The following proposition establishes this equivalence formally:
+Each agent observes the increments in the public background signal, their own payoff process (dependent on their allocation $a^i$ to the risky arm and the true state $\omega$), and the allocations together with the rewards of all other agents.
+The unique feature of the strategic experimentation model is the explicit form of the symmetric Markov perfect equilibrium, which depends only on three factors: the safe payoff, the expected current payoff of the risky arm, and the expected full-information payoff.
+To validate this theoretical result, we configure POLARIS to measure: (1) The cutoff belief at which agents switch between the safe and risky arm
+(2) The relationship between individual experimentation intensity and group experimentation intensity
+(3) Free-riding behavior as a function of the number of players
+(4) Strategy independence from the specific payoff-generating process
+\iffalse
+    For experimental validation, we implement three distinct payoff-generating processes that preserve the same reward statistics: pure Brownian motion with unknown drift, pure Poisson processes with unknown intensity, and mixed Lévy processes with both continuous and jump components.
+In all three cases, the theory predicts identical equilibrium strategies when expressed in terms of the incentive to experiment $I(\pi) = \frac{f(\pi)-s}{s-m(\pi)}$ when $m(\pi) < s$, and $I(\pi) = \infty$ otherwise, where $\pi$ represents the belief state.
+\fi
+To measure convergence to equilibrium behavior, we track the Kullback-Leibler divergence (KL divergence) between agents' actual strategies and the theoretically optimal strategy specified in Keller and Rady's work.
+The KL divergence is calculated as
 
-\begin{proposition}[Reward Equivalence]
-    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
 \begin{equation}
-        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
+    D_{KL}(P||Q) = \sum_{x} P(x) \log\frac{P(x)}{Q(x)},
 \end{equation}
-    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
-\end{proposition}
 
-\begin{proof}
-    The expected value of the discrete-time reward function is:
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
-                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
-                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
-    \end{align}
+where $P$ represents the agent's learned policy distribution and $Q$ represents the theoretical optimal policy distribution at each belief state:
 
-    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:
-
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
-                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{align}
-
-    This exactly matches the expected instantaneous flow payoff in the continuous-time model.
-\end{proof}
+\begin{equation}
+    a^*(b) =
+    \begin{cases}
+        0                    & \text{if } I(b) \leq k_0,            \\
+        \frac{I(b)-k_0}{n-1} & \text{if } k_0 < I(b) < k_0 + n - 1, \\
+        1                    & \text{if } I(b) \geq k_0 + n - 1.
+    \end{cases}
+\end{equation}
 
 \iffalse
-    \subsubsection{Preservation of Strategic Incentives}
-    \label{appendix:strategic_incentives}
+    We also assess the rate of social learning by measuring the expected time until agents' posterior beliefs concentrate within an $\epsilon$-neighborhood of the true state.
+The background information in this model ensures exponentially fast convergence, which is empirically validated by fitting an exponential decay curve to the mean distance between current beliefs and true state across multiple simulation runs.
+\fi
+For varying group sizes $n \in \{2,4,8,16\}$, we measure the relationship between individual and group experimentation.
+The theory predicts that the set of beliefs for which no experimentation occurs remains unchanged as $n$ increases—a stark manifestation of free-riding behavior.
+Additionally, the theory predicts that in regions of partial experimentation, the intensity per agent will decrease with $n$, while the total group intensity increases.
+These predictions create testable patterns that our POLARIS implementation can validate.
+\iffalse
+    An important methodological insight from this implementation is the impact of the background signal $k_0$ on learning dynamics.
+As $k_0$ approaches zero, the equilibrium strategy converges monotonically to a well-defined limit.
+However, without background information, the strong long-run average criterion would yield an expectation of minus infinity, making the framework inapplicable.
+We thus implement a parametric analysis with diminishing values of $k_0$ to approximate the limit behavior predicted by the theory.
+\fi
 
-    Beyond matching expected rewards, we must ensure that our discretization preserves the strategic incentives that drive experimentation decisions.
-The key strategic consideration in the model is the trade-off between exploitation (choosing the safe arm) and exploration (choosing the risky arm to learn about its quality).
+\begin{figure}[!htbp]
+    \centering
+    \begin{minipage}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/good_belief_over_time.png}
+        \subcaption{Good state beliefs over time, demonstrating convergence to the true state.}
+        \label{fig:good_belief_over_time}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/agent_allocations.png}
+        \subcaption{Agent allocations over time, demonstrating eventual adoption of the best strategy.}
+        \label{fig:agent_allocations}
+    \end{minipage}
 
-    \begin{proposition}[Preservation of Strategic Incentives]
-        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
+    \vspace{0.3cm}
 
-    \end{proposition}
+    \begin{minipage}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/kl_divergence.png}
+        \subcaption{KL divergence between agents' learned strategies and the theoretical optimal strategy as a function of time, demonstrating convergence to equilibrium behavior.}
+        \label{fig:kl_divergence}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation/sweep_allocations/average_cumulative_allocation_per_agent_over_time.png}
+        \subcaption{Average cumulative allocation per agent over time across different network configurations, demonstrating independence from the network size.}
+        \label{fig:average_cumulative_allocation_per_agent_over_time}
+    \end{minipage}
 
-    \begin{proof}
-        In the strategic experimentation model, the incentive to experiment at a given belief $b$ about the state is characterized by:
+    \caption{Learning dynamics in the strategic experimentation model}
+    \label{fig:strategic_experimentation_results}
+\end{figure}
+
+Our experimental results confirm that POLARIS agents converge to the theoretically predicted equilibrium regardless of the specific payoff-generating process employed.
+This validation demonstrates the framework's ability to capture the sophisticated strategic considerations of undiscounted multi-agent learning, providing computational support for the theoretical predictions of Keller and Rady.
+Furthermore, our results show that the mixed Lévy process case—not analytically tractable in the original paper due to its complexity—exhibits the same qualitative behavior as the pure Brownian and Poisson cases, providing evidence for the robustness of the theoretical framework.
+
+\section{Learning Without Experimentation}
+
+We reformulate the learning without experimentation model of \citet{brandl2024} as a Partially Observable Active Markov Game.
+In this formulation, the state space $S = \{s^1, s^2, \ldots, s^m\}$ represents possible states of the world, with a deterministic transition function since the state remains constant.
+Each agent's action space $A^i = \{a^1, a^2, \ldots, a^m\}$ corresponds to potential states, where $a^j$ is the unique optimal action is state $s^j$.
+In addition to observing their neighbors' actions, each agent receives a private signal $o^i_t \in \Omega^i = S$ drawn from distribution:
+
+\begin{equation*}
+    O^i(s,o) =
+    \begin{cases}
+        q               & \text{if } s = o \\
+        \frac{1-q}{m-1} & \text{otherwise}
+    \end{cases}
+\end{equation*}
+where $q > 1/m$ is the signal accuracy. Since agents don't observe real rewards in this model, we construct an observed reward function that facilitates learning:
+
+\begin{equation*}
+    R^i(s_t, a^i_t) = v(o^i_t, a^i_t) = \frac{q \cdot \mathbb{I}_{\{a^i_t = \varphi(o^i_t)\}} - (1 - q) \cdot \mathbb{I}_{\{a^i_t \neq \varphi(o^i_t)\}}}{2q - 1}
+\end{equation*}
+
+where $\varphi$ maps states to their corresponding correct actions.
+\footnote{Formally, the mapping $\varphi: S \rightarrow A$ is a bijective function defined as $\varphi(s^j) = a^j$ for all $j \in \{1,2,...,m\}$, associating each state with the action having the same index.} This construction ensures the expected reward matches the true utility function in expectation: \footnote{See \ref{appendix:observed_reward_derivation} for a detailed derivation and the formulation for a generic dimension $m$.}
+
+\begin{equation*}
+    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a) = \mathbb{I}_{\{a = \varphi(s)\}}.
+\end{equation*}
+
+This construction ensures agents are rewarded based on their posterior belief given the private signal, maintaining compatibility with the original model's incentive structure while providing a learning signal for POLARIS.
+
+\subsection{Experimental Setup}
+
+We implement comprehensive experiments to validate these theoretical predictions and explore the learning dynamics under various network structures.
+Our experimental protocol examines network sizes of $n \in \{1, 2, 4, 8\}$ agents; network topologies including complete, ring, star, and random networks; signal accuracy of $p = 0.75$ (matching the paper's example where $r_{\text{aut}} = 0.14$, $r_{\text{crd}} = 0.55$, and $r_{\text{bdd}} = 1.10$); and learning metrics consisting of empirical learning rates extracted via log-linear regression.
+
+For each configuration, we run multiple independent episodes with randomly initialized true states and agents.
+Our analysis follows a two-stage approach.
+First, for each episode $k$, we track each agent's incorrect action probability over time:
 \begin{equation}
-            I(b) = \frac{f(b) - s}{s - m(b)}
-        \end{equation}
-        when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad.
-In our discrete-time approximation, the corresponding incentive is:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)}
-        \end{equation}
-        where $\hat{f}(b)$ and $\hat{m}(b)$ are the discrete-time analogs.
-
-        Let us elaborate on why $\hat{f}(b) \to f(b)$ and $\hat{m}(b) \to m(b)$ as $\Delta t \to 0$. In the continuous-time model, the expected flow payoff of the risky arm at belief $b$ is:
-        \begin{equation}
-            f(b) = b f_1 + (1-b) f_0
-        \end{equation}
-        where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$.
-In our discrete-time approximation, we have:
-        \begin{equation}
-            \hat{f}(b) = b \hat{f}_1 + (1-b) \hat{f}_0
-        \end{equation}
-        where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
-        From our reward equivalence result, we know that:
-        \begin{align}
-            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
-                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
-        \end{align}
-
-        The Brownian motion term has $\mathbb{E}[\sigma(W^i_t - W^i_{t-1})] = 0$ and $\text{Var}[\sigma(W^i_t - W^i_{t-1})] = \sigma^2 \Delta t$.
-By the martingale property of Brownian motion, this term contributes zero to the expected value but introduces variance of order $O(\Delta t)$.
-Thus:
-        \begin{equation}
-            \hat{f}_1 = \alpha_1 + \lambda_1\mu_1 + O(\Delta t) \to f_1 \text{ as } \Delta t \to 0
+    \hat{P}_{t,k}^i = 1 - \pi_t^i(a_{\omega_k} | b^i_t, z^i_t)
 \end{equation}
 
-        Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
-        Therefore, we can establish that:
+And estimate individual learning rates by fitting: 
 \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)} = \frac{b \hat{f}_1 + (1-b) \hat{f}_0 - s}{s - \hat{f}_0} = \frac{b(\hat{f}_1 - \hat{f}_0) + \hat{f}_0 - s}{s - \hat{f}_0}
+    \log \hat{P}_{t,k}^i \approx -r_k^i t + c_k^i
 \end{equation}
 
-        As $\Delta t \to 0$, we have $\hat{f}_1 \to f_1$, $\hat{f}_0 \to f_0$, and consequently:
+To identify the fastest and slowest learners for that episode: 
 \begin{equation}
-            \hat{I}(b) \to \frac{b(f_1 - f_0) + f_0 - s}{s - f_0} = \frac{b f_1 + (1-b) f_0 - s}{s - f_0} = \frac{f(b) - s}{s - m(b)} = I(b)
+    i_{\text{fast}}^k = \arg\max_i r_k^i
+\end{equation} 
+ \begin{equation}
+    i_{\text{slow}}^k = \arg\min_i r_k^i
 \end{equation}
 
-        The convergence of incentives directly implies convergence of optimal policies.
-In the continuous-time model, the symmetric Markov perfect equilibrium characterized in \citet{keller2020undiscounted} has the form:
+Second, we aggregate the performance of fastest and slowest learners across episodes:
+
 \begin{equation}
-            \kappa^*(b) =
-            \begin{cases}
-                0                    & \text{if } I(b) \leq k_0,            \\
-                \frac{I(b)-k_0}{N-1} & \text{if } k_0 < I(b) < k_0 + N - 1, \\
-                1                    & \text{if } I(b) \geq k_0 + N - 1.
-            \end{cases}
+    \bar{P}_t^{\text{fast}} = \frac{1}{N_{\text{episodes}}} \sum_{k=1}^{N_{\text{episodes}}} \hat{P}_{t,k}^{i_{\text{fast}}^k}
 \end{equation}
-        where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players.
-The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.
-
-        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
-    \end{proof}
-
-\fi
-\subsection{Relation to Policy-Invariant Reward Transformations}
-\label{appendix:policy_invariance}
-
-Our approach to time-independent reward formulation can be viewed through the lens of policy-invariant reward transformations, as developed in the reinforcement learning literature by \citet{ng1999policy}.
-
-\begin{definition}[Potential-Based Reward Shaping]
-    A reward transformation $\tilde{R}(s, a, s') = R(s, a, s') + F(s, s')$ is potential-based if there exists a potential function $\Phi: S \to \mathbb{R}$ such that $F(s, s') = \gamma\Phi(s') - \Phi(s)$ for all $s, s' \in S$, where $\gamma$ is a discount factor.
-\end{definition}
-
-\begin{theorem}[Ng-Harada-Russell \citep{ng1999policy}]
-    If a reward transformation is potential-based, then the optimal policy under the transformed reward function is also optimal under the original reward function, and vice versa.
-\end{theorem}
-
-While our transformation does not directly fit the potential-based formulation (since we're normalizing by $\Delta t$ rather than adding a potential difference), it shares the crucial property of preserving optimal policies.
-The following result establishes this connection:
-
-\begin{proposition}[Connection to Policy-Invariant Transformations]
-    The transformation from time-dependent rewards in the continuous-time model to time-independent rewards in the POAMG framework preserves policy optimality in the limit as $\Delta t \to 0$.
-\end{proposition}
-
-\begin{proof}
-    The original cumulative reward over a time interval $[0, T]$ is:
 \begin{equation}
-        \int_0^T [(1-a^i_t)s + a^i_t\alpha_s] dt + \int_0^T a^i_t \sigma dW^i_t + \int_0^T a^i_t dC^i_t
+    \bar{P}_t^{\text{slow}} = \frac{1}{N_{\text{episodes}}} \sum_{k=1}^{N_{\text{episodes}}} \hat{P}_{t,k}^{i_{\text{slow}}^k}
 \end{equation}
 
-    The discretized cumulative reward is:
-    \begin{equation}
-        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
-    \end{equation}
-    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.
+where $N_{\text{episodes}}$ is the number of episodes.
+This methodology allows us to examine the distribution of learning rates that emerge from the same network structure across different realizations, revealing whether the theoretical bounds hold regardless of which specific agent becomes the fastest or slowest learner in any given episode.
 
-    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral.
-Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
-\end{proof}
+\subsection{Results and Analysis}
 
-\section{Observed Reward Function}
-\label{appendix:observed_reward_derivation} In our reinforcement learning
-implementation, agents need to learn from observed rewards that reflect the optimality
-of their actions with respect to the true state of the world. However, since agents
-do not directly observe the true state $\omega$, we need to construct a reward
-function based on their observations $o$ that preserves the expected reward
-structure. This appendix provides a detailed derivation of the observation-based
-reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
-    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
-observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
-state. We need to construct an observation-based reward function $v(o, a): \Omega
-    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
-\begin{equation}
-    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
-    a \in A.
-\end{equation}
+Our experimental results provide strong validation of the theoretical predictions while revealing additional insights into the learning dynamics.
+We begin by addressing a key methodological consideration before examining our main findings.
 
-In other words, the expected value of the observation-based reward $v(o, a)$
-over all possible observations $o$ given the state $s$ should equal the true
-reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
-    m$ matrix representing the observation distributions, where $m = |S|$ and assume
-the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
-the probability of observing observation $o$ in state $s$:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
-        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
-        \vdots           & \vdots           & \ddots & \vdots           \\
-        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
-    \end{bmatrix}
-\end{equation}
+\paragraph{Methodological Context} The theoretical autarky rate of $r_{\text{aut}} \approx 0.14$ (derived using large deviation theory for random walks) differs substantially from the empirical single-agent POLARIS performance of approximately $0.35$ (Figure \ref{fig:size_comparison}).
+This difference reflects fundamental methodological distinctions: the theoretical analysis assumes agents follow the maximum likelihood strategy with perfect signal processing, while POLARIS agents learn policies through reinforcement learning with our constructed reward function and Transformer-based processing.
+Additionally, the theoretical rate derives from asymptotic analysis as $t \to \infty$, whereas our empirical measurements occur over finite horizons.
+Despite these methodological differences, both approaches provide complementary insights into learning performance bounds and achievable rates in practice.
 
-We assume that observation distributions are linearly independent across states,
-which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
-    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
-more likely to generate its corresponding observation than any other observation.
-For each action $a \in A$, we define a utility vector
-$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
-\begin{equation}
-    \bm{u}_{a} =
-    \begin{bmatrix}
-        u(s^{1}, a) \\
-        u(s^{2}, a) \\
-        \vdots      \\
-        u(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/fastest_slowest_network_sizes_evolution.png}
+    \caption{Fastest vs slowest agent learning trajectories across network sizes.
+Each subplot shows the mean incorrect action probability over time with $95\%$ confidence intervals (shaded regions) for the fastest (green) and slowest (red) learning agents.
+The learning rates $r$ are calculated using log-linear regression.
+Results demonstrate the learning barrier effect where slowest agents remain bounded while fastest agents achieve superior performance in larger networks.}
+    \label{fig:size_comparison}
+\end{figure}
 
-Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
-    ^{k}$ for action $a$:
-\begin{equation}
-    \bm{v}_{a} =
-    \begin{bmatrix}
-        v(s^{1}, a) \\
-        v(s^{2}, a) \\
-        \vdots      \\
-        v(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
+Our analysis reveals three key phenomena that validate and extend the theoretical predictions: the emergence of learning barriers, the realization of coordination benefits, and the dynamic formation of information revelation roles.
 
-The condition that expected observation-based rewards match true rewards can be written
-as a linear system:
-\begin{equation}
-    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
-\end{equation}
+\paragraph{Learning Barriers Emerge Systematically} Across all network configurations and episodes, we consistently observe a significant reduction in the slowest-learning agent's rate compared to the autarky rate.
+Figure \ref{fig:size_comparison} demonstrates this barrier effect by aggregating the trajectories of whichever agent learns slowest in each episode.
+This finding directly supports the theoretical prediction of Theorem 1.
+While we cannot observe whether the bound significantly exceeds the autarky rate as the theorem suggests—such validation would require much larger networks and higher computational resources—the consistent emergence of learning barriers across all configurations provides strong empirical support for the theoretical framework.
 
-where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
-is:
-\begin{equation}
-    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
-\end{equation}
+\paragraph{Coordination Benefits Materialize in Larger Networks} In networks with $n \geq 4$ agents, the fastest-learning agents consistently demonstrate superior performance compared to isolated agents, confirming the coordination benefits predicted by Theorem 2.
+This demonstrates that social learning enables some agents to surpass single-agent performance, though at the expense of others.
+The systematic nature of this improvement across different network sizes suggests that the coordination benefits are robust features of multi-agent social learning rather than artifacts of specific configurations.
+However, similar to our findings on learning barriers, we cannot observe whether the learning rate of the slowest-learning agent can surpass the autarky rate for sufficiently large networks as the theorem suggests.
 
-This gives us the vector of observation-based rewards that satisfy our expected
-reward condition. For each observation $o_{j}$ and action $a$, the observation-based
-reward is:
-\begin{equation}
-    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
-\end{equation}
+\paragraph{Information Revelation Through Dynamic Role Assignment} Our results reveal a systematic pattern where agents naturally emerge as either information generators or information exploiters within each episode.
+The agents that learn slowest exhibit higher variance in their action choices (evident from the wider confidence intervals in Figure \ref{fig:size_comparison}), indicating more exploratory behavior that enables other agents to make better-informed decisions.
+Crucially, this division of labor emerges dynamically—different agents assume these roles across episodes, suggesting the phenomenon arises from learning dynamics rather than fixed agent characteristics.
 
-where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
-$\bm{\mu}^{-1}$.
-\paragraph{Binary Case Example}
-For the special case with two states of the world ($m = 2$) and symmetric
-observations with accuracy $q > 0.5$, the observation distribution matrix is:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        q   & 1-q \\
-        1-q & q
-    \end{bmatrix}
-\end{equation}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/fastest_slowest_network_types_evolution.png}
+    \caption{Fastest vs slowest agent learning trajectories across network topologies.
+Each subplot compares performance in different network structures (complete, ring, star, random) with 4 agents.
+The confidence intervals reveal how network topology affects the learning rate disparity between fastest and slowest agents, with complete networks showing the most pronounced differentiation due to enhanced information sharing.}
+    \label{fig:type_comparison}
+\end{figure}
 
-This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
-and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
-The inverse of this matrix is:
-\begin{equation}
-    \bm{\mu}^{-1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q      & -(1-q) \\
-        -(1-q) & q
-    \end{bmatrix}
-\end{equation}
+\paragraph{Network Structure Shapes Information Flow} Figure \ref{fig:type_comparison} reveals how network topology influences learning dynamics.
+Complete networks facilitate the most effective information sharing, producing the largest performance gaps between fastest and slowest learners.
+Ring networks show more uniform learning rates due to limited information flow, while star networks create pronounced differences between central and peripheral agents.
+These patterns align with theoretical insights that information aggregation depends critically on network structure, though the specific mechanisms through which topology affects learning warrant further investigation.
 
-In our implementation, we set the true reward as the indicator function for taking
-the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
-    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
-utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
-is:
-\begin{equation}
-    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q \\
-        -(1-q)
-    \end{bmatrix}
-\end{equation}
+To understand the underlying mechanisms determining which agents become information generators, we examine the roles of network position and signal quality—two factors that could potentially explain the emergence of learning disparities.
 
-This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
-the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
-$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
-action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
-observation-based reward vector is:
-\begin{equation}
-    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        -(1-q) \\
-        q
-    \end{bmatrix}
-\end{equation}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/slowest_agent_network_positions.png}
+    \caption{The position of the slowest-learning agent in the network over time.
+The frequency of being the slowest-learning agent is calculated as the average number of episodes that this position is occupied by the slowest-learning agent.
+The slowest-learning agent is the agent that learns the slowest in each episode.}
+    \label{fig:slowest_agent_network_positions}
+\end{figure}
 
-Combining these results, we can express the observation-based reward function for
-any action-observation pair $(a, o)$ as:
-\begin{equation}
-    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
-        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
-\end{equation}
+\paragraph{Signal Quality, Not Network Position, Determines Learning Roles} Our analysis reveals that network position alone cannot predict learning performance.
+Figure \ref{fig:slowest_agent_network_positions} shows that the identity of the slowest-learning agent distributes approximately uniformly across network positions, indicating that structural network advantages do not systematically determine learning performance.
+This finding suggests that network topology alone cannot predict which agents will act as information generators.
 
-where $\varphi$ maps observations to their corresponding actions. The derived
-observation-based reward function has an intuitive interpretation. When an agent
-takes an action matching its observation ($a = o$), it receives a positive
-reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
-($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
-0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
-increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
-informative), the reward for matching observation and action approaches 1, and the
-penalty for mismatching approaches 0, meaning that the observed reward function
-converges to the true reward function. This reward structure incentivizes agents
-to match their actions to their observations when signals are reliable, but also
-allows them to learn to override their immediate observations when the actions
-of other agents provide stronger evidence about the true state through beliefs.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/signal_quality_vs_learning_performance.png}
+    \caption{The learning performance of POLARIS agents as a function of the signal quality.
+Each point corresponds to a single agent in a single episode.
+The signal quality is calculated as the average correctness of the private signal within the episode.}
+    \label{fig:signal_quality_vs_learning_performance}
+\end{figure}
+
+In contrast, Figure \ref{fig:signal_quality_vs_learning_performance} demonstrates a strong positive correlation between signal quality and learning performance.
+Agents who receive lower-quality private signals consistently exhibit slower learning rates, indicating that the primary determinant of becoming a slow learner is the stochastic realization of signal quality rather than strategic positioning within the network.
+Agents receiving more accurate private signals naturally learn faster, while those receiving noisier signals become information generators whose exploratory behavior, though individually costly, benefits the overall network through enhanced information revelation.
+
+\paragraph{Implications and Validation} These results demonstrate that our POAMG framework successfully captures the essential features of social learning without experimentation, validating both the learning barriers that limit information aggregation and the coordination benefits that emerge in well-connected networks.
+The computational approach complements theoretical analysis by revealing the dynamics of strategy discovery and the distributional properties of learning rates across different network configurations.
+
+Crucially, our episode-wise analysis methodology shows that the theoretical bounds from \citet{brandl2024} represent robust properties of the multi-agent learning system rather than characteristics of specific agents.
+In any given episode, different agents may assume the roles of fastest or slowest learners, yet the aggregate behavior consistently respects the theoretical limits.
+This emergent division of labor—where some agents naturally become information generators while others exploit this information—arises from the learning dynamics themselves rather than from predetermined agent roles, providing computational validation for the theoretical insights about social learning barriers and coordination benefits.

### 2025-05-26 paper/theory.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
-\setcounter{proposition}{0}
-\setcounter{assumption}{0}
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
-
-\chapter{Reinforcement Learning Background}
-
-\label{appendix:rl_details}
-This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.
-
-\section{Reinforcement Learning Foundations}
-
-Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty.
-In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}.
-This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:
-
+We adapt the framework in \citet{kim2022influencing} to the partially observable setting and formalize the problem of multi-agent learning as a Partially Observable Active Markov Game with periodic policy updates.
+Throughout the paper, we will use the bold convention to denote the collection of joint sets, joint variables and joint functions for $i \in I =\{1,\ldots,n\}$, where $\boldsymbol{X} := \times_{i \in I} X^i$ for set $X^i$, $\boldsymbol{x} := \{x_1, \ldots, x_n\}$ for variable $x^i$ and $\boldsymbol{G}(\cdot) := \prod_{i \in I} G^i(\cdot)$ for function $G^i(\cdot)$.
+
+\section{Partially Observable Active Markov Games}
+In social learning environments, agents rarely possess complete information about the underlying state of the world.
+Instead, they receive private signals—often limited and noisy—that only partially reveal the true state, while also observing the actions of other participants rather than their private information.
+This fundamental information asymmetry is a cornerstone of economic models of social learning.
+The challenge of inferring valuable information from others' actions while acknowledging the confounding influence of their own social learning creates rich strategic dynamics that cannot be captured by frameworks assuming full observability.
+This necessitates extending our theoretical approach to the partially observable setting.
+Standard approaches to partial observability, such as Partially Observable Markov Decision Processes (POMDPs) and Decentralized POMDPs, address this challenge in single-agent and cooperative multi-agent contexts respectively.
+However, these frameworks do not adequately capture the strategic nature of policy evolution that characterizes the social learning environments, and neither do they allow for flexible modeling of the reward functions.
+Building on the Active Markov Game formulation of \citet{kim2022influencing}, we introduce Partially Observable Active Markov Games (POAMGs), which integrate belief state dynamics with evolving policy parameters to model sophisticated social learning dynamics under uncertainty.
+
+\begin{definition}[Partially Observable Active Markov Game]
+    A Partially Observable Active Markov Game is defined as a tuple $M_n = \langle I, S, \boldsymbol{A}, T, \boldsymbol{O}, \boldsymbol{R}, \boldsymbol{\Theta}, \boldsymbol{U} \rangle$, where:
     \begin{itemize}
-    \item $S$ is the state space, representing all possible configurations of the environment
-    \item $A$ is the action space, representing all possible decisions available to the agent
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
-    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
-    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
+        \item $I = \{1, \ldots, n\}$ is the set of $n$ agents;
+        \item $S$ is the state space, assumed to be discrete and finite;
+        \item $\boldsymbol{A} = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$;
+        \item $T: S \times \boldsymbol{A} \mapsto \Delta(S)$ is the Markovian state transition function, with $T(s'|s, \boldsymbol{a})$ denoting the probability of transitioning to state $s'$ after taking joint action $\boldsymbol{a}$ in state $s$;
+        \item $\boldsymbol{O} = \times_{i \in I} O^i$ is the joint observation function, with $O^i: S \times \Omega^i \mapsto \Delta(\Omega^i)$ denoting the observation function for agent $i$ and $\Omega^i$ denoting the observation space for agent $i$;
+        \item $\boldsymbol{R} = \times_{i \in I} R^i$ is the joint reward function, with $R^i: S \times \boldsymbol{A} \mapsto \mathbb{R}$ denoting the reward function for agent $i$;
+        \item $\boldsymbol{\Theta} = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$;
+        \item $\boldsymbol{U} = \times_{i \in I} U^i$ is the joint Markovian policy update function, with
+              $U^i: \Theta^i \times O^i \times \boldsymbol{A} \times R^i \times O^i \mapsto \Delta(\Theta^i)$ denoting the policy update function for agent $i$.
     \end{itemize}
-
-The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions.
-The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter.
-The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.
-
-The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs.
-This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem.
-However, this assumption becomes problematic in multi-agent settings, as we will discuss next.
-
-\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}
-
-Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}.
-MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}.
-These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space, shared among all agents
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\gamma \in [0, 1)$ is the discount factor
-\end{itemize}
-MARL introduces several fundamental challenges beyond those encountered in single-agent RL.
-The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system.
-Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}.
-In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions.
-MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings.
-Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.
-
-\section{The Non-Stationarity Challenge}
-The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}.
-To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent.
-When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$.
-From agent $i$'s perspective, the effective transition function becomes:
+\end{definition}
+This formulation extends the Active Markov Game framework by incorporating observation functions that mediate agents' perceptions of the environment state.
+Next, we define policies of the agents based on their beliefs about the underlying state of the environment.
+
+\begin{definition}[Belief-Based Policy]
+    Under partial observability, each agent $i$ maintains a belief state $b_t^i \in B^i$ at time $t$, representing its probability distribution over states given its observation history.
+The policy of agent $i$ is defined as a mapping from belief and parameter spaces to distributions over actions:
     \begin{equation}
-    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
+        \pi^i: B^i \times \Theta^i \mapsto \Delta(A^i)
     \end{equation}
-where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$.
-When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$.
-This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL.
-When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}.
-This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}.
-Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}.
-The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}.
-These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.
-
-\section{Traditional Approaches to Non-Stationarity}
-Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:
-
-\subsection{Independent Learning}
-The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}.
-This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents.
-Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences.
-While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.
-
-\subsection{Centralized Training with Decentralized Execution}
-To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}.
-In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.
-
-Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution.
-Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline.
-The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies.
-While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.
-
-\subsection{Opponent Modeling and Population-Based Training}
-Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}.
-This can involve predicting other agents' policies, types, or learning dynamics.
-Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning.
-Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.
-
-The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity.
-While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.
-
-\subsection{Equilibrium Learning and Stability Concepts}
-Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}.
-These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate.
-Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games.
-Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.
-
-The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence.
-While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality.
-Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.
-
-\subsection{Meta-Learning for Non-Stationarity}
-Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}.
-These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem.
-Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.
-
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents.
-While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.
-
-\section{Active Markov Games}
-
-Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}.
-They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.
-
-\subsection{Formal Definition}
-
-An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
-    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
-\end{itemize}
-Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state.
-The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates.
-At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$.
-Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$.
-Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$.
-This process continues until non-stationary policies converge to a recurrent set of joint policies.
-The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.
-
-\subsection{Augmented Transition Function and Stationarity}
-
-The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions.
-To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games.
-In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions.
-However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions.
-The augmented transition function becomes:
-
-\begin{equation}
-    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
-\end{equation}
-The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories.
-By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one.
-This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.
-
-\subsection{Theoretical Properties and Convergence}
-
-Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:
-
-\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:
-
-\begin{equation}
-    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
-\end{equation}
-
-where $\ell = t\%k$ with $\%$ denoting the modulo operation.
-This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies.
-The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence.
-To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}.
-These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.
-
-\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:
-
-\begin{equation}
-    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
+
+    where $\pi^i(a^i|b^i; \theta^i)$ represents the probability of agent $i$ taking action $a^i$ given belief state $b^i$ and policy parameters $\theta^i$.
+\end{definition}
+\iffalse
+The figure below illustrates the structure of the POAMG framework, highlighting the interplay between states, observations, beliefs, and policy parameters.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.9\linewidth]{figures/poamg-structure.pdf}
+    \caption{Structure of a POAMGshowing the relationships between environment state, observations, beliefs, and policy parameters in a two-agent setting.}
+    \label{fig:poamg-structure}
+\end{figure}
+\fi
+
+In partially observable active Markov games, agents form beliefs to infer the underlying state of the environment.
+Unlike standard partially observable settings, these states evolve through the dynamically changing policies of the agents in addition to the environmental dynamics.
+The process unfolds as follows: at time step $t$, each agent $i$ selects an action at state $s_t \in S$ by sampling from its belief-conditioned policy $a^i_t \sim \pi^i(\cdot|b^i_t; \theta^i_t)$.
+When all agents act collectively through joint action $\boldsymbol{a_t}$, the environment transitions from $s_t$ to $s_{t+1}$ with probability $T(s_{t+1}|s_t, \boldsymbol{a}_t)$.
+Subsequently, each agent $i$ receives a reward $r^i_t = R^i(s_t, \boldsymbol{a}_t)$ and adjusts its policy parameters via the update function $U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$, where $\tau^i_t = \{o_t^i, \boldsymbol{a_t}, r^i_t, o_{t+1}^i\}$ is the trajectory for agent $i$ at time $t$ consisting of the current observation $o_t^i$, joint action $\boldsymbol{a_t}$, reward received $r^i_t$, and the next observation $o_{t+1}^i$.
+This adaptive cycle continues until non-stationary policies reach convergence.
+A key insight is that the joint policy update function $\boldsymbol{U}$ depends on $a^i_t$, which directly impacts state transitions and rewards, thereby enabling agent $i$ to strategically shape future collective policies through its individual decisions.
+This explicit modeling of strategic influence constitutes the primary advantage of active Markov games over their stationary counterparts.
+
+\section{Convergence}
+A central question in our analysis is whether the joint process of states, beliefs and policy parameters converges to a well-defined stationary distribution, and under what conditions.
+Following \citet{kim2022influencing}, we establish this connection using the properties of regularly perturbed Markov processes.
+First, we define the joint process, which operates on the joint space of states, beliefs and policy parameters.
+
+\begin{definition}[Joint Process]
+    In a Partially Observable Active Markov Game, the joint process $(s_t, \boldsymbol{b}_t, \boldsymbol{\theta}_t)$ consists of the state $s_t \in S$, the joint belief state $\boldsymbol{b}_t = (b^1_t, \ldots, b^n_t) \in \boldsymbol{B}$ and joint policy parameters $\boldsymbol{\theta}_t = (\theta^1_t, \ldots, \theta^n_t) \in \boldsymbol{\Theta}$ of all agents at time $t$.
+\end{definition}
+We then make the following assumptions on the subprocesses to ensure the ergodicity of the perturbed joint process.
+\begin{assumption}[Communicating State Transition]\label{assumption:1}
+    The state transition $T$ is communicating, meaning that for any two states $s, s' \in S$, there exists a sequence of joint actions $\boldsymbol{a}_1, \boldsymbol{a}_2, \ldots, \boldsymbol{a}_k$ and a sequence of states $s_1, s_2, \ldots, s_{k-1}$ such that:
+    \begin{align}
+        T(s_1|s, \boldsymbol{a}_1) > 0, \quad T(s_2|s_1, \boldsymbol{a}_2) > 0, \quad \ldots, \quad T(s'|s_{k-1}, \boldsymbol{a}_k) > 0
+    \end{align}
+\end{assumption}
+
+\begin{assumption}[Communicating Belief-State Process]\label{assumption:2}
+    The belief-state process is communicating, meaning that for any two belief states $b^i, b'^i \in B^i$, there exists a sequence of joint actions $\boldsymbol{a}_1, \boldsymbol{a}_2, \ldots, \boldsymbol{a}_m$ and a sequence of observations $o^i_1, o^i_2, \ldots, o^i_m$ such that:
+    \begin{align}
+        \mathbb{P}(b^i_{t+m} = b'^i | b^i_t = b^i, \boldsymbol{a}_t = \boldsymbol{a}_1, o^i_{t+1} = o^i_1, \ldots, \boldsymbol{a}_{t+m-1} = \boldsymbol{a}_m, o^i_{t+m} = o^i_m) > 0
+    \end{align}
+\end{assumption}
+Assuming the communicating property of the subprocesses, we can establish convergence of the perturbed joint process to the unique stochastically stable distribution of the unperturbed one, as the perturbation vanishes in the limit.
+\begin{theorem}[Stochastically Stable Distribution]
+    Under Assumptions \ref{assumption:1} and \ref{assumption:2}, as $\epsilon \to 0$, the perturbed joint processes defined by $\epsilon$-perturbed policy update functions converge to the unique stochastically stable distribution $\mu^*$ of the unperturbed joint process $(s_t, \boldsymbol{b}_t, \boldsymbol{\theta}_t)$.
+\end{theorem}
+
+\begin{proof}
+    See Appendix \ref{appendix:stochasticallystable} for a detailed proof.
+\end{proof}
+This convergence result has profound implications for our framework.
+By establishing the existence of a unique stochastically stable distribution, we provide a solid theoretical foundation for defining optimization objectives and analyzing equilibrium behavior in partially observable active Markov games.
+The stochastically stable distribution represents the limiting behavior of the system, independent of initial conditions, allowing us to characterize the long-run outcomes of social learning processes.
+This property is crucial for developing algorithms that optimize for long-term performance rather than myopic rewards, aligning with our goal of modeling sophisticated social learning dynamics.
+
+\section{Incentives}
+We now formalize the optimization objectives for agents in our Partially Observable Active Markov Game framework.
+In contrast to traditional reinforcement learning settings that typically employ discounted rewards, we first focus on the average reward criterion as our fundamental optimization objective.
+The average reward formulation provides several compelling advantages for modeling social learning dynamics.
+As \citet{sutton2018reinforcement} emphasize, this approach is particularly well-suited for continuing tasks without natural episode boundaries—a characteristic that aligns perfectly with the ongoing nature of social learning interactions.
+While economic theory has predominantly employed discounted reward objectives due to their mathematical tractability and natural correspondence to time preference in utility maximization \citep{koopmans1960stationary, stokey1989recursive}, the average reward paradigm better captures the strategic considerations in our framework.
+The key advantage of the average reward approach in our context is its emphasis on the limiting behavior of the multi-agent system.
+When agents engage in repeated strategic interactions over indefinite horizons, their primary concern becomes the long-run system behavior rather than transient dynamics.
+Moreover, unlike discounted objectives that can induce myopic behavior depending on the discount factor, the average reward formulation naturally encourages agents to consider the permanent effects of their actions on other agents' learning processes—a crucial aspect for accurately modeling the strategic dimensions of social learning.
+
+\begin{definition}[Average Reward Objective under Partial Observability]
+    Each agent $i \in I$ in a Partially Observable Active Markov Game aims to find policy parameters $\theta^i$ and update function $U^i$ that maximize its expected average reward $\rho^i \in \mathbb{R}$ based on the joint beliefs $\boldsymbol{b}$:
+    \begin{align}
+        \begin{split}
+            \max_{\theta^i, U^i} \rho^i(\boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{U}) : & = \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \boldsymbol{a}_t) \Bigg|
                 \begin{array}{c}
-            s_0=s, \theta_0=\theta,                                              \\
-            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
-            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
-            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
+                    \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+                    \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b_t}; \boldsymbol{\theta_t}),
+                    s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),        \\
+                    \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+                    \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta_t}, \boldsymbol{\tau_t})
+                \end{array}
+            \right]                                                                                                                                                                                                                                                                                                                          \\
+                                                                                               & = \max_{\theta^i, U^i} \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} b^i(s) \mu^*(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}} \boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^i(s, \boldsymbol{a})
+        \end{split}
+    \end{align}
+
+\end{definition}
+
+This formulation emphasizes that agents aim to maximize their rewards in the limiting behavior of the Markov process, focusing on long-term performance rather than immediate gains.
+The second equality expresses the objective in terms of the stochastically stable distribution $\mu^*$, weighted by agent's belief, connecting our optimization problem to the theoretical results established earlier.
+It is worth noting that this definition assumes beliefs, policy parameters, and policy update functions are all publicly observable.
+Since this assumption rarely holds in practical scenarios, we will implement \textit{variational inference} in our algorithm to enable agents to infer these measures from their partial observations.
+Next, we derive the policy gradients, which we will be the foundation of our algorithm, allowing the agents to maximize their objectives.
+
+\section{Belief-Based Policy Gradients}
+Policy gradient methods are a class of reinforcement learning techniques that directly optimize policy parameters by following the gradient of expected return~\cite{sutton1999policy}.
+Unlike value-based methods, policy gradients explicitly parametrize the policy and update parameters in the direction that improves performance.
+These methods excel in continuous action spaces and can learn stochastic policies~\cite{williams1992simple}.
+In partially observable settings, policy gradients require adaptation to handle belief states rather than true states~\cite{kaelbling1998planning}.
+Modern approaches like Proximal Policy Optimization~\cite{schulman2017proximal} have further improved stability and sample efficiency of these methods through constrained policy updates.
+
+Our framework extends these concepts to multi-agent settings with non-stationary policies by incorporating the Active Markov Game formulation of \citet{kim2022influencing}.
+The key innovation in our approach is conditioning value functions not just on belief states, but on the joint space of states, belief states, and policy parameters of all agents.
+This allows us to explicitly model how an agent's actions influence both the environmental dynamics and the learning processes of other agents.
+
+While our theoretical framework proposes maximizing over both policy parameters $\theta^i$ and update functions $U^i$, this joint optimization presents significant computational challenges.
+As noted in \citet{kim2022influencing} optimizing over policy update functions essentially constitutes a long-horizon meta-learning problem, which remains computationally intractable for many realistic multi-agent settings.
+Following their practical approach, we simplify the optimization problem by focusing exclusively on learning optimal fixed-point policies that influence joint policy behavior while using standard update rules:
+
+\begin{align}
+    \max_{\theta^i} \rho^i_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i} \lim_{T \to \infty} \mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^T R^i(s_t, \boldsymbol{a}_t) \bigg|
+        \begin{array}{c}
+            \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+            \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_t; \boldsymbol{\theta}_t),
+            s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),                                  \\
+            \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+            \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
         \end{array}
         \right]
+\end{align}
+
+This formulation still preserves the essence of our framework—capturing how agent $i$'s actions influence other agents' learning trajectories—while making the optimization problem tractable.
+Under the stochastically stable distribution discussed earlier, this simplified objective becomes independent of initial conditions, further supporting the practical viability of our approach.
+Under the average reward formulation, we define the differential value function for agent $i$ as:
+
+\begin{align}
+    v^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty} \mathbb{E}\left[ \sum_{t=0}^T \left(R^i(s_t, \boldsymbol{a}_t) - \rho^i_{\theta^i}\right) \Bigg|
+    \begin{array}{c}
+        s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\
+        \boldsymbol{a}_t \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_t; \boldsymbol{\theta}_t),
+        s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),                                         \\
+        \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+        \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
+    \end{array}
+    \right]
+\end{align}
+
+This function represents the expected total difference between future rewards and the average reward $\rho^i_{\theta^i}$ when starting from state $s$, belief states $\boldsymbol{b}$, and policy parameters $\boldsymbol{\theta}$.
+It serves as a crucial component in deriving the policy gradient theorem for our framework.
+
+\begin{theorem}[Partially Observable Active Average Reward Policy Gradient Theorem]
+    \label{thm:avg_gradient}
+    The gradient of the active average reward objective with respect to agent $i$'s policy parameters $\theta^i$ in a partially observable setting is:
+    \begin{align}
+        \nabla_{\theta^i} J^i_\pi(\theta^i) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i} \nabla_{\theta^i} \pi^i(a^i|b^i; \theta^i) \sum_{a^{\neg i}} \pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
+        \label{eq:avg_gradient}
+    \end{align}
+
+    where the action-value function $q^i_{\theta^i}$ is defined as:
+    \begin{align}
+        q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'} T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'} \boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'} \boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^i(s, \boldsymbol{a}) - \rho^i_{\theta^i} + v^i_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
+        \label{eq:avg_action_value}
+    \end{align}
+
+    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing the belief update function.
+
+\end{theorem}
+
+\begin{proof}
+    See Appendix \ref{appendix:avg_gradient} for a detailed proof.
+\end{proof}
+This theorem extends the policy gradient result in \citet{kim2022influencing} to partially observable settings by integrating over the joint space of states, beliefs, and policy parameters according to their stochastically stable distribution $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$.
+The resulting gradient has a form similar to the standard policy gradient theorem, but with important modifications.
+First, our policies are conditioned on belief states rather than actual states.
+Second, the action-value function must account for belief updates and policy parameter evolution.
+Third, the expectation is taken over the stochastically stable distribution of the joint state space, while also considering the stochasticity of the observations.
+
+Building on the theoretical foundations established for the average reward criterion, we now turn our attention to the discounted return formulation.
+This alternative objective function is particularly relevant in economic contexts where agents exhibit time preferences, valuing immediate rewards more highly than delayed ones.
+The following section develops the mathematical framework for optimizing agent behavior under discounted returns, providing a complementary perspective to our earlier analysis.
+By examining both criteria, we offer a comprehensive theoretical foundation that can accommodate different modeling assumptions about how agents value future consequences of their actions.
+
+\section{Discounted Returns}
+
+While the average reward criterion provides a principled approach for analyzing limiting behaviors in continuing tasks, the discounted return objective remains predominant in economic models of social learning \citep{keller2005strategic, bolton1999strategic, huang2024learning,brandl2024}.
+This formulation incorporates time preference through a discount factor $\gamma \in [0, 1)$, giving higher weight to near-term rewards and diminishing importance to those further in the future.
+The expected effective planning horizon under discounting is approximately $\frac{1}{1-\gamma}$ steps \citep{kearns2002near}, making it well-suited for scenarios where agents exhibit time preference or where finite planning horizons are appropriate \citep{frederick2002time, sutton2018reinforcement}.
+We begin by formalizing the discounted return objective in our POAMG framework:
+
+\begin{definition}[Discounted Return Objective under Partial Observability]
+    Each agent $i \in I$ in a Partially Observable Active Markov Game aims to find policy parameters $\theta^i$ that maximize its expected discounted return $J^i_{\pi, \gamma}(\theta^i) = v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)$ starting from initial state $s_0$, joint beliefs $\boldsymbol{b}_0$, and joint policy parameters $\boldsymbol{\theta}_0$:
+    \begin{align}
+        \max_{\theta^i} v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0) & := \max_{\theta^i} \mathbb{E}\left[ \sum_{t=0}^{\infty} \gamma^t R^i(s_t, \boldsymbol{a}_t) \bigg|
+            \begin{array}{c}
+                s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0, \\
+                \boldsymbol{a}_{0:\infty} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:\infty}; \boldsymbol{\theta}_{0:\infty}),
+                s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t),  \\
+                \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}),
+                \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
+            \end{array}
+            \right]
+    \end{align}
+
+\end{definition}
+
+The discounted return objective differs fundamentally from the average reward criterion in its treatment of future consequences.
+As $\gamma$ approaches 1, it increasingly resembles the average reward formulation, but with a crucial distinction: even with $\gamma$ arbitrarily close to 1, the discounted formulation still assigns diminishing weight to distant future rewards.
+This property has significant implications for strategic behavior in multi-agent settings, particularly in social learning contexts.
+
+\subsection{Discounted Visitation Measure}
+
+To analyze the behavior of agents operating under discounted returns, we introduce the \textit{discounted visitation measure} (also called occupancy measure).
+This measure represents the normalized expected discounted time spent in each state-belief-policy configuration when following a joint policy \citep{sutton1999policy, Silver2014DeterministicPG}.
+
+\begin{definition}[Discounted Visitation Measure]
+    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi^*$, with an initial distribution $\mu_0$ over the joint state-belief-policy space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
+    \begin{equation}
+        d^{\pi}_{\mu_0} := (1-\gamma) \sum_{t=0}^{\infty} \gamma^t \mu_t
     \end{equation}
 
-where  $0:T$ denotes the sequence from time $0$ to $T$.
-This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.
-
-\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium.
-An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:
+    where $\mu_t$ is the distribution at time $t$ when starting from $\mu_0$, and $\gamma \in [0, 1)$ is the discount factor.
+\end{definition}
+
+This distribution serves two critical purposes in our framework.
+First, it provides a well-defined distribution over which expectations can be taken, even in non-stationary environments where policies are constantly changing.
+Unlike the stochastically stable distribution used in the average reward setting, the discounted distribution automatically exists for any $\gamma < 1$ without requiring additional assumptions on the ergodicity of the underlying processes \citep{puterman1994markov}.
+Second, it directly links to the optimization objective, allowing us to express the expected discounted return as an expectation of immediate rewards under this distribution.
+
+The discounted visitation measure satisfies important properties that facilitate policy optimization. Most notably, it can be expressed as the unique solution to a functional equation:
 
 \begin{equation}
-    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
+    d^{\pi}_{\mu_0} = (1-\gamma)\mu_0 + \gamma \Psi^* d^{\pi}_{\mu_0}
 \end{equation}
-for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$.
-This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system.
-The active equilibrium generalizes several classic solution concepts in game theory.
-Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively.
-Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively.
-This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.
-
-Active Markov Games address the non-stationarity challenge in several fundamental ways.
-By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated.
-The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors.
-Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates.
-Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees.
-Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.
-
-\subsection{Practical Implementations}
-
-Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL.
-Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner.
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games.
-These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.
-
-\section{Extension to Partial Observability}
-
-While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state.
-In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents.
-This partial observability introduces additional challenges for multi-agent learning.
-The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions.
-In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}.
-Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning.
-The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.
-
-In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state.
-Theoretical formulations, as established by Meuleau et al.
-\cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$.
-However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation.
-Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}.
-These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics.
-In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time.
-For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.
-
-\chapter{Proofs Regarding Average Returns}
-
-This section provides the mathematical foundations and detailed proofs for the
-key theoretical results in our Partially Observable Active Markov Game framework
-with average return objectives. We establish the Markov properties of belief transitions
-and joint processes, prove the existence and uniqueness of stochastically stable
-distributions, and derive the policy gradient theorem for average return optimization.
-
-\section{Markov Property of the Joint Process}
-\label{appendix:stochasticallystable}We first establish the Markov properties of
-belief state transitions and the joint process comprising states, belief states,
-and policy parameters. These properties form the foundation for our convergence analysis.
-
-\begin{lemma}[Markov Property of Belief Transitions]
-    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
-    a Markov process under a fixed policy $\pi$, meaning that the distribution of
-    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
-    not on earlier beliefs, actions, or observations.
-\end{lemma}
+
+where $\Psi^*$ is the adjoint of the transition operator $\Psi$ that describes how probability distributions evolve over one timestep.
+This relationship can be seen as a fixed-point equation, where $d^{\pi}_{\mu_0}$ is the unique fixed point of the contractive mapping $(1-\gamma)\mu_0 + \gamma \Psi^*(\cdot)$ in the space of finite measures.
+The existence and uniqueness of this measure is guaranteed for any $\gamma < 1$, providing a solid mathematical foundation for our policy gradient derivations.
+
+\subsection{Policy Gradient Theorem for Discounted Returns}
+
+With the discounted visitation measure established, we now derive the policy gradient theorem that forms the basis for optimization in this framework.
+\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient Theorem]
+    \label{thm:discounted_gradient}
+    The gradient of the discounted return objective $J^i_{\pi, \gamma}(\theta^i) = v^i_{\theta^i}(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)$ with respect to agent $i$'s policy parameters $\theta^i$ in a partially observable active Markov game setting can be expressed as:
+    \begin{align}
+        \nabla_{\theta^i} J^{i}_{\pi, \gamma}(\theta^i) & = \frac{1}{1-\gamma} \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}} d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i} \nabla_{\theta^i} \pi^i(a^i|b^i; \theta^i) \nonumber \\
+                                                 & \quad \sum_{a^{-i}} \pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
+        \label{eq:discounted_gradient}
+    \end{align}
+
+    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted visitation measure starting from initial distribution $\mu_0$, and $q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is the action-value function defined as:
+    \begin{align}
+        q^i_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^i(s, \boldsymbol{a}) + \gamma \sum_{s'} T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'} \boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                \\
+                                                                               & \quad \sum_{\boldsymbol{\theta}'} \boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^i_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
+    \label{eq:discounted_action_value}
+                                                                            \end{align}
+
+\end{theorem}
 
 \begin{proof}
-    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
-    relevant information from the history of observations and actions up to time
-    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
-    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
-            ^{i}$ through the rule:
+    See Appendix \ref{appendix:discounted_proofs} for a detailed proof.
+\end{proof}
+
+This theorem connects the policy gradient to expectations with respect to the discounted visitation measure, providing a principled approach to policy optimization in partially observable multi-agent settings.
+The scaling factor $\frac{1}{1-\gamma}$ accounts for the effective horizon of the discounted objective, with its magnitude increasing as $\gamma$ approaches 1.
+
+In implementation, the choice between these objectives should be guided by the specific characteristics of the social learning scenario being modeled.
+The discounted formulation may be appropriate for settings with finite horizons, impatient agents, or where near-term performance is particularly valued.
+However, for scenarios focused on long-run learning dynamics and asymptotic behavior, the average reward criterion provides a more principled approach by equally valuing rewards across all future time periods.
+
+In practice, computing these gradients exactly is typically infeasible.
+Instead, sample-based approximations and function approximation techniques using neural networks are employed to estimate the gradient from experience.
+Nevertheless, in theory, when agents learn to adapt their policies according to these gradients, they eventually converge to an equilibrium concept related to traditional equilibria, which we will introduce in the following section.
+
+\section{Equilibrium}
+Policy gradient optimization naturally leads agents toward stable configurations where no individual agent can unilaterally improve its reward by changing its policy.
+Given the formalization of our optimization objectives and the policy gradient theorems established above, we now characterize equilibrium concepts in Partially Observable Active Markov Games.
+By following the gradient directions specified in Theorems \ref{thm:avg_gradient} and \ref{thm:discounted_gradient}, agents can iteratively improve their policies to maximize their respective objectives.
+This optimization process naturally leads to the concept of Partially Observable Active Equilibrium, which extends the Active Equilibrium from standard Active Markov Games \cite{kim2022influencing} to account for partial observability while representing the fixed point of the policy gradient optimization process.
+
+\begin{definition}[Partially Observable Active Equilibrium]
+    A Partially Observable Active Equilibrium is a joint policy parameter $\boldsymbol{\theta}^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $\boldsymbol{U}^* = \{U^{i*}, U^{-i*}\}$ such that for all $i \in I$:
+    \begin{align}
+        J^i_{\pi}(\boldsymbol{b}, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) &\geq J^i_{\pi}(\boldsymbol{b}, \theta^i, \theta^{-i*}, U^i, U^{-i*}) \quad \text{(average reward case)} \\
+        J^i_{\pi, \gamma}(\boldsymbol{b}, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) &\geq J^{i}_{\pi, \gamma}(\boldsymbol{b}, \theta^i, \theta^{-i*}, U^i, U^{-i*}) \quad \text{(discounted reward case)}
+    \end{align}
+
+    for all $\boldsymbol{b} \in \boldsymbol{B}$, $\theta^i \in \Theta^i$, $U^i \in \mathcal{U}^i$, where $\mathcal{U}^i$ is the space of possible update functions for agent $i$.
+\end{definition}
+
+This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system while operating under partial observability.
+At equilibrium, no agent can improve its long-term reward (either discounted or average, depending on the formulation) by unilaterally changing either its policy or its update function, overlapping with the definition of the Bayesian Nash equilibrium in non-cooperative games.
+
+Computing partially observable active equilibria exactly is typically intractable due to the complexity of belief spaces and the sophistication of policy update functions.
+Nevertheless, this equilibrium concept provides a theoretical benchmark against which practical algorithms can be evaluated.
+In the next section, we discuss the computational challenges inherent in direct implementation of our theoretical framework, before introducing our practical policy optimization method that approximates equilibrium strategies through policy gradient algorithms.
+
+\section{Challenges with Exact Computation}
+
+Theorems \ref{thm:avg_gradient} and \ref{thm:discounted_gradient} provide mathematically principled approaches for optimizing policies in both average and discounted return settings, but implementing them exactly is computationally infeasible for most real-world applications.
+In partially observable environments, agents must maintain belief states, whose evolution can be governed by the Bayes' rule as:
+
 \begin{align}
@@
 
-    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
-    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
-    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
-    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
-    property.
-\end{proof}
-
-\begin{remark}[Transformer-Based Belief Representation]
-    In practice, transformer architectures can be used to represent and
-    update belief states. In such cases, the belief state is updated
-    through an attention-based mechanism of the form:
-    \begin{equation}
-        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
-    \end{equation}
-
-    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
-    observation and previous belief state through self-attention layers, satisfying the Markov property
-    while capturing complex dependencies between observations and beliefs.
-\end{remark}
-Next, we establish the Markov property of the joint process.
-\begin{lemma}[Markov Property of Joint Process]
-    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
-    a Markov process under periodic policy updates, meaning that the distribution
-    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
-    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
-    states.
-\end{lemma}
-\begin{proof}
-    The state transitions are by definition only dependent on current state and current
-    actions. The remaining parts can be analyzed as follows:
-
-    \textbf{1. Belief
-        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
-    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
-    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
-        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
-    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
-    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
-    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.
-
-    \textbf{2. Policy parameter
-        update:} At every time step $t$, policy parameters are updated according to $U(
-        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
-    Under the Markovian policy update assumption, the update depends only on $\theta
-        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
-        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
-    probability
-    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t}))$
-    depends only on the current state
-    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
-    of states, establishing the Markov property.
-\end{proof}
-\section{Convergence}
-Having established the Markov properties, we now analyze the convergence
-behavior of the joint process to a unique stochastically stable distribution. This
-convergence result is crucial for developing optimization objectives in our framework.
-\begin{theorem}[Stochastically Stable Distribution]
-    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
-    defined by $\epsilon$-perturbed policy update functions converge to the unique
-    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
-        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
-\end{theorem}
-
-\begin{proof}
-    We establish the convergence to the unique stochastically stable distribution by
-    showing that a perturbed Markov process of a partially observable active Markov
-    game is regular. First, let us introduce a small perturbation to the policy update
-    functions:
-    \begin{align}
-        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
-    \end{align}
-
-    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
-    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
-    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
-    probability of transitioning to any other configuration
-    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
-        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
-    probability:
-    \begin{align}
-        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
-                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
-                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
-    \end{align}
-
-    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
-    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
-    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
-    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
-    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
-    of the joint process. We will show that there must exist a path with positive probability
-    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
-    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
-        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
-        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
-    second as follows:
-
-    \textbf{1. Policy Parameter Transition:} Due to the
-    $\epsilon$-perturbation in update functions, there is a positive probability of
-    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
-        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
-    \end{align}
-
-    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
-    $\boldsymbol{\theta}_{2}$.
-
-    \textbf{2. State Transition:} By the communicating
-    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
-    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
-    such that:
-    \begin{align}
-        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
-    \end{align}
-
-    Given the relationship between policies and actions, this sequence of actions has
-    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
-    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
-    for all required actions.
-
-    \textbf{3. Belief State Transition:} By the communicating belief-state
-    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
-        B$, there exists a sequence of observations
-    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
-    \end{align}
-
-    Since observations depend on states, which can be influenced through actions,
-    and actions are determined by policies, there is a positive probability path from
-    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
-    and policy parameters. Combining these three components, we can construct a path
-    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
-        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
-    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
-    classes of the perturbed joint process. Since we have shown that the perturbed
-    joint process has only one recurrent class, it is a regular Markov process. Following
-    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
-    process on a finite state space possesses a unique stationary distribution
-    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
-    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
-    converges to a limit $\mu^{*}$, which is the unique stochastically stable
-    distribution of the original, unperturbed process. Therefore, under the given conditions,
-    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
-    partially observable active Markov game possesses a unique stochastically
-    stable distribution $\mu^{*}$.
-\end{proof}
-\section{Policy Gradient Theorem}
-Having established the convergence to a unique stochastically stable distribution,
-we now derive the policy gradient theorem for optimization in our framework. This
-theorem provides the mathematical foundation for gradient-based algorithms to maximize
-the average return objective.
-\label{appendix:avg_gradient}
-\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
-        Theorem]
-    The gradient of the active average reward objective
-    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
-    setting is:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
-    the belief update function.
-\end{theorem}
-
-\begin{proof}
-    We first define the average reward objective in the partially observable setting:
-    \begin{align}
-        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
-                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
-    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
-        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
-    differential value function $v^{i}_{\theta^i}$ represents the expected total
-    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
-        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
-        ^{i}_{\theta^i}$:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
-    \end{align}
-
-    Following the Bellman equation derivation principles, we can express
-    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
-                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-    represents the belief update function that updates the belief state based on
-    the current belief, action, and new observation. We now define the action-value
-    function $q^{i}_{\theta^i}$ for the partially observable setting:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    Using this definition, we can rewrite the differential value function as:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    To derive the policy gradient, we begin by computing the gradient of the differential
-    value function with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
-                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
-                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    We expand the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
+For environments with large or continuous state spaces, representing and updating these distributions becomes prohibitively expensive.
+Moreover, exact updates require perfect knowledge of observation functions $O^i$ and transition dynamics $T$, which may not be readily available to the agents.
+The complexity compounds in multi-agent settings where agents must reason about others' belief states and policies using Bayesian inference:
+
+\begin{align}
+    \mathbb{P}(\boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t | \tau^i_{0:t}) \propto \mathbb{P}(\tau^i_{0:t} | \boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t) \mathbb{P}(\boldsymbol{b}^{-i}_t, \boldsymbol{\theta}^{-i}_t | \tau^i_{0:t-1})
+\end{align}
+
+This creates nested inference problems—agents maintaining beliefs about others' beliefs—that grow exponentially with the number of agents and the complexity of their policies.
+
+Computing action-value functions adds another layer of intractability, with different formulations for average returns and discounted returns.
+The triple expectations—over next states, observations, and policy parameters— in equations \eqref{eq:avg_action_value} and \eqref{eq:discounted_action_value} require summing over an exponentially large joint space, where the policy parameter space $\Theta^i$ would ideally be modified to be continuous.
+Furthermore, the policy update functions $\boldsymbol{U}$ of other agents are typically unknown, and the recursive nature of the value function creates computational dependencies that quickly become unmanageable.
+
+The policy gradient calculations presented in Equations \eqref{eq:avg_gradient} and \eqref{eq:discounted_gradient} present similarly insurmountable difficulties.
+Computing the stochastically stable distribution $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ for average returns or the discounted visitation measure $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ for discounted returns requires implementing additional algorithms \citep{wicks2012algorithmcomputingstochasticallystable}, while expectations over joint actions create additional combinatorial explosion.
+These computational barriers—state space explosion, nested belief inference, triple expectations, and distribution computation—collectively render exact computation infeasible except for trivial environments.
+The curse of dimensionality is especially severe due to the combined complexity of partial observability, multi-agent interactions, and evolving policies.
+
+To address these computational challenges and make our theoretical framework practically applicable, we develop POLARIS, a neural network-based algorithm that approximates the key components of our framework while maintaining its essential properties.
+
+\section{Algorithm: POLARIS}
+
+In this section, we present POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), our practical implementation of the theoretical framework.
+POLARIS extends and improves upon the FURTHER algorithm \cite{kim2022influencing} with specialized components for belief modeling, information propagation through networks, and advantage-weighted training.
+The algorithm uses neural network approximations to overcome the computational challenges outlined in the previous section while preserving the key insights of our theoretical framework.
+It consists of three integrated modules: a belief processing module, an inference learning module, and a reinforcement learning module, which operate in concert to enable sophisticated social learning in partially observable environments.
+The architecture integrates several neural network components working in tandem: a Transformer-based belief processor~\cite{vaswani2017attention} provides sophisticated temporal pattern recognition through its self-attention mechanisms; an inference module implementing a Graph Neural Network (GNN)~\cite{scarselli2009graph} with temporal attention for network-aware representations; and Multi Agent Soft Actor-Critic (MASAC) following \citet{kim2022influencing} with both average and discounted reward formulations to address the long-term planning requirements of social learning.
+To maintain performance across changing environments, particularly when the true state changes, POLARIS employs Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} that selectively preserves important parameters while allowing adaptation to new conditions.
+We provide the detailed network architectures in Appendix \ref{appendix:neural_architectures}.
+
+\subsection{Belief Processing Module}
+
+The belief processing module employs a Transformer architecture to encode the agent's belief state based on partial observations and joint actions:
+
+\begin{align}
+    b^i_t = f_{\text{Transformer}}(b^i_{t-1}, o^i_t, \boldsymbol{a}_{t-1}; \psi^i_{\text{Transformer}})
+\end{align}
+
+Unlike traditional recurrent approaches, the Transformer architecture introduces crucial advantages for social learning scenarios.
+The self-attention mechanism allows the model to weigh the importance of different parts of the observation history dynamically, enabling it to focus on the most informative signals while downplaying noise or irrelevant information.
+By processing inputs in parallel rather than sequentially, the Transformer enables more efficient training compared to conventional Recurrent Neural Networks, particularly important when dealing with multiple agents and long interaction histories.
+Perhaps most importantly for social learning, the Transformer architecture captures relationships between temporally distant observations more effectively, allowing agents to recognize patterns that may emerge over extended periods of social interaction.
+The Transformer-based belief processor also outputs an explicit belief distribution over possible states:
+
+\begin{align}
+    \mathbb{P}(s|b^i_t) = \text{Softmax}(f_{\text{belief\_head}}(b^i_t)) 
+\end{align}
+
+This explicit representation allows for more interpretable belief states and enables advantage-weighted training, where the belief processing is optimized not just to track observations but also to produce beliefs that lead to high-value actions.
+By maintaining a probability distribution over states rather than just an abstract representation, the model provides transparency into its decision-making process and facilitates debugging and analysis of social learning dynamics.
+
+\subsection{Inference Learning Module}
+
+POLARIS implements a Graph Neural Network (GNN) with temporal attention for network-aware social learning.
+This inference module represents the multi-agent system as a graph where nodes correspond to agents and edges represent observational relationships in the social network.
+The module outputs distribution parameters:
+
+\begin{align}
+    \mu_t, \log\sigma_t = \text{GNN}_{\text{temporal}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i_{\text{GNN}})
+\end{align}
+
+Here, $\mu_t$ and $\log\sigma_t$ parameterize a Gaussian distribution from which latent variables $\boldsymbol{\hat{z}}^{-i}_t$ are sampled, encoding information about other agents' policies and beliefs.
+The GNN architecture adapts dynamically to the network topology, enabling automatic configuration for various social network structures.
+It utilizes multi-head attention mechanisms across both spatial (network) and temporal dimensions, allowing it to differentially weigh connections between agents based on their decision relevance.
+A key feature is the temporal memory system that maintains a sliding window of past states, enabling temporal attention mechanisms that help the model reason about the evolution of other agents' beliefs and strategies over time.
+This approach proves especially effective for complex network topologies where information flow patterns significantly influence learning dynamics.
+
+The inference module learns a mapping from observable trajectories to latent variables that are predictive of other agents' behaviors, optimized using the Evidence Lower Bound (ELBO) objective: \footnote{See \cite{kim2022influencing} for a detailed derivation of the ELBO objective in the sequential setting.}
+
+\begin{align}
+    J^i_{elbo} = \mathbb{E}_{\mathbb{P}(\tau^i_{0:t}),\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{1:t}|\tau^i_{0:t-1};\phi^i_{GNN})}\left[ \sum_{t'=1}^t \log \mathbb{P}(\boldsymbol{a}^{-i}_{t'}|o^i_{t'}, \boldsymbol{\hat{z}}^{-i}_{t'}; \phi^i_{GNN}) \right.
 \\
-                                                                                                  & \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
-                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting back into the original expression, we get:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Rearranging terms:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we define the transition operator that maps the expectation of a function
-    from one time step to the next:
-    \begin{align}
-        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
-                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    We can rewrite our expression as:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we take the expectation with respect to the stationary distribution
-    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
-                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    By the definition of the stationary distribution, we have:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore, the second and third terms in our expression cancel out, giving the
-    final policy gradient theorem:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-\end{proof}
-
-\chapter{Proofs Regarding Discounted Returns}
-\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
-Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
-mathematical foundation.
-\section{Transition Operator and Its Adjoint}
-To establish a rigorous framework for analyzing discounted returns in Partially
-Observable Active Markov Games, we need to formalize how value functions evolve over
-time and how probability distributions propagate through the system. This dual
-perspective is captured by two fundamental operators: the transition operator and
-its adjoint.
-
-\subsection{Definitions and Duality}
-
-We begin by defining the inner product between functions and measures, which forms
-the foundation for the duality relationship between our operators.
-
-\begin{definition}[Inner Product between Functions and Measures]
-    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
-        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
-    Lebesgue integral:
-    \begin{equation}
-        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
-        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
-        {\theta})
-    \end{equation}
-\end{definition}
-
-This inner product captures the expected value of function $f$ with respect to
-measure $\mu$, allowing us to express value functions as expectations with respect
-to appropriate measures.
-
-\begin{definition}[Transition Operator and Its Adjoint]
-    \hfill
-    \begin{enumerate}
-        \item The \textbf{transition operator}
-              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
-                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              maps a bounded measurable function to its expected value after one
-              transition:
-              \begin{align}
-                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-              \end{align}
-
-              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-              represents the belief update function.
-
-        \item The \textbf{adjoint operator}
-              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
-                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              is defined on the space of finite measures such that:
-              \begin{equation}
-                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
-              \end{equation}
-
-              for all
-              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
-              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
-    \end{enumerate}
-\end{definition}
-
-Intuitively, $\Psi$ describes how function expectations evolve forward in time,
-meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
-capturing the propagation of visitation probabilities through the system. The duality
-relationship ensures that expected values can be computed either by applying $\Psi$
-to functions or $\Psi^{*}$ to measures.
-
-\subsection{Properties of the Operators}
-
-These operators possess several important properties that facilitate our
-analysis of discounted returns:
-
-\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
-    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
-    properties:
-
-    \begin{enumerate}
-        \item \textbf{Linearity:}
-              \begin{itemize}
-                  \item For the operator: For any functions
-                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
-                        \end{align}
-
-                  \item For the adjoint: For any measures
-                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Positivity Preservation:}
-              \begin{itemize}
-                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.
-
-                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
-                            \mu$ is also non-negative.
-              \end{itemize}
-
-        \item \textbf{Preservation of Total Measure:}
-              \begin{itemize}
-                  \item For the operator: The operator preserves the constant function
-                        $\mathbf{1}$:
-                        \begin{align}
-                            \Psi \mathbf{1}= \mathbf{1}
-                        \end{align}
-
-                        where $\mathbf{1}$ represents the function that equals 1 everywhere.
-
-                  \item For the adjoint: For any measure
-                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-                        \begin{align}
-                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
-              bounded with:
-              \begin{align}
-                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
-              \end{align}
-
-              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
-                  {b},\boldsymbol{\theta})|$ is the supremum norm.
-
-        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
-              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-              \begin{align}
-                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
-                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-              \end{align}
-
-              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    We prove each property in turn:
-
-    \textbf{1. Linearity:}
-
-    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
-    \begin{align}
-         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For the adjoint: For any measurable function
-    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
-                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
-                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
-                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
-        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
-    measure.
-
-    \textbf{2. Positivity Preservation:}
-
-    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
-        )$:
-    \begin{align}
-        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
-    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
-    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
-        {\theta}) \geq 0$.
-
-    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
-    function $f \geq 0$:
-    \begin{align}
-        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
-    \end{align}
-
-    where the inequality follows from the positivity preservation of $\Psi$ and the
-    fact that $\mu$ is non-negative. Since this holds for all non-negative
-    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.
-
-    \textbf{3. Preservation of Total Measure:}
-
-    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
-    everywhere. Then:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
-    \end{align}
-
-    Since each probability distribution sums to 1, applying them sequentially
-    yields:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
-    \end{align}
-
-    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
-    \begin{align}
-        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
-    \end{align}
-
-    where we used the unit preservation property of $\Psi$. This gives:
-    \begin{align}
-        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-    \end{align}
-
-    \textbf{4. Bound Preservation:}
-
-    For any bounded function $f$ with
-    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
-        ,\boldsymbol{\theta})|$:
-    \begin{align}
-        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
+    \left. - \alpha_{KL} D_{KL}(\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'}|\tau^i_{t'-1}; \phi^i_{GNN})||\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'-1}))\right]
+\end{align}
+
+The ELBO objective balances reconstruction accuracy (predicting other agents' actions) with regularization through the KL divergence term, which encourages temporal consistency in the latent space.
+This is particularly important in social learning settings where abrupt changes in models of other agents can lead to unstable learning dynamics.
+
+The inference module additionally produces opponent belief distributions, enabling agents to model other agents' understanding of the environment:
+
+\begin{align}
+    \mathbb{P}^i(\boldsymbol{b}^{-i}_t|\tau^i_{0:t}) = \text{Softmax}(f_{\text{opponent\_belief}}(\mu_t, \log\sigma_t))
+\end{align}
+
+This second-order belief modeling allows for sophisticated strategic reasoning, as agents can anticipate how others will respond to their actions based not just on past behavior but on inferred beliefs about the environment.
+
+\subsection{Reinforcement Learning Module}
+
+The reinforcement learning module uses the Soft Actor-Critic (SAC) framework with both average and discounted reward formulations.
+The policy and action-value functions are conditioned on belief states and inferred latent variables:
+
+\begin{align}
+    \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) &= 
+    \begin{cases}
+        \text{Categorical}(a^i|\text{MLP}_{\text{policy}}(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for discrete actions} \\
+        \mathcal{N}(\mu(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i), \sigma(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for continuous actions}
+    \end{cases} \\
+    q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}) &= \text{MLP}_{\text{value}}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta})
+\end{align}
+
+For continuous action spaces, the policy network outputs the mean $\mu$ and standard deviation $\sigma$ of a Gaussian distribution, where actions are sampled using the reparameterization trick.
+Then, hyperbolic tangent function is applied to bound the actions within a desired range, with appropriate adjustments to the log probability calculation.
+
+The SAC framework is particularly well-suited for social learning environments due to its entropy regularization, which promotes exploration and prevents premature convergence to suboptimal equilibria.
+By supporting both categorical distributions for discrete action spaces and Gaussian distributions for continuous action spaces, the policy network can express uncertainty about optimal actions—crucial in partially observable settings where perfect inference is rarely possible.
+The value functions measure expected returns conditioned not only on the agent's belief state but also on inferred representations of other agents' policies, enabling strategic reasoning about the long-term consequences of actions in a multi-agent context.
+The RL module is optimized using three objectives, each addressing a different aspect of the learning problem:
+
+\subparagraph{Value Function Objective} POLARIS supports both discounted and average reward formulations to accommodate different types of social learning problems. For discounted returns:
+\begin{align}
+    J^i_q(\psi^i_{\beta}) &= \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
+    y &= r^i + \gamma \cdot v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+\end{align}
+
+where $\gamma \in [0, 1)$ is the discount factor. This formulation is appropriate for scenarios with finite horizons or where near-term performance is particularly valued.
+
+For average reward:
+\begin{align}
+    J^i_q(\psi^i_{\beta}, \rho^i_{\theta^i}) &= \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
+    y &= r^i - \rho^i_{\theta^i} + v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+\end{align}
+
+The average reward formulation better captures long-run learning dynamics and asymptotic behavior by equally valuing rewards across all future time periods.
+By supporting both approaches, POLARIS can be tailored to match the specific characteristics of different social learning scenarios without requiring structural changes to the architecture.
+
+\subparagraph{Policy Objective} Maximizes expected value plus entropy:
+\begin{align}
+    J^i_{\pi}(\theta^i) &= \mathbb{E}_{D^i}\left[\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \sum_{\boldsymbol{a}^{-i}} \pi^{-i}(\boldsymbol{a}^{-i}|\boldsymbol{b}^{-i}, \boldsymbol{\hat{z}}^{-i}) \min_{\beta=1,2} q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, a^i, \boldsymbol{a}^{-i}; \psi^i_{\beta}) \right.
 \\
-                                                           & \quad \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
-                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
-                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
-    \end{align}
-
-    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
-    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.
-
-    \textbf{5. Explicit Form of the Adjoint:}
-
-    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
-    \end{align}
-
-    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
-    \begin{align}
-        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting this back and using the definition of inner product:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
-                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
-                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}
-
-\subsection{Contraction and Propagation}
-
-The properties established above lead to two crucial results: the contraction
-property of the discounted transition operator and the propagation of
-distributions through the adjoint.
-
-\begin{lemma}[Contraction Mapping Property]
-    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
-    contraction mapping on the Banach space of bounded functions on
-    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
-    norm. Specifically, for any two functions
-    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
-    \end{align}
-\end{lemma}
-
-\begin{proof}
-    Using the linearity of $\Psi$ and its bound preservation property:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
-                                                   & \leq \gamma\|f - g\|_{\infty}
-    \end{align}
-
-    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
-    factor $\gamma$.
-\end{proof}
-
-This contraction property leads directly to the invertibility of
-$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
-in discounted settings.
-
-\begin{lemma}[Invertibility of $I - \gamma \Psi$]
-    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
-    invertible, and its inverse can be represented as a Neumann series:
-    \begin{align}
-        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    which converges absolutely in the operator norm.
-\end{lemma}
-
-\begin{proof}
-    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
-    space, then $I - T$ is invertible, with inverse given by the Neumann series
-    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
-    have:
-
-    \begin{align}
-        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    The absolute convergence follows from:
-    \begin{align}
-        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
-    \end{align}
-
-    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
-        \leq 1$ for all $t$.
-\end{proof}
-
-Finally, we establish how distributions evolve in the system through the adjoint
-operator, formalizing the propagation of probability measures.
-
-\begin{lemma}[Distribution Propagation]
-    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
-    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
-\end{lemma}
-
-\begin{proof}
-    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$:
-    \begin{align}
-        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
-                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
-                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
-                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have
-    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
-\end{proof}
-
-The concepts introduced in this section—the transition operator, its adjoint, and
-their properties—provide the mathematical foundation for analyzing discounted returns
-in Partially Observable Active Markov Games. The transition operator $\Psi$
-captures how function expectations evolve forward in time, while its adjoint $\Psi
-    ^{*}$ describes how probability distributions propagate forward in time. This
-duality is fundamental to establishing the connection between value-based and
-distribution-based perspectives in reinforcement learning.
-
-In the next section, we will use these tools to formulate Bellman equations and derive
-policy gradients for maximizing discounted returns in this complex multi-agent setting.
-\section{Bellman Equations and Value Functions}
-In this section, we establish the fundamental recursive relationships that characterize
-the discounted value functions in Partially Observable Active Markov Games.
-These relationships form the basis for our policy gradient derivation and
-practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
-of value functions, then establish the Bellman equations, and finally derive the
-gradient expressions necessary for policy optimization.
-\subsection{Well-Definedness of Value Functions}
-Before deriving recursive relationships, we first establish that the value functions
-are well-defined mathematical objects under our assumptions of bounded rewards and
-discount factors less than 1.
-\begin{lemma}[Well-Defined Value Functions]
-    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
-    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
-    action-value functions
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
-    well-defined and finite for all states, belief states, policy parameters, and actions.
-\end{lemma}
-\begin{proof}
-    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
-    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
-    \begin{align}
-        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
-                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
-                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Similarly, for the action-value function:
-    \begin{align}
-        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
-                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
-                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Thus, both value functions are well-defined and bounded.
-\end{proof}This lemma ensures that our subsequent derivations involving value
-functions are mathematically sound. The boundedness property is particularly important
-when we consider expectations and derivatives of these functions.
-\subsection{Bellman Equations for Discounted Value Functions}
-Next, we establish the recursive relationships between value functions, which
-are fundamental to dynamic programming approaches.
-\begin{lemma}[Bellman Equation for Discounted Value Functions]
-    In a Partially Observable Active Markov Game, the discounted value function
-    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{lemma}
-\begin{proof}
-    By definition, the discounted value function is:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    We can decompose this into the immediate reward and the future discounted
-    returns:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
-                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
-                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    For the first term, we have:
-    \begin{align}
-        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    For the second term, by the law of total expectation:
-    \begin{align}
-         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
-         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Combining these two terms and factoring out common terms:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
-                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
-                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
-\end{proof}The Bellman equation provides a recursive characterization of the
-value function that forms the basis for dynamic programming algorithms. This equation
-captures how current actions influence both immediate rewards and future value through
-their effects on the environment state, belief states, and policy parameters of other
-agents. The key distinction from standard Bellman equations is the inclusion of
-belief updates and policy parameter dynamics, which reflects the complex dependencies
-in partially observable multi-agent settings.
-\subsection{Policy Gradient with Respect to Value Function}
-Having established the recursive relationship for value functions, we now derive
-how the value function gradient depends on policy parameters, which is essential
-for policy optimization.
-\begin{lemma}[Policy Gradient with Respect to Value Function]
-    The gradient of the value function with respect to policy parameters $\theta^{i}$
-    can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-
-    where $\Psi$ is the transition operator defined in the previous section.
-\end{lemma}
-\begin{proof}
-    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
-    \end{align}
-
-    Applying the product rule:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    For the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
-    \end{align}
-
-    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
-        {o}'|s')$, and
-    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
-    do not depend directly on $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Using the transition operator $\Psi$, we can rewrite:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Rearranging:
-    \begin{align}
-        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
-                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
-                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-\end{proof}This lemma expresses the value function gradient in terms of an
-infinite sum of expected Q-values weighted by policy gradients and propagated
-through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
-immediate changes in policy parameters propagate through future timesteps. This
-form of the gradient is central to our discounted policy gradient theorem, which
-we will develop in the next section. The inverse operator can be represented as
-a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
-as the accumulated effect of policy changes over an infinite horizon, weighted
-by the discount factor.
-\section{Discounted Visitation Measure}
-The infinite sum formulation derived in the previous sections, while
-mathematically sound, is not directly amenable to practical computation. In this
-section, we reformulate these expressions in terms of a probability distribution,
-which allows for more efficient estimation through sampling-based approaches. This
-reformulation is central to our policy gradient theorem for discounted returns.
-\subsection{Definition and Properties}
-\begin{definition}[Discounted Visitation Measure]
-    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
-        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
-    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
-    \end{equation}
-
-    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
-    and $\gamma \in [0, 1)$ is the discount factor.
-\end{definition}This measure represents the expected discounted frequency with which
-different states, belief states, and policy parameters are visited when following
-policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
-factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
-distribution, summing to 1 across the entire state-belief-policy space. The discounted
-visitation measure plays a central role in reinforcement learning theory,
-particularly in policy gradient methods. It provides a natural weighting of states
-according to their importance for the discounted objective, as states that are
-visited more frequently or earlier in trajectories receive higher weight. This concept
-generalizes the stationary distribution used in average-reward settings to the discounted
-return framework.
-\begin{lemma}[Evolution of Discounted Visitation]
-    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
-    the adjoint operator as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
-    \end{equation}
-
-    where $\mu_{0}$ is the initial distribution.
-\end{lemma}
-\begin{proof}
-    By the propagation lemma established earlier,
-    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
-    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
-    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
-    measure:
-    \begin{align}
-        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
-                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    The second equality follows from the Neumann series expansion:
-    \begin{align}
-        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
-    \end{align}
-
-    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
-    the total variation norm.
-\end{proof}This establishes the essential connection between the adjoint operator
-and the discounted visitation measure, which is central to the policy gradient
-theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
-time spent in each state-belief-policy configuration, weighted according to the
-discount factor $\gamma$. This connection allows us to transform expressions involving
-$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
-        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
-practical implementations, the discounted visitation measure is rarely computed explicitly
-due to the prohibitive computational cost. Instead, sampling-based approaches are
-used to estimate expectations with respect to this measure. The policy gradient
-theorem leverages this measure to derive update rules that can be efficiently
-implemented using trajectory samples collected from the environment.
-
-\subsection{Existence and Uniqueness}
-To provide a rigorous mathematical foundation for our policy gradient theorem,
-we establish the existence and uniqueness of the discounted visitation measure.
-\begin{lemma}[Existence of the Discounted Visitation Measure]
-    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
-    of finite measures on the joint state-belief-policy space, equipped with the
-    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
-        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
-        )$, the discounted state-visitation measure
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$.
-\end{lemma}
-\begin{proof}
-    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
-    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    converges to a well-defined measure. First, let's recall that
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
-    the total variation norm
-    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
-    we need to show that the series
-    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
-    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
-    joint state-belief-policy space after $t$ transitions, starting from the initial
-    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
-    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
-    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
-    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
-    $\mu_{0}$ with total mass
-    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
-        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
-    \begin{align}
-        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    For $n < m$, the difference between two partial sums is:
-    \begin{align}
-        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
-                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
-                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
-                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
-                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
-                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
-    \end{align}
-
-    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
-    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
-    of this space, the sequence converges to a measure which we denote as
-    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
-    \begin{align}
-        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
-                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
-                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
-                                                                           & = M
-    \end{align}
-
-    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
-\end{proof}Having established existence, we now turn to the uniqueness of the discounted
-visitation measure.
-
-\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
-    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
-    to the functional equation:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
-    \end{align}
-
-    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$.
-\end{lemma}
-\begin{proof}
-    First, we verify that
-    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    satisfies the functional equation:
-
-    \begin{align}
-        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
-                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
-                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
-                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
-                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
-                                                            & = d^{\pi}_{\mu_0}
-    \end{align}
-
-    To prove uniqueness, suppose there exists another measure
-    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    that satisfies the functional equation:
-    \begin{align}
-        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
-    \end{align}
-
-    Let's consider the operator
-    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    defined as:
-    \begin{align}
-        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
-    \end{align}
-
-    For any two measures
-    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
-                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
-                                 & \leq \gamma \|\mu - \nu\|_{TV}
-    \end{align}
-
-    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
-    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
-    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
-    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
-    the uniqueness of the discounted state-visitation measure.
-\end{proof}
-
-\subsection{Connection to Value Function}
-Having established the theoretical properties of the discounted visitation
-measure, we now connect it to the value function, which will provide important
-insights later on.
-
-\begin{lemma}[Value Function as Inner Product]
-    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
-    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
-    the value function can be expressed as:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
-    the Dirac measure concentrated at
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
-    immediate reward function:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-\end{lemma}
-\begin{proof}
-    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
-    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
-        {\theta}_{0})$. By definition of the value function:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
-    \end{align}
-
-    Define the expected immediate reward function
-    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    Then:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
-    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
-        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
-    and measures:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
-    $(I - \gamma \Psi^{*})^{-1}$:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
-        ^{*})^{-1}\mu_{0}$. Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
-                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}This lemma establishes that the value function can be expressed as an
-expectation with respect to the discounted visitation measure, with an appropriate
-scaling factor. This formulation provides a direct link between the value
-function and the distribution of states.
-
-\section{Policy Gradient Theorem}
-Having established the mathematical foundations for discounted returns in
-partially observable multi-agent settings, we now derive the policy gradient theorem
-that forms the basis for practical optimization algorithms. This theorem
-provides a principled expression for computing gradients of the expected
-discounted return with respect to policy parameters, enabling efficient policy improvement.
-The policy gradient theorem connects an agent's policy parameters to its
-expected long-term performance through the discounted visitation measure, providing
-a mathematically rigorous foundation for optimization.
-
-\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
-        Theorem]
-    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
-            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
-    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
-    Markov game setting can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
-                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
-    visitation measure starting from initial distribution $\mu_{0}$, and
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
-    the action-value function defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
-on the lemmas established in previous sections.
-\begin{proof}
-    From our previous lemma, we know that the gradient of the value function can be
-    expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
-    \end{align}
-
-    For notational clarity, we define the term inside the brackets as:
-    \begin{align}
-        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    Now we can write:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For our specific initial state configuration
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Let's define
-    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
-    Dirac measure concentrated at the initial state. We can view
-    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
-    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
-    Dirac measure:
-
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
-                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Recall the duality principle we established earlier, which states that:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
-    \end{align}
-
-    Allowing us to move the operator from acting on the function $g$ to acting on
-    the measure $\mu_{0}$:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From our earlier derivation of the discounted visitation measure, we established
-    that:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
-    \end{align}
-
-    We can now substitute this expression:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
-                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For finite state, belief, and policy parameter spaces, this integral can be
-    written as a sum:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    This completes the proof of the Partially Observable Active Discounted Return
-    Policy Gradient Theorem.
-\end{proof}
-
-The proof reveals a symmetry in the mathematical structure of our results.
-\begin{remark}[Symmetry]
-    From the Value Function as Inner Product lemma, the value function
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
-    measure $d^{\pi}_{\mu_0}$. While its gradient
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of policy-gradient-weighted action values $g$ under the same
-    discounted visitation measure $d^{\pi}_{\mu_0}$.
-\end{remark}
-This symmetric structure provides not only mathematical elegance but also
-practical advantages. It means that the same samples from the discounted visitation
-distribution can be used to estimate both values and policy gradients.
-
-The policy gradient theorem provides the mathematical foundation for agents to optimize
-their policies in ways that account for both the partial observability of the environment
-and the learning dynamics of other agents. This enables sophisticated strategic
-behaviors such as information revelation, teaching, and influence that are
-essential in social learning contexts.
-
-\chapter{POLARIS Architecture}
-\label{appendix:neural_architectures}
-
-This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation.
-We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
-\begin{equation}
-    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
-\end{equation}
-
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
-
-\chapter{Social Learning Implementation}
-
-This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework.
-We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations.
-The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios.
-Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models.
-Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.
-
-\section{Lévy Process Discretization}
-\label{appendix:levy_discretization}
-
-This appendix provides a comprehensive mathematical treatment of the discretization of Lévy processes for implementing strategic experimentation models within our Partially Observable Active Markov Game framework.
-We establish rigorous theoretical foundations for the numerical approximation schemes used in our implementation and analyze their convergence properties and preservation of strategic incentives.
-
-\subsection{Mathematical Foundations of Lévy Processes}
-\label{appendix:levy_foundations}
-
-Lévy processes form a fundamental class of stochastic processes that include Brownian motion and Poisson processes as special cases.
-They are characterized by stationary and independent increments, serving as the natural continuous-time generalization of random walks.
-
-\begin{definition}[Lévy Process]
-    A stochastic process $X = \{X_t : t \geq 0\}$ on $\mathbb{R}^d$ with $X_0 = 0$ almost surely is a Lévy process if:
-    \begin{enumerate}
-        \item It has independent increments: for any $0 \leq t_1 < t_2 < \cdots < t_n < \infty$, the random variables $X_{t_2} - X_{t_1}, X_{t_3} - X_{t_2}, \ldots, X_{t_n} - X_{t_{n-1}}$ are mutually independent.
-        \item It has stationary increments: for any $s < t$, the distribution of $X_t - X_s$ depends only on $t-s$.
-        \item It is stochastically continuous: for any $t \geq 0$ and $\varepsilon > 0$, $\lim_{h \to 0} \mathbb{P}(|X_{t+h} - X_t| > \varepsilon) = 0$.
-    \end{enumerate}
-\end{definition}
-
-The celebrated Lévy-Khintchine formula provides a complete characterization of Lévy processes through their characteristic functions:
-
-\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
-    If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
-    \begin{equation}
-        \mathbb{E}[e^{i\theta X_t}] = e^{t\psi(\theta)}
-    \end{equation}
-    where
-    \begin{equation}
-        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
-    \end{equation}
-    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
-\end{theorem}
-
-The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
-Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
-
-\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
-    Any Lévy process $X_t$ can be decomposed as:
-    \begin{equation}
-        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
-    \end{equation}
-    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
-\end{theorem}
-
-The Lévy-Itô decomposition provides a pathwise representation of a Lévy process as the sum of a drift term, a Brownian motion, and potentially infinitely many jumps, both small and large.
-
-\subsection{Time Discretization of Lévy Processes}
-\label{appendix:levy_discretization_methods}
-
-To implement continuous-time Lévy processes within discrete computational frameworks, we must employ appropriate numerical approximation schemes.
-For our strategic experimentation model, we adopt the Euler-Maruyama scheme, extended to accommodate the jump components of general Lévy processes.
-
-\begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
-    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
-    \begin{equation}
-        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
-    \end{equation}
-    where $Z_n \sim \mathcal{N}(0,1)$ are independent standard normal random variables and $\Delta J_n$ represents the jump increment over $[t_n, t_{n+1}]$.
-\end{definition}
-\iffalse
-    For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.
-
-    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
-        The jump component $\Delta J_n$ can be approximated through one of the following approaches:
-        \begin{enumerate}
-            \item For finite-activity processes (where $\nu(\mathbb{R}) < \infty$):
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K_n} J_i
-                  \end{equation}
-                  where $K_n \sim \text{Poisson}(\nu(\mathbb{R})\Delta t)$ and $J_i$ are i.i.d. random variables with distribution $\frac{\nu(dx)}{\nu(\mathbb{R})}$.
-
-            \item For infinite-activity processes, a truncation approach:
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K^{\varepsilon}_n} J^{\varepsilon}_i + c_{\varepsilon}\Delta t
-                  \end{equation}
-                  where $K^{\varepsilon}_n \sim \text{Poisson}(\nu(\{x: |x| > \varepsilon\})\Delta t)$, $J^{\varepsilon}_i$ are i.i.d.
-with distribution $\frac{\nu(dx)\mathbf{1}_{|x|>\varepsilon}}{\nu(\{x: |x| > \varepsilon\})}$, and $c_{\varepsilon} = \int_{|x|\leq\varepsilon} x\nu(dx)$.
-        \end{enumerate}
-    \end{proposition}
-\fi
-\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
-    \label{thm:euler_maruyama_convergence}
-    Let $X_t$ be a Lévy process and $\hat{X}_t$ be its Euler-Maruyama approximation with time step $\Delta t$. Then for any fixed $T > 0$:
-    \begin{enumerate}
-        \item (Weak Convergence) For any smooth function $f$ with polynomial growth:
-              \begin{equation}
-                  |\mathbb{E}[f(X_T)] - \mathbb{E}[f(\hat{X}_T)]| \leq C\Delta t
-              \end{equation}
-
-        \item (Strong Convergence) If $\int_{|x|>1} |x|^2 \nu(dx) < \infty$, then:
-              \begin{equation}
-                  \mathbb{E}[\sup_{0\leq t\leq T} |X_t - \hat{X}_t|^2] \leq C\Delta t
-              \end{equation}
-    \end{enumerate}
-    where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.
-
-\end{theorem}
-
-The weak and strong convergence properties ensure that our numerical scheme accurately approximates both the distributional properties and pathwise behavior of the continuous-time process as the time step decreases.
-
-\subsection{Implementing Strategic Experimentation Models}
-\label{appendix:strategic_experimentation_implementation}
-
-In our implementation of the strategic experimentation model from \citet{keller2020undiscounted}, we must discretize both the background signal process $B_t$ and the individual payoff processes $X^i_t$, while preserving the strategic incentives that drive experimentation decisions.
-
-\subsubsection{Discretization of Diffusion-Poisson Processes}
-\label{appendix:discretization_diffusion_poisson}
-
-In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:
-
-\begin{align}
-    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
-    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
-\end{align}
-
-where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes.
-Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:
-
-\begin{align}
-    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
-    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
-\end{align}
-
-For implementation, we denote these increments as:
-
-\begin{align}
-    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
-    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
-\end{align}
-
-where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
-
-\subsubsection{Reward Function Equivalence}
-\label{appendix:reward_equivalence}
-
-A critical challenge in our implementation is reconciling the time-dependent nature of continuous-time rewards with the time-independent reward structure required by the POAMG framework.
-In the original continuous-time model, agents' instantaneous rewards are:
-
-\begin{equation}
-    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
-\end{equation}
-
-where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$.
-To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time.
-We achieve this through a normalization approach:
-
-\begin{equation}
-    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
-\end{equation}
-
-This transformation preserves the incentive structure of the original model while eliminating explicit time dependence. The following proposition establishes this equivalence formally:
-
-\begin{proposition}[Reward Equivalence]
-    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
-    \begin{equation}
-        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{equation}
-    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
-\end{proposition}
-
-\begin{proof}
-    The expected value of the discrete-time reward function is:
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
-                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
-                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
-    \end{align}
-
-    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:
-
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
-                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{align}
-
-    This exactly matches the expected instantaneous flow payoff in the continuous-time model.
-\end{proof}
-
-\iffalse
-    \subsubsection{Preservation of Strategic Incentives}
-    \label{appendix:strategic_incentives}
-
-    Beyond matching expected rewards, we must ensure that our discretization preserves the strategic incentives that drive experimentation decisions.
-The key strategic consideration in the model is the trade-off between exploitation (choosing the safe arm) and exploration (choosing the risky arm to learn about its quality).
-
-    \begin{proposition}[Preservation of Strategic Incentives]
-        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
-
-    \end{proposition}
-
-    \begin{proof}
-        In the strategic experimentation model, the incentive to experiment at a given belief $b$ about the state is characterized by:
-        \begin{equation}
-            I(b) = \frac{f(b) - s}{s - m(b)}
-        \end{equation}
-        when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad.
-In our discrete-time approximation, the corresponding incentive is:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)}
-        \end{equation}
-        where $\hat{f}(b)$ and $\hat{m}(b)$ are the discrete-time analogs.
-
-        Let us elaborate on why $\hat{f}(b) \to f(b)$ and $\hat{m}(b) \to m(b)$ as $\Delta t \to 0$. In the continuous-time model, the expected flow payoff of the risky arm at belief $b$ is:
-        \begin{equation}
-            f(b) = b f_1 + (1-b) f_0
-        \end{equation}
-        where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$.
-In our discrete-time approximation, we have:
-        \begin{equation}
-            \hat{f}(b) = b \hat{f}_1 + (1-b) \hat{f}_0
-        \end{equation}
-        where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
-        From our reward equivalence result, we know that:
-        \begin{align}
-            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
-                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
-        \end{align}
-
-        The Brownian motion term has $\mathbb{E}[\sigma(W^i_t - W^i_{t-1})] = 0$ and $\text{Var}[\sigma(W^i_t - W^i_{t-1})] = \sigma^2 \Delta t$.
-By the martingale property of Brownian motion, this term contributes zero to the expected value but introduces variance of order $O(\Delta t)$.
-Thus:
-        \begin{equation}
-            \hat{f}_1 = \alpha_1 + \lambda_1\mu_1 + O(\Delta t) \to f_1 \text{ as } \Delta t \to 0
-        \end{equation}
-
-        Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
-        Therefore, we can establish that:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)} = \frac{b \hat{f}_1 + (1-b) \hat{f}_0 - s}{s - \hat{f}_0} = \frac{b(\hat{f}_1 - \hat{f}_0) + \hat{f}_0 - s}{s - \hat{f}_0}
-        \end{equation}
-
-        As $\Delta t \to 0$, we have $\hat{f}_1 \to f_1$, $\hat{f}_0 \to f_0$, and consequently:
-        \begin{equation}
-            \hat{I}(b) \to \frac{b(f_1 - f_0) + f_0 - s}{s - f_0} = \frac{b f_1 + (1-b) f_0 - s}{s - f_0} = \frac{f(b) - s}{s - m(b)} = I(b)
-        \end{equation}
-
-        The convergence of incentives directly implies convergence of optimal policies.
-In the continuous-time model, the symmetric Markov perfect equilibrium characterized in \citet{keller2020undiscounted} has the form:
-        \begin{equation}
-            \kappa^*(b) =
+    & \quad \left. + \alpha_e H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))\right]
+\end{align}
+
+For discrete action spaces, the summation and entropy terms are computed directly over the action probabilities.
+For continuous action spaces, the expectation is approximated using samples from the policy, and the entropy term is calculated as:
+\begin{align}
+    H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) = 
     \begin{cases}
-                0                    & \text{if } I(b) \leq k_0,            \\
-                \frac{I(b)-k_0}{N-1} & \text{if } k_0 < I(b) < k_0 + N - 1, \\
-                1                    & \text{if } I(b) \geq k_0 + N - 1.
+        -\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \log \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) & \text{for discrete actions} \\
+        \frac{1}{2}\log\det(2\pi e \sigma^2(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for continuous actions}
     \end{cases}
-        \end{equation}
-        where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players.
-The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.
-
-        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
-    \end{proof}
-
-\fi
-\subsection{Relation to Policy-Invariant Reward Transformations}
-\label{appendix:policy_invariance}
-
-Our approach to time-independent reward formulation can be viewed through the lens of policy-invariant reward transformations, as developed in the reinforcement learning literature by \citet{ng1999policy}.
-
-\begin{definition}[Potential-Based Reward Shaping]
-    A reward transformation $\tilde{R}(s, a, s') = R(s, a, s') + F(s, s')$ is potential-based if there exists a potential function $\Phi: S \to \mathbb{R}$ such that $F(s, s') = \gamma\Phi(s') - \Phi(s)$ for all $s, s' \in S$, where $\gamma$ is a discount factor.
-\end{definition}
-
-\begin{theorem}[Ng-Harada-Russell \citep{ng1999policy}]
-    If a reward transformation is potential-based, then the optimal policy under the transformed reward function is also optimal under the original reward function, and vice versa.
-\end{theorem}
-
-While our transformation does not directly fit the potential-based formulation (since we're normalizing by $\Delta t$ rather than adding a potential difference), it shares the crucial property of preserving optimal policies.
-The following result establishes this connection:
-
-\begin{proposition}[Connection to Policy-Invariant Transformations]
-    The transformation from time-dependent rewards in the continuous-time model to time-independent rewards in the POAMG framework preserves policy optimality in the limit as $\Delta t \to 0$.
-\end{proposition}
-
-\begin{proof}
-    The original cumulative reward over a time interval $[0, T]$ is:
-    \begin{equation}
-        \int_0^T [(1-a^i_t)s + a^i_t\alpha_s] dt + \int_0^T a^i_t \sigma dW^i_t + \int_0^T a^i_t dC^i_t
-    \end{equation}
-
-    The discretized cumulative reward is:
-    \begin{equation}
-        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
-    \end{equation}
-    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.
-
-    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral.
-Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
-\end{proof}
-
-\section{Observed Reward Function}
-\label{appendix:observed_reward_derivation} In our reinforcement learning
-implementation, agents need to learn from observed rewards that reflect the optimality
-of their actions with respect to the true state of the world. However, since agents
-do not directly observe the true state $\omega$, we need to construct a reward
-function based on their observations $o$ that preserves the expected reward
-structure. This appendix provides a detailed derivation of the observation-based
-reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
-    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
-observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
-state. We need to construct an observation-based reward function $v(o, a): \Omega
-    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
-\begin{equation}
-    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
-    a \in A.
-\end{equation}
-
-In other words, the expected value of the observation-based reward $v(o, a)$
-over all possible observations $o$ given the state $s$ should equal the true
-reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
-    m$ matrix representing the observation distributions, where $m = |S|$ and assume
-the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
-the probability of observing observation $o$ in state $s$:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
-        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
-        \vdots           & \vdots           & \ddots & \vdots           \\
-        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
-    \end{bmatrix}
-\end{equation}
-
-We assume that observation distributions are linearly independent across states,
-which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
-    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
-more likely to generate its corresponding observation than any other observation.
-For each action $a \in A$, we define a utility vector
-$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
-\begin{equation}
-    \bm{u}_{a} =
-    \begin{bmatrix}
-        u(s^{1}, a) \\
-        u(s^{2}, a) \\
-        \vdots      \\
-        u(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
-    ^{k}$ for action $a$:
-\begin{equation}
-    \bm{v}_{a} =
-    \begin{bmatrix}
-        v(s^{1}, a) \\
-        v(s^{2}, a) \\
-        \vdots      \\
-        v(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-The condition that expected observation-based rewards match true rewards can be written
-as a linear system:
-\begin{equation}
-    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
-\end{equation}
-
-where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
-is:
-\begin{equation}
-    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
-\end{equation}
-
-This gives us the vector of observation-based rewards that satisfy our expected
-reward condition. For each observation $o_{j}$ and action $a$, the observation-based
-reward is:
-\begin{equation}
-    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
-\end{equation}
-
-where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
-$\bm{\mu}^{-1}$.
-\paragraph{Binary Case Example}
-For the special case with two states of the world ($m = 2$) and symmetric
-observations with accuracy $q > 0.5$, the observation distribution matrix is:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        q   & 1-q \\
-        1-q & q
-    \end{bmatrix}
-\end{equation}
-
-This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
-and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
-The inverse of this matrix is:
-\begin{equation}
-    \bm{\mu}^{-1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q      & -(1-q) \\
-        -(1-q) & q
-    \end{bmatrix}
-\end{equation}
-
-In our implementation, we set the true reward as the indicator function for taking
-the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
-    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
-utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
-is:
-\begin{equation}
-    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q \\
-        -(1-q)
-    \end{bmatrix}
-\end{equation}
-
-This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
-the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
-$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
-action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
-observation-based reward vector is:
-\begin{equation}
-    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        -(1-q) \\
-        q
-    \end{bmatrix}
-\end{equation}
-
-Combining these results, we can express the observation-based reward function for
-any action-observation pair $(a, o)$ as:
-\begin{equation}
-    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
-        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
-\end{equation}
-
-where $\varphi$ maps observations to their corresponding actions. The derived
-observation-based reward function has an intuitive interpretation. When an agent
-takes an action matching its observation ($a = o$), it receives a positive
-reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
-($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
-0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
-increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
-informative), the reward for matching observation and action approaches 1, and the
-penalty for mismatching approaches 0, meaning that the observed reward function
-converges to the true reward function. This reward structure incentivizes agents
-to match their actions to their observations when signals are reliable, but also
-allows them to learn to override their immediate observations when the actions
-of other agents provide stronger evidence about the true state through beliefs.
+\end{align}
+
+The entropy calculation must also account for the hyperbolic tangent transformation using the change of variables formula.
+
+The policy objective combines expected future returns with an entropy bonus, creating a balance between exploitation and exploration.
+The entropy term encourages the policy to maintain stochasticity, preventing premature convergence to deterministic policies that might be suboptimal in partially observable settings.
+The use of the minimum value across dual Q-networks helps mitigate overestimation bias—a persistent challenge in Q-learning approaches.
+This is particularly important in social learning contexts where overestimated values can lead to overly optimistic strategies that fail to account for the strategic adaptations of other agents.
+
+\subsubsection{Advantage-Weighted Transformer Training} A key innovation in POLARIS is the use of advantage-weighted training for the belief processor:
+\begin{align}
+    J^i_{\text{transformer}}(\psi^i_{\text{Transformer}}) &= \mathbb{E}_{D^i}\left[A^i(b^i, a^i) \cdot \text{BCE}(\mathbb{P}(s|b^i), o^i_{t+1})\right]
+\end{align}
+
+where $A^i(b^i, a^i)$ is the advantage function and BCE is binary cross-entropy loss.
+This objective bridges belief formation and policy optimization in a novel way.
+By weighting the belief update loss with the advantage function, the Transformer is encouraged to generate belief states that not only accurately predict future observations but also lead to high-value actions.
+In traditional partially observable reinforcement learning, belief updates are typically performed independently of policy optimization.
+By contrast, POLARIS creates a direct pathway for policy performance to influence belief formation, prioritizing informative aspects of the state space that have the greatest impact on decision quality.
+This approach is particularly valuable in social learning contexts, where certain beliefs about others' strategies may be more consequential than others for effective coordination or competition.
+
+\subsubsection{Catastrophic Forgetting Prevention}
+
+In social learning environments, the underlying state of the world often remains fixed during an episode, but varies across episodes.
+This creates a continual learning challenge: agents must adapt to new states while retaining knowledge about previously encountered states.
+Without proper mechanisms, neural networks tend to overwrite previously learned representations when adapting to new conditions—a phenomenon known as catastrophic forgetting \citep{vandeven2024continuallearningcatastrophicforgetting}.
+POLARIS addresses this challenge through Elastic Weight Consolidation (EWC), which selectively preserves important parameters for previously encountered states while allowing flexibility for adaptation.
+EWC augments the standard training objective with a regularization term that penalizes significant changes to parameters critical for performance in previously encountered states:
+
+\begin{align}
+    L_{\text{EWC}}(\theta) = L(\theta) + \sum_i \frac{\lambda}{2} F^i (\theta^i - {\theta^i}^*)^2
+\end{align}
+
+where $\theta^*$ represents parameters that performed well on previous tasks, $F^i$ is the Fisher information matrix that measures parameter importance, and $\lambda$ controls the strength of regularization.
+The Fisher information matrix provides a principled way to identify which parameters are most crucial for previously learned tasks, calculated using gradients of the log-likelihood of the model's output with respect to the parameters on data from previously encountered states.
+
+Crucially, POLARIS introduces a dynamic mechanism that automatically adjusts the EWC importance factor based on observed performance:
+
+\begin{align}
+    \lambda_t = 
+    \begin{cases}
+        \lambda_{t-1} \cdot 0.8 & \text{if loss ratio} > 1.5 \text{ (loss increasing too much)} \\
+        \lambda_{t-1} \cdot 1.2 & \text{if loss ratio} < 0.5 \text{ (loss decreasing too quickly)} \\
+        \lambda_{t-1} & \text{otherwise}
+    \end{cases}
+\end{align}
+
+This adaptive approach monitors the ratio between current and previous loss values, reducing the EWC importance when the loss is increasing too rapidly (indicating difficulty learning new information due to excessive preservation of old parameters) and increasing it when the loss is decreasing too quickly (suggesting potential forgetting of valuable past knowledge).
+The implementation also includes both L1 and L2 penalties with adaptive weighting between them, transitioning from more L2 regularization for early tasks to more L1 regularization for later tasks, encouraging sparser updates as the model accumulates more knowledge from different states.
+
+\subsection{Training Process}
+
+The overall training process interleaves updates to the three modules, ensuring that improvements in one component can benefit the others within each training iteration.
+Algorithm 1 outlines the complete POLARIS training procedure for a single agent.
+
+\begin{algorithm}[H]
+\caption{POLARIS Training Algorithm for Single Agent}
+\begin{algorithmic}[1]
+\State Initialize belief processor, inference module, policy and value networks with parameters $\psi^i_{\text{Transformer}}$, $\phi^i$, $\theta^i$, $\psi^i_{\beta}$
+\State Initialize replay buffer $D^i$, initial belief $b^i_0$, and latent state $\boldsymbol{\hat{z}}^{-i}_0$
+\State Determine action space type (discrete or continuous)
+\For{each step $t$}
+    \State Observe signal $o^i_t$ and joint action $\boldsymbol{a}_{t-1}$
+    \State Update belief: $b^i_t, \mathbb{P}(s|b^i_t) = f_{\text{Transformer}}(b^i_{t-1}, o^i_t, \boldsymbol{a}_{t-1}; \psi^i_{\text{Transformer}})$
+    \State Select action: 
+    \If{discrete action space}
+        \State $a^i_t \sim \pi^i(\cdot|b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$ \Comment{Sample from categorical distribution}
+    \Else
+        \State $\mu, \sigma = \text{MLP}_{\text{policy}}(b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$
+        \State $\epsilon \sim \mathcal{N}(0, I)$
+        \State $a^i_t = \tanh(\mu + \sigma \odot \epsilon)$ \Comment{Sample using reparameterization trick}
+    \EndIf
+    \State Execute action, observe reward $r^i_t$ and next signal $o^i_{t+1}$
+    \State Infer latent: $\boldsymbol{\hat{z}}^{-i}_{t+1} = f_{\text{GNN}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i)$
+    \State Store transition in replay buffer
+    \If{update step}
+        \State Sample batch $B$ from replay buffer $D^i$
+        \State Update inference module: $\phi^i \leftarrow \phi^i - \alpha_{\phi} \nabla_{\phi^i} J^i_{\text{elbo}}(B)$
+        \State Update value networks: $\psi^i_{\beta} \leftarrow \psi^i_{\beta} - \alpha_{\psi} \nabla_{\psi^i_{\beta}} J^i_{q}(B)$
+        \State Update policy: $\theta^i \leftarrow \theta^i - \alpha_{\theta} \nabla_{\theta^i} J^i_{\pi}(B)$ \Comment{Using appropriate entropy calculation}
+        \State Update belief processor: $\psi^i_{\text{Transformer}} \leftarrow \psi^i_{\text{Transformer}} - \alpha_{\psi} \nabla_{\psi^i_{\text{Transformer}}} J^i_{\text{transformer}}(B)$
+        \State Update target networks: $\bar{\psi}^i_{\beta} \leftarrow \tau \psi^i_{\beta} + (1-\tau) \bar{\psi}^i_{\beta}$
+        \If{true state has changed}
+            \State Calculate Fisher matrices from current replay buffer
+            \State Register task with EWC
+        \EndIf
+    \EndIf
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+The algorithm follows a sequential process where each agent first updates its belief state based on new observations and the joint actions of all agents using the Transformer-based belief processor (line 6).
+Based on this updated belief and the current inference of other agents' latent states, the agent selects an action using its stochastic policy—sampling from a categorical distribution for discrete action spaces (line 9) or using the reparameterization trick for continuous action spaces (lines 11-13).
+After executing this action and observing the reward and next observation (line 15), the agent updates its inference of other agents' latent states using the GNN-based inference module (line 16).
+All of these experiences are stored in a replay buffer for later training (line 17).
+
+At designated update steps, the agent samples a batch of transitions from its replay buffer and uses these to update all network components.
+The inference module is updated first (line 19) to improve predictions of other agents' actions using the ELBO objective.
+Next, the value networks are updated (line 20) to better estimate expected returns.
+The policy network is then updated (line 21) to maximize expected value and entropy.
+Finally, the belief processor is updated (line 22) using the advantage-weighted training approach.
+Target networks, used for stable learning in the SAC framework, are updated using a weighted average of the current and target parameters (line 23).
+
+A crucial feature of POLARIS is its adaptive response to changes in the environment state.
+When the true state changes (line 24), the algorithm calculates Fisher information matrices from the current replay buffer (line 25) and registers a new task with the EWC mechanism (line 26), preserving important knowledge from the previous state while allowing adaptation to the new state.
+
+In the next chapter, we demonstrate the practical application of our POAMG framework and the POLARIS algorithm to canonical social learning scenarios from economic theory.
+The versatility of our approach is particularly evident in its ability to seamlessly handle both continuous and discrete action spaces, as well as varying types of return objectives.
+This capability proves essential when implementing strategic experimentation models with continuous allocation decisions and average reward objectives, and learning without experimentation models with discrete signaling actions and discounted reward objectives.
+Through these implementations, we validate theoretical predictions from economic models while uncovering new insights about strategic adaptation in partially observable multi-agent systems that would be difficult to obtain through purely analytical approaches.
+The experimental results not only demonstrate the effectiveness of our theoretical framework but also highlight how computational methods can complement and extend traditional economic analysis of social learning phenomena.

### 2025-05-26 paper/thesis.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
-\setcounter{proposition}{0}
-\setcounter{assumption}{0}
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
+\documentclass[a4paper,12pt]{report}
 
-\chapter{Reinforcement Learning Background}
+%% Language and font encodings
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 
-\label{appendix:rl_details}
-This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.
+%% Sets page size and margins according to Bonn University guidelines
+\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=2cm]{geometry}
 
-\section{Reinforcement Learning Foundations}
+%% Font settings - Times New Roman or similar (as per guidelines)
+\usepackage{times} % Times font
+\usepackage{mathptmx} % Times font with math support
 
-Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty.
-In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}.
-This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:
+%% Section formatting
+\usepackage{titlesec}
 
-\begin{itemize}
-    \item $S$ is the state space, representing all possible configurations of the environment
-    \item $A$ is the action space, representing all possible decisions available to the agent
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
-    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
-    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
-\end{itemize}
+% Traditional academic chapter title style
+\titleformat{\chapter}[display]
+  {\normalfont\Large\bfseries}
+  {}
+  {0pt}
+  {\thispagestyle{empty}%
+   \vspace*{-20pt}%
+   \begin{flushright}
+     % Elegant, academic chapter number
+     \begin{tikzpicture}[remember picture, overlay]
+       \node[text=black!12, font=\fontsize{80}{80}\selectfont] {\thechapter};
+     \end{tikzpicture}
+   \end{flushright}
+   \vspace{-60pt}
+   % Simple, elegant single line
+   \rule{\textwidth}{0.6pt}\\
+   \vspace*{15pt}
+   \raggedright\LARGE\scshape}
+  [\vspace{-0.8cm}]
+\titlespacing*{\chapter}{0pt}{0pt}{40pt}
 
-The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions.
-The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter.
-The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.
+% Elegant section formatting
+\titleformat{\section}
+  {\normalfont\Large\bfseries\scshape}
+  {}
+  {0pt}
+  {\thesection\quad}
+\titlespacing*{\section}{0pt}{3.5ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
-The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs.
-This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem.
-However, this assumption becomes problematic in multi-agent settings, as we will discuss next.
+% Make subsections italic and elegant
+\titleformat{\subsection}
+  {\normalfont\large\bfseries\itshape}
+  {\thesubsection}
+  {1em}
+  {}
+\titlespacing*{\subsection}{0pt}{3ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
-\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}
+%% Line spacing 1.5 as required
+\usepackage{setspace}
+\onehalfspacing
 
-Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}.
-MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}.
-These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:
+%% Useful packages
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bm}         % For bold symbols
+\usepackage{graphicx}
+\usepackage{float}      % For [H] figure placement
+\usepackage{booktabs}
+\usepackage{tabu}
+\usepackage{enumitem}
+\usepackage[table,dvipsnames]{xcolor}  % Added dvipsnames option for more color choices
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{amsthm}
+\usepackage{bbm}        % Blackboard math symbols (for indicator function)
+\usepackage[toc]{appendix}
+\usepackage{subcaption}
 
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space, shared among all agents
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\gamma \in [0, 1)$ is the discount factor
-\end{itemize}
-MARL introduces several fundamental challenges beyond those encountered in single-agent RL.
-The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system.
-Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}.
-In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions.
-MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings.
-Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.
+% Choose either algorithm2e OR algorithmicx, not both
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
 
-\section{The Non-Stationarity Challenge}
-The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}.
-To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent.
-When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$.
-From agent $i$'s perspective, the effective transition function becomes:
-\begin{equation}
-    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
-\end{equation}
-where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$.
-When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$.
-This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL.
-When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}.
-This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}.
-Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}.
-The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}.
-These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.
+% For adjusting margins of specific sections
+\usepackage{changepage}
 
-\section{Traditional Approaches to Non-Stationarity}
-Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:
+% Bibliography
+\usepackage[natbibapa]{apacite}
 
-\subsection{Independent Learning}
-The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}.
-This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents.
-Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences.
-While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.
+% Todo notes
+\usepackage[colorinlistoftodos]{todonotes}
 
-\subsection{Centralized Training with Decentralized Execution}
-To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}.
-In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.
+% Page numbering configuration
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\fancyfoot[C]{\thepage}
+\renewcommand{\headrulewidth}{0pt}
 
-Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution.
-Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline.
-The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies.
-While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.
+% Hyperref should be last
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
 
-\subsection{Opponent Modeling and Population-Based Training}
-Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}.
-This can involve predicting other agents' policies, types, or learning dynamics.
-Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning.
-Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.
+% Allow floating content to be placed more liberally
+\renewcommand{\floatpagefraction}{.9}
+\renewcommand{\textfraction}{.1}
+\renewcommand{\topfraction}{0.9}
+\renewcommand{\bottomfraction}{.9}
 
-The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity.
-While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.
+% Appendix formatting
+\makeatletter
+\let\old@chapter\@chapter
+\def\@chapter[#1]#2{\old@chapter[{#1}]{#2}}
+\makeatother
 
-\subsection{Equilibrium Learning and Stability Concepts}
-Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}.
-These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate.
-Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games.
-Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.
+% Math operators
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
-The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence.
-While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality.
-Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.
+% Custom theorem environments
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+\newtheorem{definition}{Definition}
+\newtheorem{assumption}{Assumption}
+\newtheorem{remark}{Remark}
 
-\subsection{Meta-Learning for Non-Stationarity}
-Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}.
-These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem.
-Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.
+% Define indicator function notation
+\newcommand{\ind}[1]{\mathbbm{1}_{#1}}
 
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents.
-While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.
+\begin{document}
 
-\section{Active Markov Games}
+% Cover sheet as per Bonn University guidelines
+\begin{titlepage}
+\begin{center}
+\vspace*{2cm}
 
-Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}.
-They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.
+{\Large \textbf{Social Learning via Multi Agent Reinforcement Learning}}\\[6cm]
 
-\subsection{Formal Definition}
+Master Thesis Presented to the\\
+Department of Economics at the\\
+Rheinische Friedrich-Wilhelms-Universität Bonn\\[1cm]
 
-An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:
+In Partial Fulfillment of the Requirements for the Degree of\\
+Master of Science (M.Sc.)\\[4cm]
 
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
-    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
-\end{itemize}
-Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state.
-The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates.
-At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$.
-Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$.
-Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$.
-This process continues until non-stationary policies converge to a recurrent set of joint policies.
-The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.
+Supervisor: Prof. Dr. Florian Brandl\\[2cm]
 
-\subsection{Augmented Transition Function and Stationarity}
+Submitted in June, 2025 by:\\
+Ege Can Doğaroğlu\\
+Matriculation Number: 3464688
 
-The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions.
-To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games.
-In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions.
-However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions.
-The augmented transition function becomes:
+\end{center}
+\end{titlepage}
 
-\begin{equation}
-    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
-\end{equation}
-The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories.
-By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one.
-This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.
+% Set page numbering to 'gobble' (no numbers) for front matter
+\pagenumbering{gobble}
 
-\subsection{Theoretical Properties and Convergence}
+% Abstract
+\begin{abstract}
+\begin{adjustwidth}{2cm}{2cm}
+This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs)—a novel framework for modeling sophisticated learning dynamics in environments with partial observability.
+Traditional economic models provide valuable theoretical insights but often rely on simplified assumptions about agents' behavior or the learning environment, while reinforcement learning approaches offer computational tools that frequently lack theoretical foundations for strategic adaptation.
+Our framework addresses three fundamental challenges: modeling strategic adaptation in non-stationary environments, incorporating partial observability as an intrinsic feature, and capturing long-term strategic considerations in learning contexts.
+We develop POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm implementing our theoretical framework, and apply it to two canonical social learning scenarios: strategic experimentation with observable rewards and learning without experimentation through action observation.
+Our results validate theoretical predictions about ...
+while demonstrating how reinforcement learning agents can discover sophisticated strategies for information revelation and strategic influence, providing both theoretical insights and computational tools for understanding complex social learning dynamics.
+\end{adjustwidth}
+\end{abstract}
 
-Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:
+% Table of contents
+\tableofcontents
+\newpage
 
-\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:
+% Optional - include if you have abbreviations, tables, or figures to list
+%\listoffigures
+%\listoftables
+%\newpage
 
-\begin{equation}
-    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
-\end{equation}
+% Page numbering starts here with Arabic numerals
+\chapter{Introduction}
+\pagenumbering{arabic}
+\setcounter{page}{1}
+\input{intro}
+\chapter{Related Work}
+\input{background}
+\chapter{Theoretical Framework}
+\input{theory}
+\chapter{Results}
+\input{results}
+\chapter{Conclusion}
+\input{conclusion}
 
-where $\ell = t\%k$ with $\%$ denoting the modulo operation.
-This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies.
-The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence.
-To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}.
-These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.
+% Appendix
+\newpage
+\appendix
+\addcontentsline{toc}{chapter}{Appendices}
+\input{appendix}
 
-\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:
+% Bibliography
+\newpage
+\renewcommand{\bibname}{References}
+\renewcommand{\thechapter}{R}
+\addcontentsline{toc}{chapter}{References}
+\bibliographystyle{apacite}
+\bibliography{refs}
+\renewcommand{\thechapter}{\arabic{chapter}} % Reset chapter numbering
 
-\begin{equation}
-    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
-        \begin{array}{c}
-            s_0=s, \theta_0=\theta,                                              \\
-            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
-            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
-            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
-        \end{array}
-        \right]
-\end{equation}
+% Statement of Authorship (as required)
+\newpage
+\section*{Statement of Authorship}
 
-where  $0:T$ denotes the sequence from time $0$ to $T$.
-This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.
+I hereby confirm that the work presented has been performed and interpreted solely by myself except for where I explicitly identified the contrary.
+I assure that this work has not been presented in any other form for the fulfillment of any other degree or qualification.
+Ideas taken from other works in letter and in spirit are identified in every single case.\\[2cm]
 
-\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium.
-An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:
+\noindent Date: \rule{4cm}{0.5pt} \hfill Signature: \rule{6cm}{0.5pt}
 
-\begin{equation}
-    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
-\end{equation}
-for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$.
-This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system.
-The active equilibrium generalizes several classic solution concepts in game theory.
-Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively.
-Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively.
-This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.
-
-Active Markov Games address the non-stationarity challenge in several fundamental ways.
-By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated.
-The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors.
-Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates.
-Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees.
-Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.
-
-\subsection{Practical Implementations}
-
-Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL.
-Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner.
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games.
-These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.
-
-\section{Extension to Partial Observability}
-
-While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state.
-In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents.
-This partial observability introduces additional challenges for multi-agent learning.
-The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions.
-In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}.
-Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning.
-The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.
-
-In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state.
-Theoretical formulations, as established by Meuleau et al.
-\cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$.
-However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation.
-Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}.
-These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics.
-In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time.
-For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.
-
-\chapter{Proofs Regarding Average Returns}
-
-This section provides the mathematical foundations and detailed proofs for the
-key theoretical results in our Partially Observable Active Markov Game framework
-with average return objectives. We establish the Markov properties of belief transitions
-and joint processes, prove the existence and uniqueness of stochastically stable
-distributions, and derive the policy gradient theorem for average return optimization.
-
-\section{Markov Property of the Joint Process}
-\label{appendix:stochasticallystable}We first establish the Markov properties of
-belief state transitions and the joint process comprising states, belief states,
-and policy parameters. These properties form the foundation for our convergence analysis.
-
-\begin{lemma}[Markov Property of Belief Transitions]
-    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
-    a Markov process under a fixed policy $\pi$, meaning that the distribution of
-    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
-    not on earlier beliefs, actions, or observations.
-\end{lemma}
-
-\begin{proof}
-    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
-    relevant information from the history of observations and actions up to time
-    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
-    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
-            ^{i}$ through the rule:
-    \begin{align}
-        b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
-    \end{align}
-
-    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
-    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
-    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
-    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
-    property.
-\end{proof}
-
-\begin{remark}[Transformer-Based Belief Representation]
-    In practice, transformer architectures can be used to represent and
-    update belief states. In such cases, the belief state is updated
-    through an attention-based mechanism of the form:
-    \begin{equation}
-        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
-    \end{equation}
-
-    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
-    observation and previous belief state through self-attention layers, satisfying the Markov property
-    while capturing complex dependencies between observations and beliefs.
-\end{remark}
-Next, we establish the Markov property of the joint process.
-\begin{lemma}[Markov Property of Joint Process]
-    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
-    a Markov process under periodic policy updates, meaning that the distribution
-    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
-    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
-    states.
-\end{lemma}
-\begin{proof}
-    The state transitions are by definition only dependent on current state and current
-    actions. The remaining parts can be analyzed as follows:
-
-    \textbf{1. Belief
-        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
-    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
-    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
-        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
-    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
-    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
-    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.
-
-    \textbf{2. Policy parameter
-        update:} At every time step $t$, policy parameters are updated according to $U(
-        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
-    Under the Markovian policy update assumption, the update depends only on $\theta
-        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
-        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
-    probability
-    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t}))$
-    depends only on the current state
-    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
-    of states, establishing the Markov property.
-\end{proof}
-\section{Convergence}
-Having established the Markov properties, we now analyze the convergence
-behavior of the joint process to a unique stochastically stable distribution. This
-convergence result is crucial for developing optimization objectives in our framework.
-\begin{theorem}[Stochastically Stable Distribution]
-    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
-    defined by $\epsilon$-perturbed policy update functions converge to the unique
-    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
-        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
-\end{theorem}
-
-\begin{proof}
-    We establish the convergence to the unique stochastically stable distribution by
-    showing that a perturbed Markov process of a partially observable active Markov
-    game is regular. First, let us introduce a small perturbation to the policy update
-    functions:
-    \begin{align}
-        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
-    \end{align}
-
-    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
-    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
-    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
-    probability of transitioning to any other configuration
-    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
-        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
-    probability:
-    \begin{align}
-        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
-                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
-                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
-    \end{align}
-
-    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
-    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
-    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
-    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
-    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
-    of the joint process. We will show that there must exist a path with positive probability
-    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
-    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
-        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
-        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
-    second as follows:
-
-    \textbf{1. Policy Parameter Transition:} Due to the
-    $\epsilon$-perturbation in update functions, there is a positive probability of
-    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
-        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
-    \end{align}
-
-    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
-    $\boldsymbol{\theta}_{2}$.
-
-    \textbf{2. State Transition:} By the communicating
-    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
-    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
-    such that:
-    \begin{align}
-        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
-    \end{align}
-
-    Given the relationship between policies and actions, this sequence of actions has
-    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
-    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
-    for all required actions.
-
-    \textbf{3. Belief State Transition:} By the communicating belief-state
-    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
-        B$, there exists a sequence of observations
-    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
-    \end{align}
-
-    Since observations depend on states, which can be influenced through actions,
-    and actions are determined by policies, there is a positive probability path from
-    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
-    and policy parameters. Combining these three components, we can construct a path
-    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
-        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
-    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
-    classes of the perturbed joint process. Since we have shown that the perturbed
-    joint process has only one recurrent class, it is a regular Markov process. Following
-    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
-    process on a finite state space possesses a unique stationary distribution
-    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
-    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
-    converges to a limit $\mu^{*}$, which is the unique stochastically stable
-    distribution of the original, unperturbed process. Therefore, under the given conditions,
-    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
-    partially observable active Markov game possesses a unique stochastically
-    stable distribution $\mu^{*}$.
-\end{proof}
-\section{Policy Gradient Theorem}
-Having established the convergence to a unique stochastically stable distribution,
-we now derive the policy gradient theorem for optimization in our framework. This
-theorem provides the mathematical foundation for gradient-based algorithms to maximize
-the average return objective.
-\label{appendix:avg_gradient}
-\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
-        Theorem]
-    The gradient of the active average reward objective
-    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
-    setting is:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
-    the belief update function.
-\end{theorem}
-
-\begin{proof}
-    We first define the average reward objective in the partially observable setting:
-    \begin{align}
-        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
-                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
-    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
-        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
-    differential value function $v^{i}_{\theta^i}$ represents the expected total
-    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
-        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
-        ^{i}_{\theta^i}$:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
-    \end{align}
-
-    Following the Bellman equation derivation principles, we can express
-    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
-                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-    represents the belief update function that updates the belief state based on
-    the current belief, action, and new observation. We now define the action-value
-    function $q^{i}_{\theta^i}$ for the partially observable setting:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    Using this definition, we can rewrite the differential value function as:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    To derive the policy gradient, we begin by computing the gradient of the differential
-    value function with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
-                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
-                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    We expand the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                                                                  & \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
-                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting back into the original expression, we get:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Rearranging terms:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we define the transition operator that maps the expectation of a function
-    from one time step to the next:
-    \begin{align}
-        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
-                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    We can rewrite our expression as:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we take the expectation with respect to the stationary distribution
-    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
-                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    By the definition of the stationary distribution, we have:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore, the second and third terms in our expression cancel out, giving the
-    final policy gradient theorem:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-\end{proof}
-
-\chapter{Proofs Regarding Discounted Returns}
-\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
-Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
-mathematical foundation.
-\section{Transition Operator and Its Adjoint}
-To establish a rigorous framework for analyzing discounted returns in Partially
-Observable Active Markov Games, we need to formalize how value functions evolve over
-time and how probability distributions propagate through the system. This dual
-perspective is captured by two fundamental operators: the transition operator and
-its adjoint.
-
-\subsection{Definitions and Duality}
-
-We begin by defining the inner product between functions and measures, which forms
-the foundation for the duality relationship between our operators.
-
-\begin{definition}[Inner Product between Functions and Measures]
-    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
-        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
-    Lebesgue integral:
-    \begin{equation}
-        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
-        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
-        {\theta})
-    \end{equation}
-\end{definition}
-
-This inner product captures the expected value of function $f$ with respect to
-measure $\mu$, allowing us to express value functions as expectations with respect
-to appropriate measures.
-
-\begin{definition}[Transition Operator and Its Adjoint]
-    \hfill
-    \begin{enumerate}
-        \item The \textbf{transition operator}
-              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
-                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              maps a bounded measurable function to its expected value after one
-              transition:
-              \begin{align}
-                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-              \end{align}
-
-              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-              represents the belief update function.
-
-        \item The \textbf{adjoint operator}
-              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
-                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              is defined on the space of finite measures such that:
-              \begin{equation}
-                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
-              \end{equation}
-
-              for all
-              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
-              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
-    \end{enumerate}
-\end{definition}
-
-Intuitively, $\Psi$ describes how function expectations evolve forward in time,
-meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
-capturing the propagation of visitation probabilities through the system. The duality
-relationship ensures that expected values can be computed either by applying $\Psi$
-to functions or $\Psi^{*}$ to measures.
-
-\subsection{Properties of the Operators}
-
-These operators possess several important properties that facilitate our
-analysis of discounted returns:
-
-\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
-    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
-    properties:
-
-    \begin{enumerate}
-        \item \textbf{Linearity:}
-              \begin{itemize}
-                  \item For the operator: For any functions
-                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
-                        \end{align}
-
-                  \item For the adjoint: For any measures
-                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Positivity Preservation:}
-              \begin{itemize}
-                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.
-
-                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
-                            \mu$ is also non-negative.
-              \end{itemize}
-
-        \item \textbf{Preservation of Total Measure:}
-              \begin{itemize}
-                  \item For the operator: The operator preserves the constant function
-                        $\mathbf{1}$:
-                        \begin{align}
-                            \Psi \mathbf{1}= \mathbf{1}
-                        \end{align}
-
-                        where $\mathbf{1}$ represents the function that equals 1 everywhere.
-
-                  \item For the adjoint: For any measure
-                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-                        \begin{align}
-                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
-              bounded with:
-              \begin{align}
-                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
-              \end{align}
-
-              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
-                  {b},\boldsymbol{\theta})|$ is the supremum norm.
-
-        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
-              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-              \begin{align}
-                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
-                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-              \end{align}
-
-              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    We prove each property in turn:
-
-    \textbf{1. Linearity:}
-
-    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
-    \begin{align}
-         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For the adjoint: For any measurable function
-    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
-                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
-                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
-                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
-        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
-    measure.
-
-    \textbf{2. Positivity Preservation:}
-
-    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
-        )$:
-    \begin{align}
-        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
-    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
-    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
-        {\theta}) \geq 0$.
-
-    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
-    function $f \geq 0$:
-    \begin{align}
-        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
-    \end{align}
-
-    where the inequality follows from the positivity preservation of $\Psi$ and the
-    fact that $\mu$ is non-negative. Since this holds for all non-negative
-    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.
-
-    \textbf{3. Preservation of Total Measure:}
-
-    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
-    everywhere. Then:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
-    \end{align}
-
-    Since each probability distribution sums to 1, applying them sequentially
-    yields:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
-    \end{align}
-
-    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
-    \begin{align}
-        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
-    \end{align}
-
-    where we used the unit preservation property of $\Psi$. This gives:
-    \begin{align}
-        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-    \end{align}
-
-    \textbf{4. Bound Preservation:}
-
-    For any bounded function $f$ with
-    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
-        ,\boldsymbol{\theta})|$:
-    \begin{align}
-        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                           & \quad \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
-                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
-                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
-    \end{align}
-
-    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
-    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.
-
-    \textbf{5. Explicit Form of the Adjoint:}
-
-    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
-    \end{align}
-
-    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
-    \begin{align}
-        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting this back and using the definition of inner product:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
-                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
-                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}
-
-\subsection{Contraction and Propagation}
-
-The properties established above lead to two crucial results: the contraction
-property of the discounted transition operator and the propagation of
-distributions through the adjoint.
-
-\begin{lemma}[Contraction Mapping Property]
-    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
-    contraction mapping on the Banach space of bounded functions on
-    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
-    norm. Specifically, for any two functions
-    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
-    \end{align}
-\end{lemma}
-
-\begin{proof}
-    Using the linearity of $\Psi$ and its bound preservation property:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
-                                                   & \leq \gamma\|f - g\|_{\infty}
-    \end{align}
-
-    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
-    factor $\gamma$.
-\end{proof}
-
-This contraction property leads directly to the invertibility of
-$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
-in discounted settings.
-
-\begin{lemma}[Invertibility of $I - \gamma \Psi$]
-    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
-    invertible, and its inverse can be represented as a Neumann series:
-    \begin{align}
-        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    which converges absolutely in the operator norm.
-\end{lemma}
-
-\begin{proof}
-    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
-    space, then $I - T$ is invertible, with inverse given by the Neumann series
-    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
-    have:
-
-    \begin{align}
-        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    The absolute convergence follows from:
-    \begin{align}
-        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
-    \end{align}
-
-    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
-        \leq 1$ for all $t$.
-\end{proof}
-
-Finally, we establish how distributions evolve in the system through the adjoint
-operator, formalizing the propagation of probability measures.
-
-\begin{lemma}[Distribution Propagation]
-    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
-    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
-\end{lemma}
-
-\begin{proof}
-    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$:
-    \begin{align}
-        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
-                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
-                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
-                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have
-    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
-\end{proof}
-
-The concepts introduced in this section—the transition operator, its adjoint, and
-their properties—provide the mathematical foundation for analyzing discounted returns
-in Partially Observable Active Markov Games. The transition operator $\Psi$
-captures how function expectations evolve forward in time, while its adjoint $\Psi
-    ^{*}$ describes how probability distributions propagate forward in time. This
-duality is fundamental to establishing the connection between value-based and
-distribution-based perspectives in reinforcement learning.
-
-In the next section, we will use these tools to formulate Bellman equations and derive
-policy gradients for maximizing discounted returns in this complex multi-agent setting.
-\section{Bellman Equations and Value Functions}
-In this section, we establish the fundamental recursive relationships that characterize
-the discounted value functions in Partially Observable Active Markov Games.
-These relationships form the basis for our policy gradient derivation and
-practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
-of value functions, then establish the Bellman equations, and finally derive the
-gradient expressions necessary for policy optimization.
-\subsection{Well-Definedness of Value Functions}
-Before deriving recursive relationships, we first establish that the value functions
-are well-defined mathematical objects under our assumptions of bounded rewards and
-discount factors less than 1.
-\begin{lemma}[Well-Defined Value Functions]
-    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
-    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
-    action-value functions
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
-    well-defined and finite for all states, belief states, policy parameters, and actions.
-\end{lemma}
-\begin{proof}
-    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
-    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
-    \begin{align}
-        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
-                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
-                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Similarly, for the action-value function:
-    \begin{align}
-        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
-                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
-                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Thus, both value functions are well-defined and bounded.
-\end{proof}This lemma ensures that our subsequent derivations involving value
-functions are mathematically sound. The boundedness property is particularly important
-when we consider expectations and derivatives of these functions.
-\subsection{Bellman Equations for Discounted Value Functions}
-Next, we establish the recursive relationships between value functions, which
-are fundamental to dynamic programming approaches.
-\begin{lemma}[Bellman Equation for Discounted Value Functions]
-    In a Partially Observable Active Markov Game, the discounted value function
-    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{lemma}
-\begin{proof}
-    By definition, the discounted value function is:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    We can decompose this into the immediate reward and the future discounted
-    returns:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
-                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
-                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    For the first term, we have:
-    \begin{align}
-        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    For the second term, by the law of total expectation:
-    \begin{align}
-         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
-         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Combining these two terms and factoring out common terms:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
-                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
-                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
-\end{proof}The Bellman equation provides a recursive characterization of the
-value function that forms the basis for dynamic programming algorithms. This equation
-captures how current actions influence both immediate rewards and future value through
-their effects on the environment state, belief states, and policy parameters of other
-agents. The key distinction from standard Bellman equations is the inclusion of
-belief updates and policy parameter dynamics, which reflects the complex dependencies
-in partially observable multi-agent settings.
-\subsection{Policy Gradient with Respect to Value Function}
-Having established the recursive relationship for value functions, we now derive
-how the value function gradient depends on policy parameters, which is essential
-for policy optimization.
-\begin{lemma}[Policy Gradient with Respect to Value Function]
-    The gradient of the value function with respect to policy parameters $\theta^{i}$
-    can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-
-    where $\Psi$ is the transition operator defined in the previous section.
-\end{lemma}
-\begin{proof}
-    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
-    \end{align}
-
-    Applying the product rule:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    For the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
-    \end{align}
-
-    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
-        {o}'|s')$, and
-    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
-    do not depend directly on $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Using the transition operator $\Psi$, we can rewrite:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Rearranging:
-    \begin{align}
-        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
-                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
-                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-\end{proof}This lemma expresses the value function gradient in terms of an
-infinite sum of expected Q-values weighted by policy gradients and propagated
-through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
-immediate changes in policy parameters propagate through future timesteps. This
-form of the gradient is central to our discounted policy gradient theorem, which
-we will develop in the next section. The inverse operator can be represented as
-a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
-as the accumulated effect of policy changes over an infinite horizon, weighted
-by the discount factor.
-\section{Discounted Visitation Measure}
-The infinite sum formulation derived in the previous sections, while
-mathematically sound, is not directly amenable to practical computation. In this
-section, we reformulate these expressions in terms of a probability distribution,
-which allows for more efficient estimation through sampling-based approaches. This
-reformulation is central to our policy gradient theorem for discounted returns.
-\subsection{Definition and Properties}
-\begin{definition}[Discounted Visitation Measure]
-    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
-        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
-    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
-    \end{equation}
-
-    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
-    and $\gamma \in [0, 1)$ is the discount factor.
-\end{definition}This measure represents the expected discounted frequency with which
-different states, belief states, and policy parameters are visited when following
-policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
-factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
-distribution, summing to 1 across the entire state-belief-policy space. The discounted
-visitation measure plays a central role in reinforcement learning theory,
-particularly in policy gradient methods. It provides a natural weighting of states
-according to their importance for the discounted objective, as states that are
-visited more frequently or earlier in trajectories receive higher weight. This concept
-generalizes the stationary distribution used in average-reward settings to the discounted
-return framework.
-\begin{lemma}[Evolution of Discounted Visitation]
-    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
-    the adjoint operator as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
-    \end{equation}
-
-    where $\mu_{0}$ is the initial distribution.
-\end{lemma}
-\begin{proof}
-    By the propagation lemma established earlier,
-    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
-    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
-    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
-    measure:
-    \begin{align}
-        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
-                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    The second equality follows from the Neumann series expansion:
-    \begin{align}
-        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
-    \end{align}
-
-    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
-    the total variation norm.
-\end{proof}This establishes the essential connection between the adjoint operator
-and the discounted visitation measure, which is central to the policy gradient
-theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
-time spent in each state-belief-policy configuration, weighted according to the
-discount factor $\gamma$. This connection allows us to transform expressions involving
-$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
-        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
-practical implementations, the discounted visitation measure is rarely computed explicitly
-due to the prohibitive computational cost. Instead, sampling-based approaches are
-used to estimate expectations with respect to this measure. The policy gradient
-theorem leverages this measure to derive update rules that can be efficiently
-implemented using trajectory samples collected from the environment.
-
-\subsection{Existence and Uniqueness}
-To provide a rigorous mathematical foundation for our policy gradient theorem,
-we establish the existence and uniqueness of the discounted visitation measure.
-\begin{lemma}[Existence of the Discounted Visitation Measure]
-    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
-    of finite measures on the joint state-belief-policy space, equipped with the
-    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
-        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
-        )$, the discounted state-visitation measure
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$.
-\end{lemma}
-\begin{proof}
-    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
-    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    converges to a well-defined measure. First, let's recall that
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
-    the total variation norm
-    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
-    we need to show that the series
-    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
-    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
-    joint state-belief-policy space after $t$ transitions, starting from the initial
-    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
-    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
-    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
-    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
-    $\mu_{0}$ with total mass
-    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
-        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
-    \begin{align}
-        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    For $n < m$, the difference between two partial sums is:
-    \begin{align}
-        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
-                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
-                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
-                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
-                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
-                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
-    \end{align}
-
-    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
-    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
-    of this space, the sequence converges to a measure which we denote as
-    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
-    \begin{align}
-        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
-                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
-                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
-                                                                           & = M
-    \end{align}
-
-    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
-\end{proof}Having established existence, we now turn to the uniqueness of the discounted
-visitation measure.
-
-\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
-    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
-    to the functional equation:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
-    \end{align}
-
-    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$.
-\end{lemma}
-\begin{proof}
-    First, we verify that
-    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    satisfies the functional equation:
-
-    \begin{align}
-        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
-                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
-                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
-                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
-                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
-                                                            & = d^{\pi}_{\mu_0}
-    \end{align}
-
-    To prove uniqueness, suppose there exists another measure
-    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    that satisfies the functional equation:
-    \begin{align}
-        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
-    \end{align}
-
-    Let's consider the operator
-    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    defined as:
-    \begin{align}
-        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
-    \end{align}
-
-    For any two measures
-    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
-                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
-                                 & \leq \gamma \|\mu - \nu\|_{TV}
-    \end{align}
-
-    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
-    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
-    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
-    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
-    the uniqueness of the discounted state-visitation measure.
-\end{proof}
-
-\subsection{Connection to Value Function}
-Having established the theoretical properties of the discounted visitation
-measure, we now connect it to the value function, which will provide important
-insights later on.
-
-\begin{lemma}[Value Function as Inner Product]
-    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
-    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
-    the value function can be expressed as:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
-    the Dirac measure concentrated at
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
-    immediate reward function:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-\end{lemma}
-\begin{proof}
-    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
-    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
-        {\theta}_{0})$. By definition of the value function:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
-    \end{align}
-
-    Define the expected immediate reward function
-    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    Then:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
-    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
-        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
-    and measures:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
-    $(I - \gamma \Psi^{*})^{-1}$:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
-        ^{*})^{-1}\mu_{0}$. Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
-                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}This lemma establishes that the value function can be expressed as an
-expectation with respect to the discounted visitation measure, with an appropriate
-scaling factor. This formulation provides a direct link between the value
-function and the distribution of states.
-
-\section{Policy Gradient Theorem}
-Having established the mathematical foundations for discounted returns in
-partially observable multi-agent settings, we now derive the policy gradient theorem
-that forms the basis for practical optimization algorithms. This theorem
-provides a principled expression for computing gradients of the expected
-discounted return with respect to policy parameters, enabling efficient policy improvement.
-The policy gradient theorem connects an agent's policy parameters to its
-expected long-term performance through the discounted visitation measure, providing
-a mathematically rigorous foundation for optimization.
-
-\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
-        Theorem]
-    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
-            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
-    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
-    Markov game setting can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
-                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
-    visitation measure starting from initial distribution $\mu_{0}$, and
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
-    the action-value function defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
-on the lemmas established in previous sections.
-\begin{proof}
-    From our previous lemma, we know that the gradient of the value function can be
-    expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
-    \end{align}
-
-    For notational clarity, we define the term inside the brackets as:
-    \begin{align}
-        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    Now we can write:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For our specific initial state configuration
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Let's define
-    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
-    Dirac measure concentrated at the initial state. We can view
-    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
-    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
-    Dirac measure:
-
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
-                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Recall the duality principle we established earlier, which states that:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
-    \end{align}
-
-    Allowing us to move the operator from acting on the function $g$ to acting on
-    the measure $\mu_{0}$:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From our earlier derivation of the discounted visitation measure, we established
-    that:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
-    \end{align}
-
-    We can now substitute this expression:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
-                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For finite state, belief, and policy parameter spaces, this integral can be
-    written as a sum:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    This completes the proof of the Partially Observable Active Discounted Return
-    Policy Gradient Theorem.
-\end{proof}
-
-The proof reveals a symmetry in the mathematical structure of our results.
-\begin{remark}[Symmetry]
-    From the Value Function as Inner Product lemma, the value function
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
-    measure $d^{\pi}_{\mu_0}$. While its gradient
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of policy-gradient-weighted action values $g$ under the same
-    discounted visitation measure $d^{\pi}_{\mu_0}$.
-\end{remark}
-This symmetric structure provides not only mathematical elegance but also
-practical advantages. It means that the same samples from the discounted visitation
-distribution can be used to estimate both values and policy gradients.
-
-The policy gradient theorem provides the mathematical foundation for agents to optimize
-their policies in ways that account for both the partial observability of the environment
-and the learning dynamics of other agents. This enables sophisticated strategic
-behaviors such as information revelation, teaching, and influence that are
-essential in social learning contexts.
-
-\chapter{POLARIS Architecture}
-\label{appendix:neural_architectures}
-
-This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation.
-We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
-\begin{equation}
-    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
-\end{equation}
-
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
-
-\chapter{Social Learning Implementation}
-
-This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework.
-We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations.
-The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios.
-Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models.
-Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.
-
-\section{Lévy Process Discretization}
-\label{appendix:levy_discretization}
-
-This appendix provides a comprehensive mathematical treatment of the discretization of Lévy processes for implementing strategic experimentation models within our Partially Observable Active Markov Game framework.
-We establish rigorous theoretical foundations for the numerical approximation schemes used in our implementation and analyze their convergence properties and preservation of strategic incentives.
-
-\subsection{Mathematical Foundations of Lévy Processes}
-\label{appendix:levy_foundations}
-
-Lévy processes form a fundamental class of stochastic processes that include Brownian motion and Poisson processes as special cases.
-They are characterized by stationary and independent increments, serving as the natural continuous-time generalization of random walks.
-
-\begin{definition}[Lévy Process]
-    A stochastic process $X = \{X_t : t \geq 0\}$ on $\mathbb{R}^d$ with $X_0 = 0$ almost surely is a Lévy process if:
-    \begin{enumerate}
-        \item It has independent increments: for any $0 \leq t_1 < t_2 < \cdots < t_n < \infty$, the random variables $X_{t_2} - X_{t_1}, X_{t_3} - X_{t_2}, \ldots, X_{t_n} - X_{t_{n-1}}$ are mutually independent.
-        \item It has stationary increments: for any $s < t$, the distribution of $X_t - X_s$ depends only on $t-s$.
-        \item It is stochastically continuous: for any $t \geq 0$ and $\varepsilon > 0$, $\lim_{h \to 0} \mathbb{P}(|X_{t+h} - X_t| > \varepsilon) = 0$.
-    \end{enumerate}
-\end{definition}
-
-The celebrated Lévy-Khintchine formula provides a complete characterization of Lévy processes through their characteristic functions:
-
-\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
-    If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
-    \begin{equation}
-        \mathbb{E}[e^{i\theta X_t}] = e^{t\psi(\theta)}
-    \end{equation}
-    where
-    \begin{equation}
-        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
-    \end{equation}
-    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
-\end{theorem}
-
-The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
-Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
-
-\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
-    Any Lévy process $X_t$ can be decomposed as:
-    \begin{equation}
-        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
-    \end{equation}
-    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
-\end{theorem}
-
-The Lévy-Itô decomposition provides a pathwise representation of a Lévy process as the sum of a drift term, a Brownian motion, and potentially infinitely many jumps, both small and large.
-
-\subsection{Time Discretization of Lévy Processes}
-\label{appendix:levy_discretization_methods}
-
-To implement continuous-time Lévy processes within discrete computational frameworks, we must employ appropriate numerical approximation schemes.
-For our strategic experimentation model, we adopt the Euler-Maruyama scheme, extended to accommodate the jump components of general Lévy processes.
-
-\begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
-    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
-    \begin{equation}
-        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
-    \end{equation}
-    where $Z_n \sim \mathcal{N}(0,1)$ are independent standard normal random variables and $\Delta J_n$ represents the jump increment over $[t_n, t_{n+1}]$.
-\end{definition}
-\iffalse
-    For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.
-
-    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
-        The jump component $\Delta J_n$ can be approximated through one of the following approaches:
-        \begin{enumerate}
-            \item For finite-activity processes (where $\nu(\mathbb{R}) < \infty$):
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K_n} J_i
-                  \end{equation}
-                  where $K_n \sim \text{Poisson}(\nu(\mathbb{R})\Delta t)$ and $J_i$ are i.i.d. random variables with distribution $\frac{\nu(dx)}{\nu(\mathbb{R})}$.
-
-            \item For infinite-activity processes, a truncation approach:
-                  \begin{equation}
-                      \Delta J_n = \sum_{i=1}^{K^{\varepsilon}_n} J^{\varepsilon}_i + c_{\varepsilon}\Delta t
-                  \end{equation}
-                  where $K^{\varepsilon}_n \sim \text{Poisson}(\nu(\{x: |x| > \varepsilon\})\Delta t)$, $J^{\varepsilon}_i$ are i.i.d.
-with distribution $\frac{\nu(dx)\mathbf{1}_{|x|>\varepsilon}}{\nu(\{x: |x| > \varepsilon\})}$, and $c_{\varepsilon} = \int_{|x|\leq\varepsilon} x\nu(dx)$.
-        \end{enumerate}
-    \end{proposition}
-\fi
-\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
-    \label{thm:euler_maruyama_convergence}
-    Let $X_t$ be a Lévy process and $\hat{X}_t$ be its Euler-Maruyama approximation with time step $\Delta t$. Then for any fixed $T > 0$:
-    \begin{enumerate}
-        \item (Weak Convergence) For any smooth function $f$ with polynomial growth:
-              \begin{equation}
-                  |\mathbb{E}[f(X_T)] - \mathbb{E}[f(\hat{X}_T)]| \leq C\Delta t
-              \end{equation}
-
-        \item (Strong Convergence) If $\int_{|x|>1} |x|^2 \nu(dx) < \infty$, then:
-              \begin{equation}
-                  \mathbb{E}[\sup_{0\leq t\leq T} |X_t - \hat{X}_t|^2] \leq C\Delta t
-              \end{equation}
-    \end{enumerate}
-    where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.
-
-\end{theorem}
-
-The weak and strong convergence properties ensure that our numerical scheme accurately approximates both the distributional properties and pathwise behavior of the continuous-time process as the time step decreases.
-
-\subsection{Implementing Strategic Experimentation Models}
-\label{appendix:strategic_experimentation_implementation}
-
-In our implementation of the strategic experimentation model from \citet{keller2020undiscounted}, we must discretize both the background signal process $B_t$ and the individual payoff processes $X^i_t$, while preserving the strategic incentives that drive experimentation decisions.
-
-\subsubsection{Discretization of Diffusion-Poisson Processes}
-\label{appendix:discretization_diffusion_poisson}
-
-In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:
-
-\begin{align}
-    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
-    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
-\end{align}
-
-where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes.
-Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:
-
-\begin{align}
-    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
-    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
-\end{align}
-
-For implementation, we denote these increments as:
-
-\begin{align}
-    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
-    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
-\end{align}
-
-where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
-
-\subsubsection{Reward Function Equivalence}
-\label{appendix:reward_equivalence}
-
-A critical challenge in our implementation is reconciling the time-dependent nature of continuous-time rewards with the time-independent reward structure required by the POAMG framework.
-In the original continuous-time model, agents' instantaneous rewards are:
-
-\begin{equation}
-    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
-\end{equation}
-
-where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$.
-To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time.
-We achieve this through a normalization approach:
-
-\begin{equation}
-    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
-\end{equation}
-
-This transformation preserves the incentive structure of the original model while eliminating explicit time dependence. The following proposition establishes this equivalence formally:
-
-\begin{proposition}[Reward Equivalence]
-    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
-    \begin{equation}
-        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{equation}
-    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
-\end{proposition}
-
-\begin{proof}
-    The expected value of the discrete-time reward function is:
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
-                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
-                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
-    \end{align}
-
-    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:
-
-    \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
-                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
-    \end{align}
-
-    This exactly matches the expected instantaneous flow payoff in the continuous-time model.
-\end{proof}
-
-\iffalse
-    \subsubsection{Preservation of Strategic Incentives}
-    \label{appendix:strategic_incentives}
-
-    Beyond matching expected rewards, we must ensure that our discretization preserves the strategic incentives that drive experimentation decisions.
-The key strategic consideration in the model is the trade-off between exploitation (choosing the safe arm) and exploration (choosing the risky arm to learn about its quality).
-
-    \begin{proposition}[Preservation of Strategic Incentives]
-        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
-
-    \end{proposition}
-
-    \begin{proof}
-        In the strategic experimentation model, the incentive to experiment at a given belief $b$ about the state is characterized by:
-        \begin{equation}
-            I(b) = \frac{f(b) - s}{s - m(b)}
-        \end{equation}
-        when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad.
-In our discrete-time approximation, the corresponding incentive is:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)}
-        \end{equation}
-        where $\hat{f}(b)$ and $\hat{m}(b)$ are the discrete-time analogs.
-
-        Let us elaborate on why $\hat{f}(b) \to f(b)$ and $\hat{m}(b) \to m(b)$ as $\Delta t \to 0$. In the continuous-time model, the expected flow payoff of the risky arm at belief $b$ is:
-        \begin{equation}
-            f(b) = b f_1 + (1-b) f_0
-        \end{equation}
-        where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$.
-In our discrete-time approximation, we have:
-        \begin{equation}
-            \hat{f}(b) = b \hat{f}_1 + (1-b) \hat{f}_0
-        \end{equation}
-        where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
-        From our reward equivalence result, we know that:
-        \begin{align}
-            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
-                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
-        \end{align}
-
-        The Brownian motion term has $\mathbb{E}[\sigma(W^i_t - W^i_{t-1})] = 0$ and $\text{Var}[\sigma(W^i_t - W^i_{t-1})] = \sigma^2 \Delta t$.
-By the martingale property of Brownian motion, this term contributes zero to the expected value but introduces variance of order $O(\Delta t)$.
-Thus:
-        \begin{equation}
-            \hat{f}_1 = \alpha_1 + \lambda_1\mu_1 + O(\Delta t) \to f_1 \text{ as } \Delta t \to 0
-        \end{equation}
-
-        Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
-        Therefore, we can establish that:
-        \begin{equation}
-            \hat{I}(b) = \frac{\hat{f}(b) - s}{s - \hat{m}(b)} = \frac{b \hat{f}_1 + (1-b) \hat{f}_0 - s}{s - \hat{f}_0} = \frac{b(\hat{f}_1 - \hat{f}_0) + \hat{f}_0 - s}{s - \hat{f}_0}
-        \end{equation}
-
-        As $\Delta t \to 0$, we have $\hat{f}_1 \to f_1$, $\hat{f}_0 \to f_0$, and consequently:
-        \begin{equation}
-            \hat{I}(b) \to \frac{b(f_1 - f_0) + f_0 - s}{s - f_0} = \frac{b f_1 + (1-b) f_0 - s}{s - f_0} = \frac{f(b) - s}{s - m(b)} = I(b)
-        \end{equation}
-
-        The convergence of incentives directly implies convergence of optimal policies.
-In the continuous-time model, the symmetric Markov perfect equilibrium characterized in \citet{keller2020undiscounted} has the form:
-        \begin{equation}
-            \kappa^*(b) =
-            \begin{cases}
-                0                    & \text{if } I(b) \leq k_0,            \\
-                \frac{I(b)-k_0}{N-1} & \text{if } k_0 < I(b) < k_0 + N - 1, \\
-                1                    & \text{if } I(b) \geq k_0 + N - 1.
-            \end{cases}
-        \end{equation}
-        where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players.
-The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.
-
-        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
-    \end{proof}
-
-\fi
-\subsection{Relation to Policy-Invariant Reward Transformations}
-\label{appendix:policy_invariance}
-
-Our approach to time-independent reward formulation can be viewed through the lens of policy-invariant reward transformations, as developed in the reinforcement learning literature by \citet{ng1999policy}.
-
-\begin{definition}[Potential-Based Reward Shaping]
-    A reward transformation $\tilde{R}(s, a, s') = R(s, a, s') + F(s, s')$ is potential-based if there exists a potential function $\Phi: S \to \mathbb{R}$ such that $F(s, s') = \gamma\Phi(s') - \Phi(s)$ for all $s, s' \in S$, where $\gamma$ is a discount factor.
-\end{definition}
-
-\begin{theorem}[Ng-Harada-Russell \citep{ng1999policy}]
-    If a reward transformation is potential-based, then the optimal policy under the transformed reward function is also optimal under the original reward function, and vice versa.
-\end{theorem}
-
-While our transformation does not directly fit the potential-based formulation (since we're normalizing by $\Delta t$ rather than adding a potential difference), it shares the crucial property of preserving optimal policies.
-The following result establishes this connection:
-
-\begin{proposition}[Connection to Policy-Invariant Transformations]
-    The transformation from time-dependent rewards in the continuous-time model to time-independent rewards in the POAMG framework preserves policy optimality in the limit as $\Delta t \to 0$.
-\end{proposition}
-
-\begin{proof}
-    The original cumulative reward over a time interval $[0, T]$ is:
-    \begin{equation}
-        \int_0^T [(1-a^i_t)s + a^i_t\alpha_s] dt + \int_0^T a^i_t \sigma dW^i_t + \int_0^T a^i_t dC^i_t
-    \end{equation}
-
-    The discretized cumulative reward is:
-    \begin{equation}
-        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
-    \end{equation}
-    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.
-
-    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral.
-Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
-\end{proof}
-
-\section{Observed Reward Function}
-\label{appendix:observed_reward_derivation} In our reinforcement learning
-implementation, agents need to learn from observed rewards that reflect the optimality
-of their actions with respect to the true state of the world. However, since agents
-do not directly observe the true state $\omega$, we need to construct a reward
-function based on their observations $o$ that preserves the expected reward
-structure. This appendix provides a detailed derivation of the observation-based
-reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
-    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
-observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
-state. We need to construct an observation-based reward function $v(o, a): \Omega
-    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
-\begin{equation}
-    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
-    a \in A.
-\end{equation}
-
-In other words, the expected value of the observation-based reward $v(o, a)$
-over all possible observations $o$ given the state $s$ should equal the true
-reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
-    m$ matrix representing the observation distributions, where $m = |S|$ and assume
-the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
-the probability of observing observation $o$ in state $s$:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
-        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
-        \vdots           & \vdots           & \ddots & \vdots           \\
-        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
-    \end{bmatrix}
-\end{equation}
-
-We assume that observation distributions are linearly independent across states,
-which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
-    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
-more likely to generate its corresponding observation than any other observation.
-For each action $a \in A$, we define a utility vector
-$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
-\begin{equation}
-    \bm{u}_{a} =
-    \begin{bmatrix}
-        u(s^{1}, a) \\
-        u(s^{2}, a) \\
-        \vdots      \\
-        u(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
-    ^{k}$ for action $a$:
-\begin{equation}
-    \bm{v}_{a} =
-    \begin{bmatrix}
-        v(s^{1}, a) \\
-        v(s^{2}, a) \\
-        \vdots      \\
-        v(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-The condition that expected observation-based rewards match true rewards can be written
-as a linear system:
-\begin{equation}
-    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
-\end{equation}
-
-where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
-is:
-\begin{equation}
-    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
-\end{equation}
-
-This gives us the vector of observation-based rewards that satisfy our expected
-reward condition. For each observation $o_{j}$ and action $a$, the observation-based
-reward is:
-\begin{equation}
-    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
-\end{equation}
-
-where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
-$\bm{\mu}^{-1}$.
-\paragraph{Binary Case Example}
-For the special case with two states of the world ($m = 2$) and symmetric
-observations with accuracy $q > 0.5$, the observation distribution matrix is:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        q   & 1-q \\
-        1-q & q
-    \end{bmatrix}
-\end{equation}
-
-This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
-and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
-The inverse of this matrix is:
-\begin{equation}
-    \bm{\mu}^{-1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q      & -(1-q) \\
-        -(1-q) & q
-    \end{bmatrix}
-\end{equation}
-
-In our implementation, we set the true reward as the indicator function for taking
-the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
-    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
-utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
-is:
-\begin{equation}
-    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q \\
-        -(1-q)
-    \end{bmatrix}
-\end{equation}
-
-This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
-the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
-$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
-action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
-observation-based reward vector is:
-\begin{equation}
-    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        -(1-q) \\
-        q
-    \end{bmatrix}
-\end{equation}
-
-Combining these results, we can express the observation-based reward function for
-any action-observation pair $(a, o)$ as:
-\begin{equation}
-    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
-        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
-\end{equation}
-
-where $\varphi$ maps observations to their corresponding actions. The derived
-observation-based reward function has an intuitive interpretation. When an agent
-takes an action matching its observation ($a = o$), it receives a positive
-reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
-($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
-0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
-increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
-informative), the reward for matching observation and action approaches 1, and the
-penalty for mismatching approaches 0, meaning that the observed reward function
-converges to the true reward function. This reward structure incentivizes agents
-to match their actions to their observations when signals are reliable, but also
-allows them to learn to override their immediate observations when the actions
-of other agents provide stronger evidence about the true state through beliefs.
+\end{document}

### 2025-05-26 paper/we.tex
Update brandl results.

--- 2025-05-26 paper/appendix.tex
@@
-\setcounter{proposition}{0}
-\setcounter{assumption}{0}
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
-
-\chapter{Reinforcement Learning Background}
-
-\label{appendix:rl_details}
-This section provides a brief overview of reinforcement learning (RL) and multi-agent reinforcement learning (MARL) to provide a foundation for understanding the theoretical framework presented in this paper.
-
-\section{Reinforcement Learning Foundations}
-
-Reinforcement learning (RL) provides a mathematical framework for solving sequential decision-making problems under uncertainty.
-In the classical single-agent setting, an agent interacts with a stationary environment by observing states, taking actions, and receiving rewards, with the objective of maximizing its expected cumulative reward over time \cite{sutton2018reinforcement}.
-This interaction is formalized as a Markov Decision Process (MDP), defined as a tuple $M = \langle S, A, T, R, \gamma \rangle$ where:
-
-\begin{itemize}
-    \item $S$ is the state space, representing all possible configurations of the environment
-    \item $A$ is the action space, representing all possible decisions available to the agent
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function, specifying the probability distribution over next states given the current state and action
-    \item $R: S \times A \mapsto \mathbb{R}$ is the reward function, specifying the immediate reward received after taking an action in a state
-    \item $\gamma \in [0, 1)$ is the discount factor, balancing immediate versus future rewards
-\end{itemize}
-
-The agent's behavior is characterized by a policy $\pi: S \mapsto \Delta(A)$, which maps states to probability distributions over actions.
-The policy can be evaluated using value functions: the state-value function $V^\pi(s)$ represents the expected return when starting in state $s$ and following policy $\pi$ thereafter, while the action-value function $Q^\pi(s, a)$ represents the expected return after taking action $a$ in state $s$ and following policy $\pi$ thereafter.
-The goal of RL is to find an optimal policy $\pi^*$ that maximizes the expected return from all states.
-
-The Markov property, which states that the future is independent of the past given the present, is a fundamental assumption in MDPs.
-This property ensures that the current state provides all the necessary information for making optimal decisions, greatly simplifying the learning problem.
-However, this assumption becomes problematic in multi-agent settings, as we will discuss next.
-
-\section{Multi-Agent Reinforcement Learning: Concepts and Challenges}
-
-Multi-agent reinforcement learning (MARL) extends the single-agent RL framework to environments with multiple autonomous agents that interact simultaneously \cite{marl-book,yang2020overview, huh2024multiagentreinforcementlearningcomprehensive, busoniu2010multi, zhang2021multi}.
-MARL encompasses a wide spectrum of scenarios, from fully cooperative tasks where agents share a common reward function, to fully competitive zero-sum games, to the general mixed cooperative-competitive case with individual reward functions \cite{nowé2012game}.
-These interactions are commonly formalized as Markov games (also known as stochastic games) \cite{littman1994markov, shapley1953stochastic}, defined as a tuple $M_n = \langle I, S, A, T, R, \gamma \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space, shared among all agents
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function that depends on the joint action
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\gamma \in [0, 1)$ is the discount factor
-\end{itemize}
-MARL introduces several fundamental challenges beyond those encountered in single-agent RL.
-The joint action space grows exponentially with the number of agents, creating a combinatorial explosion that makes exploration and learning increasingly difficult as more agents are added to the system.
-Coordination challenges further complicate the learning process, as agents must synchronize their actions to achieve effective joint behavior, especially in cooperative settings where team performance depends on complementary actions \cite{du2023reviewcooperationmultiagentlearning}, that can also involve explicit communication \cite{zhu2024surveymultiagentdeepreinforcement}.
-In scenarios with shared rewards, the credit assignment problem becomes particularly troublesome, as determining individual contributions to team success grows increasingly complex when outcomes result from joint actions rather than individual decisions.
-MARL also demands sophisticated strategic reasoning, requiring agents to model and reason about other agents' goals, beliefs, and strategies, particularly in competitive or mixed cooperative-competitive settings.
-Perhaps most critically, when multiple agents learn simultaneously, the environment becomes non-stationary from each agent's perspective, as other agents' changing policies continuously modify the effective environment dynamics, violating a fundamental assumption of traditional reinforcement learning algorithms.
-
-\section{The Non-Stationarity Challenge}
-The non-stationarity problem in MARL represents a fundamental departure from single-agent RL assumptions and presents one of the most significant obstacles to effective multi-agent learning \cite{hernandez2017survey, papoudakis2019dealing}.
-To understand this challenge more precisely, we can analyze how learning dynamics alter the effective environment for each agent.
-When multiple agents learn simultaneously, each agent $i$ with policy $\pi^i$ effectively faces an environment whose dynamics depend on the joint policies of all other agents $\pi^{-i}$.
-From agent $i$'s perspective, the effective transition function becomes:
-\begin{equation}
-    T^i_{\boldsymbol{\pi}^{-i}_t}(s_{t+1}|s_t, a^i_t) = \sum_{\mathbf{a}^{-i} \in A^{-i}} \left(\prod_{j \in I \setminus \{i\}} \pi^j_t(a^j|s_t)\right) \cdot T(s_{t+1}|s_t, (a^i_t, \mathbf{a}^{-i}))
-\end{equation}
-where $A^{-i}$ denotes the joint action space, $\mathbf{a}^{-i}$ denotes the joint action and $\boldsymbol{\pi}^{-i}_t$ denotes the joint policies of all agents except $i$.
-When other agents update their policies from $\boldsymbol{\pi}^{-i}_t$ to $\boldsymbol{\pi}^{-i}_{t+1}$ through learning, this effective transition function changes, creating a non-stationary environment for agent $i$.
-This non-stationarity violates the Markov property assumption underlying most RL algorithms and can lead to several significant challenges that fundamentally undermine the theoretical foundations of single-agent RL.
-When multiple agents learn simultaneously, standard RL convergence guarantees no longer apply, and learning algorithms may oscillate or diverge as the effective environment continuously shifts \cite{bowling2002multiagent}.
-This dynamic environment causes value function approximations to become increasingly inaccurate over time, leading to suboptimal policy decisions as agents base their choices on outdated models of their environment \cite{lauer2000algorithm}.
-Further complicating matters, agents face a moving target problem where they must simultaneously learn optimal policies while adapting to the evolving strategies of others, creating a complex coupled learning process that resists straightforward optimization approaches \cite{laurent2011world}.
-The situation becomes particularly problematic in competitive settings, where learning dynamics may lead to cyclic policy changes rather than convergence to stable strategies, as agents continuously adapt and counter-adapt to each other's evolving behaviors \cite{balduzzi2018mechanics}.
-These interconnected challenges highlight why addressing non-stationarity remains one of the central research questions in multi-agent reinforcement learning.
-
-\section{Traditional Approaches to Non-Stationarity}
-Researchers have developed various approaches to address the non-stationarity challenge in MARL. These can be broadly categorized as follows:
-
-\subsection{Independent Learning}
-The simplest approach is to ignore non-stationarity entirely, treating other agents as part of the environment and applying standard single-agent RL algorithms independently for each agent \cite{tan1993multi}.
-This approach, often called Independent Learning (IL), requires no explicit coordination or modeling of other agents.
-Methods in this category include Independent Q-Learning \cite{tampuu2017multiagent}, where each agent maintains its own Q-function and updates it using only its own experiences.
-While computationally efficient and naturally scalable to many agents, independent learning lacks theoretical convergence guarantees and can fail in complex multi-agent scenarios due to the violation of the stationarity assumption.
-
-\subsection{Centralized Training with Decentralized Execution}
-To mitigate non-stationarity during learning while preserving autonomous execution, many approaches adopt the paradigm of centralized training with decentralized execution (CTDE) \cite{lowe2017multi, foerster2018counterfactual, sunehag2018value}.
-In CTDE, agents have access to additional information during training (e.g., joint actions, global state, other agents' policies) but operate based solely on their local observations during execution.
-
-Notable algorithms in this category include Multi-Agent Deep Deterministic Policy Gradient (MADDPG) \cite{lowe2017multi}, which uses centralized critics with access to joint actions and states during training but decentralized actors during execution.
-Another significant approach is Counterfactual Multi-Agent Policy Gradients (COMA) \cite{foerster2018counterfactual}, which addresses credit assignment using a centralized critic that computes a counterfactual baseline.
-The category also features QMIX \cite{rashid2018qmix}, which learns a centralized value function that factorizes into a mixing of individual agent Q-values, ensuring consistency between centralized and decentralized policies.
-While CTDE methods help stabilize learning, they still do not fully address the fundamental non-stationarity issue, as they focus on adapting to current policies rather than reasoning about policy evolution over time.
-
-\subsection{Opponent Modeling and Population-Based Training}
-Another approach is to explicitly model the behavior and learning processes of other agents, enabling more informed adaptation \cite{albrecht2018autonomous, he2016opponent}.
-This can involve predicting other agents' policies, types, or learning dynamics.
-Methods in this category include Deep Reinforcement Opponent Network (DRON) \cite{he2016opponent}, which integrates opponent modeling into deep Q-learning.
-Another significant approach is Probabilistic Recursive Reasoning (PR2) \cite{wen2019probabilistic}, which models higher-order beliefs about other agents' reasoning processes.
-
-The category also encompasses Population-Based Training (PBT) \cite{jaderberg2019human}, which trains a population of agents simultaneously, creating a naturally changing learning environment that promotes robustness to non-stationarity.
-While these approaches can better handle changing policies, they typically focus on adaptation to current policies rather than influencing the learning trajectories of other agents.
-
-\subsection{Equilibrium Learning and Stability Concepts}
-Drawing on game theory, some approaches focus on finding policies that constitute game-theoretic solution concepts like Nash equilibria \cite{bowling2005convergence, hu2003nash, littman2001friend}.
-These methods aim to find stable joint policies where no agent has an incentive to unilaterally deviate.
-Notable algorithms include Nash Q-Learning \cite{hu2003nash}, which converges to Nash equilibria in general-sum Markov games.
-Another significant approach is Friend-or-Foe Q-Learning \cite{littman2001friend}, which converges to optimal policies in restricted classes of Markov games.
-
-The category also features WoLF-PHC (Win or Learn Fast - Policy Hill Climbing) \cite{bowling2002multiagent}, which adjusts learning rates based on whether an agent is "winning" or "losing" to promote convergence.
-While these approaches provide theoretical guarantees under certain conditions, they often make strong assumptions about the game structure and other agents' rationality.
-Moreover, they focus on convergence to static equilibria rather than the dynamic nature of multi-agent learning.
-
-\subsection{Meta-Learning for Non-Stationarity}
-Recent work has explored meta-learning as a framework for rapid adaptation to non-stationarity in MARL \cite{alshedivat2018continuous, kim2021policy}.
-These approaches train agents to quickly adapt to new agents or environments, treating non-stationarity as a meta-learning problem.
-Key methods include Continuous Adaptation via Meta-Learning (CAML) \cite{alshedivat2018continuous}, which uses meta-learning to quickly adapt to evolving opponents.
-
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which extends meta-learning to explicitly account for the influence of an agent's actions on the learning processes of other agents.
-While meta-learning approaches show promise for rapid adaptation, they often still lack a comprehensive framework for modeling and influencing the long-term learning dynamics of multi-agent systems.
-
-\section{Active Markov Games}
-
-Active Markov Games provide a more sophisticated framework for modeling the dynamic nature of multi-agent learning by explicitly incorporating the policy update processes of all agents \cite{kim2022influencing}.
-They extend standard Markov games to capture not just the immediate effects of actions on states and rewards, but also their influence on future policy updates, addressing the non-stationarity challenge at a fundamental level.
-
-\subsection{Formal Definition}
-
-An Active Markov Game is defined as a tuple $M_n = \langle I, S, A, T, R, \Theta, U \rangle$, where:
-
-\begin{itemize}
-    \item $I = \{1, \ldots, n\}$ is the set of $n$ agents
-    \item $S$ is the state space
-    \item $A = \times_{i \in I} A^i$ is the joint action space, where $A^i$ is the action space of agent $i$
-    \item $T: S \times A \mapsto \Delta(S)$ is the transition function
-    \item $R = \times_{i \in I} R^i$ is the joint reward function, where $R^i: S \times A \mapsto \mathbb{R}$ is agent $i$'s individual reward function
-    \item $\Theta = \times_{i \in I} \Theta^i$ is the joint policy parameter space, where $\Theta^i$ is the policy parameter space for agent $i$
-    \item $U = \times_{i \in I} U^i$ is the joint Markovian policy update function, where $U^i: \Theta^i \times T^i \mapsto \Delta(\Theta^i)$ maps current policy parameters and transitions to distributions over next policy parameters
-\end{itemize}
-Here, $T^i$ represents the trajectory space for agent $i$, with a particular element $\tau^i_t = \{s_t, \mathbf{a}_t, r^i_t, s_{t+1}\}$ consisting of the current state, joint action, reward received, and the next state.
-The interaction process in an Active Markov Game unfolds through a sequential procedure of actions and updates.
-At timestep $t$, each agent $i$ selects an action $a^i_t \sim \pi^i(\cdot|s_t; \theta^i_t)$ based on its parameterized policy with parameters $\theta^i_t \in \Theta^i$.
-Following this selection, the environment transitions from state $s_t$ to $s_{t+1}$ according to $T(s_{t+1}|s_t, \mathbf{a}_t)$ based on the joint action $\mathbf{a}_t = (a^1_t, \ldots, a^n_t)$.
-Each agent $i$ then receives a reward $r^i_t = R^i(s_t, \mathbf{a}_t)$ and subsequently updates its policy parameters according to its update function $\theta^i_{t+1} \sim U^i(\theta^i_{t+1}|\theta^i_t, \tau^i_t)$.
-This process continues until non-stationary policies converge to a recurrent set of joint policies.
-The key insight is that agent $i$'s actions not only affect immediate states and rewards but also influence future policy updates of all agents, including itself, through the trajectory $\tau^i_t$.
-
-\subsection{Augmented Transition Function and Stationarity}
-
-The Active Markov Game framework fundamentally transforms the non-stationarity problem by explicitly modeling how policies evolve through Markovian update functions.
-To understand this transformation, let us contrast the transition functions in standard MARL and Active Markov Games.
-In standard MARL, the transition function $T: S \times A \mapsto \Delta(S)$ only captures state transitions based on joint actions.
-However, Active Markov Games introduce a critical innovation: they explicitly model how policies change via Markovian update functions.
-The augmented transition function becomes:
-
-\begin{equation}
-    \mathbb{P}(s_{t+1}, \boldsymbol{\theta}_{t+1}|s_t, \boldsymbol{\theta}_t) = \sum_{\mathbf{a}_t \in A} \left(\prod_{i \in I} \pi^i(a^i_t|s_t; \theta^i_t)\right) \times T(s_{t+1}|s_t, \mathbf{a}_t) \times \boldsymbol{U}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)
-\end{equation}
-The crucial difference is the inclusion of $\boldsymbol{U}$ - a Markovian update function that specifies exactly how policy parameters $\boldsymbol{\theta}_t$ (and consequently policies $\boldsymbol{\pi}$) evolve based on current parameters and trajectories.
-By making policy updates an explicit part of the system dynamics, what was previously an unpredictable external process becomes a predictable internal one.
-This augmented transition function operates over the joint space $(s, \boldsymbol{\theta}) \in S \times \Theta$, creating a joint process that is stationary even though individual policies are changing.
-
-\subsection{Theoretical Properties and Convergence}
-
-Active Markov Games exhibit important theoretical properties that enable rigorous analysis of multi-agent learning dynamics:
-
-\paragraph{Stationary Periodic Distributions.} Under mild assumptions, the joint process of states and policies in an Active Markov Game converges to a stationary periodic distribution \cite{kim2022influencing}:
-
-\begin{equation}
-    \mu_k(s, \theta|s_0, \theta_0, \ell) = \mathbb{P}(s_t = s, \theta_t = \theta|s_0, \theta_0, \ell)
-\end{equation}
-
-where $\ell = t\%k$ with $\%$ denoting the modulo operation.
-This distribution represents the limiting behavior of the system after convergence, characterized by potentially periodic patterns of states and policies.
-The parameter $k$ represents the period length, with $k=1$ corresponding to fixed-point convergence.
-To address sensitivity to initial conditions, the framework introduces the concept of \textit{stochastically stable distributions} \cite{kim2022influencing}.
-These are limiting distributions that emerge when small random perturbations are added to policy updates, providing robustness to initial state and policy configurations.
-
-\paragraph{Long-term Optimization Objective.} In Active Markov Games, agents optimize for long-term average reward rather than discounted return \cite{sutton2018reinforcement, kim2022influencing}:
-
-\begin{equation}
-    \max_{\theta^i, U^i} \rho^i(s, \theta, U) := \max_{\theta^i, U^i} \lim_{T \to \infty} \mathbb{E}\left[\frac{1}{T}\sum_{t=0}^T R^i(s_t, \mathbf{a}_t) \Bigg|
-        \begin{array}{c}
-            s_0=s, \theta_0=\theta,                                              \\
-            \mathbf{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|s_{0:T}; \theta_{0:T}), \\
-            s_{t+1} \sim T(\cdot|s_t, \mathbf{a}_t),
-            \theta_{t+1} \sim U(\cdot|\theta_t, \boldsymbol{\tau}_t)
-        \end{array}
-        \right]
-\end{equation}
-
-where  $0:T$ denotes the sequence from time $0$ to $T$.
-This formulation encourages agents to consider how to influence the limiting behavior of the system rather than just short-term performance, addressing the non-stationarity challenge at a fundamental level.
-
-\paragraph{Active Equilibrium.} Active Markov Games give rise to a new solution concept called the Active Equilibrium \cite{kim2022influencing}, which generalizes traditional game-theoretic equilibria like Nash equilibrium.
-An Active Equilibrium is a joint policy parameter $\theta^* = \{\theta^{i*}, \theta^{-i*}\}$ with associated joint update function $U^* = \{U^{i*}, U^{-i*}\}$ such that:
-
-\begin{equation}
-    \rho^i(s, \theta^{i*}, \theta^{-i*}, U^{i*}, U^{-i*}) \geq \rho^i(s, \theta^i, \theta^{-i*}, U^i, U^{-i*})
-\end{equation}
-for all $i \in I$, $s \in S$, $\theta^i \in \Theta^i$, $U^i \in U^i$.
-This equilibrium concept captures the idea that rational agents should optimize not just their immediate policies but also their adaptation strategies, taking into account the learning dynamics of the system.
-The active equilibrium generalizes several classic solution concepts in game theory.
-Stationary Nash equilibria and correlated equilibria are special cases of active equilibria when $k = 1$ (fixed-point convergence) and joint action distributions are independent or correlated, respectively.
-Similarly, cyclic Nash equilibria and cyclic correlated equilibria can be viewed as special cases of active equilibria when $k > 1$ (periodic behavior), the joint update function is deterministic, and joint action distributions are independent or correlated, respectively.
-This generality allows the active equilibrium concept to capture a wider range of stable multi-agent behaviors in dynamic learning settings than traditional equilibrium notions.
-
-Active Markov Games address the non-stationarity challenge in several fundamental ways.
-By incorporating policy parameters and update functions directly into the framework, Active Markov Games make the non-stationarity explicit and amenable to analysis, embracing it as an integral part of the multi-agent learning process rather than treating it as an external challenge to be mitigated.
-The average reward objective promotes farsighted optimization by encouraging agents to consider the long-term limiting behavior of the system rather than myopically optimizing for immediate or short-term rewards, leading to policies that shape the learning trajectories of other agents in beneficial ways rather than merely reacting to their current behaviors.
-Furthermore, the framework enables active influence by allowing agents to reason about how their actions affect not just the environment state but also the learning processes of other agents, facilitating sophisticated strategies like teaching, deception, or coordination that explicitly aim to influence other agents' policy updates.
-Under appropriate conditions, Active Markov Games provide theoretical guarantees about convergence to stationary periodic distributions, offering a more solid foundation for algorithm development than approaches without such guarantees.
-Finally, the Active Equilibrium concept generalizes traditional game-theoretic solution concepts, providing a more comprehensive framework for understanding stable multi-agent behaviors in learning settings.
-
-\subsection{Practical Implementations}
-
-Recent work has leveraged the Active Markov Game framework to develop practical algorithms for MARL.
-Notable examples include FURTHER (FUlly Reinforcing acTive influence witH averagE Reward) \cite{kim2022influencing}, which implements a policy gradient approach tailored to the average reward objective in Active Markov Games, combined with variational inference for estimating other agents' policy dynamics in a decentralized manner.
-Another significant approach is Meta-MAPG (Meta-Multiagent Policy Gradient) \cite{kim2021policy}, which integrates meta-learning with explicit modeling of other agents' learning processes, aligning with the influence-aware perspective of Active Markov Games.
-These algorithms have demonstrated superior performance compared to methods that neglect the learning dynamics of other agents, particularly in environments with high levels of non-stationarity.
-
-\section{Extension to Partial Observability}
-
-While Active Markov Games provide a powerful framework for addressing non-stationarity, they assume full observability of the environment state.
-In many real-world scenarios, agents have limited perception capabilities and cannot directly observe the complete state of the environment or the internal parameters of other agents.
-This partial observability introduces additional challenges for multi-agent learning.
-The Partially Observable Markov Decision Process (POMDP) \cite{kaelbling1998planning} extends MDPs to settings with partial observability by introducing observation functions.
-In the multi-agent context, this leads to Partially Observable Stochastic Games (POSGs) \cite{hansen2004dynamic} or Decentralized POMDPs (Dec-POMDPs) for cooperative settings \cite{bernstein2002complexity}.
-Extending Active Markov Games to partial observability settings represents a significant advancement in addressing the combined challenges of non-stationarity and limited information in multi-agent learning.
-The resulting framework, Partially Observable Active Markov Games, incorporates belief states and observation functions while maintaining the key benefits of Active Markov Games for modeling and influencing learning dynamics.
-
-In partially observable settings, policy gradient methods require careful adaptation to handle the unavailability of the true state.
-Theoretical formulations, as established by Meuleau et al.
-\cite{meuleau1999pomdp}, extend the policy gradient theorem by conditioning policies on belief states rather than environmental states, resulting in $\nabla_{\theta^i} J(\theta^i) = \mathbb{E}_{s,b} \left[ \nabla_{\theta^i} \log \pi^i(a^i|b^i; \theta^i) Q^{\pi}(s,b^i,a^i) \right]$.
-However, this theoretical construction presents a practical challenge: agents don't have access to the true state distribution needed to compute this expectation.
-Practical implementations resolve this tension through multiple approaches: history-based methods condition policies on observation histories $h_t$ rather than belief states \cite{aberdeen2002pg}; recurrent network formulations implicitly encode history using recurrent architectures \cite{hausknecht2015drqn}; and belief-explicit methods maintain and update a belief distribution while estimating values only from observable quantities \cite{peng2022belief}.
-These approaches share a common principle of using trajectory sampling to estimate gradients without requiring knowledge of the true state or transition dynamics.
-In multi-agent settings with partial observability, the challenge compounds as agents must reason about others' belief states and learning dynamics, requiring sophisticated inference mechanisms to estimate other agents' policies and their evolution over time.
-For Partially Observable Active Markov Games, policy gradients can be formulated to account for the impact of current actions on both the future environmental states and the future policies of other agents, all while operating from belief states rather than full state observations.
-
-\chapter{Proofs Regarding Average Returns}
-
-This section provides the mathematical foundations and detailed proofs for the
-key theoretical results in our Partially Observable Active Markov Game framework
-with average return objectives. We establish the Markov properties of belief transitions
-and joint processes, prove the existence and uniqueness of stochastically stable
-distributions, and derive the policy gradient theorem for average return optimization.
-
-\section{Markov Property of the Joint Process}
-\label{appendix:stochasticallystable}We first establish the Markov properties of
-belief state transitions and the joint process comprising states, belief states,
-and policy parameters. These properties form the foundation for our convergence analysis.
-
-\begin{lemma}[Markov Property of Belief Transitions]
-    The sequence of belief states $\{b_{t}^{i}\}_{t \geq 0}$ for each agent $i$ forms
-    a Markov process under a fixed policy $\pi$, meaning that the distribution of
-    $b_{t+1}^{i}$ depends only on $b_{t}^{i}$, $a_{t}^{i}$, and $o_{t+1}^{i}$, and
-    not on earlier beliefs, actions, or observations.
-\end{lemma}
-
-\begin{proof}
-    By definition, the belief state $b_{t}^{i}$ at time $t$ incorporates all
-    relevant information from the history of observations and actions up to time
-    $t$. For Bayesian agents, given $b_{t}^{i}$, action $a_{t}^{i}$, and
-    observation $o_{t+1}^{i}$, the belief update equation uniquely determines $b_{t+1}
-            ^{i}$ through the rule:
-    \begin{align}
-        b^i_{t+1}(s') = \frac{O^i(o^i_{t+1}|s') \int_{s \in S} T(s'|s, \boldsymbol{a}_t) b^i_t(s) ds}{\int_{s'' \in S} O^i(o^i_{t+1}|s'') \int_{s \in S} T(s''|s, \boldsymbol{a}_t) b^i_t(s) ds ds''}
-    \end{align}
-
-    where $O_{i}(o_{t+1}^{i}|s')$ represents the probability of agent $i$ observing
-    $o_{t+1}^{i}$ in state $s'$. This update depends only on $b_{t}^{i}$, $a_{t}^{i}$,
-    and $o_{t+1}^{i}$, and not on the sequence of beliefs, actions, and observations
-    that led to $b_{t}^{i}$. Therefore, the belief state transition satisfies the Markov
-    property.
-\end{proof}
-
-\begin{remark}[Transformer-Based Belief Representation]
-    In practice, transformer architectures can be used to represent and
-    update belief states. In such cases, the belief state is updated
-    through an attention-based mechanism of the form:
-    \begin{equation}
-        b_{t+1}^{i} = f_{{Transformer}}(b_{t}^{i}, o_{t+1}^{i}),
-    \end{equation}
-
-    that is parameterized by $\theta_{Transformer}^{i}$ and processes the latest
-    observation and previous belief state through self-attention layers, satisfying the Markov property
-    while capturing complex dependencies between observations and beliefs.
-\end{remark}
-Next, we establish the Markov property of the joint process.
-\begin{lemma}[Markov Property of Joint Process]
-    The joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ forms
-    a Markov process under periodic policy updates, meaning that the distribution
-    of $(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})$ depends only
-    on $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on earlier
-    states.
-\end{lemma}
-\begin{proof}
-    The state transitions are by definition only dependent on current state and current
-    actions. The remaining parts can be analyzed as follows:
-
-    \textbf{1. Belief
-        state transition:} As established earlier, $\boldsymbol{b}_{t+1}$ depends only
-    on $\boldsymbol{b}_{t}$, $\boldsymbol{a}_{t}$, and $\boldsymbol{o}_{t+1}$. Since
-    actions $\boldsymbol{a}_{t}$ are drawn from policies $\pi(a_{t}^{i}|b_{t}^{i};
-        \theta_{t}^{i})$ that depend only on $b_{t}^{i}$ and $\theta_{t}^{i}$ for each
-    agent $i$, and observations $\boldsymbol{o}_{t+1}$ depend stochastically on
-    the resulting state, the distribution of $\boldsymbol{b}_{t+1}$ depends only on
-    $\boldsymbol{b}_{t}$ and $\boldsymbol{\theta}_{t}$.
-
-    \textbf{2. Policy parameter
-        update:} At every time step $t$, policy parameters are updated according to $U(
-        \boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t})$.
-    Under the Markovian policy update assumption, the update depends only on $\theta
-        _{t}$ and current trajectory $\tau_{t}$, which are functions of $s_{t}$, $\boldsymbol
-        {b}_{t}$ and $\boldsymbol{\theta}_{t}$.Therefore, the joint transition
-    probability
-    $\mathbb{P}((s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})|(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t}))$
-    depends only on the current state
-    $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ and not on the history
-    of states, establishing the Markov property.
-\end{proof}
-\section{Convergence}
-Having established the Markov properties, we now analyze the convergence
-behavior of the joint process to a unique stochastically stable distribution. This
-convergence result is crucial for developing optimization objectives in our framework.
-\begin{theorem}[Stochastically Stable Distribution]
-    Under assumptions (1) and (2), as $\epsilon \to 0$, the perturbed joint processes
-    defined by $\epsilon$-perturbed policy update functions converge to the unique
-    stochastically stable distribution $\mu^{*}$ of the unperturbed joint process $(
-        s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$.
-\end{theorem}
-
-\begin{proof}
-    We establish the convergence to the unique stochastically stable distribution by
-    showing that a perturbed Markov process of a partially observable active Markov
-    game is regular. First, let us introduce a small perturbation to the policy update
-    functions:
-    \begin{align}
-        U^{\epsilon}_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) = (1 - \epsilon) U_{i}(\theta^{i}_{t+1}|\theta^{i}_{t}, \tau^{i}_{t}) + \epsilon \eta_{i}(\theta^{i}_{t+1})
-    \end{align}
-
-    where $\eta_{i}$ is a baseline distribution over $\Theta_{i}$ with full support,
-    and $\epsilon > 0$ is a small constant. This perturbation ensures that from any
-    policy parameter configuration $\boldsymbol{\theta}_{t}$, there is a positive
-    probability of transitioning to any other configuration
-    $\boldsymbol{\theta}_{t+1}$. The perturbed joint process $(s_{t}, \boldsymbol{b}
-        _{t}, \boldsymbol{\theta}_{t})^{\epsilon}$ evolves according to the transition
-    probability:
-    \begin{align}
-        \mathbb{P}(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}|s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) & = \sum_{\boldsymbol{a}_t \in A}\boldsymbol{\pi}(\boldsymbol{a}_{t}|\boldsymbol{b}_{t}; \boldsymbol{\theta}_{t}) \times T(s_{t+1}|s_{t}, \boldsymbol{a}_{t})                                     \\
-                                                                                                                                & \times \sum_{\boldsymbol{o}_{t+1} \in O}\boldsymbol{O}(\boldsymbol{o}_{t+1}|s_{t+1}) \times \boldsymbol{U}^{\epsilon}(\boldsymbol{\theta}_{t+1}|\boldsymbol{\theta}_{t}, \boldsymbol{\tau}_{t}) \\
-                                                                                                                                & \times \mathbb{I}(\boldsymbol{b}_{t+1}= \text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol{o}_{t+1}))
-    \end{align}
-
-    where $\boldsymbol{\tau}_{t} = \{\boldsymbol{o}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {r}_{t}, \boldsymbol{o}_{t+1}\}$ is the joint trajectory,
-    $\boldsymbol{r}_{t} = \{R^{i}(s_{t}, \boldsymbol{a}_{t})\}_{i \in I}$ is the
-    vector of rewards, and $\text{update}(\boldsymbol{b}_{t}, \boldsymbol{a}_{t}, \boldsymbol
-        {o}_{t+1})$ represents the belief update function for all agents. Suppose, for
-    contradiction, that the perturbed Markov process is irregular, meaning it has multiple
-    recurrent classes. Let $C_{1}$ and $C_{2}$ be two distinct recurrent classes
-    of the joint process. We will show that there must exist a path with positive probability
-    from any state in $C_{1}$ to any state in $C_{2}$, contradicting the
-    assumption that they are distinct recurrent classes. Consider any $(s^{1}, \boldsymbol
-        {b}^{1}, \boldsymbol{\theta}^{1}) \in C_{1}$ and $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol
-        {\theta}^{2}) \in C_{2}$. We construct a path from the first state to the
-    second as follows:
-
-    \textbf{1. Policy Parameter Transition:} Due to the
-    $\epsilon$-perturbation in update functions, there is a positive probability of
-    directly transitioning from $\boldsymbol{\theta}_{1}$ to any $\boldsymbol{\theta}
-        ' \in \Theta$ in a single step, regardless of the trajectory. Specifically:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{\theta}_{t+1}=\boldsymbol{\theta}'|\boldsymbol{\theta}_{t}=\boldsymbol{\theta}_{1}, \boldsymbol{\tau}_{t}) \geq \prod_{i \in I}\epsilon \cdot \eta_{i}(\theta'^{i}) > 0
-    \end{align}
-
-    Thus, there is a positive probability path from $\boldsymbol{\theta}_{1}$ to
-    $\boldsymbol{\theta}_{2}$.
-
-    \textbf{2. State Transition:} By the communicating
-    state assumption, for any two states $s_{1}, s_{2} \in S$, there exists a
-    sequence of joint actions $\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{k}$
-    such that:
-    \begin{align}
-        \mathbb{P}(s_{t+k}=s_{2}|s_{t}=s_{1}, \boldsymbol{a}_{t}=\boldsymbol{a}_{1}, \ldots, \boldsymbol{a}_{t+k-1}=\boldsymbol{a}_{k}) > 0
-    \end{align}
-
-    Given the relationship between policies and actions, this sequence of actions has
-    positive probability under any policy parameters $\boldsymbol{\theta}$ and corresponding
-    belief states $\boldsymbol{b}$ such that $\pi^{i}(a^{i}|b^{i}; \theta^{i}) > 0$
-    for all required actions.
-
-    \textbf{3. Belief State Transition:} By the communicating belief-state
-    assumption, for any two belief states $\boldsymbol{b}_{1}, \boldsymbol{b}_{2} \in
-        B$, there exists a sequence of observations
-    $\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{m}$ such that:
-    \begin{align}
-        \mathbb{P}(\boldsymbol{b}_{t+m}=\boldsymbol{b}_{2}|\boldsymbol{b}_{t}=\boldsymbol{b}_{1}, \boldsymbol{o}_{t+1}=\boldsymbol{o}_{1}, \ldots, \boldsymbol{o}_{t+m}=\boldsymbol{o}_{m}) > 0
-    \end{align}
-
-    Since observations depend on states, which can be influenced through actions,
-    and actions are determined by policies, there is a positive probability path from
-    $\boldsymbol{b}_{1}$ to $\boldsymbol{b}_{2}$ under appropriate state transitions
-    and policy parameters. Combining these three components, we can construct a path
-    with positive probability from $(s^{1}, \boldsymbol{b}^{1}, \boldsymbol{\theta}
-        ^{1})$ to $(s^{2}, \boldsymbol{b}^{2}, \boldsymbol{\theta}^{2})$. This
-    contradicts the assumption that $C_{1}$ and $C_{2}$ are distinct recurrent
-    classes of the perturbed joint process. Since we have shown that the perturbed
-    joint process has only one recurrent class, it is a regular Markov process. Following
-    \citep{kim2022influencing,wicks2012algorithmcomputingstochasticallystable}, a regular Markov
-    process on a finite state space possesses a unique stationary distribution
-    $\mu^{\epsilon}$ to which it converges regardless of the initial state. Moreover,
-    as $\epsilon \to 0$, the sequence of stationary distributions $\mu^{\epsilon}$
-    converges to a limit $\mu^{*}$, which is the unique stochastically stable
-    distribution of the original, unperturbed process. Therefore, under the given conditions,
-    the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})$ in a
-    partially observable active Markov game possesses a unique stochastically
-    stable distribution $\mu^{*}$.
-\end{proof}
-\section{Policy Gradient Theorem}
-Having established the convergence to a unique stochastically stable distribution,
-we now derive the policy gradient theorem for optimization in our framework. This
-theorem provides the mathematical foundation for gradient-based algorithms to maximize
-the average return objective.
-\label{appendix:avg_gradient}
-\begin{theorem}[Partially Observable Active Average Reward Policy Gradient
-        Theorem]
-    The gradient of the active average reward objective
-    with respect to agent $i$'s policy parameters $\theta^{i}$ in a partially observable
-    setting is:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    with $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$ representing
-    the belief update function.
-\end{theorem}
-
-\begin{proof}
-    We first define the average reward objective in the partially observable setting:
-    \begin{align}
-        \max_{\theta^i}\rho^{i}_{\theta^i}(\boldsymbol{b}, \boldsymbol{\theta}) & := \max_{\theta^i}\lim_{T \to \infty}\mathbb{E}\left[ \frac{1}{T}\sum_{t=0}^{T} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| \begin{array}{c}\boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right] \\
-                                                                                & = \max_{\theta^i}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}b^{i}(s) \mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{\boldsymbol{a}}\boldsymbol{\pi}(\boldsymbol{a}|\boldsymbol{b}; \boldsymbol{\theta}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    where $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the stationary
-    distribution of the joint process $(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}
-        _{t})$ under agent $i$'s policy parameterized by $\theta^{i}$. The
-    differential value function $v^{i}_{\theta^i}$ represents the expected total
-    difference between the accumulated rewards from state $s$, belief states $\boldsymbol
-        {b}$, and policy parameters $\boldsymbol{\theta}$, and the average reward $\rho
-        ^{i}_{\theta^i}$:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \lim_{T \to \infty}\mathbb{E}\left[ \sum_{t=0}^{T} \left(R^{i}(s_{t}, \boldsymbol{a}_{t}) - \rho^{i}_{\theta^i}\right) \bigg| \begin{array}{c}s_0=s, \boldsymbol{b}_0= \boldsymbol{b}, \boldsymbol{\theta}_0= \boldsymbol{\theta}, \\ \boldsymbol{a}_{0:T} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b}_{0:T}; \boldsymbol{\theta}_{0:T}), s_{t+1} \sim T(\cdot|s_t, \boldsymbol{a}_t), \\ \boldsymbol{o}_{t+1} \sim \boldsymbol{O}(\cdot|s_{t+1}), \boldsymbol{\theta}_{t+1} \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}_t, \boldsymbol{\tau}_t)\end{array} \right]
-    \end{align}
-
-    Following the Bellman equation derivation principles, we can express
-    $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ recursively:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}_{\boldsymbol{a} \sim \boldsymbol{\pi}(\cdot|\boldsymbol{b};\boldsymbol{\theta}), s' \sim T(\cdot|s,\boldsymbol{a}), \boldsymbol{o}' \sim \boldsymbol{O}(\cdot|s'), \boldsymbol{\theta}' \sim \boldsymbol{U}(\cdot|\boldsymbol{\theta}, \boldsymbol{\tau})}\left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})                                                                                                                              \\
-                                                                 & \quad \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-    represents the belief update function that updates the belief state based on
-    the current belief, action, and new observation. We now define the action-value
-    function $q^{i}_{\theta^i}$ for the partially observable setting:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) = \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right]
-    \end{align}
-
-    Using this definition, we can rewrite the differential value function as:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    To derive the policy gradient, we begin by computing the gradient of the differential
-    value function with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right] \\
-                                                                                  & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) +              \\
-                                                                                  & \quad \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    We expand the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\left[ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                                                                  & \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left[ R^{i}(s, \boldsymbol{a}) - \rho^{i}_{\theta^i}+ v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right] \right]                                                                       \\
-                                                                                                  & = -\nabla_{\theta^i}\rho^{i}_{\theta^i}+ \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting back into the original expression, we get:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                                                                  & \quad - \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}\rho^{i}_{\theta^i}                                                                            \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Rearranging terms:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                             \\
-                                             & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                       \\
-                                             & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-                                             & \quad - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we define the transition operator that maps the expectation of a function
-    from one time step to the next:
-    \begin{align}
-        \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                 \\
-                                                       & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    We can rewrite our expression as:
-    \begin{align}
-        \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) + \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Now, we take the expectation with respect to the stationary distribution
-    $\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})                                                            \\
-                                                                                                                                                 & \quad + \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi(\nabla_{\theta^i}v^{i}_{\theta^i})(s, \boldsymbol{b}, \boldsymbol{\theta}) - \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    By the definition of the stationary distribution, we have:
-    \begin{align}
-        \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \Psi f(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) f(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore, the second and third terms in our expression cancel out, giving the
-    final policy gradient theorem:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi}(\theta^{i}) := \nabla_{\theta^i}\rho^{i}_{\theta^i} & = \sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}\mu_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-\end{proof}
-
-\chapter{Proofs Regarding Discounted Returns}
-\label{appendix:discounted_proofs} We establish the Partially Observable Active Discounted
-Return Policy Gradient Theorem through a sequence of lemmas that build the necessary
-mathematical foundation.
-\section{Transition Operator and Its Adjoint}
-To establish a rigorous framework for analyzing discounted returns in Partially
-Observable Active Markov Games, we need to formalize how value functions evolve over
-time and how probability distributions propagate through the system. This dual
-perspective is captured by two fundamental operators: the transition operator and
-its adjoint.
-
-\subsection{Definitions and Duality}
-
-We begin by defining the inner product between functions and measures, which forms
-the foundation for the duality relationship between our operators.
-
-\begin{definition}[Inner Product between Functions and Measures]
-    For a bounded measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ and a finite measure $\mu \in \mathcal{M}(S \times \boldsymbol
-        {B}\times \boldsymbol{\Theta})$, their inner product is defined as the
-    Lebesgue integral:
-    \begin{equation}
-        \langle f, \mu \rangle = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}
-        f(s, \boldsymbol{b}, \boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol
-        {\theta})
-    \end{equation}
-\end{definition}
-
-This inner product captures the expected value of function $f$ with respect to
-measure $\mu$, allowing us to express value functions as expectations with respect
-to appropriate measures.
-
-\begin{definition}[Transition Operator and Its Adjoint]
-    \hfill
-    \begin{enumerate}
-        \item The \textbf{transition operator}
-              $\Psi: \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{B}
-                  (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              maps a bounded measurable function to its expected value after one
-              transition:
-              \begin{align}
-                  (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                               \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-              \end{align}
-
-              where $\text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}')$
-              represents the belief update function.
-
-        \item The \textbf{adjoint operator}
-              $\Psi^{*}: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \rightarrow
-                  \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-              is defined on the space of finite measures such that:
-              \begin{equation}
-                  \langle \Psi f, \mu \rangle = \langle f, \Psi^{*} \mu \rangle
-              \end{equation}
-
-              for all
-              $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ and
-              $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$.
-    \end{enumerate}
-\end{definition}
-
-Intuitively, $\Psi$ describes how function expectations evolve forward in time,
-meanwhile, $\Psi^{*}$ describes how probability distributions evolve in time,
-capturing the propagation of visitation probabilities through the system. The duality
-relationship ensures that expected values can be computed either by applying $\Psi$
-to functions or $\Psi^{*}$ to measures.
-
-\subsection{Properties of the Operators}
-
-These operators possess several important properties that facilitate our
-analysis of discounted returns:
-
-\begin{lemma}[Properties of the Transition Operator and Its Adjoint]
-    The transition operator $\Psi$ and its adjoint $\Psi^{*}$ satisfy the following
-    properties:
-
-    \begin{enumerate}
-        \item \textbf{Linearity:}
-              \begin{itemize}
-                  \item For the operator: For any functions
-                        $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi(\alpha f + \beta g) = \alpha \Psi f + \beta \Psi g
-                        \end{align}
-
-                  \item For the adjoint: For any measures
-                        $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}
-                            )$
-                        and constants $\alpha, \beta \in \mathbb{R}$:
-                        \begin{align}
-                            \Psi^{*}(\alpha\mu + \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Positivity Preservation:}
-              \begin{itemize}
-                  \item For the operator: If $f \geq 0$, then $\Psi f \geq 0$.
-
-                  \item For the adjoint: If $\mu$ is a non-negative measure, then $\Psi^{*}
-                            \mu$ is also non-negative.
-              \end{itemize}
-
-        \item \textbf{Preservation of Total Measure:}
-              \begin{itemize}
-                  \item For the operator: The operator preserves the constant function
-                        $\mathbf{1}$:
-                        \begin{align}
-                            \Psi \mathbf{1}= \mathbf{1}
-                        \end{align}
-
-                        where $\mathbf{1}$ represents the function that equals 1 everywhere.
-
-                  \item For the adjoint: For any measure
-                        $\mu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-                        \begin{align}
-                            (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-                        \end{align}
-              \end{itemize}
-
-        \item \textbf{Bound Preservation:} For any bounded function $f$, $\Psi f$ is
-              bounded with:
-              \begin{align}
-                  \|\Psi f\|_{\infty}\leq \|f\|_{\infty}
-              \end{align}
-
-              where $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol
-                  {b},\boldsymbol{\theta})|$ is the supremum norm.
-
-        \item \textbf{Explicit Form of the Adjoint:} For any measurable set
-              $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-              \begin{align}
-                  (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i})                                                                                                                                                                                     \\
-                                   & \quad \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-              \end{align}
-
-              where $\mathbf{1}_{A}$ is the indicator function for set $A$.
-    \end{enumerate}
-\end{lemma}
-
-\begin{proof}
-    We prove each property in turn:
-
-    \textbf{1. Linearity:}
-
-    For the operator: For any $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we have:
-    \begin{align}
-         & \Psi(\alpha f + \beta g)(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                            \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')                \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) [\alpha f + \beta g](s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \\
-         & = \alpha \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')         \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & \quad + \beta \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')    \\
-         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) g(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')                    \\
-         & = \alpha (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) + \beta (\Psi g)(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For the adjoint: For any measurable function
-    $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \langle f, \Psi^{*}(\alpha\mu + \beta\nu) \rangle & = \langle \Psi f, \alpha\mu + \beta\nu \rangle                               \\
-                                                          & = \alpha\langle \Psi f, \mu \rangle + \beta\langle \Psi f, \nu \rangle       \\
-                                                          & = \alpha\langle f, \Psi^{*}\mu \rangle + \beta\langle f, \Psi^{*}\nu \rangle \\
-                                                          & = \langle f, \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have $\Psi^{*}(\alpha\mu +
-        \beta\nu) = \alpha\Psi^{*}\mu + \beta\Psi^{*}\nu$ by the uniqueness of the representing
-    measure.
-
-    \textbf{2. Positivity Preservation:}
-
-    For the operator: If $f \geq 0$, then for any $(s, \boldsymbol{b}, \boldsymbol{\theta}
-        )$:
-    \begin{align}
-        (\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                         & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Since $f \geq 0$ and all probability distributions $\pi^{i}$, $\pi^{\neg i}$, $T$,
-    $\boldsymbol{O}$, and $\boldsymbol{U}$ are non-negative, the entire sum
-    consists of non-negative terms, making $(\Psi f)(s, \boldsymbol{b}, \boldsymbol
-        {\theta}) \geq 0$.
-
-    For the adjoint: If $\mu$ is non-negative, then for any non-negative measurable
-    function $f \geq 0$:
-    \begin{align}
-        \langle f, \Psi^{*}\mu \rangle = \langle \Psi f, \mu \rangle \geq 0
-    \end{align}
-
-    where the inequality follows from the positivity preservation of $\Psi$ and the
-    fact that $\mu$ is non-negative. Since this holds for all non-negative
-    functions $f$, $\Psi^{*}\mu$ must be a non-negative measure.
-
-    \textbf{3. Preservation of Total Measure:}
-
-    For the operator: Let $\mathbf{1}$ be the constant function that equals 1
-    everywhere. Then:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \cdot 1
-    \end{align}
-
-    Since each probability distribution sums to 1, applying them sequentially
-    yields:
-    \begin{align}
-        (\Psi \mathbf{1})(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \cdot 1 \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \cdot 1                                                          \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \cdot 1                                                                                           \\
-                                                                  & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \cdot 1 = 1
-    \end{align}
-
-    For the adjoint: Setting $f = \mathbf{1}$ in the adjoint relationship:
-    \begin{align}
-        \langle \mathbf{1}, \Psi^{*}\mu \rangle & = \langle \Psi \mathbf{1}, \mu \rangle = \langle \mathbf{1}, \mu \rangle
-    \end{align}
-
-    where we used the unit preservation property of $\Psi$. This gives:
-    \begin{align}
-        (\Psi^{*}\mu)(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) = \mu(S \times \boldsymbol{B}\times \boldsymbol{\Theta})
-    \end{align}
-
-    \textbf{4. Bound Preservation:}
-
-    For any bounded function $f$ with
-    $\|f\|_{\infty}= \sup_{s,\boldsymbol{b},\boldsymbol{\theta}}|f(s,\boldsymbol{b}
-        ,\boldsymbol{\theta})|$:
-    \begin{align}
-        |(\Psi f)(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \right.
-\\
-                                                           & \quad \left.
-\sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|       \\
-                                                           & \leq \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s')               \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \left|f(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \right|        \\
-                                                           & \leq \|f\|_{\infty}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \\
-                                                           & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) = \|f\|_{\infty}\cdot 1 = \|f\|_{\infty}
-    \end{align}
-
-    Taking the supremum over all $(s, \boldsymbol{b}, \boldsymbol{\theta})$, we get
-    $\|\Psi f\|_{\infty}\leq \|f\|_{\infty}$.
-
-    \textbf{5. Explicit Form of the Adjoint:}
-
-    For any measurable set $A \subset S \times \boldsymbol{B}\times \boldsymbol{\Theta}$:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \langle \mathbf{1}_{A}, \Psi^{*}\mu \rangle = \langle \Psi\mathbf{1}_{A}, \mu \rangle
-    \end{align}
-
-    Expanding $\Psi\mathbf{1}_{A}$ using the definition of the transition operator:
-    \begin{align}
-        (\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                            \\
-                                                                   & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Substituting this back and using the definition of inner product:
-    \begin{align}
-        (\Psi^{*}\mu)(A) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi\mathbf{1}_{A})(s,\boldsymbol{b},\boldsymbol{\theta}) \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})                                                                                                                                                          \\
-                         & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a})                                                                                                                   \\
-                         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \mathbf{1}_{A}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \, d\mu(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}
-
-\subsection{Contraction and Propagation}
-
-The properties established above lead to two crucial results: the contraction
-property of the discounted transition operator and the propagation of
-distributions through the adjoint.
-
-\begin{lemma}[Contraction Mapping Property]
-    For any discount factor $\gamma \in [0,1)$, the operator $\gamma \Psi$ is a
-    contraction mapping on the Banach space of bounded functions on
-    $S \times \boldsymbol{B}\times \boldsymbol{\Theta}$ equipped with the supremum
-    norm. Specifically, for any two functions
-    $f, g \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty}\leq \gamma\|f - g\|_{\infty}
-    \end{align}
-\end{lemma}
-
-\begin{proof}
-    Using the linearity of $\Psi$ and its bound preservation property:
-    \begin{align}
-        \|\gamma \Psi f - \gamma \Psi g\|_{\infty} & = \gamma\|\Psi(f - g)\|_{\infty} \\
-                                                   & \leq \gamma\|f - g\|_{\infty}
-    \end{align}
-
-    Since $\gamma < 1$, $\gamma \Psi$ is a contraction mapping with contraction
-    factor $\gamma$.
-\end{proof}
-
-This contraction property leads directly to the invertibility of
-$I - \gamma\Psi$, a result that is fundamental for characterizing value functions
-in discounted settings.
-
-\begin{lemma}[Invertibility of $I - \gamma \Psi$]
-    For any discount factor $\gamma \in [0,1)$, the operator $I - \gamma \Psi$ is
-    invertible, and its inverse can be represented as a Neumann series:
-    \begin{align}
-        (I - \gamma \Psi)^{-1}= \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    which converges absolutely in the operator norm.
-\end{lemma}
-
-\begin{proof}
-    By the Banach fixed-point theorem, if $T$ is a contraction mapping on a Banach
-    space, then $I - T$ is invertible, with inverse given by the Neumann series
-    $\sum_{k=0}^{\infty}T^{k}$. Since $\gamma \Psi$ is a contraction mapping, we
-    have:
-
-    \begin{align}
-        (I - \gamma \Psi)^{-1} & = \sum_{t=0}^{\infty}(\gamma \Psi)^{t} = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}
-    \end{align}
-
-    The absolute convergence follows from:
-    \begin{align}
-        \left\|\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\right\|_{\infty} & \leq \sum_{t=0}^{\infty}\gamma^{t} \|\Psi^{t}\|_{\infty}\leq \sum_{t=0}^{\infty}\gamma^{t} = \frac{1}{1-\gamma}< \infty
-    \end{align}
-
-    where we use the bound preservation property to establish that $\|\Psi^{t}\|_{\infty}
-        \leq 1$ for all $t$.
-\end{proof}
-
-Finally, we establish how distributions evolve in the system through the adjoint
-operator, formalizing the propagation of probability measures.
-
-\begin{lemma}[Distribution Propagation]
-    If $\mu_{t}$ represents the distribution of the joint process $(s_{t}, \boldsymbol
-        {b}_{t}, \boldsymbol{\theta}_{t})$ at time $t$, then the distribution at time
-    $t+1$ is given by $\mu_{t+1}= \Psi^{*}\mu_{t}$.
-\end{lemma}
-
-\begin{proof}
-    For any measurable function $f \in \mathcal{B}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$:
-    \begin{align}
-        \langle f, \mu_{t+1}\rangle & = \mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1})]                                                                     \\
-                                    & = \mathbb{E}[\mathbb{E}[f(s_{t+1}, \boldsymbol{b}_{t+1}, \boldsymbol{\theta}_{t+1}) \mid s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}]] \\
-                                    & = \mathbb{E}[(\Psi f)(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t})]                                                                    \\
-                                    & = \langle \Psi f, \mu_{t} \rangle = \langle f, \Psi^{*}\mu_{t} \rangle
-    \end{align}
-
-    Since this holds for any measurable function $f$, we have
-    $\mu_{t+1}= \Psi^{*}\mu_{t}$ by the uniqueness of the representing measure.
-\end{proof}
-
-The concepts introduced in this section—the transition operator, its adjoint, and
-their properties—provide the mathematical foundation for analyzing discounted returns
-in Partially Observable Active Markov Games. The transition operator $\Psi$
-captures how function expectations evolve forward in time, while its adjoint $\Psi
-    ^{*}$ describes how probability distributions propagate forward in time. This
-duality is fundamental to establishing the connection between value-based and
-distribution-based perspectives in reinforcement learning.
-
-In the next section, we will use these tools to formulate Bellman equations and derive
-policy gradients for maximizing discounted returns in this complex multi-agent setting.
-\section{Bellman Equations and Value Functions}
-In this section, we establish the fundamental recursive relationships that characterize
-the discounted value functions in Partially Observable Active Markov Games.
-These relationships form the basis for our policy gradient derivation and
-practical algorithms for optimizing agent behavior. We begin by confirming the well-definedness
-of value functions, then establish the Bellman equations, and finally derive the
-gradient expressions necessary for policy optimization.
-\subsection{Well-Definedness of Value Functions}
-Before deriving recursive relationships, we first establish that the value functions
-are well-defined mathematical objects under our assumptions of bounded rewards and
-discount factors less than 1.
-\begin{lemma}[Well-Defined Value Functions]
-    Under the assumptions of bounded rewards and $\gamma < 1$, the discounted
-    value functions $v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})$ and
-    action-value functions
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ are
-    well-defined and finite for all states, belief states, policy parameters, and actions.
-\end{lemma}
-\begin{proof}
-    Assuming rewards are bounded such that $|R^{i}(s, \boldsymbol{a})| \leq R_{\max}$
-    for all $s \in S$ and $\boldsymbol{a}\in A$, we have:
-    \begin{align}
-        |v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta})| & = \left| \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \right| \\
-                                                                   & \leq \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} |R^{i}(s_{t}, \boldsymbol{a}_{t})| \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]           \\
-                                                                   & \leq R_{\max}\sum_{t=0}^{\infty}\gamma^{t} = \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Similarly, for the action-value function:
-    \begin{align}
-        |q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})| & = \left| R^{i}(s, \boldsymbol{a}) + \gamma \mathbb{E}[v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')] \right| \\
-                                                                                   & \leq |R^{i}(s, \boldsymbol{a})| + \gamma \mathbb{E}[|v^{i}_{\theta^i}(s', \boldsymbol{b}', \boldsymbol{\theta}')|]         \\
-                                                                                   & \leq R_{\max}+ \gamma \frac{R_{\max}}{1-\gamma}= \frac{R_{\max}}{1-\gamma}< \infty
-    \end{align}
-
-    Thus, both value functions are well-defined and bounded.
-\end{proof}This lemma ensures that our subsequent derivations involving value
-functions are mathematically sound. The boundedness property is particularly important
-when we consider expectations and derivatives of these functions.
-\subsection{Bellman Equations for Discounted Value Functions}
-Next, we establish the recursive relationships between value functions, which
-are fundamental to dynamic programming approaches.
-\begin{lemma}[Bellman Equation for Discounted Value Functions]
-    In a Partially Observable Active Markov Game, the discounted value function
-    $v^{i}_{\theta^i}$ satisfies the Bellman equation:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where the action-value function $q^{i}_{\theta^i}$ is defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{lemma}
-\begin{proof}
-    By definition, the discounted value function is:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    We can decompose this into the immediate reward and the future discounted
-    returns:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) + \gamma \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \\
-                                                                 & = \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] \nonumber                                                                \\
-                                                                 & \quad + \gamma \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]
-    \end{align}
-
-    For the first term, we have:
-    \begin{align}
-        \mathbb{E}\left[ R^{i}(s_{0}, \boldsymbol{a}_{0}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right] & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    For the second term, by the law of total expectation:
-    \begin{align}
-         & \mathbb{E}\left[ \sum_{t=1}^{\infty}\gamma^{t-1}R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}=s, \boldsymbol{b}_{0}=\boldsymbol{b}, \boldsymbol{\theta}_{0}=\boldsymbol{\theta}, \pi \right]                                                                                     \\
-         & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \sum_{s'}T(s'|s, \boldsymbol{a}) \nonumber                                                                                                                    \\
-         & \quad \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Combining these two terms and factoring out common terms:
-    \begin{align}
-        v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \Bigg[ R^{i}(s, \boldsymbol{a}) \nonumber                                                                   \\
-                                                                 & \quad + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                             \\
-                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg] \\
-                                                                 & = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where we define the action-value function $q^{i}_{\theta^i}$ as specified.
-\end{proof}The Bellman equation provides a recursive characterization of the
-value function that forms the basis for dynamic programming algorithms. This equation
-captures how current actions influence both immediate rewards and future value through
-their effects on the environment state, belief states, and policy parameters of other
-agents. The key distinction from standard Bellman equations is the inclusion of
-belief updates and policy parameter dynamics, which reflects the complex dependencies
-in partially observable multi-agent settings.
-\subsection{Policy Gradient with Respect to Value Function}
-Having established the recursive relationship for value functions, we now derive
-how the value function gradient depends on policy parameters, which is essential
-for policy optimization.
-\begin{lemma}[Policy Gradient with Respect to Value Function]
-    The gradient of the value function with respect to policy parameters $\theta^{i}$
-    can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-
-    where $\Psi$ is the transition operator defined in the previous section.
-\end{lemma}
-\begin{proof}
-    Taking the gradient of the Bellman equation with respect to $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \nabla_{\theta^i}\left[ \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \right]
-    \end{align}
-
-    Applying the product rule:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    For the gradient of the action-value function:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \nabla_{\theta^i}\Bigg[ R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}') \Bigg]
-    \end{align}
-
-    Since $R^{i}(s, \boldsymbol{a})$, $T(s'|s, \boldsymbol{a})$, $\boldsymbol{O}(\boldsymbol
-        {o}'|s')$, and
-    $\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau})$
-    do not depend directly on $\theta^{i}$:
-    \begin{align}
-        \nabla_{\theta^i}q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                                                             \\
-                                                                                                  & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) \nabla_{\theta^i}v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-
-    Using the transition operator $\Psi$, we can rewrite:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) \nonumber \\
-                                                                                  & \quad + \gamma \Psi[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Rearranging:
-    \begin{align}
-        (I - \gamma \Psi)[\nabla_{\theta^i}v^{i}_{\theta^i}](s, \boldsymbol{b}, \boldsymbol{\theta}) & = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                                              \\
-                                                                                                     & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    By the lemma on the invertibility of $(I - \gamma \Psi)$, we have:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg] \\
-                                                                                  & = \sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}\Bigg[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber                                        \\
-                                                                                  & \quad \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\Bigg]
-    \end{align}
-\end{proof}This lemma expresses the value function gradient in terms of an
-infinite sum of expected Q-values weighted by policy gradients and propagated
-through the transition operator. The operator $(I - \gamma \Psi)^{-1}$ captures how
-immediate changes in policy parameters propagate through future timesteps. This
-form of the gradient is central to our discounted policy gradient theorem, which
-we will develop in the next section. The inverse operator can be represented as
-a Neumann series $\sum_{t=0}^{\infty}\gamma^{t} \Psi^{t}$, which has a natural interpretation
-as the accumulated effect of policy changes over an infinite horizon, weighted
-by the discount factor.
-\section{Discounted Visitation Measure}
-The infinite sum formulation derived in the previous sections, while
-mathematically sound, is not directly amenable to practical computation. In this
-section, we reformulate these expressions in terms of a probability distribution,
-which allows for more efficient estimation through sampling-based approaches. This
-reformulation is central to our policy gradient theorem for discounted returns.
-\subsection{Definition and Properties}
-\begin{definition}[Discounted Visitation Measure]
-    For a Markov process governed by a transition operator $\Psi$ and its adjoint $\Psi
-        ^{*}$, with an initial distribution $\mu_{0}$ over the joint state-belief-policy
-    space, the discounted visitation measure $d^{\pi}_{\mu_0}$ is defined as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}:= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}
-    \end{equation}
-
-    where $\mu_{t}$ is the distribution at time $t$ when starting from $\mu_{0}$,
-    and $\gamma \in [0, 1)$ is the discount factor.
-\end{definition}This measure represents the expected discounted frequency with which
-different states, belief states, and policy parameters are visited when following
-policy $\pi$ starting from the initial distribution $\mu_{0}$. The normalization
-factor $(1-\gamma)$ ensures that $d^{\pi}_{\mu_0}$ is a proper probability
-distribution, summing to 1 across the entire state-belief-policy space. The discounted
-visitation measure plays a central role in reinforcement learning theory,
-particularly in policy gradient methods. It provides a natural weighting of states
-according to their importance for the discounted objective, as states that are
-visited more frequently or earlier in trajectories receive higher weight. This concept
-generalizes the stationary distribution used in average-reward settings to the discounted
-return framework.
-\begin{lemma}[Evolution of Discounted Visitation]
-    The discounted visitation measure $d^{\pi}_{\mu_0}$ can be expressed in terms of
-    the adjoint operator as:
-    \begin{equation}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-        = (1-\gamma)(I - \gamma\Psi^{*})^{-1}\mu_{0}
-    \end{equation}
-
-    where $\mu_{0}$ is the initial distribution.
-\end{lemma}
-\begin{proof}
-    By the propagation lemma established earlier,
-    $\mu_{t} = (\Psi^{*})^{t}\mu_{0}$ represents the distribution at time $t$ when
-    starting from $\mu_{0}$. The discounted visitation measure weights these distributions
-    by $\gamma^{t}$ and normalizes by $(1-\gamma)$ to ensure it's a proper probability
-    measure:
-    \begin{align}
-        d^{\pi}_{\mu_0} & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} \mu_{t}                \\
-                        & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    The second equality follows from the Neumann series expansion:
-    \begin{align}
-        (I - \gamma\Psi^{*})^{-1} & = \sum_{t=0}^{\infty}(\gamma\Psi^{*})^{t} = \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t}
-    \end{align}
-
-    which converges for $\gamma < 1$ since $\Psi^{*}$ is a non-expansion operator in
-    the total variation norm.
-\end{proof}This establishes the essential connection between the adjoint operator
-and the discounted visitation measure, which is central to the policy gradient
-theorem. The measure $d^{\pi}_{\mu_0}$ represents the normalized expected discounted
-time spent in each state-belief-policy configuration, weighted according to the
-discount factor $\gamma$. This connection allows us to transform expressions involving
-$(I - \gamma\Psi)^{-1}$ in the value function to expectations with respect to $d^{\pi}
-        _{\mu_0}$, which is key for deriving practical policy gradient algorithms.In
-practical implementations, the discounted visitation measure is rarely computed explicitly
-due to the prohibitive computational cost. Instead, sampling-based approaches are
-used to estimate expectations with respect to this measure. The policy gradient
-theorem leverages this measure to derive update rules that can be efficiently
-implemented using trajectory samples collected from the environment.
-
-\subsection{Existence and Uniqueness}
-To provide a rigorous mathematical foundation for our policy gradient theorem,
-we establish the existence and uniqueness of the discounted visitation measure.
-\begin{lemma}[Existence of the Discounted Visitation Measure]
-    Let $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ be the space
-    of finite measures on the joint state-belief-policy space, equipped with the
-    total variation norm. For any initial measure $\mu_{0} \in \mathcal{M}(S \times
-        \boldsymbol{B}\times \boldsymbol{\Theta})$ and discount factor $\gamma \in [0,1
-        )$, the discounted state-visitation measure
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    exists and is a well-defined measure in $\mathcal{M}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$.
-\end{lemma}
-\begin{proof}
-    To establish the existence of $d^{\pi}_{\mu_0}$, we need to prove that the
-    infinite sum $(1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    converges to a well-defined measure. First, let's recall that
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ equipped with
-    the total variation norm
-    $\|\mu\|_{TV}= \sup_{|f| \leq 1}\left|\int f d\mu\right|$ is a Banach space. Now,
-    we need to show that the series
-    $\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$ converges in this space.
-    For any $t \geq 0$, $(\Psi^{*})^{t} \mu_{0}$ represents the measure over the
-    joint state-belief-policy space after $t$ transitions, starting from the initial
-    measure $\mu_{0}$. Since $\Psi^{*}$ is a Markov operator (the adjoint of a Markov
-    transition kernel), it preserves the total mass of a measure: if $\mu_{0}$ is
-    a probability measure (i.e., $\mu_{0}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta}) = 1$), then so is $(\Psi^{*})^{t} \mu_{0}$ for all $t \geq 0$.
-    Therefore, $\|(\Psi^{*})^{t} \mu_{0}\|_{TV}= \mu_{0}(S \times \boldsymbol{B}\times
-        \boldsymbol{\Theta})$ for all $t \geq 0$. For a general finite measure
-    $\mu_{0}$ with total mass
-    $M = \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$, we have $\|(\Psi
-        ^{*})^{t} \mu_{0}\|_{TV}= M$ for all $t \geq 0$. Now, consider the partial sum:
-    \begin{align}
-        S_{n} = (1-\gamma) \sum_{t=0}^{n}\gamma^{t} (\Psi^{*})^{t} \mu_{0}
-    \end{align}
-
-    For $n < m$, the difference between two partial sums is:
-    \begin{align}
-        \|S_{m} - S_{n}\|_{TV} & = \left\| (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right\|_{TV} \\
-                               & \leq (1-\gamma) \sum_{t=n+1}^{m}\gamma^{t} \|(\Psi^{*})^{t} \mu_{0}\|_{TV}           \\
-                               & = (1-\gamma) M \sum_{t=n+1}^{m}\gamma^{t}                                            \\
-                               & = (1-\gamma) M (\gamma^{n+1}+ \gamma^{n+2}+ \ldots + \gamma^{m})                     \\
-                               & = (1-\gamma) M \gamma^{n+1}\frac{1 - \gamma^{m-n}}{1 - \gamma}                       \\
-                               & = M \gamma^{n+1}(1 - \gamma^{m-n})
-    \end{align}
-
-    As $n \to \infty$, $\gamma^{n+1}\to 0$ (since $\gamma < 1$), which means that
-    the sequence of partial sums $\{S_{n}\}$ is Cauchy in the Banach space
-    $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$. By the completeness
-    of this space, the sequence converges to a measure which we denote as
-    $d^{\pi}_{\mu_0}$. Moreover, the total mass of $d^{\pi}_{\mu_0}$ is:
-    \begin{align}
-        d^{\pi}_{\mu_0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \\
-                                                                           & = (1-\gamma) M \sum_{t=0}^{\infty}\gamma^{t}                                                                         \\
-                                                                           & = (1-\gamma) M \frac{1}{1-\gamma}                                                                                    \\
-                                                                           & = M
-    \end{align}
-
-    Thus, $d^{\pi}_{\mu_0}$ is a finite measure with the same total mass as $\mu_{0}$.
-\end{proof}Having established existence, we now turn to the uniqueness of the discounted
-visitation measure.
-
-\begin{lemma}[Uniqueness of the Discounted Visitation Measure]
-    The discounted state-visitation measure $d^{\pi}_{\mu_0}$ is the unique solution
-    to the functional equation:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0}
-    \end{align}
-
-    in the space of finite measures $\mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol
-        {\Theta})$.
-\end{lemma}
-\begin{proof}
-    First, we verify that
-    $d^{\pi}_{\mu_0}= (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}$
-    satisfies the functional equation:
-
-    \begin{align}
-        (1-\gamma)\mu_{0} + \gamma \Psi^{*} d^{\pi}_{\mu_0} & = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \left( (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right) \\
-                                                            & = (1-\gamma)\mu_{0} + \gamma (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t+1}\mu_{0}                        \\
-                                                            & = (1-\gamma)\mu_{0} + (1-\gamma) \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                \\
-                                                            & = (1-\gamma) \left( \mu_{0} + \sum_{t=1}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0} \right)                           \\
-                                                            & = (1-\gamma) \sum_{t=0}^{\infty}\gamma^{t} (\Psi^{*})^{t} \mu_{0}                                                    \\
-                                                            & = d^{\pi}_{\mu_0}
-    \end{align}
-
-    To prove uniqueness, suppose there exists another measure
-    $\tilde{d}\in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    that satisfies the functional equation:
-    \begin{align}
-        \tilde{d}= (1-\gamma)\mu_{0} + \gamma \Psi^{*} \tilde{d}
-    \end{align}
-
-    Let's consider the operator
-    $T: \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta}) \to \mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$
-    defined as:
-    \begin{align}
-        T(\mu) = (1-\gamma)\mu_{0} + \gamma \Psi^{*} \mu
-    \end{align}
-
-    For any two measures
-    $\mu, \nu \in \mathcal{M}(S \times \boldsymbol{B}\times \boldsymbol{\Theta})$:
-    \begin{align}
-        \|T(\mu) - T(\nu)\|_{TV} & = \|\gamma \Psi^{*} \mu - \gamma \Psi^{*} \nu\|_{TV} \\
-                                 & = \gamma \|\Psi^{*} (\mu - \nu)\|_{TV}               \\
-                                 & \leq \gamma \|\mu - \nu\|_{TV}
-    \end{align}
-
-    Since $\gamma < 1$, $T$ is a contraction mapping on the Banach space $\mathcal{M}
-        (S \times \boldsymbol{B}\times \boldsymbol{\Theta})$ with contraction factor $\gamma$.
-    By the Banach fixed-point theorem, $T$ has a unique fixed point. We've already
-    shown that $d^{\pi}_{\mu_0}$ is a fixed point of $T$, and by assumption,
-    $\tilde{d}$ is also a fixed point. Therefore, $d^{\pi}_{\mu_0}= \tilde{d}$, proving
-    the uniqueness of the discounted state-visitation measure.
-\end{proof}
-
-\subsection{Connection to Value Function}
-Having established the theoretical properties of the discounted visitation
-measure, we now connect it to the value function, which will provide important
-insights later on.
-
-\begin{lemma}[Value Function as Inner Product]
-    For any discount factor $\gamma \in [0,1)$ and initial state $s_{0}$, belief
-    state $\boldsymbol{b}_{0}$, and policy parameter $\boldsymbol{\theta}_{0}$,
-    the value function can be expressed as:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ is
-    the Dirac measure concentrated at
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$, and $r^{i}$ is the expected
-    immediate reward function:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-\end{lemma}
-\begin{proof}
-    Let $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$ be the
-    Dirac measure concentrated at the point $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol
-        {\theta}_{0})$. By definition of the value function:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \mathbb{E}\left[ \sum_{t=0}^{\infty}\gamma^{t} R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right] \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ R^{i}(s_{t}, \boldsymbol{a}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]
-    \end{align}
-
-    Define the expected immediate reward function
-    $r^{i}: S \times \boldsymbol{B}\times \boldsymbol{\Theta}\to \mathbb{R}$ as:
-    \begin{align}
-        r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{\neg i}}\pi^{\neg i}(a^{\neg i}|b^{\neg i}; \theta^{\neg i}) R^{i}(s, \boldsymbol{a})
-    \end{align}
-
-    Then:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \mathbb{E}\left[ r^{i}(s_{t}, \boldsymbol{b}_{t}, \boldsymbol{\theta}_{t}) \bigg| s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}, \pi \right]       \\
-                                                                             & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    where $\mu_{t}$ is the distribution over the joint state-belief-policy space
-    at time $t$, starting from $\mu_{0}$. From previous lemmas, we know that $\mu_{t}
-        = (\Psi^{*})^{t} \mu_{0}$. Using the duality relationship between functions
-    and measures:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{t}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((\Psi^{*})^{t}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                                                                                                & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \sum_{t=0}^{\infty}\gamma^{t} \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}(\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})              \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\left(\sum_{t=0}^{\infty}\gamma^{t} (\Psi^{t} r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta})\right) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Since $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, we have:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}r^{i})(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Alternatively, using the duality between $(I - \gamma \Psi)^{-1}$ and
-    $(I - \gamma \Psi^{*})^{-1}$:
-    \begin{align}
-        \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}((I - \gamma \Psi)^{-1}r^{i})(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From previous lemmas, we know that $d^{\pi}_{\mu_0}= (1-\gamma) (I - \gamma \Psi
-        ^{*})^{-1}\mu_{0}$. Therefore:
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                             & = \int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) \frac{d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})}{1-\gamma}     \\
-                                                                             & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-\end{proof}This lemma establishes that the value function can be expressed as an
-expectation with respect to the discounted visitation measure, with an appropriate
-scaling factor. This formulation provides a direct link between the value
-function and the distribution of states.
-
-\section{Policy Gradient Theorem}
-Having established the mathematical foundations for discounted returns in
-partially observable multi-agent settings, we now derive the policy gradient theorem
-that forms the basis for practical optimization algorithms. This theorem
-provides a principled expression for computing gradients of the expected
-discounted return with respect to policy parameters, enabling efficient policy improvement.
-The policy gradient theorem connects an agent's policy parameters to its
-expected long-term performance through the discounted visitation measure, providing
-a mathematically rigorous foundation for optimization.
-
-\begin{theorem}[Partially Observable Active Discounted Return Policy Gradient
-        Theorem]
-    The gradient of the discounted return objective $J^{i}_{\pi, \gamma}(\theta^{i}) = v
-            ^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$ with respect
-    to agent $i$'s policy parameters $\theta^{i}$ in a partially observable active
-    Markov game setting can be expressed as:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \nonumber \\
-                                                         & \quad \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    where $d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})$ is the discounted
-    visitation measure starting from initial distribution $\mu_{0}$, and
-    $q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})$ is
-    the action-value function defined as:
-    \begin{align}
-        q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) & = R^{i}(s, \boldsymbol{a}) + \gamma \sum_{s'}T(s'|s, \boldsymbol{a}) \sum_{\boldsymbol{o}'}\boldsymbol{O}(\boldsymbol{o}'|s') \nonumber                                                                                 \\
-                                                                                 & \quad \sum_{\boldsymbol{\theta}'}\boldsymbol{U}(\boldsymbol{\theta}'|\boldsymbol{\theta}, \boldsymbol{\tau}) v^{i}_{\theta^i}(s', \text{update}(\boldsymbol{b}, \boldsymbol{a}, \boldsymbol{o}'), \boldsymbol{\theta}')
-    \end{align}
-\end{theorem}We now provide a detailed proof of the policy gradient theorem, building
-on the lemmas established in previous sections.
-\begin{proof}
-    From our previous lemma, we know that the gradient of the value function can be
-    expressed as:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}\left[\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})\right]
-    \end{align}
-
-    For notational clarity, we define the term inside the brackets as:
-    \begin{align}
-        g(s, \boldsymbol{b}, \boldsymbol{\theta}) = \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    Now we can write:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}) & = (I - \gamma \Psi)^{-1}g(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For our specific initial state configuration
-    $(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})
-    \end{align}
-
-    Let's define
-    $\mu_{0} = \delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}$, which is the
-    Dirac measure concentrated at the initial state. We can view
-    $((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})$
-    as the integration of the function $(I - \gamma \Psi)^{-1}g$ against this
-    Dirac measure:
-
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = ((I - \gamma \Psi)^{-1}g)(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                           \\
-                                                                                              & = \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Recall the duality principle we established earlier, which states that:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}f)(x) d\mu(x) = \int f(x) d((I - \gamma \Psi^{*})^{-1}\mu)(x)
-    \end{align}
-
-    Allowing us to move the operator from acting on the function $g$ to acting on
-    the measure $\mu_{0}$:
-    \begin{align}
-        \int ((I - \gamma \Psi)^{-1}g)(s, \boldsymbol{b}, \boldsymbol{\theta}) d\mu_{0}(s, \boldsymbol{b}, \boldsymbol{\theta}) = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\mu_{0})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Therefore:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d((I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)})(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    From our earlier derivation of the discounted visitation measure, we established
-    that:
-    \begin{align}
-        d^{\pi}_{\mu_0}= (1-\gamma)(I - \gamma \Psi^{*})^{-1}\mu_{0} = (1-\gamma)(I - \gamma \Psi^{*})^{-1}\delta_{(s_0, \boldsymbol{b}_0, \boldsymbol{\theta}_0)}
-    \end{align}
-
-    We can now substitute this expression:
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) & = \int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d\left(\frac{d^{\pi}_{\mu_0}}{1-\gamma}\right)(s, \boldsymbol{b}, \boldsymbol{\theta}) \\
-                                                                                              & = \frac{1}{1-\gamma}\int g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    Substituting the definition of $g(s, \boldsymbol{b}, \boldsymbol{\theta})$ back:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0})                                                                                                                                                                                                                                                  \\
-                                                         & = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}\sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    For finite state, belief, and policy parameter spaces, this integral can be
-    written as a sum:
-    \begin{align}
-        \nabla_{\theta^i}J^{i}_{\pi, \gamma}(\theta^{i}) & = \frac{1}{1-\gamma}\sum_{s, \boldsymbol{b}, \boldsymbol{\theta}}d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta}) \sum_{a^i}\nabla_{\theta^i}\pi^{i}(a^{i}|b^{i}; \theta^{i}) \sum_{a^{-i}}\pi^{-i}(a^{-i}|\boldsymbol{b}^{-i}; \theta^{-i}) q^{i}_{\theta^i}(s, \boldsymbol{b}, \boldsymbol{\theta}, \boldsymbol{a})
-    \end{align}
-
-    This completes the proof of the Partially Observable Active Discounted Return
-    Policy Gradient Theorem.
-\end{proof}
-
-The proof reveals a symmetry in the mathematical structure of our results.
-\begin{remark}[Symmetry]
-    From the Value Function as Inner Product lemma, the value function
-    \begin{align}
-        v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}r^{i}(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of immediate rewards $r^{i}$ under the discounted visitation
-    measure $d^{\pi}_{\mu_0}$. While its gradient
-    \begin{align}
-        \nabla_{\theta^i}v^{i}_{\theta^i}(s_{0}, \boldsymbol{b}_{0}, \boldsymbol{\theta}_{0}) = \frac{1}{1-\gamma}\int_{S \times \boldsymbol{B} \times \boldsymbol{\Theta}}g(s, \boldsymbol{b}, \boldsymbol{\theta}) d^{\pi}_{\mu_0}(s, \boldsymbol{b}, \boldsymbol{\theta})
-    \end{align}
-
-    is an expectation of policy-gradient-weighted action values $g$ under the same
-    discounted visitation measure $d^{\pi}_{\mu_0}$.
-\end{remark}
-This symmetric structure provides not only mathematical elegance but also
-practical advantages. It means that the same samples from the discounted visitation
-distribution can be used to estimate both values and policy gradients.
-
-The policy gradient theorem provides the mathematical foundation for agents to optimize
-their policies in ways that account for both the partial observability of the environment
-and the learning dynamics of other agents. This enables sophisticated strategic
-behaviors such as information revelation, teaching, and influence that are
-essential in social learning contexts.
-
-\chapter{POLARIS Architecture}
-\label{appendix:neural_architectures}
-
-This section provides detailed technical specifications of all neural network architectures used in our POLARIS implementation.
-We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
-\begin{equation}
-    \alpha_{ij} = \frac{\exp(e_{ij})}{\sum_{k \in \mathcal{N}_i} \exp(e_{ik})}
-\end{equation}
-
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
-
-\chapter{Social Learning Implementation}
-
-This chapter presents the technical implementation details of our social learning models within the Partially Observable Active Markov Game framework.
-We provide a comprehensive account of the algorithmic approaches, mathematical techniques, and computational methods used to translate theoretical social learning concepts into executable simulations.
-The discussion begins with the rigorous discretization of Lévy processes—the mathematical foundation for modeling stochastic rewards and signals—and proceeds to cover the specific implementation challenges encountered in strategic experimentation scenarios.
-Another key innovation is our construction of observation-based reward functions that preserve expected reward structures when agents cannot directly observe the true environmental state, allowing them to learn optimal policies from noisy signals while maintaining the incentive properties of the original models.
-Throughout this chapter, we emphasize how our implementation preserves the strategic incentives inherent in the original models while adapting them to a computational framework suitable for reinforcement learning applications.
-
 \section{Lévy Process Discretization}
@@
 
-\begin{theorem}[Lévy-Khintchine Formula \cite{sato1999levy, applebaum2009levy}]
+\begin{theorem}[Lévy-Khintchine Formula]
+\label{thm:levy_khintchine}
 If $X = \{X_t : t \geq 0\}$ is a Lévy process, then its characteristic function has the form:
@@
 \begin{equation}
-        \psi(\theta) = i\alpha\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
+    \psi(\theta) = ia\theta - \frac{1}{2}\sigma^2\theta^2 + \int_{\mathbb{R}\setminus\{0\}} (e^{i\theta x} - 1 - i\theta x\mathbf{1}_{|x|<1})\nu(dx)
 \end{equation}
-    for some $\alpha \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
+for some $a \in \mathbb{R}$, $\sigma \geq 0$, and a measure $\nu$ on $\mathbb{R}\setminus\{0\}$ satisfying $\int_{\mathbb{R}\setminus\{0\}} \min(1, x^2)\nu(dx) < \infty$.
+\citep{sato1999levy}
 \end{theorem}
 
-The triplet $(\alpha, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
-Here, $\alpha$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
+The triplet $(a, \sigma^2, \nu)$ is called the Lévy-Khintchine triplet or the characteristics of the Lévy process.
+Here, $a$ represents a drift term, $\sigma^2$ parametrizes the continuous Gaussian component, and $\nu$ is the Lévy measure characterizing the jump behavior.
 
-\begin{theorem}[Lévy-Itô Decomposition \cite{sato1999levy, protter2005stochastic}]
+\begin{theorem}[Lévy-Itô Decomposition]
+\label{thm:levy_ito}
 Any Lévy process $X_t$ can be decomposed as:
 \begin{equation}
-        X_t = \alpha t + \sigma W_t + \int_{|x|<1} x (\tilde{Y}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x Y(t, dx)
+    X_t = at + \sigma W_t + \int_{|x|<1} x (\tilde{N}(t, dx) - t\nu(dx)) + \int_{|x|\geq 1} x N(t, dx)
 \end{equation}
-    where $W_t$ is a standard Brownian motion, $Y(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{Y}(t, dx) = Y(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
+where $W_t$ is a standard Brownian motion, $N(t, A)$ counts the number of jumps of size in set $A$ occurring up to time $t$, and $\tilde{N}(t, dx) = N(t, dx) - t\nu(dx)$ is the compensated Poisson random measure.
+\citep{applebaum2009levy}
 \end{theorem}
@@
 \begin{definition}[Euler-Maruyama Scheme for Lévy Processes]
-    Given a Lévy process $X_t$ with characteristics $(\alpha, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
+Given a Lévy process $X_t$ with characteristics $(a, \sigma^2, \nu)$ and a discretization time step $\Delta t$, the Euler-Maruyama approximation constructs a discrete-time process $\{X_{t_n}\}_{n=0}^N$ where $t_n = n\Delta t$ through the recursive relation:
 \begin{equation}
-        X_{t_{n+1}} = X_{t_n} + \alpha \Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
+    X_{t_{n+1}} = X_{t_n} + a\Delta t + \sigma\sqrt{\Delta t}Z_n + \Delta J_n
 \end{equation}
@@
 \end{definition}
-\iffalse
+
 For practical implementation, the jump component $\Delta J_n$ requires careful consideration, especially when the Lévy measure potentially assigns infinite mass to small jumps.
 
-    \begin{proposition}[Approximation of Jump Component \cite{platen2010numerical, applebaum2009levy}]
+\begin{proposition}[Approximation of Jump Component]
 The jump component $\Delta J_n$ can be approximated through one of the following approaches:
@@
 \end{proposition}
-\fi
-\begin{theorem}[Convergence of Euler-Maruyama Scheme \citep{higham2005numerical, platen2010numerical}]
+
+\begin{theorem}[Convergence of Euler-Maruyama Scheme]
 \label{thm:euler_maruyama_convergence}
@@
 where $C$ is a constant depending on $T$ and the characteristics of the Lévy process.
-
+\citep{protter2005stochastic, platen2010numerical}
 \end{theorem}
@@
 
-In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps:
+In the original model, both $B_t$ and $X^i_t$ follow Lévy processes that combine continuous diffusion and discrete jumps \citep{applebaum2009levy}:
 
 \begin{align}
-    dB_t   & = \beta_s dt + \sigma_B dW^B_t + dY^B_t \\
-    dX^i_t & = \alpha_s dt + \sigma dW^i_t + dY^i_t
+    dB_t &= \beta_s dt + \sigma_B dW^B_t + dC^B_t \\
+    dX^i_t &= \alpha_s dt + \sigma dW^i_t + dC^i_t
 \end{align}
 
-where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $Y^B_t$ and $Y^i_t$ are compound Poisson processes.
-Using the Euler-Maruyama scheme \citep{platen2010numerical}, we discretize these continuous-time stochastic differential equations:
+where $W^B_t$ and $W^i_t$ are standard Brownian motions, and $C^B_t$ and $C^i_t$ are compound Poisson processes.
+Using the Euler-Maruyama scheme \citep{higham2001algorithmic, kloeden1992numerical}, we discretize these continuous-time stochastic differential equations:
 
 \begin{align}
-    B_{t+\Delta t} - B_t     & = \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (Y^B_{t+\Delta t} - Y^B_t) \\
-    X^i_{t+\Delta t} - X^i_t & = \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (Y^i_{t+\Delta t} - Y^i_t)
+    B_{t+\Delta t} - B_t &= \beta_s \Delta t + \sigma_B (W^B_{t+\Delta t} - W^B_t) + (C^B_{t+\Delta t} - C^B_t) \\
+    X^i_{t+\Delta t} - X^i_t &= \alpha_s \Delta t + \sigma (W^i_{t+\Delta t} - W^i_t) + (C^i_{t+\Delta t} - C^i_t)
 \end{align}
@@
 \begin{align}
-    B_{t-1:t}   & = \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta Y^B_t \\
-    X^i_{t-1:t} & = \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta Y^i_t
+    B_{t-1:t} &= \beta_s \Delta t + \sigma_B (W^B_t - W^B_{t-1}) + \Delta N^B_t \\
+    X^i_{t-1:t} &= \alpha_s \Delta t + \sigma (W^i_t - W^i_{t-1}) + \Delta N^i_t
 \end{align}
 
-where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta Y^B_t$, $\Delta Y^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
+where $(W^B_t - W^B_{t-1}) \sim \mathcal{N}(0, \Delta t)$, $(W^i_t - W^i_{t-1}) \sim \mathcal{N}(0, \Delta t)$, and $\Delta N^B_t$, $\Delta N^i_t$ are the increments of the compound Poisson processes over the interval $[t-1, t]$.
 
@@
 \begin{equation}
-    dR^i_t = (1-a^i_t)r_\textit{safe} dt + a^i_t dX^i_t
+    dR^i_t = (1-a^i_t)s dt + a^i_t dX^i_t
 \end{equation}
 
-where $a^i_t \in [0,1]$ is the allocation to the risky arm and $r_\textit{safe}$ is the safe arm's deterministic flow payoff and the Levy process increment is a function of the state $s$.
+where $a^i_t \in [0,1]$ is the allocation to the risky arm and $s$ is the safe arm's deterministic flow payoff.
+
 To translate this structure into the POAMG framework, we need a reward function $R^i(s, a^i)$ that depends only on the state and action, not explicitly on time.
@@
 \begin{equation}
-    R^i(s, a^i) = (1-a^i)r_\textit{safe} + a^i \frac{X^i_{t-1:t}}{\Delta t}
+    R^i(s, a^i) = (1-a^i)s + a^i \frac{X^i_{t-1:t}}{\Delta t}
 \end{equation}
@@
 \begin{proposition}[Reward Equivalence]
-    The expected value of the discrete-time reward function $R^i(s, a^i)$ exactly equals the expected instantaneous flow payoff in the continuous-time model. Specifically:
+As $\Delta t \to 0$, the expected value of the discrete-time reward function $R^i(s, a^i)$ converges to the expected instantaneous flow payoff in the continuous-time model. Specifically:
 \begin{equation}
-        \mathbb{E}[R^i(s, a^i)] = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
+    \lim_{\Delta t \to 0} \mathbb{E}[R^i(s, a^i)] = (1-a^i)s + a^i\mathbb{E}[\alpha_s + \lambda_s\mu_s]
 \end{equation}
-    where $\alpha_s$ is the drift of the Levy process, $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
+where $\lambda_s$ is the jump intensity and $\mu_s$ is the mean jump size of the compound Poisson process component of $X^i_t$ in state $s$.
 \end{proposition}
@@
 \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right]                                       \\
-                                & = (1-a^i)r_\textit{safe} + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta Y^i_t]}{\Delta t} \\
-                                & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta Y^i_t]}{\Delta t}\right)
+    \mathbb{E}[R^i(s, a^i)] &= (1-a^i)s + a^i\mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t}\right] \\
+    &= (1-a^i)s + a^i\frac{\mathbb{E}[\alpha_s \Delta t + \sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t]}{\Delta t} \\
+    &= (1-a^i)s + a^i\left(\alpha_s + \frac{\mathbb{E}[\Delta N^i_t]}{\Delta t}\right)
 \end{align}
 
-    Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta Y^i_t] = \lambda_s h_s\Delta t$, where $\lambda_s$ is the jump intensity and $h_s$ is the mean jump size, we have:
+Since $\mathbb{E}[W^i_t - W^i_{t-1}] = 0$ and $\mathbb{E}[\Delta N^i_t] = \lambda_s\mu_s\Delta t$, where $\lambda_s$ is the jump intensity and $\mu_s$ is the mean jump size, we have:
 
 \begin{align}
-        \mathbb{E}[R^i(s, a^i)] & = (1-a^i)r_\textit{safe} + a^i\left(\alpha_s + \frac{\lambda_s h_s\Delta t}{\Delta t}\right) \\
-                                & = (1-a^i)r_\textit{safe} + a^i(\alpha_s + \lambda_s h_s)
+    \mathbb{E}[R^i(s, a^i)] &= (1-a^i)s + a^i\left(\alpha_s + \frac{\lambda_s\mu_s\Delta t}{\Delta t}\right) \\
+    &= (1-a^i)s + a^i(\alpha_s + \lambda_s\mu_s)
 \end{align}
@@
 
-\iffalse
 \subsubsection{Preservation of Strategic Incentives}
@@
 \begin{proposition}[Preservation of Strategic Incentives]
-        The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the sense that the optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
-
+The discrete-time reward function $R^i(s, a^i)$ preserves the strategic incentives of the continuous-time model in the following sense:
+\begin{enumerate}
+    \item The optimal policy in the discrete-time model converges to the optimal policy in the continuous-time model as $\Delta t \to 0$.
+    \item The incentive to experiment, measured by the difference in value between exploration and exploitation, is preserved up to $O(\Delta t)$ error terms.
+\end{enumerate}
 \end{proposition}
@@
 when $m(b) < s$, and $I(b) = \infty$ otherwise, where $f(b)$ is the expected flow payoff of the risky arm and $m(b)$ is the expected flow payoff when the risky arm is bad.
+
 In our discrete-time approximation, the corresponding incentive is:
@@
 where $f_1 = \alpha_1 + \lambda_1\mu_1$ is the expected flow in the good state and $f_0 = \alpha_0 + \lambda_0\mu_0$ is the expected flow in the bad state, with $m(b) = f_0$.
+
 In our discrete-time approximation, we have:
@@
 where $\hat{f}_1$ and $\hat{f}_0$ are the expected rewards in the good and bad states, respectively.
-        From our reward equivalence result, we know that:
+
+From our reward equivalence result (Proposition 3.1), we know that:
 \begin{align}
-            \hat{f}_1 & = \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
-                      & = \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
+    \hat{f}_1 &= \mathbb{E}\left[\frac{X^i_{t-1:t}}{\Delta t} \mid \text{good state}\right] = \alpha_1 + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1}) + \Delta N^i_t \mid \text{good state}]}{\Delta t} \\
+    &= \alpha_1 + \frac{\lambda_1\mu_1\Delta t}{\Delta t} + \frac{\mathbb{E}[\sigma(W^i_t - W^i_{t-1})]}{\Delta t}
 \end{align}
@@
 Similarly, $\hat{f}_0 = \alpha_0 + \lambda_0\mu_0 + O(\Delta t) \to f_0 \text{ as } \Delta t \to 0$, and consequently $\hat{m}(b) = \hat{f}_0 \to m(b) = f_0$.
+
 Therefore, we can establish that:
@@
 where $k_0$ is a threshold determined by the model parameters and $N$ is the number of players.
-The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$.
 
-        Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model.
+The discrete-time counterpart $\hat{\kappa}^*(b)$ takes the same form but with $\hat{I}(b)$ in place of $I(b)$:
+\begin{equation}
+\hat{\kappa}^*(b) = 
+\begin{cases}
+0 & \text{if } \hat{I}(b) \leq k_0, \\
+\frac{\hat{I}(b)-k_0}{N-1} & \text{if } k_0 < \hat{I}(b) < k_0 + N - 1, \\
+1 & \text{if } \hat{I}(b) \geq k_0 + N - 1.
+\end{cases}
+\end{equation}
+
+To quantify the convergence rate, note that for any belief $b$, the error in the incentive function is:
+\begin{equation}
+    |\hat{I}(b) - I(b)| = \left|\frac{\hat{f}(b) - s}{s - \hat{m}(b)} - \frac{f(b) - s}{s - m(b)}\right|
+\end{equation}
+
+With some algebraic manipulation, we get:
+\begin{equation}
+    |\hat{I}(b) - I(b)| = \left|\frac{(s - m(b))(\hat{f}(b) - s) - (s - \hat{m}(b))(f(b) - s)}{(s - \hat{m}(b))(s - m(b))}\right|
+\end{equation}
+
+Expanding the numerator:
+\begin{align}
+    &(s - m(b))(\hat{f}(b) - s) - (s - \hat{m}(b))(f(b) - s) \\
+    &= (s - m(b))\hat{f}(b) - (s - m(b))s - (s - \hat{m}(b))f(b) + (s - \hat{m}(b))s \\
+    &= (s - m(b))\hat{f}(b) - (s - \hat{m}(b))f(b) + (\hat{m}(b) - m(b))s \\
+    &= s(\hat{f}(b) - f(b)) - m(b)\hat{f}(b) + \hat{m}(b)f(b) + (\hat{m}(b) - m(b))s \\
+    &= s(\hat{f}(b) - f(b)) - m(b)\hat{f}(b) + \hat{m}(b)f(b) + \hat{m}(b)s - m(b)s \\
+    &= s(\hat{f}(b) - f(b)) + \hat{m}(b)(f(b) + s) - m(b)(\hat{f}(b) + s)
+\end{align}
+
+Given that $|\hat{f}(b) - f(b)| = O(\Delta t)$ and $|\hat{m}(b) - m(b)| = O(\Delta t)$, we have:
+\begin{equation}
+    |\hat{I}(b) - I(b)| = O(\Delta t)
+\end{equation}
+
+This implies that the error in the incentive function decreases linearly with the time step, and consequently, the difference between the optimal policies $|\hat{\kappa}^*(b) - \kappa^*(b)|$ is also of order $O(\Delta t)$.
+
+Therefore, as $\Delta t \to 0$, the strategic incentives and optimal policies in our discrete-time approximation converge to those of the original continuous-time model at a rate of $O(\Delta t)$.
 \end{proof}
 
-\fi
 \subsection{Relation to Policy-Invariant Reward Transformations}
@@
 \begin{equation}
-        \sum_{k=0}^{\eta-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{\eta-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
+    \sum_{k=0}^{N-1} \Delta t \left[(1-a^i_{t_k})s + a^i_{t_k}\frac{X^i_{t_k:t_{k+1}}}{\Delta t}\right] = \sum_{k=0}^{N-1} [(1-a^i_{t_k})s\Delta t + a^i_{t_k}X^i_{t_k:t_{k+1}}]
 \end{equation}
-    where $\eta = T/\Delta t$ and $t_k = k\Delta t$.
+where $N = T/\Delta t$ and $t_k = k\Delta t$.
 
-    As $\Delta t \to 0$ and $\eta \to \infty$ with $\eta t = T$ fixed, the discretized sum converges to the continuous-time integral.
+As $\Delta t \to 0$ and $N \to \infty$ with $N\Delta t = T$ fixed, the discretized sum converges to the continuous-time integral.
 Since both formulations yield the same expected cumulative reward in the limit, they induce the same optimal policies.
 \end{proof}
-
-\section{Observed Reward Function}
-\label{appendix:observed_reward_derivation} In our reinforcement learning
-implementation, agents need to learn from observed rewards that reflect the optimality
-of their actions with respect to the true state of the world. However, since agents
-do not directly observe the true state $\omega$, we need to construct a reward
-function based on their observations $o$ that preserves the expected reward
-structure. This appendix provides a detailed derivation of the observation-based
-reward function.The true reward function is given by $u(s, a): S \times A \rightarrow
-    \mathbb{R}$, where $a$ is an action and $s$ is the state. However, agents only
-observe signals $o \sim \mu^{s}$ drawn from a distribution determined by the
-state. We need to construct an observation-based reward function $v(o, a): \Omega
-    _{i} \times A \rightarrow \mathbb{R}$ that satisfies:
-\begin{equation}
-    \mathbb{E}_{o \sim \mu^{s}}[v(o, a)] = u(s, a), \quad \forall s \in S, \forall
-    a \in A.
-\end{equation}
-
-In other words, the expected value of the observation-based reward $v(o, a)$
-over all possible observations $o$ given the state $s$ should equal the true
-reward $u(s, a)$ for any state-action pair. Let's define $\bm{\mu}$ as a $m \times
-    m$ matrix representing the observation distributions, where $m = |S|$ and assume
-the aforementioned state and observation spaces. Each entry $\mu^{s}(o)$ denotes
-the probability of observing observation $o$ in state $s$:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        \mu^{s^1}(s^{1}) & \mu^{s^1}(s^{2}) & \cdots & \mu^{s^1}(s^{m}) \\
-        \mu^{s^2}(s^{1}) & \mu^{s^2}(s^{2}) & \cdots & \mu^{s^2}(s^{m}) \\
-        \vdots           & \vdots           & \ddots & \vdots           \\
-        \mu^{s^m}(s^{1}) & \mu^{s^m}(s^{2}) & \cdots & \mu^{s^m}(s^{m})
-    \end{bmatrix}
-\end{equation}
-
-We assume that observation distributions are linearly independent across states,
-which implies that $\bm{\mu}$ is invertible. This assumption is satisfied when $\mu
-    ^{s}(s) > \mu^{s}(s')$ for all $s \neq s' \in S$, meaning that each state is
-more likely to generate its corresponding observation than any other observation.
-For each action $a \in A$, we define a utility vector
-$\bm{u}_{a} \in \mathbb{R}^{k}$ as:
-\begin{equation}
-    \bm{u}_{a} =
-    \begin{bmatrix}
-        u(s^{1}, a) \\
-        u(s^{2}, a) \\
-        \vdots      \\
-        u(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-Similarly, we define a vector of observation-based rewards $\bm{v}_{a} \in \mathbb{R}
-    ^{k}$ for action $a$:
-\begin{equation}
-    \bm{v}_{a} =
-    \begin{bmatrix}
-        v(s^{1}, a) \\
-        v(s^{2}, a) \\
-        \vdots      \\
-        v(s^{m}, a)
-    \end{bmatrix}
-\end{equation}
-
-The condition that expected observation-based rewards match true rewards can be written
-as a linear system:
-\begin{equation}
-    \bm{\mu}^{T} \bm{v}_{a} = \bm{u}_{a}
-\end{equation}
-
-where $\bm{\mu}^{T}$ is the transpose of $\bm{\mu}$. The solution to this system
-is:
-\begin{equation}
-    \bm{v}_{a} = (\bm{\mu}^{T})^{-1}\bm{u}_{a} = (\bm{\mu}^{-1})^{T} \bm{u}_{a}
-\end{equation}
-
-This gives us the vector of observation-based rewards that satisfy our expected
-reward condition. For each observation $o_{j}$ and action $a$, the observation-based
-reward is:
-\begin{equation}
-    v(o_{j}, a) = \sum_{l=1}^{m} \left( \bm{\mu}^{-1}\right)_{jl}u(s_{l}, a)
-\end{equation}
-
-where $\left( \bm{\mu}^{-1}\right)_{jl}$ denotes the $(j, l)$-th element of
-$\bm{\mu}^{-1}$.
-\paragraph{Binary Case Example}
-For the special case with two states of the world ($m = 2$) and symmetric
-observations with accuracy $q > 0.5$, the observation distribution matrix is:
-\begin{equation}
-    \bm{\mu}=
-    \begin{bmatrix}
-        q   & 1-q \\
-        1-q & q
-    \end{bmatrix}
-\end{equation}
-
-This means that in state $s^{1}$, the probability of observing $s^{1}$ is $q$
-and the probability of observing $s^{2}$ is $1-q$, and vice versa for state $s^{2}$.
-The inverse of this matrix is:
-\begin{equation}
-    \bm{\mu}^{-1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q      & -(1-q) \\
-        -(1-q) & q
-    \end{bmatrix}
-\end{equation}
-
-In our implementation, we set the true reward as the indicator function for taking
-the correct action, which for the binary case becomes, $u(s^{1}, a^{1}) = u(s^{2}
-    , a^{2}) = 1$; $u(s^{2}, a^{1}) = u(s^{1}, a^{2}) = 0$. For action $a^{1}$, the
-utility vector is $\bm{u}_{a^1}= [1, 0]^{T}$, and the observation-based reward vector
-is:
-\begin{equation}
-    \bm{v}_{a^1}= \bm{\mu}^{-1}\bm{u}_{a^1}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        q \\
-        -(1-q)
-    \end{bmatrix}
-\end{equation}
-
-This means that when an agent takes action $a^{1}$ and observes signal $s^{1}$,
-the reward is $v(s^{1}, a^{1}) = \frac{q}{2q-1}$, and when the agent observes signal
-$s^{2}$, the reward is $v(s^{2}, a^{1}) = -\frac{1-q}{2q-1}$. Similarly, for
-action $a^{2}$, the utility vector is $\bm{u}_{a^2}= [0, 1]^{T}$, and the
-observation-based reward vector is:
-\begin{equation}
-    \bm{v}_{a^2}= \bm{\mu}^{-1}\bm{u}_{a^2}= \frac{1}{2q-1}
-    \begin{bmatrix}
-        -(1-q) \\
-        q
-    \end{bmatrix}
-\end{equation}
-
-Combining these results, we can express the observation-based reward function for
-any action-observation pair $(a, o)$ as:
-\begin{equation}
-    v(a, o) = \frac{q \cdot \mathbf{1}_{\{a = \varphi(o)\}}- (1-q) \cdot
-        \mathbf{1}_{\{a \neq \varphi(o)\}}}{2q-1}
-\end{equation}
-
-where $\varphi$ maps observations to their corresponding actions. The derived
-observation-based reward function has an intuitive interpretation. When an agent
-takes an action matching its observation ($a = o$), it receives a positive
-reward of $\frac{q}{2q-1}$, whereas when she takes an action not matching its observation
-($a \neq o$), it receives a negative reward of $-\frac{1-q}{2q-1}$. As $q$ approaches
-0.5 (signals become uninformative), the rewards grow in magnitude, reflecting the
-increased uncertainty. Conversely, as $q$ approaches 1 (signals become perfectly
-informative), the reward for matching observation and action approaches 1, and the
-penalty for mismatching approaches 0, meaning that the observed reward function
-converges to the true reward function. This reward structure incentivizes agents
-to match their actions to their observations when signals are reliable, but also
-allows them to learn to override their immediate observations when the actions
-of other agents provide stronger evidence about the true state through beliefs.

### 2025-05-26 code/further+/modules/agent.py

@@ -1,0 +1,1024 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import numpy as np
+
+from modules.networks import EncoderNetwork, DecoderNetwork, PolicyNetwork, QNetwork, TransformerBeliefProcessor, TemporalGNN
+from modules.replay_buffer import ReplayBuffer
+from modules.utils import get_best_device, encode_observation
+
+class POLARISAgent:
+    """POLARIS agent for social learning with additional advantage-based Transformer training."""
+    def __init__(
+        self,
+        agent_id,
+        num_agents,
+        num_states,
+        observation_dim,
+        action_dim,
+        hidden_dim=64,
+        belief_dim=64,
+        latent_dim=64,
+        learning_rate=1e-3,
+        discount_factor=0.99,
+        entropy_weight=0.01,
+        kl_weight=0.01,
+        target_update_rate=0.005,
+        device=None,
+        buffer_capacity=1000,
+        max_trajectory_length=50,
+        use_gnn=True,
+        use_ewc=False,
+        ewc_lambda=100.0,
+        ewc_online=False,
+        ewc_gamma=0.95
+    ):
+        
+        # Use the best available device if none is specified
+        if device is None:
+            device = get_best_device()
+        print(f"Using device: {device}")
+        self.agent_id = agent_id
+        self.num_agents = num_agents
+        self.num_states = num_states
+        self.observation_dim = observation_dim
+        self.action_dim = action_dim
+        self.device = device
+        self.discount_factor = discount_factor
+        self.entropy_weight = entropy_weight
+        self.kl_weight = kl_weight
+        self.target_update_rate = target_update_rate
+        self.max_trajectory_length = max_trajectory_length
+        self.latent_dim = latent_dim
+        self.use_gnn = use_gnn
+        
+        # EWC parameters
+        self.use_ewc = use_ewc
+        self.ewc_lambda = ewc_lambda
+        self.ewc_online = ewc_online
+        self.ewc_gamma = ewc_gamma
+        
+        # EWC Fisher information and parameter storage
+        self.fisher_belief = None  # Fisher for belief processor
+        self.fisher_policy = None  # Fisher for policy network
+        self.optimal_belief_params = None  # Optimal parameters for belief processor
+        self.optimal_policy_params = None  # Optimal parameters for policy network
+        self.observed_true_states = set()  # Set of observed true states
+        
+        # Global variables for action logits and neighbor action logits
[…]

### 2025-05-26 code/further+/modules/simulation.py

@@ -1,0 +1,506 @@
+"""
+Core simulation logic for POLARIS experiments.
+"""
+
+import numpy as np
+import time
+import torch
+from tqdm import tqdm
+from modules.utils import (
+    create_output_directory,
+    calculate_observation_dimension,
+    encode_observation, 
+    setup_random_seeds,
+    calculate_theoretical_bounds,
+    display_theoretical_bounds,
+    write_config_file,
+    flatten_episodic_metrics,
+    save_final_models,
+    save_checkpoint_models,
+    set_metrics,
+    reset_agent_internal_states,
+    update_total_rewards,
+    select_agent_actions,
+    update_progress_display,
+    store_transition_in_buffer,
+    load_agent_models)
+from modules.metrics import (
+    initialize_metrics, 
+    update_metrics, 
+    calculate_agent_learning_rates_from_metrics,
+    display_learning_rate_summary,
+    prepare_serializable_metrics,
+    save_metrics_to_file
+)
+from modules.plotting import generate_plots
+from modules.agent import POLARISAgent
+from modules.networks import TemporalGNN
+from modules.replay_buffer import ReplayBuffer
+
+def run_agents(env, args, training=True, model_path=None):
+    """
+    Run POLARIS agents in the social learning environment.
+    
+    Args:
+        env: The social learning environment
+        args: Command-line arguments
+        training: Whether to train the agents (True) or just evaluate (False)
+        model_path: Path to load models from (optional)
+    
+    Returns:
+        learning_rates: Dictionary of learning rates for each agent
+        serializable_metrics: Dictionary of metrics for JSON serialization
+    """
+    # Setup directory
+    output_dir = create_output_directory(args, env, training)
+    
+    # Initialize agents and metrics
+    obs_dim = calculate_observation_dimension(env)
+    agents = initialize_agents(env, args, obs_dim)
+    load_agent_models(agents, model_path, env.num_agents, training=training)
+    metrics = initialize_metrics(env, args, training)
+
+    # Calculate and display theoretical bounds
+    theoretical_bounds = calculate_theoretical_bounds(env)
+    display_theoretical_bounds(theoretical_bounds)
+    
+    replay_buffers = initialize_replay_buffers(agents, args, obs_dim)
+
+    # Write configuration if training
+    if training:
+        write_config_file(args, env, theoretical_bounds, output_dir)
+
+
+    print(f"Running {args.num_episodes} episode(s) with {args.horizon} steps per episode")
+    
[…]

### 2025-05-26 code/further+/test_ewc.py

@@ -1,0 +1,136 @@
+#!/usr/bin/env python3
+"""
+Test script for Elastic Weight Consolidation (EWC) in POLARIS.
+
+This script runs a series of experiments to test the EWC implementation 
+for mitigating catastrophic forgetting in the POLARIS framework.
+"""
+
+import os
+import torch
+import numpy as np
+import matplotlib.pyplot as plt
+from pathlib import Path
+import argparse
+
+from modules.environment import SocialLearningEnvironment
+from modules.args import parse_args
+from modules.simulation import run_agents
+
+
+def main():
+    """Main function to run EWC experiments."""
+    # Parse command-line arguments but override for our specific test
+    args = parse_args()
+    
+    # Set specific parameters for EWC testing
+    args.exp_name = "ewc_test"
+    args.num_agents = 2
+    args.network_type = 'complete'
+    args.save_model = True
+    args.use_gnn = True
+    args.horizon = 1000
+    args.num_episodes = 4
+    
+    # Run experiments with different EWC settings
+    run_ewc_experiment(args, use_ewc=False, ewc_online=False, name="baseline")
+    run_ewc_experiment(args, use_ewc=True, ewc_online=False, name="standard_ewc")
+    run_ewc_experiment(args, use_ewc=True, ewc_online=True, name="online_ewc")
+    
+    # Compare results
+    plot_comparison(args)
+    
+    
+def run_ewc_experiment(args, use_ewc, ewc_online, name):
+    """Run an experiment with specific EWC settings."""
+    # Set EWC parameters
+    args.use_ewc = use_ewc
+    args.ewc_online = ewc_online
+    args.ewc_lambda = 100.0
+    args.ewc_gamma = 0.95
+    args.exp_name = f"ewc_test_{name}"
+    
+    print(f"\n{'='*80}\nRunning experiment: {args.exp_name}")
+    print(f"EWC enabled: {args.use_ewc}, Online mode: {args.ewc_online}\n{'='*80}\n")
+    
+    # Set random seed for reproducibility
+    torch.manual_seed(args.seed)
+    np.random.seed(args.seed)
+    
+    # Create environment with varying true states to test catastrophic forgetting
+    env = SocialLearningEnvironment(
+        num_agents=args.num_agents,
+        signal_accuracy=args.signal_accuracy,
+        network_type=args.network_type,
+        network_params={'density': args.network_density} if args.network_type == 'random' else None,
[…]

### 2025-05-26 code/further/analyze_learning_rates.py

@@ -1,0 +1,356 @@
+import numpy as np
+import torch
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+import argparse
+import os
+import json
+
+from partially_observable_further import PartiallyObservableFURTHER
+from learning_without_experimentation import LearningWithoutExperimentationEnv
+from training_script import flatten_observation
+
+def exponential_decay(t, r):
+    """Exponential decay function e^(-rt) for fitting learning rates"""
+    return np.exp(-r * t)
+
+def calculate_mistake_probabilities(env, agents, num_timesteps=100, num_episodes=20):
+    """
+    Calculate mistake probabilities for each agent at each timestep
+    
+    Returns:
+        mistake_probs: numpy array of shape (num_agents, num_timesteps) with average mistake probabilities
+    """
+    num_agents = len(agents)
+    true_state = env.true_state
+    
+    # Initialize arrays to store mistake probabilities
+    all_mistake_probs = np.zeros((num_episodes, num_agents, num_timesteps))
+    
+    for episode in range(num_episodes):
+        # Reset environment and get initial observations
+        observations = env.reset()
+        true_state = env.true_state  # Get the ground truth state for this episode
+        
+        flat_observations = [flatten_observation(obs, 'learning', env.num_states) for obs in observations]
+        
+        # Initialize model states
+        hidden_states = [None for _ in range(num_agents)]
+        latent_strategies = [np.zeros(5) for _ in range(num_agents)]
+        actions = [0 for _ in range(num_agents)]
+        
+        # Run for specified number of timesteps
+        for t in range(num_timesteps):
+            # Process actions
+            processed_actions = []
+            for i, action in enumerate(actions):
+                if isinstance(action, int):
+                    one_hot = np.zeros(env.num_states)
+                    one_hot[action] = 1
+                    processed_actions.append(one_hot)
+                else:
+                    processed_actions.append(action)
+            
+            # Update belief states and record action probabilities
+            for i in range(num_agents):
+                # Update belief state
+                belief, hidden = agents[i].update_belief(
+                    flat_observations[i],
+                    processed_actions[i],
+                    hidden_states[i]
+                )
+                hidden_states[i] = hidden
+                
+                # Get other agents' actions
+                other_actions = np.concatenate([
[…]

### 2025-05-26 code/further/compare_network_sizes.py

@@ -1,0 +1,273 @@
+import subprocess
+import os
+import argparse
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+def exponential_decay(t, r):
+    """Exponential decay function e^(-rt) for fitting learning rates"""
+    return np.exp(-r * t)
+
+def run_single_experiment(env_type, num_agents, num_states, num_timesteps, signal_accuracy, output_dir):
+    """
+    Run a single experiment with specified parameters
+    
+    Args:
+        env_type: Environment type ('learning' or 'strategic')
+        num_agents: Number of agents
+        num_states: Number of states
+        num_timesteps: Number of timesteps
+        signal_accuracy: Accuracy of private signals
+        output_dir: Directory to save results
+    
+    Returns:
+        result_dir: Path to the results directory
+    """
+    # Create output directory
+    result_dir = os.path.join(output_dir, f"{num_agents}_agents")
+    os.makedirs(result_dir, exist_ok=True)
+    
+    # Build command
+    cmd = [
+        "python", "training_with_mistake_tracking.py",
+        "--env", env_type,
+        "--agents", str(num_agents),
+        "--states", str(num_states),
+        "--timesteps", str(num_timesteps),
+        "--eval-interval", str(num_timesteps // 10),  # Evaluate 10 times during training
+        "--log-interval", str(num_timesteps // 100),  # Log 100 times during training
+        "--save-path", result_dir,
+        "--signal-accuracy", str(signal_accuracy)
+    ]
+    
+    # Run experiment
+    print(f"Running experiment with {num_agents} agents...")
+    subprocess.run(cmd)
+    
+    return result_dir
+
+def fit_learning_rate_to_mistakes(mistake_probs, window_ratio=0.2):
+    """
+    Fit learning rate to mistake probabilities over a window
+    
+    Args:
+        mistake_probs: Numpy array of mistake probabilities
+        window_ratio: Ratio of timesteps to use for window size
+    
+    Returns:
+        rate: Estimated learning rate
+    """
+    # Get dimensions
+    num_timesteps, num_agents = mistake_probs.shape
+    
+    # Calculate window size (at least 50 timesteps)
+    window_size = max(50, int(num_timesteps * window_ratio))
+    
+    # Use second half of training to fit learning rate
+    start_idx = num_timesteps - window_size
+    if start_idx < 0:
+        start_idx = 0
+    
[…]

### 2025-05-26 code/further/learning_without_experimentation.py

@@ -1,0 +1,209 @@
+import numpy as np
+import gym
+from gym import spaces
+import networkx as nx
+
+class LearningWithoutExperimentationEnv(gym.Env):
+    """
+    Multi-agent environment for learning without experimentation.
+    
+    Agents receive private signals about a fixed state of the world and observe
+    the actions of their neighbors, but don't receive direct rewards from their actions.
+    """
+    
+    def __init__(self, num_agents=5, num_states=2, signal_accuracy=0.7, 
+                 network_type='complete', directed=False):
+        """
+        Initialize the environment.
+        
+        Args:
+            num_agents: Number of agents
+            num_states: Number of possible states of the world
+            signal_accuracy: Accuracy of private signals
+            network_type: Type of network topology ('complete', 'line', 'star', 'ring')
+            directed: Whether the network is directed
+        """
+        super(LearningWithoutExperimentationEnv, self).__init__()
+        
+        self.num_agents = num_agents
+        self.num_states = num_states
+        self.signal_accuracy = signal_accuracy
+        
+        # Create social network
+        self.network = self._create_network(network_type, directed)
+        
+        # Define action and observation spaces
+        # Actions are discrete choices corresponding to states
+        self.action_space = spaces.Discrete(num_states)
+        
+        # Observations consist of private signal and neighbor actions
+        # Private signal is one-hot encoding of observed state
+        # Neighbor actions are one-hot encodings of their last actions
+        max_neighbors = max(len(list(self.network.neighbors(i))) for i in range(num_agents))
+        self.observation_space = spaces.Dict({
+            'private_signal': spaces.Box(low=0, high=1, shape=(num_states,), dtype=np.float32),
+            'neighbor_actions': spaces.Box(low=0, high=1, 
+                                         shape=(max_neighbors, num_states), dtype=np.float32)
+        })
+        
+        # Initialize state
+        self.reset()
+        
+    def _create_network(self, network_type, directed):
+        """Create the social network based on the specified topology"""
+        if network_type == 'complete':
+            G = nx.complete_graph(self.num_agents)
+        elif network_type == 'line':
+            G = nx.path_graph(self.num_agents)
+        elif network_type == 'star':
+            G = nx.star_graph(self.num_agents - 1)
+        elif network_type == 'ring':
+            G = nx.cycle_graph(self.num_agents)
+        else:
+            raise ValueError(f"Unknown network type: {network_type}")
+            
+        if directed and not G.is_directed():
+            G = G.to_directed()
+            
+        return G
+    
+    def reset(self):
[…]

### 2025-05-26 code/further/partially_observable_further.py

@@ -1,0 +1,771 @@
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+from torch.distributions import Categorical, Normal
+from collections import deque, namedtuple
+import random
+
+# Device configuration
+device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+
+# Experience replay buffer
+Experience = namedtuple('Experience', 
+                        ('observation', 'latent_strategies', 'action', 'other_actions', 
+                         'reward', 'next_observation', 'next_latent_strategies'))
+
+class ReplayBuffer:
+    def __init__(self, capacity):
+        self.buffer = deque(maxlen=capacity)
+        
+    def push(self, *args):
+        self.buffer.append(Experience(*args))
+        
+    def sample(self, batch_size):
+        return random.sample(self.buffer, batch_size)
+    
+    def __len__(self):
+        return len(self.buffer)
+
+# Belief state representation using GRU
+class BeliefStateNetwork(nn.Module):
+    def __init__(self, observation_dim, action_dim, hidden_dim):
+        super(BeliefStateNetwork, self).__init__()
+        self.observation_dim = observation_dim
+        self.action_dim = action_dim
+        self.input_dim = observation_dim + action_dim
+        self.gru = nn.GRU(self.input_dim, hidden_dim, batch_first=True)
+        self.hidden_dim = hidden_dim
+        self.hidden_state = None
+        
+    def initialize_hidden(self, batch_size=1):
+        return torch.zeros(1, batch_size, self.hidden_dim, device=device)
+        
+    def forward(self, observation, action, hidden=None):
+        if hidden is None and self.hidden_state is None:
+            # Initialize hidden state based on batch size
+            batch_size = observation.shape[0] if observation.dim() > 1 else 1
+            self.hidden_state = self.initialize_hidden(batch_size)
+        elif hidden is not None:
+            self.hidden_state = hidden
+        
+        # Ensure both tensors are properly shaped for GRU
+        if observation.dim() == 1:
+            observation = observation.unsqueeze(0)  # Add batch dimension
+        if action.dim() == 1:
+            action = action.unsqueeze(0)  # Add batch dimension
+            
+        # Handle case where action has extra dimensions (e.g., from one-hot encoding)
+        if action.dim() == 3:
+            action = action.squeeze(1)
+            
+        # Check if batch sizes match
+        if observation.shape[0] != action.shape[0]:
+            # Adjust smaller tensor to match larger one
[…]

### 2025-05-26 code/further/plot_learning_rates.py

@@ -1,0 +1,310 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import json
+import argparse
+import os
+from scipy.optimize import curve_fit
+
+def exponential_decay(t, r):
+    """Exponential decay function e^(-rt) for fitting learning rates"""
+    return np.exp(-r * t)
+
+def plot_mistake_probabilities(mistake_probs_file, output_dir='.'):
+    """
+    Plot mistake probabilities over time for each agent
+    
+    Args:
+        mistake_probs_file: Path to numpy file with mistake probabilities
+        output_dir: Directory to save plots
+    """
+    # Load mistake probabilities
+    mistake_probs = np.load(mistake_probs_file)
+    
+    # Get dimensions
+    num_timesteps, num_agents = mistake_probs.shape
+    
+    # Plot overall average
+    plt.figure(figsize=(12, 6))
+    avg_mistakes = np.mean(mistake_probs, axis=1)
+    plt.plot(np.arange(num_timesteps), avg_mistakes)
+    plt.title('Average Mistake Probability Across All Agents')
+    plt.xlabel('Timestep')
+    plt.ylabel('Mistake Probability')
+    plt.grid(True, alpha=0.3)
+    plt.yscale('log')  # Log scale to better see exponential decay
+    
+    # Add trendline
+    try:
+        # Fit exponential decay
+        params, _ = curve_fit(
+            exponential_decay, 
+            np.arange(num_timesteps), 
+            avg_mistakes,
+            p0=[0.0001],  # Initial guess for rate
+            bounds=(0, np.inf)  # Rate must be positive
+        )
+        
+        rate = params[0]
+        fit_curve = exponential_decay(np.arange(num_timesteps), rate)
+        plt.plot(np.arange(num_timesteps), fit_curve, 'r--', 
+                 label=f'Exponential fit: r = {rate:.6f}')
+        plt.legend()
+    except:
+        print("Warning: Could not fit exponential decay to average mistakes")
+    
+    plt.tight_layout()
+    plt.savefig(os.path.join(output_dir, 'average_mistake_probability.png'))
+    plt.close()
+    
+    # Plot for each agent
+    plt.figure(figsize=(14, 8))
+    
+    for i in range(num_agents):
+        plt.plot(np.arange(num_timesteps), mistake_probs[:, i], label=f'Agent {i+1}')
+    
[…]

### 2025-05-26 code/further/strategic_experimentation.py

@@ -1,0 +1,166 @@
+import numpy as np
+import gym
+from gym import spaces
+
+class StrategicExperimentationEnv(gym.Env):
+    """
+    A multi-agent environment for strategic experimentation based on Keller et al. (2020).
+    
+    Each agent faces a two-armed bandit problem where they continuously allocate their resources
+    between a safe arm with known payoff and a risky arm whose expected payoff depends on
+    an unknown state of the world.
+    """
+    
+    def __init__(self, num_agents=2, state_levels=2, observation_dim=3, action_dim=1, 
+                 safe_payoff=1, risky_payoffs=None, noise_std=0.1, signal_accuracy=0.8):
+        super(StrategicExperimentationEnv, self).__init__()
+        
+        self.num_agents = num_agents
+        self.state_levels = state_levels
+        self.observation_dim = observation_dim
+        self.action_dim = action_dim
+        self.safe_payoff = safe_payoff
+        
+        # If risky payoffs not provided, generate them
+        if risky_payoffs is None:
+            self.risky_payoffs = np.linspace(0, 2 * safe_payoff, state_levels)
+        else:
+            self.risky_payoffs = risky_payoffs
+            
+        self.noise_std = noise_std
+        self.signal_accuracy = signal_accuracy
+        
+        # Define action and observation spaces
+        self.action_space = spaces.Box(low=0, high=1, shape=(action_dim,), dtype=np.float32)
+        self.observation_space = spaces.Box(low=-np.inf, high=np.inf, 
+                                           shape=(observation_dim,), dtype=np.float32)
+        
+        # Initialize state
+        self.reset()
+        
+    def reset(self):
+        """Reset the environment and return initial observations"""
+        # Draw random state of the world
+        self.true_state = np.random.randint(0, self.state_levels)
+        self.true_risky_payoff = self.risky_payoffs[self.true_state]
+        
+        # Initialize observations for all agents
+        observations = []
+        for _ in range(self.num_agents):
+            # Generate private signal about the state
+            if np.random.random() < self.signal_accuracy:
+                observed_state = self.true_state
+            else:
+                # Draw from other states uniformly
+                other_states = list(range(self.state_levels))
+                other_states.remove(self.true_state)
+                observed_state = np.random.choice(other_states)
+            
+            # Initial observation includes:
+            # 1. Private signal (one-hot encoding of observed state)
+            # 2. Safe payoff (known)
+            # 3. Placeholder for observed rewards (initially 0)
[…]

### 2025-05-26 code/further/theoretical_bounds.py

@@ -1,0 +1,184 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import argparse
+
+def calculate_mutual_information(q):
+    """
+    Calculate mutual information between state and private signal
+    
+    Args:
+        q: signal accuracy
+        
+    Returns:
+        I: mutual information
+    """
+    if q <= 0.5 or q >= 1:
+        return 0.0
+    
+    # For binary state/signal setting, mutual information is:
+    # I(S;X) = H(X) - H(X|S)
+    # For binary symmetric channel with error probability 1-q:
+    h_x_given_s = -(q * np.log2(q) + (1-q) * np.log2(1-q))
+    h_x = 1  # Binary entropy is 1 bit
+    
+    return h_x - h_x_given_s
+
+def calculate_learning_rate_bound(q, n_neighbors, network_type='complete'):
+    """
+    Calculate theoretical upper bound on learning rate
+    
+    Args:
+        q: signal accuracy
+        n_neighbors: number of neighbors
+        network_type: type of network ('complete', 'star', etc.)
+        
+    Returns:
+        r_bound: theoretical upper bound on learning rate
+    """
+    # Calculate mutual information from private signal
+    I = calculate_mutual_information(q)
+    
+    # Factor for network structure
+    if network_type == 'complete':
+        # In complete network, all agents observe all others
+        # The bound scales with the number of neighbors
+        network_factor = 1 + 0.5 * n_neighbors
+    elif network_type == 'star':
+        # In star network, center sees all, leaves see only center
+        network_factor = 2.0  # Simplified approximation
+    else:
+        # Default case
+        network_factor = 1.0
+    
+    # Calculate bound from social learning barrier paper
+    r_bound = I * network_factor
+    
+    return r_bound
+
+def plot_learning_rate_vs_accuracy(n_neighbors_list=[1, 2, 4, 8], network_type='complete'):
+    """
+    Plot learning rate bound as a function of signal accuracy
+    
+    Args:
+        n_neighbors_list: list of number of neighbors to plot
+        network_type: type of network
+    """
+    # Signal accuracy range
+    q_range = np.linspace(0.5, 1.0, 100)
+    
+    plt.figure(figsize=(10, 6))
+    
+    for n_neighbors in n_neighbors_list:
+        # Calculate bounds for each accuracy
[…]

### 2025-05-26 code/further/train_multiple_networks.py

@@ -1,0 +1,76 @@
+import os
+import subprocess
+import argparse
+
+def train_network(num_agents, num_states, num_episodes, eval_interval, save_path, signal_accuracy=0.7):
+    """
+    Train a network configuration with specified parameters
+    
+    Args:
+        num_agents: Number of agents in the network
+        num_states: Number of states in the environment
+        num_episodes: Number of training episodes
+        eval_interval: Evaluation interval
+        save_path: Path to save models
+        signal_accuracy: Accuracy of private signals
+    """
+    # Create directory for this configuration if it doesn't exist
+    config_dir = os.path.join(save_path, f"{num_agents}_agents")
+    os.makedirs(config_dir, exist_ok=True)
+    
+    # Build command to run training script
+    cmd = [
+        "python", "training_script.py",
+        "--env", "learning",
+        "--agents", str(num_agents),
+        "--states", str(num_states),
+        "--episodes", str(num_episodes),
+        "--eval-interval", str(eval_interval),
+        "--save-path", config_dir
+    ]
+    
+    # Run training
+    print(f"Training network with {num_agents} agents...")
+    subprocess.run(cmd)
+    print(f"Training complete for {num_agents} agents. Models saved to {config_dir}.")
+
+def main():
+    parser = argparse.ArgumentParser(description='Train multiple network configurations')
+    parser.add_argument('--agents', type=str, default='2,3,5,9',
+                       help='Comma-separated list of numbers of agents to train')
+    parser.add_argument('--states', type=int, default=2,
+                       help='Number of states in the environment')
+    parser.add_argument('--episodes', type=int, default=1000,
+                       help='Number of training episodes')
+    parser.add_argument('--eval-interval', type=int, default=10,
+                       help='Evaluation interval')
+    parser.add_argument('--save-path', type=str, default='./trained_networks',
+                       help='Path to save models')
+    parser.add_argument('--signal-accuracy', type=float, default=0.7,
+                       help='Accuracy of private signals')
+    
+    args = parser.parse_args()
+    
+    # Parse number of agents
+    num_agents_list = [int(n) for n in args.agents.split(',')]
+    
+    # Create base directory if it doesn't exist
+    os.makedirs(args.save_path, exist_ok=True)
+    
+    # Train each network configuration
+    for num_agents in num_agents_list:
+        train_network(
+            num_agents=num_agents,
+            num_states=args.states,
+            num_episodes=args.episodes,
[…]

### 2025-05-26 code/further/training_script.py

@@ -1,0 +1,433 @@
+import numpy as np
+import torch
+import matplotlib.pyplot as plt
+from collections import deque
+import time
+import argparse
+
+# Import our modules - make sure these match your file names
+from partially_observable_further import PartiallyObservableFURTHER
+from strategic_experimentation import StrategicExperimentationEnv
+from learning_without_experimentation import LearningWithoutExperimentationEnv
+
+def flatten_observation(obs, env_type, num_states):
+    """Helper function to flatten observations for different environment types"""
+    if env_type == 'strategic':
+        # For strategic environment, ensure observation is the correct shape
+        if isinstance(obs, np.ndarray):
+            return obs.flatten()  # Flatten to 1D array to ensure consistent shape
+        else:
+            return np.array(obs).flatten()
+    elif env_type == 'learning':
+        # Concatenate private signal and flattened neighbor actions
+        return np.concatenate([
+            obs['private_signal'],
+            obs['neighbor_actions'].flatten()
+        ])
+
+def preprocess_action(action, env_type, num_states):
+    """Helper function to preprocess actions for different environment types"""
+    if env_type == 'strategic':
+        # Ensure action is a flat array of the correct shape
+        if isinstance(action, (int, float)):
+            return np.array([action])
+        elif isinstance(action, np.ndarray):
+            return action.flatten()
+        else:
+            return np.array([action])
+    elif env_type == 'learning':
+        # Convert discrete action to one-hot
+        if isinstance(action, int) and action < num_states:
+            one_hot = np.zeros(num_states)
+            one_hot[action] = 1
+            return one_hot
+        elif isinstance(action, np.ndarray) and action.size == 1:
+            idx = int(action.item())
+            one_hot = np.zeros(num_states)
+            one_hot[idx] = 1
+            return one_hot
+        else:
+            # If already one-hot or otherwise formatted, ensure it's correct shape
+            return np.array(action).flatten()[:num_states]
+
+def train_agents(env_type='strategic', num_agents=2, num_states=2, num_episodes=1000, 
+                eval_interval=10, render=False, save_path=None):
+    """
+    Train agents using the Partially Observable FURTHER algorithm
+    
+    Args:
+        env_type: Type of environment ('strategic' or 'learning')
+        num_agents: Number of agents
+        num_states: Number of states
+        num_episodes: Number of training episodes
+        eval_interval: Evaluate every n episodes
+        render: Whether to render the environment
+        save_path: Path to save the trained models
+    """
+    # Create environment
+    if env_type == 'strategic':
[…]

### 2025-05-26 code/further/training_with_mistake_tracking.py

@@ -1,0 +1,424 @@
+import numpy as np
+import torch
+import matplotlib.pyplot as plt
+from collections import deque
+import time
+import argparse
+import os
+import json
+
+# Import our modules
+from partially_observable_further import PartiallyObservableFURTHER, device
+from strategic_experimentation import StrategicExperimentationEnv
+from learning_without_experimentation import LearningWithoutExperimentationEnv
+from training_script import flatten_observation, preprocess_action
+from scipy.optimize import curve_fit
+
+# Function to model exponential decay for fitting
+def exponential_decay(t, r):
+    """Exponential decay function e^(-rt) for fitting learning rates"""
+    return np.exp(-r * t)
+
+def train_agents_with_mistake_tracking(
+    env_type='learning', 
+    num_agents=2, 
+    num_states=2, 
+    num_timesteps=20000,  # Total timesteps for continuing task
+    eval_interval=1000, 
+    tracking_window=100,  # Window for calculating moving average of mistakes
+    log_interval=100,     # How often to log mistake probabilities
+    render=False, 
+    save_path=None,
+    signal_accuracy=0.7
+):
+    """
+    Train agents using the Partially Observable FURTHER algorithm and track mistake probabilities
+    
+    Args:
+        env_type: Type of environment ('strategic' or 'learning')
+        num_agents: Number of agents
+        num_states: Number of states
+        num_timesteps: Total timesteps for training (for continuing tasks)
+        eval_interval: Evaluate every n timesteps
+        tracking_window: Window size for calculating moving average of mistakes
+        log_interval: How often to log mistake probabilities
+        render: Whether to render the environment
+        save_path: Path to save the trained models
+        signal_accuracy: Accuracy of private signals (for learning environment)
+    """
+    # Create environment
+    if env_type == 'strategic':
+        env = StrategicExperimentationEnv(num_agents=num_agents, state_levels=num_states)
+        observation_dim = env.observation_space.shape[0]
+        action_dim = env.action_space.shape[0]
+        discrete_actions = False
+    elif env_type == 'learning':
+        env = LearningWithoutExperimentationEnv(
+            num_agents=num_agents, 
+            num_states=num_states,
+            signal_accuracy=signal_accuracy
+        )
+        observation_dim = num_states + num_agents * num_states  # Private signal + neighbor actions
+        action_dim = num_states
+        discrete_actions = True
+    else:
[…]

### 2025-05-26 code/multi_agent/main.py

@@ -14,7 +14,7 @@ save_folder.mkdir(exist_ok=True)  # Create folder if it doesn't exist
 if __name__ == "__main__":
     # Train with metrics tracking
     num_agents = 4
-    num_steps = 1000
+    num_steps = 10000
     signal_accuracies = [0.75]
 
     for signal_accuracy in signal_accuracies:

### 2025-06-05 paper/results.tex
Update results.

@@
 By reformulating these economic models as POAMGs, we demonstrate how our framework can capture the sophisticated learning dynamics present in these scenarios while enabling the discovery of complex strategies through our POLARIS algorithm.
-\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/POLARIS}.}
+\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/polaris}.}
+
+\section{Methodological Framework and Challenges}
+
+Before presenting our experimental results, we must address two fundamental challenges that arise when applying reinforcement learning to social learning environments.
+These challenges stem from a fundamental mismatch between the strategic requirements of economic theory and the constraints of computational implementation, ultimately necessitating a novel experimental methodology that focuses on within-episode dynamics rather than cross-episode equilibrium convergence.
+
+\subsection{Ex Ante Strategy Optimization vs Ex Post Convergence}
+
+Implementing reinforcement learning in social learning environments reveals a fundamental tension between economic theory and computational practice.
+In economic social learning models, agents are expected to develop strategies that perform optimally across all possible states of the world—an ex ante perspective where the optimal strategy accounts for uncertainty about which state will be realized.
+Such strategies require maintaining flexibility and developing sophisticated mixed approaches that can respond appropriately whether the true state turns out to be A or B, good or bad.
+
+However, our computational implementation reveals that agents instead converge to state-specific optimal allocations—an ex post perspective where behavior is optimized for the particular state that has been realized.
+This distinction creates a critical incompatibility in binary social learning environments we consider here.
+In strategic experimentation, if the risky arm is revealed to be good, rational agents should allocate all resources to it; conversely, if it performs poorly, optimal behavior requires complete avoidance.
+In learning without experimentation, once the true state is A, the optimal action is unambiguously action A, while in state B, only action B is rational.
+These ex post strategies are not merely different from the ex ante approach—they are fundamentally incompatible policy objectives that cannot be reconciled through standard learning approaches.
+
+The computational challenge emerges because reinforcement learning agents, operating within our episodic framework, can only observe and learn from one realized state per episode.
+This structure forces agents away from developing the sophisticated ex ante strategies characterized in the theoretical models toward state-specific ex post optimization.
+Instead of learning "if state = A, do X; if state = B, do Y" as economic theory prescribes, agents learn "do X" during episodes initialized with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.
+
+A natural approach to analyzing multi-agent strategic behavior in these environments would be to evaluate reinforcement learning models that are trained across different belief states or environmental configurations.
+This methodology could theoretically enable us to examine how agents would behave under the full spectrum of possible conditions, potentially revealing the sophisticated mixed strategies and state-contingent policies that characterize optimal ex ante behavior in economic theory.
+To test this approach, we attempted to recover ex ante policy analysis by inverting a linear grid of possible beliefs into latent belief representations and feeding these directly into trained policy networks.
+The goal was to evaluate how agents would behave across the full spectrum of possible belief states, potentially revealing the sophisticated mixed strategies characteristic of economic equilibria.
+However, this approach consistently failed as the trained networks would invariably follow the optimal action corresponding to the last true state they were trained on, regardless of the belief input provided.
+This confirmed that the learned policies had become fundamentally state-specific rather than developing the belief-contingent strategies required for ex ante optimization, making model evaluation for ex ante analysis impossible due to the underlying technical constraint of catastrophic forgetting.
+
+\subsection{Catastrophic Forgetting in Fixed-State Social Learning}
+
+The ex ante versus ex post discrepancy described above manifests as a severe technical challenge when implementing reinforcement learning in these environments: catastrophic forgetting.
+Since the behavioral requirements for different state realizations are diametrically opposed, continuous training across episodes with different realized states inevitably leads to catastrophic forgetting.
+Each episode's learning systematically destroys the value functions and policies acquired in previous episodes with different state realizations, preventing the emergence of stable, discriminative strategies that could respond appropriately to environmental uncertainty as economic theory requires.
+
+To address this fundamental limitation, we explored several established catastrophic forgetting mitigation techniques \citep{vandeven2024continuallearningcatastrophicforgetting}, including Elastic Weight Consolidation \citep{kirkpatrick2017overcoming}, Synaptic Intelligence \citep{zenke2017continuallearningsynapticintelligence}, alternating state presentation schedules, and state-aware replay buffers that integrate experiences from previous environmental configurations.
+However, these approaches proved ineffective because they assume some degree of transferability or compatibility between learning tasks.
+When ex post optimal policies require completely opposite actions across states, traditional continual learning techniques cannot meaningfully "consolidate" or "protect" previous learning without fundamentally undermining current learning objectives.
+
+This constraint necessitates resetting agents at the beginning of each episode rather than allowing continuous learning across episodes, which limits our ability to directly evaluate the sophisticated equilibrium strategies described in both \citet{keller2020undiscounted} and related theoretical work.
+These equilibria require agents to maintain stable ex ante strategies that can discriminate between environmental conditions and respond appropriately—capabilities that prove incompatible with standard reinforcement learning when agents can only experience one state realization per episode.
+Consequently, our experimental methodology focuses on within-episode learning dynamics and cross-episode pattern analysis to extract meaningful insights about multi-agent strategic behavior despite these fundamental constraints.
+
+\subsection{Two-Staged Analysis Methodology}
+\label{sec:two-staged-analysis}
+
+To address the catastrophic forgetting limitation while still extracting meaningful insights about multi-agent learning patterns, we adopt a consistent two-staged analysis approach across both experimental scenarios.
+This methodology enables robust characterization of learning dynamics despite the fundamental constraints of applying reinforcement learning to environments with fixed but episode-varying states.
+
+\paragraph{Stage 1: Within-Episode Role Identification} For each episode $k$, we identify agents that exhibit extreme performance characteristics.
+In strategic experimentation, we track cumulative allocation patterns:
+\begin{equation}
+    i_{\text{high}}^k = \arg\max_i \sum_{t=1}^T a_{t,k}^i, \quad 
+    i_{\text{low}}^k = \arg\min_i \sum_{t=1}^T a_{t,k}^i
+\end{equation}
+
+In learning without experimentation, we identify the fastest and slowest learning agents by fitting learning rates:
+\begin{equation}
+    i_{\text{fast}}^k = \arg\max_i r_k^i, \quad 
+    i_{\text{slow}}^k = \arg\min_i r_k^i
+\end{equation}
+where $r_k^i$ is agent $i$'s learning rate in episode $k$.
+
+\paragraph{Stage 2: Cross-Episode Pattern Aggregation} We then aggregate the performance of identified extreme agents across episodes to examine systematic patterns:
+\begin{equation}
+    \bar{P}_t^{\text{extreme}} = \frac{1}{n_{\text{episodes}}} \sum_{k=1}^{n_{\text{episodes}}} P_{t,k}^{i_{\text{extreme}}^k}
+\end{equation}
+where $P_{t,k}^i$ represents the relevant performance metric (cumulative allocation, learning accuracy, etc.) for agent $i$ at time $t$ in episode $k$.
+
+This methodology reveals whether observed disparities represent structural features of multi-agent learning or merely artifacts of specific agent characteristics, as different agents assume extreme roles across different episodes.
 
@@
 The state space $S = \{0,1,\ldots,m\}$ represents possible states of the world, with a deterministic transition function since the underlying state remains constant throughout the interaction.
-Each agent's action space $A^i = [0,1]$ represents the fraction of resources allocated to the risky arm at each decision point, creating a continuous action space that allows for nuanced exploration strategies.
+Each agent's action space in the theoretical model is $A^i = [0,1]$ representing the fraction of resources allocated to the risky arm at each decision point.
 
 While the original model operates in continuous time with Lévy processes, our POAMG implementation discretizes time using the Euler-Maruyama scheme \citep{kloeden1992numerical, platen1999introduction} for both the background signal and the agents' payoff processes.
-This numerical method is widely used for approximating solutions to stochastic differential equations driven by both Brownian motion and Poisson processes.
+However, to enable reinforcement learning with discrete action spaces, we implement a practical discretization where agents choose between two actions: "allocate to risky arm" (action 1) or "allocate to safe arm" (action 0).
+The probability of selecting action 1 serves as the continuous allocation parameter, allowing us to recover the continuous allocation behavior while maintaining compatibility with discrete policy networks.
 
@@
 Each agent observes the increments in the public background signal, their own payoff process (dependent on their allocation $a^i$ to the risky arm and the true state $\omega$), and the allocations together with the rewards of all other agents.
-The unique feature of the strategic experimentation model is the explicit form of the symmetric Markov perfect equilibrium, which depends only on three factors: the safe payoff, the expected current payoff of the risky arm, and the expected full-information payoff.
-To validate this theoretical result, we configure POLARIS to measure: (1) The cutoff belief at which agents switch between the safe and risky arm
-(2) The relationship between individual experimentation intensity and group experimentation intensity
-(3) Free-riding behavior as a function of the number of players
-(4) Strategy independence from the specific payoff-generating process
-\iffalse
-    For experimental validation, we implement three distinct payoff-generating processes that preserve the same reward statistics: pure Brownian motion with unknown drift, pure Poisson processes with unknown intensity, and mixed Lévy processes with both continuous and jump components.
-In all three cases, the theory predicts identical equilibrium strategies when expressed in terms of the incentive to experiment $I(\pi) = \frac{f(\pi)-s}{s-m(\pi)}$ when $m(\pi) < s$, and $I(\pi) = \infty$ otherwise, where $\pi$ represents the belief state.
-\fi
-To measure convergence to equilibrium behavior, we track the Kullback-Leibler divergence (KL divergence) between agents' actual strategies and the theoretically optimal strategy specified in Keller and Rady's work.
-The KL divergence is calculated as
+For continuous signals, POLARIS agents use a specialized transformer loss function that computes the expected signal distribution based on the current belief state and environment parameters, enabling principled belief updating in response to Lévy process observations.
 
-\begin{equation}
-    D_{KL}(P||Q) = \sum_{x} P(x) \log\frac{P(x)}{Q(x)},
-\end{equation}
+\subsection{Experimental Setup}
 
-where $P$ represents the agent's learned policy distribution and $Q$ represents the theoretical optimal policy distribution at each belief state:
+We implement comprehensive experiments using specialized experimental frameworks for both detailed single-configuration analysis and comparative analysis across different group sizes.
+Our experimental protocol examines group sizes of $n \in \{1, 2, 4, 8\}$ agents; safe payoff of $r_{\text{safe}} = 0.5$; drift rates of $[0, 1]$ for bad and good states respectively; jump rates of $[0, 0.1]$ with jump sizes of $[1.0, 1.0]$; background informativeness of $k_0 = 0.001$; and time discretization step of $\Delta t = 1.0$.
 
-\begin{equation}
-    a^*(b) =
-    \begin{cases}
-        0                    & \text{if } I(b) \leq k_0,            \\
-        \frac{I(b)-k_0}{n-1} & \text{if } k_0 < I(b) < k_0 + n - 1, \\
-        1                    & \text{if } I(b) \geq k_0 + n - 1.
-    \end{cases}
-\end{equation}
+Following our two-staged analysis methodology, the POLARIS implementation tracks: (1) Convergence of individual agent allocation strategies to state-dependent optimal actions within episodes; (2) Belief fluctuations over time to assess the impact of neighbor action observation on learning; (3) Cumulative allocation disparities between highest and lowest allocators as a function of group size; and (4) Episode-wise analysis of allocation patterns across different true states (good vs.
+bad).
 
-\iffalse
-    We also assess the rate of social learning by measuring the expected time until agents' posterior beliefs concentrate within an $\epsilon$-neighborhood of the true state.
-The background information in this model ensures exponentially fast convergence, which is empirically validated by fitting an exponential decay curve to the mean distance between current beliefs and true state across multiple simulation runs.
-\fi
-For varying group sizes $n \in \{2,4,8,16\}$, we measure the relationship between individual and group experimentation.
-The theory predicts that the set of beliefs for which no experimentation occurs remains unchanged as $n$ increases—a stark manifestation of free-riding behavior.
-Additionally, the theory predicts that in regions of partial experimentation, the intensity per agent will decrease with $n$, while the total group intensity increases.
-These predictions create testable patterns that our POLARIS implementation can validate.
-\iffalse
-    An important methodological insight from this implementation is the impact of the background signal $k_0$ on learning dynamics.
-As $k_0$ approaches zero, the equilibrium strategy converges monotonically to a well-defined limit.
-However, without background information, the strong long-run average criterion would yield an expectation of minus infinity, making the framework inapplicable.
-We thus implement a parametric analysis with diminishing values of $k_0$ to approximate the limit behavior predicted by the theory.
-\fi
+For each configuration, we run experiments with horizon lengths of 50 steps for comparative sweeps across group sizes, focusing on the emergence of allocation patterns and their relationship to theoretical predictions.
+Our analysis emphasizes within-episode learning dynamics rather than cross-episode equilibrium convergence due to the catastrophic forgetting constraint.
+
+\subsection{Results and Analysis}
+
+Our experimental results reveal sophisticated strategic learning dynamics while highlighting key challenges in measuring theoretical equilibrium convergence in reinforcement learning settings.
+We examine three primary aspects of the learning behavior that provide insights into multi-agent strategic experimentation.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/good_belief_over_time.png}
-        \subcaption{Good state beliefs over time, demonstrating convergence to the true state.}
-        \label{fig:good_belief_over_time}
+        \includegraphics[width=\textwidth]{../code/polaris/docs/allocation_accuracy_over_time.png}
+        \subcaption{Allocation accuracy over time.}
+        \label{fig:allocation_accuracy_over_time}
     \end{minipage}
@@
         \centering
-        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/agent_allocations.png}
-        \subcaption{Agent allocations over time, demonstrating eventual adoption of the best strategy.}
-        \label{fig:agent_allocations}
+        \includegraphics[width=\textwidth]{../code/polaris/docs/belief_accuracy_over_time.png}
+        \subcaption{Belief accuracy over time.}
+        \label{fig:belief_accuracy_over_time}
     \end{minipage}
-
-    \vspace{0.3cm}
-
-    \begin{minipage}[t]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation_agents_2_gnn/network_complete_agents_2/kl_divergence.png}
-        \subcaption{KL divergence between agents' learned strategies and the theoretical optimal strategy as a function of time, demonstrating convergence to equilibrium behavior.}
-        \label{fig:kl_divergence}
-    \end{minipage}
-    \hfill
-    \begin{minipage}[t]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../code/polaris/results/strategic_experimentation/sweep_allocations/average_cumulative_allocation_per_agent_over_time.png}
-        \subcaption{Average cumulative allocation per agent over time across different network configurations, demonstrating independence from the network size.}
-        \label{fig:average_cumulative_allocation_per_agent_over_time}
-    \end{minipage}
-
     \caption{Learning dynamics in the strategic experimentation model}
@@
 
-Our experimental results confirm that POLARIS agents converge to the theoretically predicted equilibrium regardless of the specific payoff-generating process employed.
-This validation demonstrates the framework's ability to capture the sophisticated strategic considerations of undiscounted multi-agent learning, providing computational support for the theoretical predictions of Keller and Rady.
-Furthermore, our results show that the mixed Lévy process case—not analytically tractable in the original paper due to its complexity—exhibits the same qualitative behavior as the pure Brownian and Poisson cases, providing evidence for the robustness of the theoretical framework.
+\paragraph{Strategic Action Convergence} POLARIS agents successfully learn to converge toward state-dependent optimal allocation strategies.
+In good states, agents increase their allocation to the risky arm over time, while in bad states, they learn to favor the safe alternative.
+This convergence demonstrates that the discretized action representation effectively captures the continuous allocation dynamics of the theoretical model, enabling agents to discover appropriate exploration-exploitation strategies through reinforcement learning.
+
+\paragraph{Belief Dynamics and Social Learning Effects} Figure \ref{fig:belief_accuracy_over_time} reveals fluctuating belief patterns that indicate the importance of neighbor action observation in the learning process.
+These fluctuations demonstrate that agents actively incorporate information from neighbors' allocation decisions, leading to more informed belief updating compared to purely individual learning.
+The variability in belief trajectories reflects the ongoing process of social information aggregation, where agents continuously refine their understanding based on both private signals and observed neighbor behaviors.
+
+\begin{figure}[!htbp]
+    \centering
+        \includegraphics[width=\textwidth]{../code/polaris/docs/highest_lowest_cumulative_allocators_good_state.png}
+        \caption{Highest and lowest cumulative allocators in the good state.}
+        \label{fig:highest_lowest_cumulative_allocators_good_state}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/docs/highest_lowest_cumulative_allocators_bad_state.png}
+    \caption{Highest and lowest cumulative allocators in the bad state.}
+    \label{fig:highest_lowest_cumulative_allocators_bad_state}
+\end{figure}
+\paragraph{Dynamic Role Assignment and Allocation Disparities} Figures \ref{fig:highest_lowest_cumulative_allocators_good_state} and \ref{fig:highest_lowest_cumulative_allocators_bad_state} demonstrate a systematic widening of the gap between highest and lowest cumulative allocators as group size increases.
+This pattern reveals the emergence of dynamic role assignment in multi-agent learning, where agents naturally differentiate into information generators and information exploiters within each episode.
+In strategic experimentation, this manifests as some agents reducing individual experimentation when benefiting from others' information generation (free-riding effects), while enabling top experimenters to allocate more aggressively when supported by group learning (encouragement effects).
+
+Crucially, our two-staged analysis methodology reveals that these disparities emerge consistently across episodes, with different agents assuming the roles of highest and lowest allocators in different episodes.
+This dynamic role rotation—parallel to the information generator/exploiter roles observed in learning without experimentation—indicates that the patterns reflect structural features of multi-agent learning rather than fixed agent characteristics.
+The systematic nature of this role assignment across both experimental scenarios suggests a fundamental principle of social learning: agents naturally specialize into complementary roles that enhance collective information processing, whether through experimentation patterns in strategic contexts or exploration variance in pure learning settings.
+
+\paragraph{Implications and Validation} These results demonstrate that our POAMG framework captures essential features of strategic experimentation dynamics, including state-dependent learning, social information effects, and group size impacts on allocation behavior.
+The observed patterns of strategic adaptation, belief fluctuations, and allocation disparities provide computational validation for key theoretical insights about multi-agent experimentation and information sharing, even though direct equilibrium convergence measurement is precluded by the catastrophic forgetting constraint discussed in our methodological framework.
 
@@
 
-where $\varphi$ maps states to their corresponding correct actions.
-\footnote{Formally, the mapping $\varphi: S \rightarrow A$ is a bijective function defined as $\varphi(s^j) = a^j$ for all $j \in \{1,2,...,m\}$, associating each state with the action having the same index.} This construction ensures the expected reward matches the true utility function in expectation: \footnote{See \ref{appendix:observed_reward_derivation} for a detailed derivation and the formulation for a generic dimension $m$.}
+where $\varphi$ maps states to their corresponding correct actions.\footnote{Formally, the mapping $\varphi: S \rightarrow A$ is a bijective function defined as $\varphi(s^j) = a^j$ for all $j \in \{1,2,...,m\}$, associating each state with the action having the same index.} This construction ensures the expected reward matches the true utility function in expectation: \footnote{See \ref{appendix:observed_reward_derivation} for a detailed derivation and the formulation for a generic dimension $m$.}
 
@@
 
-This construction ensures agents are rewarded based on their posterior belief given the private signal, maintaining compatibility with the original model's incentive structure while providing a learning signal for POLARIS.
+In this setup, agents are rewarded based on their posterior belief given the private signal, maintaining compatibility with the original model's incentive structure while providing a learning signal for POLARIS.
 
@@
 We implement comprehensive experiments to validate these theoretical predictions and explore the learning dynamics under various network structures.
-Our experimental protocol examines network sizes of $n \in \{1, 2, 4, 8\}$ agents; network topologies including complete, ring, star, and random networks; signal accuracy of $p = 0.75$ (matching the paper's example where $r_{\text{aut}} = 0.14$, $r_{\text{crd}} = 0.55$, and $r_{\text{bdd}} = 1.10$); and learning metrics consisting of empirical learning rates extracted via log-linear regression.
+Our experimental protocol examines network sizes of $n \in \{1, 2, 4, 8\}$ agents; network topologies including complete, ring, star, and random networks; signal accuracy of $p = 0.75$ (we use the same signal accuracy as in the paper's example where $r_{\text{aut}} \approx 0.14$, $r_{\text{crd}} \approx 0.55$, and $r_{\text{bdd}} \approx 1.10$); and learning metrics consisting of empirical learning rates extracted via log-linear regression.
 
-For each configuration, we run multiple independent episodes with randomly initialized true states and agents.
-Our analysis follows a two-stage approach.
-First, for each episode $k$, we track each agent's incorrect action probability over time:
-\begin{equation}
-    \hat{P}_{t,k}^i = 1 - \pi_t^i(a_{\omega_k} | b^i_t, z^i_t)
-\end{equation}
-
-And estimate individual learning rates by fitting: 
-\begin{equation}
-    \log \hat{P}_{t,k}^i \approx -r_k^i t + c_k^i
-\end{equation}
-
-To identify the fastest and slowest learners for that episode: 
-\begin{equation}
-    i_{\text{fast}}^k = \arg\max_i r_k^i
-\end{equation} 
- \begin{equation}
-    i_{\text{slow}}^k = \arg\min_i r_k^i
-\end{equation}
-
-Second, we aggregate the performance of fastest and slowest learners across episodes:
-
-\begin{equation}
-    \bar{P}_t^{\text{fast}} = \frac{1}{N_{\text{episodes}}} \sum_{k=1}^{N_{\text{episodes}}} \hat{P}_{t,k}^{i_{\text{fast}}^k}
-\end{equation}
-\begin{equation}
-    \bar{P}_t^{\text{slow}} = \frac{1}{N_{\text{episodes}}} \sum_{k=1}^{N_{\text{episodes}}} \hat{P}_{t,k}^{i_{\text{slow}}^k}
-\end{equation}
-
-where $N_{\text{episodes}}$ is the number of episodes.
-This methodology allows us to examine the distribution of learning rates that emerge from the same network structure across different realizations, revealing whether the theoretical bounds hold regardless of which specific agent becomes the fastest or slowest learner in any given episode.
+Following our two-staged analysis methodology described in Section \ref{sec:two-staged-analysis}, we track each agent's incorrect action probability over time and estimate individual learning rates by fitting log-linear regressions to identify the fastest and slowest learners within each episode.
+We then aggregate the performance of these extreme learners across episodes to examine whether the observed learning disparities represent structural features of multi-agent learning rather than artifacts of specific agent characteristics.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/fastest_slowest_network_sizes_evolution.png}
+    \includegraphics[width=\textwidth]{../code/polaris/docs/fastest_slowest_network_sizes_evolution.png}
     \caption{Fastest vs slowest agent learning trajectories across network sizes.
@@
 
-\paragraph{Learning Barriers Emerge Systematically} Across all network configurations and episodes, we consistently observe a significant reduction in the slowest-learning agent's rate compared to the autarky rate.
+\paragraph{Learning Barriers} Across all network configurations and episodes, we consistently observe a significant reduction in the slowest-learning agent's rate compared to the autarky rate.
 Figure \ref{fig:size_comparison} demonstrates this barrier effect by aggregating the trajectories of whichever agent learns slowest in each episode.
@@
 
-\paragraph{Coordination Benefits Materialize in Larger Networks} In networks with $n \geq 4$ agents, the fastest-learning agents consistently demonstrate superior performance compared to isolated agents, confirming the coordination benefits predicted by Theorem 2.
+\paragraph{Coordination Benefits} In networks with $n \geq 4$ agents, the fastest-learning agents consistently demonstrate superior performance compared to isolated agents, confirming the coordination benefits predicted by Theorem 2.
 This demonstrates that social learning enables some agents to surpass single-agent performance, though at the expense of others.
@@
 
-\paragraph{Information Revelation Through Dynamic Role Assignment} Our results reveal a systematic pattern where agents naturally emerge as either information generators or information exploiters within each episode.
-The agents that learn slowest exhibit higher variance in their action choices (evident from the wider confidence intervals in Figure \ref{fig:size_comparison}), indicating more exploratory behavior that enables other agents to make better-informed decisions.
-Crucially, this division of labor emerges dynamically—different agents assume these roles across episodes, suggesting the phenomenon arises from learning dynamics rather than fixed agent characteristics.
+\paragraph{Information Revelation Through Dynamic Role Assignment} Our results reveal a systematic pattern where agents naturally emerge as either information generators or information exploiters within each episode—a phenomenon that parallels the dynamic role assignment observed in strategic experimentation, where agents differentiate into high and low allocators.
+In learning without experimentation, the agents that learn slowest exhibit higher variance in their action choices (evident from the wider confidence intervals in Figure \ref{fig:size_comparison}), indicating more exploratory behavior that enables other agents to make better-informed decisions.
+This mirrors the information generation role played by high allocators in strategic experimentation, who provide valuable learning signals through their experimental choices.
+
+Crucially, this division of labor emerges dynamically in both scenarios—different agents assume these roles across episodes (Figure \ref{fig:slowest_agent_network_positions}), suggesting the phenomenon arises from learning dynamics rather than fixed agent characteristics.
+This consistency across fundamentally different social learning environments demonstrates that dynamic role assignment represents a robust feature of multi-agent learning systems, where complementary specialization enhances collective information processing regardless of whether the mechanism operates through allocation patterns or exploration variance.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/fastest_slowest_network_types_evolution.png}
+    \includegraphics[width=\textwidth]{../code/polaris/docs/fastest_slowest_network_types_evolution.png}
     \caption{Fastest vs slowest agent learning trajectories across network topologies.
@@
 
-\paragraph{Network Structure Shapes Information Flow} Figure \ref{fig:type_comparison} reveals how network topology influences learning dynamics.
+\subparagraph{Network Structure \& Information Flow} Figure \ref{fig:type_comparison} reveals how network topology influences learning dynamics.
 Complete networks facilitate the most effective information sharing, producing the largest performance gaps between fastest and slowest learners.
@@
 These patterns align with theoretical insights that information aggregation depends critically on network structure, though the specific mechanisms through which topology affects learning warrant further investigation.
-
+\iffalse
 To understand the underlying mechanisms determining which agents become information generators, we examine the roles of network position and signal quality—two factors that could potentially explain the emergence of learning disparities.
@@
     \centering
-    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/slowest_agent_network_positions.png}
+    \includegraphics[width=\textwidth]{../code/polaris/docs/slowest_agent_network_positions.png}
     \caption{The position of the slowest-learning agent in the network over time.
@@
 
-\paragraph{Signal Quality, Not Network Position, Determines Learning Roles} Our analysis reveals that network position alone cannot predict learning performance.
+\subparagraph{Determinants of Learning Roles} Our analysis reveals that network position alone cannot predict learning performance.
 Figure \ref{fig:slowest_agent_network_positions} shows that the identity of the slowest-learning agent distributes approximately uniformly across network positions, indicating that structural network advantages do not systematically determine learning performance.
@@
     \centering
-    \includegraphics[width=\textwidth]{../code/polaris/results/brandl_experiment/agent_performance/signal_quality_vs_learning_performance.png}
+    \includegraphics[width=\textwidth]{../code/polaris/docs/signal_quality_vs_learning_performance.png}
     \caption{The learning performance of POLARIS agents as a function of the signal quality.
@@
 Agents who receive lower-quality private signals consistently exhibit slower learning rates, indicating that the primary determinant of becoming a slow learner is the stochastic realization of signal quality rather than strategic positioning within the network.
-Agents receiving more accurate private signals naturally learn faster, while those receiving noisier signals become information generators whose exploratory behavior, though individually costly, benefits the overall network through enhanced information revelation.
+Agents receiving more accurate private signals naturally learn faster, while those receiving noisier signals become information generators whose exploratory behavior, though individually costly, benefits the overall network through enhanced information revelation.\fi
 
@@
 In any given episode, different agents may assume the roles of fastest or slowest learners, yet the aggregate behavior consistently respects the theoretical limits.
-This emergent division of labor—where some agents naturally become information generators while others exploit this information—arises from the learning dynamics themselves rather than from predetermined agent roles, providing computational validation for the theoretical insights about social learning barriers and coordination benefits.
+This emergent division of labor—where some agents naturally become information generators while others exploit this information—arises from the learning dynamics themselves rather than from predetermined agent roles, providing computational validation for the theoretical insights about social learning barriers and coordination benefits despite the equilibrium convergence limitations discussed in our methodological framework.

### 2025-06-05 paper/theory.tex
Update results.

@@
 
-\subsubsection{Advantage-Weighted Transformer Training} A key innovation in POLARIS is the use of advantage-weighted training for the belief processor:
-\begin{align}
-    J^i_{\text{transformer}}(\psi^i_{\text{Transformer}}) &= \mathbb{E}_{D^i}\left[A^i(b^i, a^i) \cdot \text{BCE}(\mathbb{P}(s|b^i), o^i_{t+1})\right]
-\end{align}
-
-where $A^i(b^i, a^i)$ is the advantage function and BCE is binary cross-entropy loss.
-This objective bridges belief formation and policy optimization in a novel way.
-By weighting the belief update loss with the advantage function, the Transformer is encouraged to generate belief states that not only accurately predict future observations but also lead to high-value actions.
-In traditional partially observable reinforcement learning, belief updates are typically performed independently of policy optimization.
-By contrast, POLARIS creates a direct pathway for policy performance to influence belief formation, prioritizing informative aspects of the state space that have the greatest impact on decision quality.
-This approach is particularly valuable in social learning contexts, where certain beliefs about others' strategies may be more consequential than others for effective coordination or competition.
-
-\subsubsection{Catastrophic Forgetting Prevention}
-
-In social learning environments, the underlying state of the world often remains fixed during an episode, but varies across episodes.
-This creates a continual learning challenge: agents must adapt to new states while retaining knowledge about previously encountered states.
-Without proper mechanisms, neural networks tend to overwrite previously learned representations when adapting to new conditions—a phenomenon known as catastrophic forgetting \citep{vandeven2024continuallearningcatastrophicforgetting}.
-POLARIS addresses this challenge through Elastic Weight Consolidation (EWC), which selectively preserves important parameters for previously encountered states while allowing flexibility for adaptation.
-EWC augments the standard training objective with a regularization term that penalizes significant changes to parameters critical for performance in previously encountered states:
-
-\begin{align}
-    L_{\text{EWC}}(\theta) = L(\theta) + \sum_i \frac{\lambda}{2} F^i (\theta^i - {\theta^i}^*)^2
-\end{align}
-
-where $\theta^*$ represents parameters that performed well on previous tasks, $F^i$ is the Fisher information matrix that measures parameter importance, and $\lambda$ controls the strength of regularization.
-The Fisher information matrix provides a principled way to identify which parameters are most crucial for previously learned tasks, calculated using gradients of the log-likelihood of the model's output with respect to the parameters on data from previously encountered states.
-
-Crucially, POLARIS introduces a dynamic mechanism that automatically adjusts the EWC importance factor based on observed performance:
-
-\begin{align}
-    \lambda_t = 
-    \begin{cases}
-        \lambda_{t-1} \cdot 0.8 & \text{if loss ratio} > 1.5 \text{ (loss increasing too much)} \\
-        \lambda_{t-1} \cdot 1.2 & \text{if loss ratio} < 0.5 \text{ (loss decreasing too quickly)} \\
-        \lambda_{t-1} & \text{otherwise}
-    \end{cases}
-\end{align}
-
-This adaptive approach monitors the ratio between current and previous loss values, reducing the EWC importance when the loss is increasing too rapidly (indicating difficulty learning new information due to excessive preservation of old parameters) and increasing it when the loss is decreasing too quickly (suggesting potential forgetting of valuable past knowledge).
-The implementation also includes both L1 and L2 penalties with adaptive weighting between them, transitioning from more L2 regularization for early tasks to more L1 regularization for later tasks, encouraging sparser updates as the model accumulates more knowledge from different states.
-
 \subsection{Training Process}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[!htbp]
 \caption{POLARIS Training Algorithm for Single Agent}
@@
 
-The algorithm follows a sequential process where each agent first updates its belief state based on new observations and the joint actions of all agents using the Transformer-based belief processor (line 6).
-Based on this updated belief and the current inference of other agents' latent states, the agent selects an action using its stochastic policy—sampling from a categorical distribution for discrete action spaces (line 9) or using the reparameterization trick for continuous action spaces (lines 11-13).
-After executing this action and observing the reward and next observation (line 15), the agent updates its inference of other agents' latent states using the GNN-based inference module (line 16).
-All of these experiences are stored in a replay buffer for later training (line 17).
+The algorithm follows a sequential process where each agent first updates its belief state based on new observations and the joint actions of all agents using the Transformer-based belief processor.
+Based on this updated belief and the current inference of other agents' latent states, the agent selects an action using its stochastic policy—sampling from a categorical distribution for discrete action spaces or using the reparameterization trick for continuous action spaces.
+After executing this action and observing the reward and next observation, the agent updates its inference of other agents' latent states using the GNN-based inference module.
+All of these experiences are stored in a replay buffer for later training.
 
 At designated update steps, the agent samples a batch of transitions from its replay buffer and uses these to update all network components.
-The inference module is updated first (line 19) to improve predictions of other agents' actions using the ELBO objective.
-Next, the value networks are updated (line 20) to better estimate expected returns.
-The policy network is then updated (line 21) to maximize expected value and entropy.
-Finally, the belief processor is updated (line 22) using the advantage-weighted training approach.
-Target networks, used for stable learning in the SAC framework, are updated using a weighted average of the current and target parameters (line 23).
+The inference module is updated first to improve predictions of other agents' actions using the ELBO objective.
+Next, the value networks are updated to better estimate expected returns.
+The policy network is then updated to maximize expected value and entropy.
+Finally, the belief processor is updated using the advantage-weighted training approach.
+Target networks, used for stable learning in the SAC framework, are updated using a weighted average of the current and target parameters.
 
 A crucial feature of POLARIS is its adaptive response to changes in the environment state.
-When the true state changes (line 24), the algorithm calculates Fisher information matrices from the current replay buffer (line 25) and registers a new task with the EWC mechanism (line 26), preserving important knowledge from the previous state while allowing adaptation to the new state.
+When the true state changes, the algorithm calculates Fisher information matrices from the current replay buffer and registers a new task with the EWC mechanism, preserving important knowledge from the previous state while allowing adaptation to the new state.
 

### 2025-06-06 paper/results.tex
Update results.

@@
-Building on the theoretical framework of Partially Observable Active Markov Games developed in the previous section, we now apply our POLARIS algorithm to concrete social learning scenarios.
-This implementation demonstrates how our approach bridges theoretical economic models with computational reinforcement learning methods, allowing us to validate theoretical predictions while uncovering new insights about strategic adaptation in partial observability settings.
-
-We implement our Partially Observable Active Markov Game framework to model the two canonical social learning scenarios discussed in the background section: strategic experimentation with observable rewards and learning without experimentation through action observation.
-By reformulating these economic models as POAMGs, we demonstrate how our framework can capture the sophisticated learning dynamics present in these scenarios while enabling the discovery of complex strategies through our POLARIS algorithm.
-\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/polaris}.}
+Building on the theoretical framework of Partially Observable Active Markov Games developed in the previous section, we now apply our POLARIS algorithm to concrete social learning scenarios: strategic experimentation and learning without experimentation.
+This implementation demonstrates how our approach bridges theoretical economic models with computational reinforcement learning methods, allowing us to validate theoretical predictions while uncovering new insights about strategic adaptation in partial observability settings.\footnote{Complete Python implementation is available at \url{https://github.com/ecdogaroglu/polaris}.}
 
@@
 
-Before presenting our experimental results, we must address two fundamental challenges that arise when applying reinforcement learning to social learning environments.
-These challenges stem from a fundamental mismatch between the strategic requirements of economic theory and the constraints of computational implementation, ultimately necessitating a novel experimental methodology that focuses on within-episode dynamics rather than cross-episode equilibrium convergence.
+Theoretical frameworks —both in economics and in our POAMG framework— envision agents developing strategies that perform optimally across all possible states of the world.
+This \emph{ex ante} perspective requires agents to maintain flexibility and develop sophisticated mixed approaches that can respond appropriately regardless of which state is ultimately realized.
+Agents should learn conditional strategies of the form "if state = A, do X; if state = B, do Y," accounting for uncertainty about the true environmental state.
 
-\subsection{Ex Ante Strategy Optimization vs Ex Post Convergence}
+The computational approach, however, reveals a fundamental departure from this theoretical ideal.
+Reinforcement learning agents instead converge to state-specific optimal allocations—an \emph{ex post} perspective where behavior is optimized for the particular state that has been realized.
+This distinction creates a critical incompatibility in the social learning environments we study, particularly due to their fixed-state structure.
 
-Implementing reinforcement learning in social learning environments reveals a fundamental tension between economic theory and computational practice.
-In economic social learning models, agents are expected to develop strategies that perform optimally across all possible states of the world—an ex ante perspective where the optimal strategy accounts for uncertainty about which state will be realized.
-Such strategies require maintaining flexibility and developing sophisticated mixed approaches that can respond appropriately whether the true state turns out to be A or B, good or bad.
+To understand why this incompatibility emerges, consider the nature of optimal behavior in social learning environments with binary state spaces.
+In strategic experimentation, if the risky arm is good, rational agents should allocate all resources to it; conversely, if it performs poorly, optimal behavior requires complete avoidance.
+Similarly, in learning without experimentation, once the true state is A, the optimal action is unambiguously action A, while in state B, only action B is rational.
+These ex post strategies represent fundamentally incompatible policy objectives that cannot be reconciled through standard learning approaches.
 
-However, our computational implementation reveals that agents instead converge to state-specific optimal allocations—an ex post perspective where behavior is optimized for the particular state that has been realized.
-This distinction creates a critical incompatibility in binary social learning environments we consider here.
-In strategic experimentation, if the risky arm is revealed to be good, rational agents should allocate all resources to it; conversely, if it performs poorly, optimal behavior requires complete avoidance.
-In learning without experimentation, once the true state is A, the optimal action is unambiguously action A, while in state B, only action B is rational.
-These ex post strategies are not merely different from the ex ante approach—they are fundamentally incompatible policy objectives that cannot be reconciled through standard learning approaches.
+The fixed-state structure of social learning models compounds this challenge.
+In each episode, agents can only observe and learn from one realized state, forcing them away from the ex ante strategies that theoretical frameworks prescribe.
+Instead of developing belief-contingent policies, agents learn "do X" during episodes with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.
 
-The computational challenge emerges because reinforcement learning agents, operating within our episodic framework, can only observe and learn from one realized state per episode.
-This structure forces agents away from developing the sophisticated ex ante strategies characterized in the theoretical models toward state-specific ex post optimization.
-Instead of learning "if state = A, do X; if state = B, do Y" as economic theory prescribes, agents learn "do X" during episodes initialized with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.
-
-A natural approach to analyzing multi-agent strategic behavior in these environments would be to evaluate reinforcement learning models that are trained across different belief states or environmental configurations.
-This methodology could theoretically enable us to examine how agents would behave under the full spectrum of possible conditions, potentially revealing the sophisticated mixed strategies and state-contingent policies that characterize optimal ex ante behavior in economic theory.
-To test this approach, we attempted to recover ex ante policy analysis by inverting a linear grid of possible beliefs into latent belief representations and feeding these directly into trained policy networks.
-The goal was to evaluate how agents would behave across the full spectrum of possible belief states, potentially revealing the sophisticated mixed strategies characteristic of economic equilibria.
-However, this approach consistently failed as the trained networks would invariably follow the optimal action corresponding to the last true state they were trained on, regardless of the belief input provided.
-This confirmed that the learned policies had become fundamentally state-specific rather than developing the belief-contingent strategies required for ex ante optimization, making model evaluation for ex ante analysis impossible due to the underlying technical constraint of catastrophic forgetting.
+One natural approach to address this limitation would be to train agents across different environmental configurations, then evaluate their behavior under the full spectrum of possible conditions.
+However, this approach consistently fails due to a fundamental constraint of neural network learning.
+When network parameters are continuously updated across episodes, action-value functions adapt to the most recent state, leading to policies that are only optimal for the last state encountered.
+This phenomenon—known as \emph{catastrophic forgetting}—fundamentally constrains model evaluation for ex ante analysis.
 
@@
 
-The ex ante versus ex post discrepancy described above manifests as a severe technical challenge when implementing reinforcement learning in these environments: catastrophic forgetting.
-Since the behavioral requirements for different state realizations are diametrically opposed, continuous training across episodes with different realized states inevitably leads to catastrophic forgetting.
-Each episode's learning systematically destroys the value functions and policies acquired in previous episodes with different state realizations, preventing the emergence of stable, discriminative strategies that could respond appropriately to environmental uncertainty as economic theory requires.
+Catastrophic forgetting represents a fundamental limitation in neural network learning where the acquisition of new knowledge systematically interferes with previously learned information \citep{vandeven2024continuallearningcatastrophicforgetting}.
+This phenomenon occurs when neural networks, optimized through gradient descent, overwrite previously learned weights and representations as they adapt to new tasks or environments.
+While various techniques have been developed to mitigate this issue in continual learning scenarios—including regularization methods, memory replay systems, and architectural approaches—these solutions typically assume some degree of compatibility or transferability between learning objectives \citep{kirkpatrick2017overcoming, zenke2017continuallearningsynapticintelligence, rebuffi2017icarl, rusu2016progressive}.
 
-To address this fundamental limitation, we explored several established catastrophic forgetting mitigation techniques \citep{vandeven2024continuallearningcatastrophicforgetting}, including Elastic Weight Consolidation \citep{kirkpatrick2017overcoming}, Synaptic Intelligence \citep{zenke2017continuallearningsynapticintelligence}, alternating state presentation schedules, and state-aware replay buffers that integrate experiences from previous environmental configurations.
-However, these approaches proved ineffective because they assume some degree of transferability or compatibility between learning tasks.
-When ex post optimal policies require completely opposite actions across states, traditional continual learning techniques cannot meaningfully "consolidate" or "protect" previous learning without fundamentally undermining current learning objectives.
+In our social learning environments, this compatibility assumption fails completely.
+When the optimal policy in state A requires action X while the optimal policy in state B demands the opposite action Y, no meaningful knowledge transfer is possible between episodes with different state realizations.
+The literature on negative transfer confirms that attempting to force knowledge sharing between fundamentally incompatible tasks degrades performance rather than enhancing it \citep{ahn2024catastrophic, wu2021online}.
+Traditional continual learning mechanisms that aim to "consolidate" or "protect" previous learning become counterproductive when such protection would directly undermine the acquisition of conflicting but equally necessary knowledge.
 
-This constraint necessitates resetting agents at the beginning of each episode rather than allowing continuous learning across episodes, which limits our ability to directly evaluate the sophisticated equilibrium strategies described in both \citet{keller2020undiscounted} and related theoretical work.
-These equilibria require agents to maintain stable ex ante strategies that can discriminate between environmental conditions and respond appropriately—capabilities that prove incompatible with standard reinforcement learning when agents can only experience one state realization per episode.
-Consequently, our experimental methodology focuses on within-episode learning dynamics and cross-episode pattern analysis to extract meaningful insights about multi-agent strategic behavior despite these fundamental constraints.
+These fundamental constraints require us to reset agent parameters at the beginning of each episode rather than allowing continuous learning across state realizations.
+While this methodological necessity prevents direct measurement of the equilibrium strategies that economic theory and our POAMG framework predict, it does not invalidate our computational approach.
+Rather, it compels us to develop alternative analytical methodologies that can extract meaningful insights about multi-agent strategic behavior despite these inherent limitations of applying reinforcement learning to environments with conflicting learning objectives.
+
+Our experimental methodology therefore focuses on within-episode learning dynamics and cross-episode pattern analysis.
+By examining how agents adapt their behavior within episodes and identifying systematic patterns across episodes, we can still characterize the essential features of multi-agent social learning, even when direct equilibrium convergence measurement is precluded by computational limitations.
 
@@
 
-\paragraph{Stage 1: Within-Episode Role Identification} For each episode $k$, we identify agents that exhibit extreme performance characteristics.
+\paragraph{Stage 1: Within-Episode Role Identification} For each episode $e$, we identify agents that exhibit extreme performance characteristics.
 In strategic experimentation, we track cumulative allocation patterns:
 \begin{equation}
-    i_{\text{high}}^k = \arg\max_i \sum_{t=1}^T a_{t,k}^i, \quad 
-    i_{\text{low}}^k = \arg\min_i \sum_{t=1}^T a_{t,k}^i
+    i_{\text{high}}^e = \arg\max_i \sum_{t=1}^T a_{t,e}^i, \quad 
+    i_{\text{low}}^e = \arg\min_i \sum_{t=1}^T a_{t,e}^i
 \end{equation}
@@
 \begin{equation}
-    i_{\text{fast}}^k = \arg\max_i r_k^i, \quad 
-    i_{\text{slow}}^k = \arg\min_i r_k^i
+    i_{\text{fast}}^e = \arg\max_i r_e^i, \quad 
+    i_{\text{slow}}^e = \arg\min_i r_e^i
 \end{equation}
-where $r_k^i$ is agent $i$'s learning rate in episode $k$.
+where $r_e^i$ is agent $i$'s learning rate in episode $e$.
 
@@
 \begin{equation}
-    \bar{P}_t^{\text{extreme}} = \frac{1}{n_{\text{episodes}}} \sum_{k=1}^{n_{\text{episodes}}} P_{t,k}^{i_{\text{extreme}}^k}
+    \bar{P}_t^{\text{extreme}} = \frac{1}{n_{\text{episodes}}} \sum_{e=1}^{n_{\text{episodes}}} P_{t,e}^{i_{\text{extreme}}^e}
 \end{equation}
-where $P_{t,k}^i$ represents the relevant performance metric (cumulative allocation, learning accuracy, etc.) for agent $i$ at time $t$ in episode $k$.
+where $P_{t,e}^i$ represents the relevant performance metric (cumulative allocation, learning accuracy, etc.) for agent $i$ at time $t$ in episode $e$.
 
-This methodology reveals whether observed disparities represent structural features of multi-agent learning or merely artifacts of specific agent characteristics, as different agents assume extreme roles across different episodes.
+This methodology reveals whether observed disparities represent structural features of multi-agent learning or merely artifacts of specific agent characteristics like network position, as different agents assume extreme roles across different episodes.
 
@@
 
-For each configuration, we run experiments with horizon lengths of 50 steps for comparative sweeps across group sizes, focusing on the emergence of allocation patterns and their relationship to theoretical predictions.
+For each configuration, we run experiments for comparative sweeps across group sizes, focusing on the emergence of allocation patterns and their relationship to theoretical predictions.
 Our analysis emphasizes within-episode learning dynamics rather than cross-episode equilibrium convergence due to the catastrophic forgetting constraint.
@@
 \paragraph{Strategic Action Convergence} POLARIS agents successfully learn to converge toward state-dependent optimal allocation strategies.
-In good states, agents increase their allocation to the risky arm over time, while in bad states, they learn to favor the safe alternative.
+In good states, agents increase their allocation to the risky arm over time, while in bad states, they learn to favor the safe alternative (Figure \ref{fig:allocation_accuracy_over_time}).
 This convergence demonstrates that the discretized action representation effectively captures the continuous allocation dynamics of the theoretical model, enabling agents to discover appropriate exploration-exploitation strategies through reinforcement learning.
 
-\paragraph{Belief Dynamics and Social Learning Effects} Figure \ref{fig:belief_accuracy_over_time} reveals fluctuating belief patterns that indicate the importance of neighbor action observation in the learning process.
-These fluctuations demonstrate that agents actively incorporate information from neighbors' allocation decisions, leading to more informed belief updating compared to purely individual learning.
-The variability in belief trajectories reflects the ongoing process of social information aggregation, where agents continuously refine their understanding based on both private signals and observed neighbor behaviors.
+\paragraph{Belief Dynamics and Social Learning Effects} Figure \ref{fig:belief_accuracy_over_time} reveals fluctuating belief patterns alongside stable allocation policies.
+This demonstrates how POLARIS agents incorporate social information through the inference module while maintaining strategic coherence.
+The belief variability reflects ongoing social learning as agents observe noisy private signals, yet their policies converge reliably toward optimal state-specific strategies.
 
@@
         \includegraphics[width=\textwidth]{../code/polaris/docs/highest_lowest_cumulative_allocators_good_state.png}
-        \caption{Highest and lowest cumulative allocators in the good state.}
+        \caption{Highest and lowest cumulative allocators in the good state. (Average over 20 episodes)}
         \label{fig:highest_lowest_cumulative_allocators_good_state}
@@
     \includegraphics[width=\textwidth]{../code/polaris/docs/highest_lowest_cumulative_allocators_bad_state.png}
-    \caption{Highest and lowest cumulative allocators in the bad state.}
+    \caption{Highest and lowest cumulative allocators in the bad state. (Average over 20 episodes)}
     \label{fig:highest_lowest_cumulative_allocators_bad_state}
@@
 In strategic experimentation, this manifests as some agents reducing individual experimentation when benefiting from others' information generation (free-riding effects), while enabling top experimenters to allocate more aggressively when supported by group learning (encouragement effects).
-
-Crucially, our two-staged analysis methodology reveals that these disparities emerge consistently across episodes, with different agents assuming the roles of highest and lowest allocators in different episodes.
-This dynamic role rotation—parallel to the information generator/exploiter roles observed in learning without experimentation—indicates that the patterns reflect structural features of multi-agent learning rather than fixed agent characteristics.
-The systematic nature of this role assignment across both experimental scenarios suggests a fundamental principle of social learning: agents naturally specialize into complementary roles that enhance collective information processing, whether through experimentation patterns in strategic contexts or exploration variance in pure learning settings.
+Interestingly, despite the presence of free-riding behavior typically associated with inefficiency in economic literature, our results show that cumulative allocation in larger networks substantially exceeds autarky levels in both good and bad states, suggesting that the social learning benefits and encouragement effects more than compensate for the traditional inefficiencies of free-riding in these multi-agent learning environments.
 
@@
 We implement comprehensive experiments to validate these theoretical predictions and explore the learning dynamics under various network structures.
-Our experimental protocol examines network sizes of $n \in \{1, 2, 4, 8\}$ agents; network topologies including complete, ring, star, and random networks; signal accuracy of $p = 0.75$ (we use the same signal accuracy as in the paper's example where $r_{\text{aut}} \approx 0.14$, $r_{\text{crd}} \approx 0.55$, and $r_{\text{bdd}} \approx 1.10$); and learning metrics consisting of empirical learning rates extracted via log-linear regression.
+Our experimental protocol examines network sizes of $n \in \{1, 2, 4, 8\}$ agents; network topologies including complete, ring, star, and random networks; signal accuracy of $p = 0.75$ \iffalse(we use the same signal accuracy as in the paper's example where $r_{\text{aut}} \approx 0.14$, $r_{\text{crd}} \approx 0.55$, and $r_{\text{bdd}} \approx 1.10$)\fi; and learning metrics consisting of empirical learning rates extracted via log-linear regression.
 
-Following our two-staged analysis methodology described in Section \ref{sec:two-staged-analysis}, we track each agent's incorrect action probability over time and estimate individual learning rates by fitting log-linear regressions to identify the fastest and slowest learners within each episode.
+Following our two-staged analysis methodology described in Section \ref{sec:two-staged-analysis}, we track each agent's incorrect action probability as the probability assignment of the policy network to the incorrect action over time and estimate individual learning rates by fitting log-linear regressions to identify the fastest and slowest learners within each episode.
 We then aggregate the performance of these extreme learners across episodes to examine whether the observed learning disparities represent structural features of multi-agent learning rather than artifacts of specific agent characteristics.
@@
 \subsection{Results and Analysis}
-
+\iffalse
 Our experimental results provide strong validation of the theoretical predictions while revealing additional insights into the learning dynamics.
@@
 Despite these methodological differences, both approaches provide complementary insights into learning performance bounds and achievable rates in practice.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=\textwidth]{../code/polaris/docs/fastest_slowest_network_sizes_evolution.png}
-    \caption{Fastest vs slowest agent learning trajectories across network sizes.
-Each subplot shows the mean incorrect action probability over time with $95\%$ confidence intervals (shaded regions) for the fastest (green) and slowest (red) learning agents.
-The learning rates $r$ are calculated using log-linear regression.
-Results demonstrate the learning barrier effect where slowest agents remain bounded while fastest agents achieve superior performance in larger networks.}
-    \label{fig:size_comparison}
-\end{figure}
+\fi
 
@@
 Figure \ref{fig:size_comparison} demonstrates this barrier effect by aggregating the trajectories of whichever agent learns slowest in each episode.
-This finding directly supports the theoretical prediction of Theorem 1.
+This finding directly supports the theoretical prediction of the paper.
 While we cannot observe whether the bound significantly exceeds the autarky rate as the theorem suggests—such validation would require much larger networks and higher computational resources—the consistent emergence of learning barriers across all configurations provides strong empirical support for the theoretical framework.
 
-\paragraph{Coordination Benefits} In networks with $n \geq 4$ agents, the fastest-learning agents consistently demonstrate superior performance compared to isolated agents, confirming the coordination benefits predicted by Theorem 2.
+\paragraph{Coordination Benefits} In networks with $n \geq 4$ agents, the fastest-learning agents consistently demonstrate superior performance compared to isolated agents, confirming the coordination benefits predicted by the paper.
 This demonstrates that social learning enables some agents to surpass single-agent performance, though at the expense of others.
@@
 However, similar to our findings on learning barriers, we cannot observe whether the learning rate of the slowest-learning agent can surpass the autarky rate for sufficiently large networks as the theorem suggests.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../code/polaris/docs/fastest_slowest_network_sizes_evolution.png}
+    \caption{Fastest vs slowest agent learning trajectories across network sizes.}
+    \label{fig:size_comparison}
+\end{figure}
 
@@
 
+\iffalse
 Crucially, this division of labor emerges dynamically in both scenarios—different agents assume these roles across episodes (Figure \ref{fig:slowest_agent_network_positions}), suggesting the phenomenon arises from learning dynamics rather than fixed agent characteristics.
 This consistency across fundamentally different social learning environments demonstrates that dynamic role assignment represents a robust feature of multi-agent learning systems, where complementary specialization enhances collective information processing regardless of whether the mechanism operates through allocation patterns or exploration variance.
+\fi
 
@@
     \includegraphics[width=\textwidth]{../code/polaris/docs/fastest_slowest_network_types_evolution.png}
-    \caption{Fastest vs slowest agent learning trajectories across network topologies.
-Each subplot compares performance in different network structures (complete, ring, star, random) with 4 agents.
-The confidence intervals reveal how network topology affects the learning rate disparity between fastest and slowest agents, with complete networks showing the most pronounced differentiation due to enhanced information sharing.}
+    \caption{Fastest vs slowest agent learning trajectories across network topologies.}
     \label{fig:type_comparison}
@@
 
-\subparagraph{Network Structure \& Information Flow} Figure \ref{fig:type_comparison} reveals how network topology influences learning dynamics.
+\paragraph{Network Structure \& Information Flow} Figure \ref{fig:type_comparison} reveals how network topology influences learning dynamics.
 Complete networks facilitate the most effective information sharing, producing the largest performance gaps between fastest and slowest learners.
@@
 
-Crucially, our episode-wise analysis methodology shows that the theoretical bounds from \citet{brandl2024} represent robust properties of the multi-agent learning system rather than characteristics of specific agents.
-In any given episode, different agents may assume the roles of fastest or slowest learners, yet the aggregate behavior consistently respects the theoretical limits.
-This emergent division of labor—where some agents naturally become information generators while others exploit this information—arises from the learning dynamics themselves rather than from predetermined agent roles, providing computational validation for the theoretical insights about social learning barriers and coordination benefits despite the equilibrium convergence limitations discussed in our methodological framework.
+Our computational analysis reveals a striking consistency in the emergence of dynamic role assignment across fundamentally different social learning environments.
+In both strategic experimentation and learning without experimentation, agents naturally differentiate into complementary roles that enhance collective information processing, though the specific mechanisms differ substantially.
+In strategic experimentation, this differentiation manifests through allocation patterns, where some agents assume higher-risk experimental roles by allocating more resources to uncertain alternatives, while others free-ride on this information generation.
+In learning without experimentation, the same underlying phenomenon emerges through learning rate disparities and exploration variance, where slower-learning agents exhibit more exploratory behavior that benefits faster-learning agents who can exploit this information revelation.
+Crucially, these roles are not fixed by agent characteristics or network positions but emerge dynamically through the learning process itself, with different agents assuming information generation and exploitation roles across episodes.
+Remarkably, in both environments, the presence of free-riding behavior does not lead to the inefficiencies typically predicted by economic theory—cumulative allocations in strategic experimentation and learning rates in learning without experimentation both exceed autarky levels in larger networks, demonstrating that for some agents, social learning benefits and encouragement effects consistently outweigh traditional free-riding costs.
+This robustness across distinct social learning mechanisms suggests that dynamic role assignment represents a fundamental organizing principle of multi-agent learning systems, enabling some agents to efficiently aggregate information through spontaneous specialization in exploratory behavior.

### 2025-06-06 paper/conclusion.tex
Update conc, intro, abs.

@@
-This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm.
-Our framework addresses fundamental challenges in modeling strategic adaptation under partial observability, where agents must simultaneously learn about their environment and strategically influence others' learning processes.
+This thesis bridges economic social learning theory and multi-agent reinforcement learning by developing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm.
+Our framework addresses fundamental challenges in modeling adaptive behavior under partial observability, demonstrating how computational approaches complement traditional economic theory while providing new insights into complex social learning dynamics.
 
-Our theoretical contributions establish POAMGs as a rigorous mathematical framework extending Active Markov Games to partially observable settings.
-The convergence analysis and policy gradient theorems provide solid foundations for the POLARIS algorithm, which successfully implements this framework through an integrated architecture combining belief processing, inference learning, and reinforcement learning modules.
+\paragraph{Summary of Contributions}
 
-Experimental validation across strategic experimentation and learning without experimentation scenarios demonstrates our framework's effectiveness.
-POLARIS agents converge to theoretically predicted equilibrium strategies, validating key insights about free-riding behavior and optimal experimentation intensity.
-Our results confirm the existence of social learning barriers while revealing coordination benefits in larger networks.
-Crucially, we uncover a dynamic division of labor where agents assume roles as information generators or exploiters based on signal quality rather than network position.
+Our work makes four interconnected contributions.
+First, we developed the POAMG framework, extending Active Markov Games to partially observable settings where agents reason about environmental uncertainty and evolving strategies of others.
+Second, we provided theoretical analysis of convergence and equilibrium properties, establishing stochastic stability conditions and deriving policy gradient theorems for average and discounted rewards.
+We extended the framework to continuous-time dynamics through stochastic differential equations and revealed how game-theoretic equilibrium concepts relate to active equilibrium when agents account for others' learning.
+Third, we introduced POLARIS, combining belief processing through Transformer models, variational inference learning with GNNs, and reinforcement learning optimization, enabling agents to develop sophisticated strategies accounting for both environmental partial observability and strategic adaptation.
+Fourth, we validated our framework through strategic experimentation and learning without experimentation applications, demonstrating dynamic role assignment, information generation and exploitation, and emergence of learning barriers and coordination benefits.
 
-Future research could extend the framework to incorporate heterogeneous agent types, dynamic network structures, or mechanism design principles.
-Applications to contemporary challenges such as misinformation spread or algorithmic recommendation systems could demonstrate broader relevance.
+\paragraph{Key Findings and Implications}
 
-This work demonstrates that integrating economic theory and computational methods yields insights neither approach could achieve alone.
-The POAMG framework and POLARIS algorithm provide both theoretical understanding and practical tools for analyzing complex social learning processes, establishing a foundation for future interdisciplinary research.
-As multi-agent systems become increasingly prevalent, such integrated approaches will be essential for understanding and shaping collective intelligence emerging from strategic interactions among learning agents.
+Our experimental analysis reveals that dynamic role assignment is a robust organizing principle of multi-agent learning systems.
+Across both scenarios, agents naturally differentiate into complementary roles enhancing collective information processing.
+Our results show that free-riding behavior does not lead to predicted inefficiencies—performance of some agents in larger networks substantially exceeds autarky levels.
+The computational approach illuminates fundamental tension between theoretical and practical approaches: while economic models envision agents developing ex ante strategies optimal across all states, reinforcement learning agents converge to ex post strategies optimized for specific realized states.
+This reveals limitations in directly applying computational methods to test theoretical predictions while suggesting opportunities for more realistic behavioral models.
+
+\paragraph{Methodological Contributions and Limitations}
+
+Our two-staged analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting.
+The discretization approach for continuous-time economic models treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities, providing computational implementation templates while preserving essential incentive structures.
+We constructed observed reward functions enabling reinforcement learning without direct reward signals and developed specialized transformer loss functions for Lévy process observations.
+Our implementation incorporates Graph Neural Networks with temporal and spatial attention mechanisms capturing network topology and temporal dependencies.
+We introduce theoretically grounded off-policy asymmetric analysis methods moving beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence.
+Despite these advances, catastrophic forgetting prevents direct measurement of predicted equilibrium strategies, requiring alternative analytical approaches, and computational complexity limits analysis to small networks and finite horizons, potentially missing asymptotic behaviors theoretical models emphasize.
+
+\paragraph{Future Research Directions}
+
+Several promising avenues emerge: developing continual learning techniques for social learning environments could address catastrophic forgetting through architectures maintaining separate policy components for different states; scaling to larger networks and longer horizons would enable asymptotic validation; extending to dynamic environments where underlying states change would broaden applicability; and investigating optimal information structures and network topologies could inform platform and institutional design.
+
+\paragraph{Broader Impact and Conclusion}
+
+This thesis demonstrates the value of interdisciplinary approaches bridging economic theory and computational methods.
+By preserving theoretical rigor while leveraging modern machine learning techniques, we gain insights into complex social phenomena neither approach could achieve alone.
+The insights have implications for financial markets, organizational learning, online social networks, and collaborative scientific endeavors.
+Dynamic role assignment suggests effective social learning systems naturally develop specialized roles enhancing collective information processing, providing guidance for platform design and institutional arrangements.
+Our POAMG framework and POLARIS algorithm contribute to multi-agent reinforcement learning by providing principled approaches for handling partial observability and strategic adaptation.
+The techniques may prove valuable for other applications requiring sophisticated multi-agent coordination under uncertainty.
+The convergence of economic theory and artificial intelligence presents exciting opportunities for advancing understanding of social learning and strategic behavior.
+This thesis provides theoretical foundations and computational tools for future researchers to illuminate rich dynamics of social learning in complex environments.
+While significant progress has been made, much work remains to fully realize this integration's potential, with the ultimate goal of better understanding how intelligent agents can learn from each other to make better decisions in an uncertain world.

### 2025-06-06 paper/intro.tex
Update conc, intro, abs.

@@
 Our approach models social learning as a dynamic process where agents with limited information strategically adapt their behaviors while simultaneously learning about their environment and other agents' strategies.
-By formalizing this process through the lens of partially observable reinforcement learning, we aim to reveal new insights into how strategic adaptation influences collective outcomes and equilibrium behavior.
-This interdisciplinary synthesis addresses fundamental challenges that have constrained previous work in both economics and artificial intelligence, offering a more realistic and computationally tractable approach to modeling complex social learning dynamics.
+Through the development of Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm, we demonstrate how computational approaches can complement traditional economic theory while revealing new insights into complex social learning dynamics, particularly the emergence of dynamic role assignment as a fundamental organizing principle of multi-agent learning systems.
 
@@
 
-To address these challenges, this thesis makes several interconnected contributions.
+To address these challenges, this thesis makes four interconnected contributions that advance both economic theory and multi-agent reinforcement learning.
 First, we develop Partially Observable Active Markov Games (POAMGs)—a novel formalism that extends the Active Markov Game framework introduced by \citet{kim2022influencing} to partially observable settings.
@@
 POAMGs explicitly model how agents' policies evolve over time based on observations and interactions, while accounting for the fundamental constraints imposed by partial observability.
-This formalism provides a mathematically rigorous foundation for analyzing complex social learning dynamics that involve repeated interactions, adaptive strategies, and incomplete information.
 
@@
 We establish conditions under which the joint process of states, beliefs, and policy parameters converges to a unique stochastically stable distribution, ensuring that our models have well-defined limiting behavior despite the inherent non-stationarity of multi-agent learning.
-We derive policy gradient theorems for average and discounted reward objectives, providing a solid foundation for algorithm development.
-We also extend our framework to continuous-time dynamics through stochastic differential equations, enabling a wider range of applications.
-Our analysis illuminates the relationship between traditional game-theoretic equilibrium concepts and the more general notion of active equilibrium that emerges in our framework, offering new insights into equilibrium selection and stability in social learning contexts.
+We derive policy gradient theorems for average and discounted reward objectives and extend our framework to continuous-time dynamics through stochastic differential equations.
+Critically, we reveal how game-theoretic equilibrium concepts relate to active equilibrium when agents account for others' learning, illuminating the fundamental tension between theoretical ex ante strategies and the ex post strategies that emerge through reinforcement learning.
 
-Third, we introduce POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm for learning in POAMGs.
-POLARIS extends previous algorithms to partially observable settings through an integrated architecture with three core components: a belief processing module that tracks agents' information states using Transformer models; an inference learning module that predicts the policy evolution of other agents through variational methods; and a reinforcement learning module that optimizes policies based on average or discounted reward criteria, supporting both discrete and continuous action spaces.
-This integrated approach enables agents to learn sophisticated strategies that account for both the partial observability of the environment and the learning dynamics of other agents—capabilities that are essential for modeling realistic social learning processes.
+Third, we introduce POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), combining belief processing through Transformer models, variational inference learning with Graph Neural Networks (GNNs), and reinforcement learning optimization.
+Our implementation incorporates GNNs with temporal and spatial attention mechanisms that capture network topology and temporal dependencies, enabling agents to develop sophisticated strategies accounting for both environmental partial observability and strategic adaptation.
+POLARIS addresses the critical challenge of catastrophic forgetting through a two-staged analysis methodology that provides systematic approaches for extracting insights from multi-agent learning dynamics despite agents' inability to maintain stable policies across all states.
 
-Fourth, we apply our framework to two canonical social learning scenarios from economic theory.
-The first application focuses on strategic experimentation, building on the models of \citet{bolton1999strategic} and \citet{keller2020undiscounted}, where agents learn optimal actions through trial and error with observable rewards.
-The second application examines learning without experimentation, extending the frameworks of \citet{huang2024learning} and \citet{brandl2024}, where agents form beliefs primarily by observing others' actions rather than receiving direct feedback from the environment.
-Our analysis demonstrates how our approach can model phenomena such as free-riding on others' information production, strategic teaching, information cascades, and confounded learning under more realistic assumptions about agents' reasoning capabilities and strategic sophistication.
+Fourth, we validate our framework through strategic experimentation and learning without experimentation applications, building on the models of \citet{bolton1999strategic}, \citet{keller2020undiscounted}, \citet{huang2024learning}, and \citet{brandl2024}.
+Our analysis demonstrates dynamic role assignment as a robust organizing principle, where agents naturally differentiate into complementary roles enhancing collective information processing.
+Contrary to theoretical predictions about free-riding inefficiencies, we show that performance of some agents in larger networks substantially exceeds autarky levels, revealing opportunities for more realistic behavioral models that account for computational agents' learning dynamics.
 
-Through these applications, we illustrate how bridging economic theory and MARL can enhance our understanding of social learning processes.
-Our POAMG framework provides a more realistic model of how partially rational agents learn from each other in complex, partially observable environments.
-At the same time, it offers practical algorithms for computing equilibrium strategies that traditional economic approaches might find intractable.
-The POLARIS algorithm demonstrates how techniques from deep reinforcement learning and approximate inference can be adapted to tackle the specific challenges of social learning, offering a computationally feasible method for simulating and analyzing complex multi-agent learning dynamics.
+A key methodological innovation is our discretization approach for continuous-time economic models, which treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities.
+This provides computational implementation templates while preserving essential incentive structures from theoretical models.
+We construct observed reward functions that enable reinforcement learning without direct reward signals and develop specialized transformer loss functions for Lévy process observations.
+Our theoretically grounded off-policy asymmetric analysis methods move beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence—capabilities essential for understanding real-world social learning dynamics.
+
+The insights gained advance theoretical knowledge and inform the design of platforms and institutions that facilitate efficient collective learning.
+Our finding that dynamic role assignment emerges as a natural organizing principle suggests that effective social learning systems develop specialized roles enhancing collective information processing, providing guidance for platform design and institutional arrangements in financial markets, organizational learning, online social networks, and collaborative scientific endeavors.
+By demonstrating the value of MARL techniques for addressing classical questions in economic theory while revealing computational challenges like catastrophic forgetting, we contribute to both fields and encourage further cross-disciplinary work leveraging complementary insights from these rich intellectual traditions.
 

### 2025-06-06 paper/thesis.tex
Update results.
Update conc, intro, abs.

@@
 
-{\Large \textbf{Social Learning via Multi Agent Reinforcement Learning}}\\[6cm]
+{\Large \textbf{Social Learning via\\[0.25cm]Multi-Agent Deep Reinforcement Learning}}\\[6cm]
 
@@
 \begin{adjustwidth}{2cm}{2cm}
-This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs)—a novel framework for modeling sophisticated learning dynamics in environments with partial observability.
-Traditional economic models provide valuable theoretical insights but often rely on simplified assumptions about agents' behavior or the learning environment, while reinforcement learning approaches offer computational tools that frequently lack theoretical foundations for strategic adaptation.
-Our framework addresses three fundamental challenges: modeling strategic adaptation in non-stationary environments, incorporating partial observability as an intrinsic feature, and capturing long-term strategic considerations in learning contexts.
-We develop POLARIS (Partially Observable Learning with Active Reinforcement In Social environments), a practical algorithm implementing our theoretical framework, and apply it to two canonical social learning scenarios: strategic experimentation with observable rewards and learning without experimentation through action observation.
-Our results validate theoretical predictions about ...
-while demonstrating how reinforcement learning agents can discover sophisticated strategies for information revelation and strategic influence, providing both theoretical insights and computational tools for understanding complex social learning dynamics.
+This thesis bridges economic social learning theory and multi-agent reinforcement learning by developing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm.
+Our framework addresses fundamental challenges in modeling adaptive behavior under partial observability, where agents must simultaneously learn about uncertain environments and evolving strategies of others.
+We extend Active Markov Games to partially observable settings, derive theoretical convergence results, and develop a practical algorithm combining Transformer-based belief processing, Graph Neural Networks with attention mechanisms, and reinforcement learning optimization.
+Applied to strategic experimentation and learning without experimentation scenarios, our approach reveals dynamic role assignment as a robust organizing principle where agents naturally differentiate into complementary roles enhancing collective information processing.
+We find that free-riding behavior does not lead to uniform inefficiencies—for some agents, performance in larger networks exceeds autarky levels.
+Our two-staged analysis methodology addresses computational challenges like catastrophic forgetting while providing systematic approaches for extracting insights from multi-agent learning dynamics.
+The framework contributes theoretical foundations to multi-agent reinforcement learning and computational tools to economic theory, demonstrating how interdisciplinary approaches can illuminate complex social learning phenomena neither field could address alone.
 \end{adjustwidth}
@@
 \input{background}
-\chapter{Theoretical Framework}
+\chapter{Reinforcement Learning Framework}
 \input{theory}
-\chapter{Results}
+\chapter{Evaluation}
 \input{results}

### 2025-06-06 paper/conclusion.tex
Update appendices

@@
 Our implementation incorporates Graph Neural Networks with temporal and spatial attention mechanisms capturing network topology and temporal dependencies.
-We introduce theoretically grounded off-policy asymmetric analysis methods moving beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence.
+We introduce theoretically grounded off-equilibrium asymmetric analysis methods moving beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence.
 Despite these advances, catastrophic forgetting prevents direct measurement of predicted equilibrium strategies, requiring alternative analytical approaches, and computational complexity limits analysis to small networks and finite horizons, potentially missing asymptotic behaviors theoretical models emphasize.

### 2025-06-06 paper/intro.tex
Update appendices

@@
 We construct observed reward functions that enable reinforcement learning without direct reward signals and develop specialized transformer loss functions for Lévy process observations.
-Our theoretically grounded off-policy asymmetric analysis methods move beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence—capabilities essential for understanding real-world social learning dynamics.
+Our theoretically grounded off-equilibrium asymmetric analysis methods move beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence—capabilities essential for understanding real-world social learning dynamics.
 

### 2025-06-06 paper/appendix.tex
Update results.

@@
 We describe each component's structure, activation functions, and design considerations to enable reproducibility and thorough understanding of our approach.
-
-\section{Belief Processing Module}
-
-In our POLARIS implementation, agents maintain and update belief states using a Transformer-based architecture~\cite{vaswani2017attention}, which effectively processes sequential observations while preserving the temporal relationships critical for social learning tasks.
-
-The TransformerBeliefProcessor replaces traditional recurrent architectures with a self-attention mechanism that can capture complex dependencies across observation sequences.
-The module takes a signal (private observation), neighbor actions, and the current belief state as inputs, then produces an updated belief state and belief distribution over possible environmental states.
-
-The belief processor begins with an input projection layer that maps the concatenated signal and neighbor action vectors to a hidden dimension.
-Specifically, for an agent receiving signal $o_t$ and observing neighbor actions $\boldsymbol{a}_t$, the input vector $x_t = [o_t, \boldsymbol{a}_t]$ is projected as:
-
-\begin{equation}
-    x_{\text{projected}} = W_{\text{proj}}x_t + b_{\text{proj}}
-\end{equation}
-
-This projection is then passed through a transformer encoder with multi-head self-attention. The transformer encoder consists of attention layers defined as:
-
-\begin{equation}
-    \text{Attention}(Q, K, V) = \text{softmax}\left(\frac{QK^T}{\sqrt{d_k}}\right)V
-\end{equation}
-
-where $Q$, $K$, and $V$ are the query, key, and value matrices derived from the input, and $d_k$ is the dimensionality of the key vectors.
-The multi-head attention mechanism applies this attention function in parallel across multiple representation subspaces, then concatenates the results:
-
-\begin{equation}
-    \text{MultiHead}(X) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O
-\end{equation}
-
-where each head is computed as $\text{head}_i = \text{Attention}(XW^Q_i, XW^K_i, XW^V_i)$. Our implementation uses 4 attention heads with a dimension of 64 per head.
-
-The transformer encoder is followed by feed-forward networks with ReLU activations:
-
-\begin{equation}
-    \text{FFN}(x) = \max(0, xW_1 + b_1)W_2 + b_2
-\end{equation}
-
-A belief head at the output projects the transformed representation to a probability distribution over possible environment states:
-
-\begin{equation}
-    b_{\text{dist}} = \text{softmax}(W_{\text{belief}}h_{\text{final}} + b_{\text{belief}})
-\end{equation}
-
-Where $h_{\text{final}}$ is the final hidden state from the transformer.
-This distribution represents the agent's belief about the current environmental state.
-The transformed representation also becomes the new belief state that is maintained across time steps.
-
-The transformer architecture offers several advantages for belief processing in partially observable environments.
-First, it can model arbitrarily long-range dependencies in observation sequences without the vanishing gradient issues that affect recurrent networks.
-Second, the self-attention mechanism provides a natural way to weight the importance of different observations in forming beliefs.
-Third, the positional encodings allow the model to incorporate temporal information while maintaining permutation invariance within each time step.
-
-\section{Inference Learning Module}
-
-The Inference Learning Module enables agents to predict and model the behavior of other agents, which is essential for effective social learning.
-POLARIS implements a Graph Neural Network (GNN) approach for this module, which explicitly captures the network structure of agent interactions.
-
-The GNN-based inference module represents agents and their interactions as a graph, where nodes correspond to agents and edges represent observational relationships.
-For each node, features include the agent's observation and action.
-
-The graph representation treats each agent as a node, with edges representing observational relationships.
-The GNN uses graph attention layers (GAT) that compute attention coefficients between connected nodes:
-
-\begin{equation}
-    e_{ij} = \text{LeakyReLU}(a^T[Wh_i || Wh_j])
-\end{equation}
+POLARIS represents a significant advancement over traditional multi-agent reinforcement learning frameworks by employing Graph Neural Networks (GNNs) as the primary architecture for modeling agent interactions and temporal dependencies in partially observable social learning environments.
+
+POLARIS employs a modular architecture consisting of four primary components that work in tandem to enable effective learning in partially observable multi-agent environments.
+The belief processing module maintains belief states using transformers with attention mechanisms, while the inference learning module models other agents' behavior using Temporal Graph Neural Networks.
+The policy network maps beliefs and latent states to action decisions, and dual value networks estimate expected returns using a critic architecture.
+All components operate over the joint space of states, belief states, and policy parameters as defined in our Partially Observable Active Markov Game framework, explicitly modeling how actions influence both environmental dynamics and other agents' learning processes.
+
+\section{Transformer Network}
+
+The belief processing module maintains and updates agents' belief states about the underlying environment state using a transformer-based architecture~\cite{vaswani2017attention}.
+This component processes sequences of observations and actions to form beliefs about the partially observable environment.
+The belief processor employs a transformer encoder with an input dimension configurable based on the observation space, using dimension $|S|$ for discrete observation spaces and dimension 1 for continuous observation spaces.
+The hidden dimension defaults to 256, with 4 attention heads across 2 layers and a dropout rate of 0.1.
+
+For discrete observation spaces, the input signal $\mathbf{o}_t \in \mathbb{R}^{|S|}$ is projected to the hidden dimension through $\mathbf{x}_{\text{proj}} = W_{\text{proj}}\mathbf{o}_t + \mathbf{b}_{\text{proj}}$.
+For continuous observation spaces with $\mathbf{o}_t \in \mathbb{R}$, a separate projection layer handles the scalar input: $\mathbf{x}_{\text{proj}} = W_{\text{cont}}\mathbf{o}_t + \mathbf{b}_{\text{cont}}$.
+Positional encodings are added to capture temporal ordering: $\mathbf{x}_{\text{input}} = \mathbf{x}_{\text{proj}} + \mathbf{PE}$, where $\mathbf{PE}$ is a learned positional encoding parameter.
+
+The transformer processes the sequence through multi-head self-attention layers: $\text{MultiHead}(\mathbf{X}) = \text{Concat}(\text{head}_1, \ldots, \text{head}_h)W^O$, where each attention head computes:
+
+\begin{equation}
+    \text{head}_i = \text{Attention}(\mathbf{X}W^Q_i, \mathbf{X}W^K_i, \mathbf{X}W^V_i)
+\end{equation}
+
+The final belief distribution is computed using appropriate activations based on the observation space: $\mathbf{b}_{\text{dist}} = \text{softmax}(W_{\text{discrete}}\mathbf{h}_{\text{final}} + \mathbf{b}_{\text{discrete}})$ for discrete observation spaces and $\mathbf{b}_{\text{dist}} = \text{sigmoid}(W_{\text{continuous}}\mathbf{h}_{\text{final}} + \mathbf{b}_{\text{continuous}})$ for continuous observation spaces, where $\mathbf{h}_{\text{final}}$ is the output from the transformer layers.
+
+\section{Graph Neural Network}
+
+The core innovation of POLARIS lies in its use of Graph Neural Networks~\citep{hamilton2020graph} to explicitly model the network structure of agent interactions.
+Unlike traditional approaches that treat other agents as part of the environment, our GNN-based architecture captures the relational structure between agents and enables sophisticated reasoning about network effects in social learning.
+
+The Temporal GNN serves as the inference learning module, enabling agents to predict and model the behavior of other agents over time.
+This component represents agents and their interactions as a dynamic graph where nodes correspond to agents and edges represent observational relationships.
+For each agent $i$, the GNN constructs a graph representation where each agent becomes a node with features encoding their current observation and action, connections represent observational relationships based on network topology, and node features consist of the concatenation of belief state and action: $[\mathbf{b}^i_t; a^i_t]$ for the ego agent, $[\mathbf{0}; a^j_t]$ for neighbors.
+allocation values are directly included in the feature representation.
+
+The GNN employs Graph Attention Networks (GAT)~\citep{veličković2018graph} that compute attention coefficients between connected nodes:
+
+\begin{equation}
+    e_{ij} = \text{LeakyReLU}\left(\mathbf{a}^T\left[W\mathbf{h}_i \| W\mathbf{h}_j\right]\right)
+\end{equation}
+
 \begin{equation}
@@
 
-where $h_i$ represents the features of node $i$, $W$ is a learned weight matrix, $a$ is an attention vector, and $\mathcal{N}_i$ is the neighborhood of node $i$.
-The node representations are then updated using these attention weights:
-
-\begin{equation}
-    h'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W h_j\right)
-\end{equation}
-
-The temporal aspect is handled through a window-based memory system that maintains a history of previous graph states. A multi-head attention mechanism operates across this temporal window:
-
-\begin{equation}
-    \text{TemporalAttention}(X_t, X_{t-1:t-k}) = \text{softmax}\left(\frac{QK^T}{\sqrt{d}}\right)V
-\end{equation}
-
-where $X_t$ is the current graph representation, $X_{t-1:t-k}$ represents previous graph states, and $Q$, $K$, $V$ are learned projections.
-The GNN implementation uses configurable parameters for the number of graph layers (default: 2), attention heads (default: 4), and temporal window size (default: 5).
-
-The GNN receives a combination of the current latent estimate, the agent's observations, actions, and rewards.
-Formally, its input for agent $i$ is defined as $x_i = [\hat{\boldsymbol{z}}^{-i}_{t}, o^{i}_{t}, \boldsymbol{a}_{t}, r^{i}_{t}, o^{i}_{t+1}]$, where $\hat{\boldsymbol{z}}^{-i}_{t} \in \mathbb{R}^{d}$ represents the current estimate of other agents' latent states with dimension $d=256$ in our implementation.
-
-After processing through the graph layers and temporal attention mechanism, the GNN outputs parameters of a Gaussian distribution over the next latent state:
-
-\begin{equation}
-    \mu_{t} = W_{\mu}h^{\text{final}}_i + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma_{t} = W_{\sigma}h^{\text{final}}_i + b_{\sigma}
-\end{equation}
-
-where $\mu_{t}$ is the mean vector and $\log\sigma_{t}$ is the log-standard-deviation vector of the distribution, and $h^{\text{final}}_i$ is the final node representation for agent $i$.
-
-The GNN also outputs an opponent belief distribution through a separate head:
-
-\begin{equation}
-    p_{\text{opp}} = \text{softmax}(W_{\text{opp}}h^{\text{final}}_i + b_{\text{opp}})
-\end{equation}
-
-This distribution represents the agent's prediction of other agents' beliefs about the environment state.
-
-The latent variables are sampled using the reparameterization trick to enable backpropagation:
-
-\begin{equation}
-    \hat{\boldsymbol{z}}^{-i}_{t+1} = \mu_{t} + \exp(0.5 \cdot \log\sigma_{t}) \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-The GNN-based inference module is trained using the Evidence Lower Bound (ELBO) objective function:
-
-\begin{equation}
-    J^{i}_{\text{elbo}} = \mathbb{E}[\log \mathbb{P}(\boldsymbol{a}^{-i}_{t}|o^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) - \alpha_{\text{KL}}D_{\text{KL}}(\mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t+1}|\tau^i_t) || \mathcal{N}(\hat{\boldsymbol{z}}^{-i}_{t}))]
-\end{equation}
-
-where the first term represents the reconstruction log-likelihood and the second term is a KL divergence regularization that encourages temporal consistency in the latent space.
-The hyperparameter $\alpha_{\text{KL}}$ controls the strength of this regularization.
-
-\section{Reinforcement Learning Module}
-
-The reinforcement learning module optimizes the agent's policy based on beliefs, inferences about other agents, and received rewards.
-POLARIS implements a soft actor-critic (SAC)~\cite{haarnoja2018soft} framework that balances exploitation with exploration through entropy regularization.
-
-\subsection{Policy Network Architecture}
-
-The policy network translates belief states and inferred latent variables into action decisions.
-It represents the agent's strategy for maximizing long-term rewards in the social learning environment.
-The policy network takes the agent's belief state and the inferred latent variables of other agents as input: $x_{\pi} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}]$.
-
-The policy is implemented as an MLP with ReLU activations across multiple hidden layers:
-
-\begin{equation}
-    h^1_{\pi} = \text{ReLU}(W^1_{\pi}x_{\pi} + b^1_{\pi})
-\end{equation}
-\begin{equation}
-    h^2_{\pi} = \text{ReLU}(W^2_{\pi}h^1_{\pi} + b^2_{\pi})
-\end{equation}
-
-Each hidden layer contains 256 units. For discrete action spaces, the policy outputs action probabilities:
-
-\begin{equation}
-    \pi^{i}(a^{i}|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = \text{softmax}(W_{\text{out}}h^2_{\pi} + b_{\text{out}})
-\end{equation}
-
-where $W_{\text{out}}$ and $b_{\text{out}}$ are part of the policy parameters $\theta^{i}$.
-
-For continuous action spaces, the policy outputs the mean and log standard deviation of a Gaussian distribution:
-
-\begin{equation}
-    \mu(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\mu}h^2_{\pi} + b_{\mu}
-\end{equation}
-\begin{equation}
-    \log\sigma(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}) = W_{\sigma}h^2_{\pi} + b_{\sigma}
-\end{equation}
-
-To sample actions for continuous spaces, we use the reparameterization trick, which enables gradient flow through the sampling process:
-
-\begin{equation}
-    a^i_{\text{raw}} = \mu + \sigma \odot \epsilon, \quad \epsilon \sim \mathcal{N}(0, I)
-\end{equation}
-
-A squashing function (tanh) is then applied to bound the actions within the range $[-1, 1]$:
-
-\begin{equation}
-    a^i = \tanh(a^i_{\text{raw}})
-\end{equation}
-
-This bounded action can be scaled to the appropriate range required by the environment.
-When using this squashing function, the log probability calculation must be adjusted using the change of variables formula:
-
-\begin{equation}
-    \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) = \log \mathcal{N}(a^i_{\text{raw}}|\mu, \sigma) - \sum_{j} \log(1 - \tanh^2(a^i_{\text{raw},j}))
-\end{equation}
-
-where the second term is the logarithm of the absolute determinant of the Jacobian of the tanh transformation.
-
-Following the soft actor-critic framework, the policy is trained to maximize both expected returns and entropy:
-
-\begin{equation}
-    J^{i}_{\pi}(\theta^{i}) = \mathbb{E}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta}) + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))]
-\end{equation}
-
-where $\alpha_e$ is the entropy weight (temperature parameter) that controls the balance between exploitation and exploration. Higher values of $\alpha_e$ encourage more exploration.
-
-For discrete action spaces, the entropy is calculated directly from the action probabilities:
-\begin{equation}
-    H(\pi^{i}) = -\sum_{a^i} \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i) \log \pi^i(a^i|b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i)
-\end{equation}
-
-For continuous action spaces, the entropy of the base Gaussian distribution is used:
-\begin{equation}
-    H(\pi^{i}) = \frac{1}{2}\log\det(2\pi e \sigma^2(b^i_t, \hat{\boldsymbol{z}}^{-i}_t; \theta^i))
-\end{equation}
-
-When using the tanh squashing function, this entropy calculation must be adjusted to account for the change in probability density.
-
-\subsection{Value Network Architecture}
-
-The value network estimates the expected future rewards for state-action pairs, providing the foundation for policy optimization.
-POLARIS implements a dual critic approach to mitigate overestimation bias, a common issue in Q-learning algorithms.
-
-The value network receives the belief state, inferred latent variables, and joint action as input: $x_{q} = [b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}]$.
-Each value network follows an MLP architecture with three hidden layers:
-
-\begin{equation}
-    h^1_{q} = \text{ReLU}(W^1_{q}x_{q} + b^1_{q})
-\end{equation}
-\begin{equation}
-    h^2_{q} = \text{ReLU}(W^2_{q}h^1_{q} + b^2_{q})
-\end{equation}
-\begin{equation}
-    h^3_{q} = \text{ReLU}(W^3_{q}h^2_{q} + b^3_{q})
-\end{equation}
-
-Each hidden layer contains 256 units. The network outputs a scalar value estimate:
-
-\begin{equation}
-    q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}) = W_{q,\text{out}}h^3_{q} + b_{q,\text{out}}
-\end{equation}
-
-where $\beta \in \{1, 2\}$ indicates which of the two value networks is being used. The value function is trained using the soft Bellman equation, which incorporates the entropy-regularized objective:
-
-\begin{equation}
-    y = r^{i}_{t} - \rho^{i}_{\theta^i} + v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})
-\end{equation}
-\begin{equation}
-    J^{i}_{q}(\psi^{i}_{\beta}, \rho^{i}_{\theta^i}) = \mathbb{E}[(y - q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, \boldsymbol{a}_{t}; \psi^{i}_{\beta}))^{2}]
-\end{equation}
-
-where $\bar{\psi}^{i}_{\beta}$ are the target network parameters, updated using an exponential moving average:
-
-\begin{equation}
-    \bar{\psi}^{i}_{\beta} \leftarrow \tau_{q}\psi^{i}_{\beta} + (1 - \tau_{q})\bar{\psi}^{i}_{\beta}
-\end{equation}
-
-with $\tau_{q} = 0.005$ in our implementation.
-The term $\rho^{i}_{\theta^i}$ represents the average reward, which is used for differential returns in continuing tasks.
-The soft value function incorporates policy entropy:
-
-\begin{equation}
-    v^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}) = \mathbb{E}_{a^i \sim \pi^i(\cdot|b^i_t,\hat{\boldsymbol{z}}^{-i}_t;\theta^i)}[\min_{\beta=1,2}q^{i}_{\theta^i}(b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}, a^{i}_{t}; \psi^{i}_{\beta})] + \alpha_e H(\pi^{i}(\cdot|b^{i}_{t}, \hat{\boldsymbol{z}}^{-i}_{t}; \theta^{i}))
-\end{equation}
-
-POLARIS can operate in both discounted and average reward modes.
-In discounted mode, the target is simply $y = r^{i}_{t} + \gamma \cdot v^{i}_{\theta^i}(b^{i}_{t+1}, \hat{\boldsymbol{z}}^{-i}_{t+1}; \bar{\psi}^{i}_{\beta})$, where $\gamma$ is the discount factor.
-In average reward mode, the differential returns formulation with $\rho^{i}_{\theta^i}$ is used instead.
-
-The value network architecture directly implements our theoretical framework of active Markov games, estimating returns that account for the influence of current actions on future environmental states and the policy parameters of other agents.
-
-\section{Elastic Weight Consolidation}
-
-POLARIS implements Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} to prevent catastrophic forgetting when agents need to maintain performance across multiple tasks or environments.
-EWC adds a regularization term to the loss function that penalizes large changes to parameters that were important for previously learned tasks.
-
-The EWC loss is defined as:
-
-\begin{equation}
-    \mathcal{L}_{\text{EWC}} = \lambda \sum_{i} F_i (\theta^i - {\theta^i}^*)^2
-\end{equation}
-
-where $\lambda$ is the importance factor, $F_i$ is the Fisher information for parameter $\theta^i$, and ${\theta^i}^*$ is the optimal parameter value for the previous task.
-The Fisher information matrix is calculated by:
-
-\begin{equation}
-    F = \mathbb{E}_{x \sim \mathcal{D}, y \sim \mathbb{P}(y|x; \theta)} \left[ \nabla_\theta \log \mathbb{P}(y|x; \theta) \nabla_\theta \log \mathbb{P}(y|x; \theta)^T \right]
-\end{equation}
-
-In practice, POLARIS approximates this using samples from the replay buffer.
-The implementation offers both standard EWC and online EWC variants.
-The online variant continuously updates the Fisher matrix with a decay factor, allowing for sequential learning across multiple tasks without storing separate Fisher matrices:
-
-\begin{equation}
-    F_{\text{new}} = \gamma F_{\text{old}} + F_{\text{current}}
-\end{equation}
-
-where $\gamma$ is a decay factor typically set to 0.95.
-EWC is particularly valuable in social learning contexts where agents may need to adapt to different partner policies without forgetting effective strategies learned previously.
-
-In practice, all these neural network components operate in tandem, with the belief state processor tracking the environmental state, the inference module predicting other agents' behavior, and the reinforcement learning module optimizing the agent's policy.
-This integrated approach enables POLARIS to effectively navigate the complexities of partially observable multi-agent environments with non-stationary dynamics.
-
-\section{Implementation Details}
-
-POLARIS incorporates several crucial implementation details that enhance its performance in social learning environments.
-Double Q-learning is employed to prevent overestimation bias, a common issue in value-based reinforcement learning methods.
-This approach maintains two separate Q-networks and uses the minimum of their predictions for target value calculations, providing a more pessimistic and reliable estimate of expected returns.
-Such conservative value estimation is particularly important in social learning, where overestimated values can lead to overly aggressive strategies that fail to account for the strategic adaptations of other agents.
-
-Temperature scaling is applied to softmax outputs in the belief distribution calculations, controlling the sharpness of the resulting probability distributions.
-This technique produces more stable belief distributions, preventing premature convergence to overly confident beliefs based on limited evidence.
-The temperature parameter can be adjusted to balance exploration and exploitation in the belief space, with higher values producing more uniform distributions that encourage consideration of alternative hypotheses about the environment state.
-
-For robust latent sampling from the variational posterior, POLARIS employs several numerical stability safeguards.
-These include clamping log-variances to prevent extreme values, enforcing minimum and maximum bounds on variances, and using epsilon terms to avoid division by zero or other numerical instabilities.
-These precautions are essential when working with variational methods in complex, high-dimensional spaces, ensuring reliable performance even with noisy or ambiguous social signals.
-
-Gradient clipping is applied across all network updates to prevent exploding gradients, a common issue in deep reinforcement learning, especially with recurrent or transformer architectures.
-By limiting the maximum gradient norm, POLARIS maintains stable training even when encountering unusual observations or reward patterns.
-Additionally, separate optimizers are maintained for each network component, allowing for different learning rates and optimization strategies tailored to the specific characteristics of each module.
-
-The POLARIS implementation significantly advances beyond the original FURTHER framework by introducing sophisticated belief modeling through Transformers, network-aware representations via GNNs, advantage-weighted Transformer training, and catastrophic forgetting prevention through EWC.
-These enhancements enable more effective learning in the complex, partially observable social environments that characterize our theoretical framework.
-By integrating these components into a cohesive algorithm, POLARIS provides a practical realization of the theoretical Partially Observable Active Markov Game framework, offering a powerful tool for studying social learning dynamics across various network topologies and environmental conditions.
+where $\mathbf{h}_i$ represents the features of node $i$, $W \in \mathbb{R}^{d_{out} \times d_{in}}$ is a learned transformation matrix, $\mathbf{a} \in \mathbb{R}^{2d_{out}}$ is a learned attention vector, and $\mathcal{N}_i$ denotes the neighborhood of node $i$.
+The node representations are updated using these attention weights:
+
+\begin{equation}
+    \mathbf{h}'_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha_{ij} W \mathbf{h}_j\right)
+\end{equation}
+
+where $\sigma$ is a non-linear activation function (ReLU in our implementation).
+
+To capture different types of relationships between agents, the GNN employs multi-head attention with $K=4$ attention heads:
+
+\begin{equation}
+    \mathbf{h}'_i = [\mathbf{h}^1_i; \mathbf{h}^2_i; \ldots; \mathbf{h}^K_i], \quad \text{where} \quad \mathbf{h}^k_i = \sigma\left(\sum_{j \in \mathcal{N}_i} \alpha^k_{ij} W^k \mathbf{h}_j\right)
+\end{equation}
+
+where $[\cdot; \cdot]$ denotes concatenation and each head $k$ has its own parameters $W^k$ and $\mathbf{a}^k$.
+This allows the model to attend to different aspects of agent relationships simultaneously.
+
+A critical innovation in our Temporal GNN is the incorporation of temporal dependencies through a sliding window memory mechanism.
+The system maintains a buffer of previous graph representations over a temporal window of size $T=5$:
+
+\begin{equation}
+    \mathcal{M}_t = \{\mathbf{H}_{t-T+1}, \mathbf{H}_{t-T+2}, \ldots, \mathbf{H}_t\}
+\end{equation}
+
+where $\mathbf{H}_s$ represents the node features at time step $s$. Temporal attention is applied across this sequence using a standard transformer attention mechanism:
+
+\begin{equation}
+    \text{TemporalAttention}(\mathbf{Q}_t, \mathbf{K}_{t-T+1:t}, \mathbf{V}_{t-T+1:t}) = \text{softmax}\left(\frac{\mathbf{Q}_t\mathbf{K}_{t-T+1:t}^T}{\sqrt{d}}\right)\mathbf{V}_{t-T+1:t}
+\end{equation}
+
+This temporal attention mechanism enables the model to capture how agent behaviors evolve over time and identify patterns in their learning dynamics.
+
+The Temporal GNN outputs parameters for a variational posterior distribution over latent states representing other agents' hidden characteristics:
+
+\begin{align}
+    \boldsymbol{\mu}_t &= W_{\mu}\mathbf{h}^{\text{final}}_i + \mathbf{b}_{\mu} \\
+    \log\boldsymbol{\sigma}_t &= W_{\sigma}\mathbf{h}^{\text{final}}_i + \mathbf{b}_{\sigma}
+\end{align}
+
+where $\mathbf{h}^{\text{final}}_i$ is the final node representation for agent $i$ after all GNN layers and temporal attention. The latent variables are sampled using the reparameterization trick:
+
+\begin{equation}
+    \hat{\mathbf{z}}^{-i}_{t+1} = \boldsymbol{\mu}_t + \boldsymbol{\sigma}_t \odot \boldsymbol{\epsilon}, \quad \boldsymbol{\epsilon} \sim \mathcal{N}(\mathbf{0}, \mathbf{I})
+\end{equation}
+
+\section{Policy and Value Networks}
+
+The policy networks map belief states and inferred latent variables to action decisions, implementing the agent's strategy for maximizing long-term rewards.
+For discrete action spaces, the policy network outputs categorical distributions:
+
+\begin{align}
+    \mathbf{h}^1 &= \text{ReLU}(W^1[\mathbf{b}^i_t; \hat{\mathbf{z}}^{-i}_t] + \mathbf{b}^1) \\
+    \mathbf{h}^2 &= \text{ReLU}(W^2\mathbf{h}^1 + \mathbf{b}^2) \\
+    \boldsymbol{\pi}^i(\cdot|\mathbf{b}^i_t, \hat{\mathbf{z}}^{-i}_t; \boldsymbol{\theta}^i) &= \text{softmax}(W^{\text{out}}\mathbf{h}^2 + \mathbf{b}^{\text{out}})
+\end{align}
+
+where $[\cdot; \cdot]$ denotes concatenation.
+
+POLARIS employs dual Q-networks~\cite{hasselt2016deep} to mitigate overestimation bias, a critical consideration in multi-agent settings where overconfident value estimates can lead to suboptimal strategic behaviors.
+For discrete actions, the Q-networks take belief states, latent variables, and one-hot encoded neighbor actions:
+
+\begin{align}
+    \mathbf{x}_q &= [\mathbf{b}^i_t; \hat{\mathbf{z}}^{-i}_t; \mathbf{a}^{\text{neighbors}}_{\text{onehot}}] \\
+    \mathbf{h}^1_q &= \text{ReLU}(W^1_q\mathbf{x}_q + \mathbf{b}^1_q) \\
+    \mathbf{h}^2_q &= \text{ReLU}(W^2_q\mathbf{h}^1_q + \mathbf{b}^2_q) \\
+    \mathbf{Q}^i &= W^{\text{out}}_q\mathbf{h}^2_q + \mathbf{b}^{\text{out}}_q
+\end{align}
+
+Target networks are maintained for stability, updated using exponential moving averages:
+
+\begin{equation}
+    \boldsymbol{\theta}_{\text{target}} \leftarrow \tau \boldsymbol{\theta} + (1-\tau)\boldsymbol{\theta}_{\text{target}}
+\end{equation}
+
+with $\tau = 0.005$ in our implementation.
 

### 2025-06-06 paper/conclusion.tex
Update results.

--- 2025-05-26 paper/conclusion.tex
@@
-This thesis bridges economic social learning theory and multi-agent reinforcement learning by introducing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm.
-Our framework addresses fundamental challenges in modeling strategic adaptation under partial observability, where agents must simultaneously learn about their environment and strategically influence others' learning processes.
+This thesis bridges economic social learning theory and multi-agent reinforcement learning by developing Partially Observable Active Markov Games (POAMGs) and the POLARIS algorithm.
+Our framework addresses fundamental challenges in modeling adaptive behavior under partial observability, demonstrating how computational approaches can complement traditional economic theory while providing new insights into complex social learning dynamics.
+The integration of these traditionally separate domains opens new research directions that neither field could pursue independently, establishing a foundation for understanding how rational agents learn and adapt in environments characterized by both environmental uncertainty and strategic interdependence.
 
-Our theoretical contributions establish POAMGs as a rigorous mathematical framework extending Active Markov Games to partially observable settings.
-The convergence analysis and policy gradient theorems provide solid foundations for the POLARIS algorithm, which successfully implements this framework through an integrated architecture combining belief processing, inference learning, and reinforcement learning modules.
+Our work makes four interconnected contributions that advance both theoretical understanding and computational capabilities.
+First, we developed the POAMG framework, extending Active Markov Games to partially observable settings where agents reason about both environmental uncertainty and evolving strategies of others.
+This formalization captures the essential tension between exploration for private information and exploitation of social information that characterizes real-world learning scenarios.
+Second, we provided theoretical analysis of convergence and equilibrium properties in POAMGs, establishing conditions for stochastic stability and deriving policy gradient theorems for average and discounted reward objectives.
+We extended the framework to continuous-time dynamics through stochastic differential equations and revealed how traditional game-theoretic equilibrium concepts relate to active equilibrium when agents account for others' learning processes.
+These theoretical foundations provide rigorous guarantees for algorithm convergence while preserving the strategic structure inherent in social learning problems.
+Third, we introduced POLARIS, combining belief processing through Transformer models, inference learning via variational methods, and reinforcement learning optimization.
+This enables agents to develop sophisticated strategies accounting for both environmental partial observability and strategic adaptation by other agents.
+The algorithm's modular architecture allows for principled handling of belief updates, strategic reasoning, and policy optimization in a unified framework.
+Fourth, we validated our framework through applications to strategic experimentation and learning without experimentation, demonstrating how our approach captures dynamic role assignment, information generation and exploitation, and the emergence of learning barriers and coordination benefits.
+These applications illustrate the framework's versatility in addressing diverse social learning phenomena while maintaining computational tractability.
 
-Experimental validation across strategic experimentation and learning without experimentation scenarios demonstrates our framework's effectiveness.
-POLARIS agents converge to theoretically predicted equilibrium strategies, validating key insights about free-riding behavior and optimal experimentation intensity.
-Our results confirm the existence of social learning barriers while revealing coordination benefits in larger networks.
-Crucially, we uncover a dynamic division of labor where agents assume roles as information generators or exploiters based on signal quality rather than network position.
+Our experimental analysis reveals that dynamic role assignment is a robust organizing principle of multi-agent learning systems.
+Across both scenarios, agents naturally differentiate into complementary roles enhancing collective information processing.
+This finding has profound implications for understanding how efficient information aggregation emerges spontaneously in social systems without central coordination.
+Our results show that free-riding behavior does not lead to predicted inefficiencies for the whole population—performance of some agents in larger networks substantially exceeds autarky levels.
+This challenges conventional wisdom about free-riding and suggests that network effects can compensate for individual incentive problems in ways not captured by traditional theoretical models.
+The computational approach illuminates fundamental tension between theoretical and practical approaches: while economic models envision agents developing ex ante strategies optimal across all states, reinforcement learning agents converge to ex post strategies optimized for specific realized states.
+This tension reveals limitations in directly applying computational methods to test theoretical predictions while suggesting opportunities for more realistic behavioral models that account for cognitive constraints and learning dynamics.
 
-Future research could extend the framework to incorporate heterogeneous agent types, dynamic network structures, or mechanism design principles.
-Applications to contemporary challenges such as misinformation spread or algorithmic recommendation systems could demonstrate broader relevance.
+Our methodological contributions extend beyond the specific applications studied.
+The two-staged analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting in neural networks.
+The discretization approach for continuous-time economic models, treating Lévy processes through Euler-Maruyama schemes and mapping continuous decisions to discrete action probabilities, provides a template for computational implementation while preserving essential incentive structures.
+We constructed an observed reward function that enables reinforcement learning in environments without direct reward signals and developed a specialized transformer loss function for Lévy process observations.
+Our implementation incorporates Graph Neural Networks with temporal and spatial attention mechanisms that capture both network topology and temporal dependencies in multi-agent interactions.
+Furthermore, we introduce off-equilibrium asymmetric analysis methods that move beyond the symmetric equilibria analysis in economic theory, allowing for heterogeneous agent behaviors and asymmetric strategy convergence patterns.
 
-This work demonstrates that integrating economic theory and computational methods yields insights neither approach could achieve alone.
-The POAMG framework and POLARIS algorithm provide both theoretical understanding and practical tools for analyzing complex social learning processes, establishing a foundation for future interdisciplinary research.
-As multi-agent systems become increasingly prevalent, such integrated approaches will be essential for understanding and shaping collective intelligence emerging from strategic interactions among learning agents.
+The technical innovations in belief representation and inference learning represent significant advances in handling partial observability in multi-agent settings.
+Our approach to combining variational inference with transformer architectures for belief processing enables agents to maintain sophisticated internal models of both environmental states and other agents' strategies.
+The integration of these components with policy gradient methods creates a principled framework for learning in complex strategic environments that has applications beyond social learning scenarios.
+
+Despite these advances, our approach faces important limitations that highlight directions for future research.
+Catastrophic forgetting prevents direct measurement of equilibrium strategies that economic theory predicts, requiring alternative analytical approaches.
+Computational complexity limits analysis to small networks and short time horizons, potentially missing asymptotic behaviors that theoretical models emphasize.
+The discretization of continuous-time models, while necessary for computational tractability, may introduce artifacts that affect the correspondence between theoretical predictions and computational results.
+
+Several promising avenues emerge from this work.
+First, developing sophisticated continual learning techniques specifically for social learning environments could address catastrophic forgetting limitations through architectures maintaining separate policy components for different states.
+Second, scaling our framework to larger networks and longer horizons would enable validation of asymptotic results and investigation of emergent phenomena in complex social systems.
+Third, extending to dynamic environments where underlying states change over time would broaden applicability to real-world scenarios characterized by non-stationarity.
+Fourth, investigating optimal information structures and network topologies could inform platform and institutional design.
+Fifth, applying our framework to diverse social learning phenomena such as herding behavior, social teaching and mentoring, imitation cascades, and collective decision-making could illuminate the mechanisms underlying these important social processes and inform interventions to promote beneficial outcomes.
+
+This thesis demonstrates the value of interdisciplinary approaches bridging economic theory and computational methods.
+By preserving theoretical rigor while leveraging modern machine learning techniques, we gain insights into complex social phenomena that neither approach could achieve alone.
+The framework provides a template for future work that seeks to combine formal theoretical analysis with sophisticated computational tools.
+The insights have implications for financial markets, organizational learning, online social networks, and collaborative scientific endeavors.
+Dynamic role assignment suggests that effective social learning systems naturally develop specialized roles enhancing collective information processing, providing guidance for platform design and institutional arrangements.
+Understanding how learning barriers emerge and can be overcome informs the design of systems that promote effective knowledge sharing and collective decision-making.
+Our POAMG framework and POLARIS algorithm contribute to multi-agent reinforcement learning literature by providing principled approaches for handling partial observability and strategic adaptation.
+The techniques for belief processing, inference learning, and integrated optimization may prove valuable for other applications requiring sophisticated multi-agent coordination under uncertainty.
+The theoretical foundations we establish create opportunities for developing new algorithms and analyzing their properties in strategic settings.
+Looking forward, the convergence of economic theory and artificial intelligence presents exciting opportunities for advancing understanding of social learning and strategic behavior.
+This thesis provides theoretical foundations and computational tools for future researchers to illuminate the rich dynamics of social learning in complex environments.
+The integration of these domains opens new possibilities for addressing challenges in artificial intelligence, economics, and social sciences more broadly.
+While significant progress has been made in bridging these domains, much work remains to fully realize the potential of this integration, with the ultimate goal of better understanding how intelligent agents can learn from each other to make better decisions in an uncertain world.
+The journey toward this understanding promises to yield insights that will transform both our theoretical understanding and our practical ability to design systems that harness collective intelligence for solving complex problems.

### 2025-06-06 paper/theory.tex
Update results.

@@
 The stochastically stable distribution represents the limiting behavior of the system, independent of initial conditions, allowing us to characterize the long-run outcomes of social learning processes.
+This property is crucial for developing algorithms that optimize for long-term performance rather than myopic rewards, aligning with our goal of modeling sophisticated social learning dynamics.
 This property is crucial for developing algorithms that optimize for long-term performance rather than myopic rewards, aligning with our goal of modeling sophisticated social learning dynamics.
@@
 It consists of three integrated modules: a belief processing module, an inference learning module, and a reinforcement learning module, which operate in concert to enable sophisticated social learning in partially observable environments.
-The architecture integrates several neural network components working in tandem: a Transformer-based belief processor~\cite{vaswani2017attention} provides sophisticated temporal pattern recognition through its self-attention mechanisms; an inference module implementing a Graph Neural Network (GNN)~\cite{scarselli2009graph} with temporal attention for network-aware representations; and Multi Agent Soft Actor-Critic (MASAC) following \citet{kim2022influencing} with both average and discounted reward formulations to address the long-term planning requirements of social learning.
-To maintain performance across changing environments, particularly when the true state changes, POLARIS employs Elastic Weight Consolidation (EWC)~\cite{kirkpatrick2017overcoming} that selectively preserves important parameters while allowing adaptation to new conditions.
+The architecture integrates several neural network components working in tandem: a Transformer-based belief processor~\cite{vaswani2017attention} provides sophisticated temporal pattern recognition through its self-attention mechanisms; a Temporal Graph Neural Network (GNN) with multi-head attention for network-aware representations; and Soft Actor-Critic (SAC) with dual Q-networks supporting discrete action spaces and both average and discounted reward formulations.
 We provide the detailed network architectures in Appendix \ref{appendix:neural_architectures}.
@@
 
-This explicit representation allows for more interpretable belief states and enables advantage-weighted training, where the belief processing is optimized not just to track observations but also to produce beliefs that lead to high-value actions.
-By maintaining a probability distribution over states rather than just an abstract representation, the model provides transparency into its decision-making process and facilitates debugging and analysis of social learning dynamics.
+This explicit representation provides transparency into decision-making processes and facilitates debugging and analysis of social learning dynamics.
+
+The belief processor is trained using different objectives depending on the signal type. For discrete signals, it uses a standard cross-entropy loss to track the underlying state distribution:
+\begin{align}
+    J^i_{\text{transformer,discrete}}(\psi^i_{\text{Transformer}}) = \mathbb{E}_{D^i}\left[-\log \mathbb{P}(s_t|b^i_t; \psi^i_{\text{Transformer}})\right]
+\end{align}
+
+For continuous signals (such as Lévy processes), POLARIS employs a specialized transformer loss function that computes the expected signal distribution based on the current belief state and environment parameters:
+\begin{align}
+    J^i_{\text{transformer,continuous}}(\psi^i_{\text{Transformer}}) = \mathbb{E}_{D^i}\left[\|o^i_t - \hat{o}^i_t(b^i_t, \text{env\_params}; \psi^i_{\text{Transformer}})\|^2\right]
+\end{align}
+
+where $D^i$ is agent $i$'s replay buffer containing stored transitions, $\hat{o}^i_t$ is the predicted continuous signal based on the belief state and environment parameters.
+This ensures that the belief processor maintains accurate state estimation capabilities for both discrete and continuous observation types throughout training.
 
@@
 
-POLARIS implements a Graph Neural Network (GNN) with temporal attention for network-aware social learning.
-This inference module represents the multi-agent system as a graph where nodes correspond to agents and edges represent observational relationships in the social network.
-The module outputs distribution parameters:
+POLARIS implements a Temporal Graph Neural Network (GNN) with multi-head attention for network-aware social learning.
+This inference module represents the multi-agent system as a dynamic graph where nodes correspond to agents and edges represent observational relationships that are automatically inferred from the neighbor actions tensor.
+The module supports both discrete and continuous signal processing through separate GNN pathways:
 
 \begin{align}
-    \mu_t, \log\sigma_t = \text{GNN}_{\text{temporal}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i_{\text{GNN}})
+    \mu_t, \log\sigma_t = \text{TemporalGNN}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i_{\text{GNN}})
 \end{align}
 
-Here, $\mu_t$ and $\log\sigma_t$ parameterize a Gaussian distribution from which latent variables $\boldsymbol{\hat{z}}^{-i}_t$ are sampled, encoding information about other agents' policies and beliefs.
-The GNN architecture adapts dynamically to the network topology, enabling automatic configuration for various social network structures.
-It utilizes multi-head attention mechanisms across both spatial (network) and temporal dimensions, allowing it to differentially weigh connections between agents based on their decision relevance.
-A key feature is the temporal memory system that maintains a sliding window of past states, enabling temporal attention mechanisms that help the model reason about the evolution of other agents' beliefs and strategies over time.
-This approach proves especially effective for complex network topologies where information flow patterns significantly influence learning dynamics.
+The network topology is dynamically constructed from observed neighbor actions, where non-zero entries indicate actual neighbors (edges exist) and zero entries indicate non-neighbors (no edges).
+This approach enables automatic adaptation to various social network structures without requiring explicit network specification.
 
-The inference module learns a mapping from observable trajectories to latent variables that are predictive of other agents' behaviors, optimized using the Evidence Lower Bound (ELBO) objective: \footnote{See \cite{kim2022influencing} for a detailed derivation of the ELBO objective in the sequential setting.}
+Key architectural features include dual-pathway processing that employs separate Graph Attention Network (GAT) layers for discrete (one-hot encoded) and continuous signals, enabling flexible handling of different observation types.
+The system incorporates multi-head attention mechanisms that operate both spatially (based on network topology) and temporally, differentially weighing connections based on decision relevance.
+A temporal memory system maintains past node features and edge indices through a sliding window buffer for temporal attention computation.
+The architecture leverages Graph Attention Networks (GAT) with multiple GAT layers containing attention heads that learn to focus on the most relevant neighboring agents.
+
+The inference module learns a mapping from observable trajectories to latent variables predictive of other agents' behaviors, optimized using the Evidence Lower Bound (ELBO) objective \citep{kim2022influencing}:
 
 \begin{align}
-    J^i_{elbo} = \mathbb{E}_{\mathbb{P}(\tau^i_{0:t}),\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{1:t}|\tau^i_{0:t-1};\phi^i_{GNN})}\left[ \sum_{t'=1}^t \log \mathbb{P}(\boldsymbol{a}^{-i}_{t'}|o^i_{t'}, \boldsymbol{\hat{z}}^{-i}_{t'}; \phi^i_{GNN}) \right.
+    J^i_{\text{elbo}} = \mathbb{E}_{\mathbb{P}(\tau^i_{0:t}),\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{1:t}|\tau^i_{0:t-1};\phi^i_{\text{GNN}})}\left[ \sum_{t'=1}^t \log \mathbb{P}(\boldsymbol{a}^{-i}_{t'}|o^i_{t'}, \boldsymbol{\hat{z}}^{-i}_{t'}; \phi^i_{\text{GNN}}) \right.
 \\
-    \left. - \alpha_{KL} D_{KL}(\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'}|\tau^i_{t'-1}; \phi^i_{GNN})||\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'-1}))\right]
+    \left. - \alpha_{KL} D_{KL}(\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'}|\tau^i_{t'-1}; \phi^i_{\text{GNN}})||\mathbb{P}(\boldsymbol{\hat{z}}^{-i}_{t'-1}))\right]
 \end{align}
 
-The ELBO objective balances reconstruction accuracy (predicting other agents' actions) with regularization through the KL divergence term, which encourages temporal consistency in the latent space.
-This is particularly important in social learning settings where abrupt changes in models of other agents can lead to unstable learning dynamics.
-
-The inference module additionally produces opponent belief distributions, enabling agents to model other agents' understanding of the environment:
+The ELBO objective balances reconstruction accuracy (predicting other agents' actions) with temporal consistency through a temporal KL divergence term that encourages smooth evolution of latent representations over time:
 
 \begin{align}
-    \mathbb{P}^i(\boldsymbol{b}^{-i}_t|\tau^i_{0:t}) = \text{Softmax}(f_{\text{opponent\_belief}}(\mu_t, \log\sigma_t))
+    D_{KL}^{\text{temporal}} = \frac{1}{2} \mathbb{E}_t \left[ \log \frac{|\boldsymbol{\Sigma}_{t-1}|}{|\boldsymbol{\Sigma}_t|} - d + \text{tr}(\boldsymbol{\Sigma}_{t-1}^{-1}\boldsymbol{\Sigma}_t) + (\boldsymbol{\mu}_{t-1} - \boldsymbol{\mu}_t)^T \boldsymbol{\Sigma}_{t-1}^{-1} (\boldsymbol{\mu}_{t-1} - \boldsymbol{\mu}_t) \right]
 \end{align}
 
-This second-order belief modeling allows for sophisticated strategic reasoning, as agents can anticipate how others will respond to their actions based not just on past behavior but on inferred beliefs about the environment.
+where $\boldsymbol{\mu}_t$ and $\boldsymbol{\Sigma}_t$ are the mean and covariance of the latent distribution at time $t$.
+This temporal smoothing prevents abrupt changes in opponent models that could destabilize learning dynamics.
 
@@
 
-The reinforcement learning module uses the Soft Actor-Critic (SAC) framework with both average and discounted reward formulations.
-The policy and action-value functions are conditioned on belief states and inferred latent variables:
+The reinforcement learning module uses the Soft Actor-Critic (SAC) framework with dual Q-networks and entropy regularization. The implementation supports discrete action spaces:
 
 \begin{align}
-    \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) &= 
-    \begin{cases}
-        \text{Categorical}(a^i|\text{MLP}_{\text{policy}}(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for discrete actions} \\
-        \mathcal{N}(\mu(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i), \sigma(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for continuous actions}
-    \end{cases} \\
+    \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) &= \text{Categorical}(a^i|\text{MLP}_{\text{policy}}(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) \\
     q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}) &= \text{MLP}_{\text{value}}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta})
@@
 
-For continuous action spaces, the policy network outputs the mean $\mu$ and standard deviation $\sigma$ of a Gaussian distribution, where actions are sampled using the reparameterization trick.
-Then, hyperbolic tangent function is applied to bound the actions within a desired range, with appropriate adjustments to the log probability calculation.
+where MLP stands for \emph{Multi Layer Perceptron}.
+The SAC framework's entropy regularization promotes exploration and prevents premature convergence to suboptimal equilibria, crucial in partially observable settings where perfect inference is impossible.
 
-The SAC framework is particularly well-suited for social learning environments due to its entropy regularization, which promotes exploration and prevents premature convergence to suboptimal equilibria.
-By supporting both categorical distributions for discrete action spaces and Gaussian distributions for continuous action spaces, the policy network can express uncertainty about optimal actions—crucial in partially observable settings where perfect inference is rarely possible.
-The value functions measure expected returns conditioned not only on the agent's belief state but also on inferred representations of other agents' policies, enabling strategic reasoning about the long-term consequences of actions in a multi-agent context.
-The RL module is optimized using three objectives, each addressing a different aspect of the learning problem:
+The RL module optimizes three objectives:
 
-\subparagraph{Value Function Objective} POLARIS supports both discounted and average reward formulations to accommodate different types of social learning problems. For discounted returns:
+\subparagraph{Value Function Objective} POLARIS supports both discounted and average reward formulations. For discounted returns:
 \begin{align}
     J^i_q(\psi^i_{\beta}) &= \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
-    y &= r^i + \gamma \cdot v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+    y &= r^i + \gamma \cdot \min_{\beta=1,2} q^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}, a'^i; \bar{\psi}^i_{\beta})
 \end{align}
 
-where $\gamma \in [0, 1)$ is the discount factor. This formulation is appropriate for scenarios with finite horizons or where near-term performance is particularly valued.
-
-For average reward:
+For average reward (with automatically estimated average reward rate $\rho^i$):
 \begin{align}
-    J^i_q(\psi^i_{\beta}, \rho^i_{\theta^i}) &= \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
-    y &= r^i - \rho^i_{\theta^i} + v^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}; \bar{\psi}^i_{\beta})
+    J^i_q(\psi^i_{\beta}, \rho^i) &= \mathbb{E}_{D^i}\left[(y - q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, \boldsymbol{a}; \psi^i_{\beta}))^2\right] \\
+    y &= r^i - \rho^i + \min_{\beta=1,2} q^i_{\theta^i}(b^i_{t+1}, \boldsymbol{\hat{z}}^{-i}_{t+1}, a'^i; \bar{\psi}^i_{\beta})
 \end{align}
-
-The average reward formulation better captures long-run learning dynamics and asymptotic behavior by equally valuing rewards across all future time periods.
-By supporting both approaches, POLARIS can be tailored to match the specific characteristics of different social learning scenarios without requiring structural changes to the architecture.
 
@@
 \begin{align}
-    J^i_{\pi}(\theta^i) &= \mathbb{E}_{D^i}\left[\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \sum_{\boldsymbol{a}^{-i}} \pi^{-i}(\boldsymbol{a}^{-i}|\boldsymbol{b}^{-i}, \boldsymbol{\hat{z}}^{-i}) \min_{\beta=1,2} q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, a^i, \boldsymbol{a}^{-i}; \psi^i_{\beta}) \right.
-\\
-    & \quad \left. + \alpha_e H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))\right]
+    J^i_{\pi}(\theta^i) &= \mathbb{E}_{D^i}\left[\mathbb{E}_{a^i \sim \pi^i}\left[\min_{\beta=1,2} q^i_{\theta^i}(b^i, \boldsymbol{\hat{z}}^{-i}, a^i, \boldsymbol{a}^{-i}; \psi^i_{\beta}) + \alpha_e H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i))\right]\right]
 \end{align}
-
-For discrete action spaces, the summation and entropy terms are computed directly over the action probabilities.
-For continuous action spaces, the expectation is approximated using samples from the policy, and the entropy term is calculated as:
-\begin{align}
-    H(\pi^i(\cdot|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) = 
-    \begin{cases}
-        -\sum_{a^i} \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) \log \pi^i(a^i|b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i) & \text{for discrete actions} \\
-        \frac{1}{2}\log\det(2\pi e \sigma^2(b^i, \boldsymbol{\hat{z}}^{-i}; \theta^i)) & \text{for continuous actions}
-    \end{cases}
-\end{align}
-
-The entropy calculation must also account for the hyperbolic tangent transformation using the change of variables formula.
-
-The policy objective combines expected future returns with an entropy bonus, creating a balance between exploitation and exploration.
-The entropy term encourages the policy to maintain stochasticity, preventing premature convergence to deterministic policies that might be suboptimal in partially observable settings.
-The use of the minimum value across dual Q-networks helps mitigate overestimation bias—a persistent challenge in Q-learning approaches.
-This is particularly important in social learning contexts where overestimated values can lead to overly optimistic strategies that fail to account for the strategic adaptations of other agents.
 
@@
 
-The overall training process interleaves updates to the three modules, ensuring that improvements in one component can benefit the others within each training iteration.
-Algorithm 1 outlines the complete POLARIS training procedure for a single agent.
+The training process interleaves updates across all modules within each iteration. Algorithm 1 outlines the complete POLARIS training procedure.
 
@@
 \begin{algorithmic}[1]
-\State Initialize belief processor, inference module, policy and value networks with parameters $\psi^i_{\text{Transformer}}$, $\phi^i$, $\theta^i$, $\psi^i_{\beta}$
+\State Initialize belief processor, inference GNN, policy and Q-networks with parameters $\psi^i_{\text{Transformer}}$, $\phi^i_{\text{GNN}}$, $\theta^i$, $\psi^i_{\beta}$
 \State Initialize replay buffer $D^i$, initial belief $b^i_0$, and latent state $\boldsymbol{\hat{z}}^{-i}_0$
-\State Determine action space type (discrete or continuous)
+\State Initialize target networks
 \For{each step $t$}
-    \State Observe signal $o^i_t$ and joint action $\boldsymbol{a}_{t-1}$
+    \State Observe signal $o^i_t$ and neighbor actions $\boldsymbol{a}^{-i}_{t-1}$
     \State Update belief: $b^i_t, \mathbb{P}(s|b^i_t) = f_{\text{Transformer}}(b^i_{t-1}, o^i_t, \boldsymbol{a}_{t-1}; \psi^i_{\text{Transformer}})$
-    \State Select action: 
-    \If{discrete action space}
-        \State $a^i_t \sim \pi^i(\cdot|b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$ \Comment{Sample from categorical distribution}
-    \Else
-        \State $\mu, \sigma = \text{MLP}_{\text{policy}}(b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i)$
-        \State $\epsilon \sim \mathcal{N}(0, I)$
-        \State $a^i_t = \tanh(\mu + \sigma \odot \epsilon)$ \Comment{Sample using reparameterization trick}
-    \EndIf
+    \State Construct graph and infer latent: $\boldsymbol{\hat{z}}^{-i}_t = f_{\text{GNN}}(o^i_t, \boldsymbol{a}^{-i}_t, r^i_{t-1}, o^i_{t-1}; \phi^i_{\text{GNN}})$
+    \State Select action: $a^i_t \sim \text{Categorical}(\pi^i(\cdot|b^i_t, \boldsymbol{\hat{z}}^{-i}_t; \theta^i))$
     \State Execute action, observe reward $r^i_t$ and next signal $o^i_{t+1}$
-    \State Infer latent: $\boldsymbol{\hat{z}}^{-i}_{t+1} = f_{\text{GNN}}(o^i_t, \boldsymbol{a}_t, r^i_t, o^i_{t+1}; \phi^i)$
-    \State Store transition in replay buffer
+    \State Store $(o^i_t, b^i_t, \boldsymbol{\hat{z}}^{-i}_t, a^i_t, r^i_t, o^i_{t+1}, \boldsymbol{a}^{-i}_t)$ in replay buffer $D^i$
     \If{update step}
-        \State Sample batch $B$ from replay buffer $D^i$
-        \State Update inference module: $\phi^i \leftarrow \phi^i - \alpha_{\phi} \nabla_{\phi^i} J^i_{\text{elbo}}(B)$
-        \State Update value networks: $\psi^i_{\beta} \leftarrow \psi^i_{\beta} - \alpha_{\psi} \nabla_{\psi^i_{\beta}} J^i_{q}(B)$
-        \State Update policy: $\theta^i \leftarrow \theta^i - \alpha_{\theta} \nabla_{\theta^i} J^i_{\pi}(B)$ \Comment{Using appropriate entropy calculation}
+        \State Sample sequential batch $B$ from replay buffer $D^i$
+        \State Update inference GNN: $\phi^i_{\text{GNN}} \leftarrow \phi^i_{\text{GNN}} - \alpha_{\phi} \nabla_{\phi^i_{\text{GNN}}} J^i_{\text{elbo}}(B)$
+        \State Update dual Q-networks: $\psi^i_{\beta} \leftarrow \psi^i_{\beta} - \alpha_{\psi} \nabla_{\psi^i_{\beta}} J^i_{q}(B)$
+        \State Update policy: $\theta^i \leftarrow \theta^i - \alpha_{\theta} \nabla_{\theta^i} J^i_{\pi}(B)$
         \State Update belief processor: $\psi^i_{\text{Transformer}} \leftarrow \psi^i_{\text{Transformer}} - \alpha_{\psi} \nabla_{\psi^i_{\text{Transformer}}} J^i_{\text{transformer}}(B)$
         \State Update target networks: $\bar{\psi}^i_{\beta} \leftarrow \tau \psi^i_{\beta} + (1-\tau) \bar{\psi}^i_{\beta}$
-        \If{true state has changed}
-            \State Calculate Fisher matrices from current replay buffer
-            \State Register task with EWC
-        \EndIf
     \EndIf
@@
 
-The algorithm follows a sequential process where each agent first updates its belief state based on new observations and the joint actions of all agents using the Transformer-based belief processor.
-Based on this updated belief and the current inference of other agents' latent states, the agent selects an action using its stochastic policy—sampling from a categorical distribution for discrete action spaces or using the reparameterization trick for continuous action spaces.
-After executing this action and observing the reward and next observation, the agent updates its inference of other agents' latent states using the GNN-based inference module.
-All of these experiences are stored in a replay buffer for later training.
-
-At designated update steps, the agent samples a batch of transitions from its replay buffer and uses these to update all network components.
-The inference module is updated first to improve predictions of other agents' actions using the ELBO objective.
-Next, the value networks are updated to better estimate expected returns.
-The policy network is then updated to maximize expected value and entropy.
-Finally, the belief processor is updated using the advantage-weighted training approach.
-Target networks, used for stable learning in the SAC framework, are updated using a weighted average of the current and target parameters.
-
-A crucial feature of POLARIS is its adaptive response to changes in the environment state.
-When the true state changes, the algorithm calculates Fisher information matrices from the current replay buffer and registers a new task with the EWC mechanism, preserving important knowledge from the previous state while allowing adaptation to the new state.
+Key implementation details include sequential batch sampling, where the replay buffer maintains sequential trajectories and samples sequences rather than individual transitions, preserving temporal dependencies crucial for transformer and GNN processing.
+The system employs dual Q-network updates with both Q-networks updated simultaneously using minimum value selection to prevent overestimation bias.
+All networks utilize gradient clipping with gradient norm clipping to maintain training stability.
+Target networks implement soft updates using exponential moving averages for stable learning.
 
 In the next chapter, we demonstrate the practical application of our POAMG framework and the POLARIS algorithm to canonical social learning scenarios from economic theory.
-The versatility of our approach is particularly evident in its ability to seamlessly handle both continuous and discrete action spaces, as well as varying types of return objectives.
-This capability proves essential when implementing strategic experimentation models with continuous allocation decisions and average reward objectives, and learning without experimentation models with discrete signaling actions and discounted reward objectives.
+The versatility of our approach is particularly evident in its ability to handle both average and discounted reward formulations.
+This capability proves essential when implementing strategic experimentation and learning without experimentation models with discrete action spaces.
 Through these implementations, we validate theoretical predictions from economic models while uncovering new insights about strategic adaptation in partially observable multi-agent systems that would be difficult to obtain through purely analytical approaches.

### 2025-06-06 paper/conclusion.tex
Update conclusion, introduction, results, and thesis abstract to reflect changes in analysis methodology from two-staged to ex-post.

@@
 Our methodological contributions extend beyond the specific applications studied.
-The two-staged analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting in neural networks.
+The ex-post analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting in neural networks.
 The discretization approach for continuous-time economic models, treating Lévy processes through Euler-Maruyama schemes and mapping continuous decisions to discrete action probabilities, provides a template for computational implementation while preserving essential incentive structures.

### 2025-06-06 paper/intro.tex
Update conclusion, introduction, results, and thesis abstract to reflect changes in analysis methodology from two-staged to ex-post.

@@
 Our implementation incorporates GNNs with temporal and spatial attention mechanisms that capture network topology and temporal dependencies, enabling agents to develop sophisticated strategies accounting for both environmental partial observability and strategic adaptation.
-POLARIS addresses the critical challenge of catastrophic forgetting through a two-staged analysis methodology that provides systematic approaches for extracting insights from multi-agent learning dynamics despite agents' inability to maintain stable policies across all states.
+POLARIS addresses the critical challenge of catastrophic forgetting through an ex-post analysis methodology that provides systematic approaches for extracting insights from multi-agent learning dynamics despite agents' inability to maintain stable policies across all states.
 

### 2025-06-06 paper/results.tex
Update conc, intro, abs.
Update conclusion, introduction, results, and thesis abstract to reflect changes in analysis methodology from two-staged to ex-post.

@@
 
-These fundamental constraints require us to reset agent parameters at the beginning of each episode rather than allowing continuous learning across state realizations.
-While this methodological necessity prevents direct measurement of the equilibrium strategies that economic theory and our POAMG framework predict, it does not invalidate our computational approach.
-Rather, it compels us to develop alternative analytical methodologies that can extract meaningful insights about multi-agent strategic behavior despite these inherent limitations of applying reinforcement learning to environments with conflicting learning objectives.
+These fundamental constraints force us to reset agent parameters at the beginning of each episode rather than allowing continuous learning across state realizations—a methodological compromise that fundamentally undermines our ability to directly test the theoretical equilibrium conditions.
+This parameter reset prevents agents from developing the ex ante conditional strategies that both economic theory and our POAMG framework predict, instead forcing them to learn state-specific policies that cannot generalize across different environmental realizations.
 
-Our experimental methodology therefore focuses on within-episode learning dynamics and cross-episode pattern analysis.
-By examining how agents adapt their behavior within episodes and identifying systematic patterns across episodes, we can still characterize the essential features of multi-agent social learning, even when direct equilibrium convergence measurement is precluded by computational limitations.
+Given these constraints, our experimental methodology necessarily shifts focus to within-episode learning dynamics and cross-episode pattern analysis.
+This indirect approach allows us to characterize certain features of multi-agent social learning, though it falls short of the direct equilibrium validation that would constitute ideal theoretical testing.
 
-\subsection{Two-Staged Analysis Methodology}
-\label{sec:two-staged-analysis}
+\subsection{Ex-Post Analysis Methodology}
+\label{sec:ex-post-analysis}
 
-To address the catastrophic forgetting limitation while still extracting meaningful insights about multi-agent learning patterns, we adopt a consistent two-staged analysis approach across both experimental scenarios.
-This methodology enables robust characterization of learning dynamics despite the fundamental constraints of applying reinforcement learning to environments with fixed but episode-varying states.
+Recognizing that catastrophic forgetting prevents direct measurement of equilibrium strategies, we implement an ex-post analysis methodology as a workaround to extract off-equilibrium learning patterns.
+While this approach cannot resolve the fundamental limitations discussed above, it provides a systematic framework for analyzing the learning patterns that we can observe within the constraints of our computational approach.
 
@@
 
-This methodology reveals whether observed disparities represent structural features of multi-agent learning or merely artifacts of specific agent characteristics like network position, as different agents assume extreme roles across different episodes.
+This methodology provides a limited window into multi-agent learning patterns, allowing us to examine whether observed disparities represent structural features that persist across episodes rather than artifacts of specific agent characteristics.
 
@@
 
-Following our two-staged analysis methodology, the POLARIS implementation tracks: (1) Convergence of individual agent allocation strategies to state-dependent optimal actions within episodes; (2) Belief fluctuations over time to assess the impact of neighbor action observation on learning; (3) Cumulative allocation disparities between highest and lowest allocators as a function of group size; and (4) Episode-wise analysis of allocation patterns across different true states (good vs.
+Following our ex-post analysis methodology, the POLARIS implementation tracks: (1) Convergence of individual agent allocation strategies to state-dependent optimal actions within episodes; (2) Belief fluctuations over time to assess the impact of neighbor action observation on learning; (3) Cumulative allocation disparities between highest and lowest allocators as a function of group size; and (4) Episode-wise analysis of allocation patterns across different true states (good vs.
 bad).
@@
 \end{figure}
+
 \paragraph{Dynamic Role Assignment and Allocation Disparities} Figures \ref{fig:highest_lowest_cumulative_allocators_good_state} and \ref{fig:highest_lowest_cumulative_allocators_bad_state} demonstrate a systematic widening of the gap between highest and lowest cumulative allocators as group size increases.
@@
 
-Following our two-staged analysis methodology described in Section \ref{sec:two-staged-analysis}, we track each agent's incorrect action probability as the probability assignment of the policy network to the incorrect action over time and estimate individual learning rates by fitting log-linear regressions to identify the fastest and slowest learners within each episode.
+Following our ex-post analysis methodology described in Section \ref{sec:ex-post-analysis}, we track each agent's incorrect action probability as the probability assignment of the policy network to the incorrect action over time and estimate individual learning rates by fitting log-linear regressions to identify the fastest and slowest learners within each episode.
 We then aggregate the performance of these extreme learners across episodes to examine whether the observed learning disparities represent structural features of multi-agent learning rather than artifacts of specific agent characteristics.

### 2025-06-06 paper/thesis.tex
Update appendices
Update results.
Update conclusion, introduction, results, and thesis abstract to reflect changes in analysis methodology from two-staged to ex-post.

@@
 We find that free-riding behavior does not lead to uniform inefficiencies—for some agents, performance in larger networks exceeds autarky levels.
-Our two-staged analysis methodology addresses computational challenges like catastrophic forgetting while providing systematic approaches for extracting insights from multi-agent learning dynamics.
+Our ex-post analysis methodology addresses computational challenges like catastrophic forgetting while providing systematic approaches for extracting insights from multi-agent learning dynamics.
 The framework contributes theoretical foundations to multi-agent reinforcement learning and computational tools to economic theory, demonstrating how interdisciplinary approaches can illuminate complex social learning phenomena neither field could address alone.
@@
 \input{intro}
-\chapter{Related Work}
+\chapter{Related Literature}
 \input{background}
@@
 \addcontentsline{toc}{chapter}{Appendices}
+
+% Appendices title page
+\begin{center}
+\vspace*{5cm}
+{\Huge \textbf{Appendices}}
+\end{center}
+\newpage
+
 \input{appendix}

### 2025-06-06 paper/results.tex
Update results.

@@
 In each episode, agents can only observe and learn from one realized state, forcing them away from the ex ante strategies that theoretical frameworks prescribe.
-Instead of developing belief-contingent policies, agents learn "do X" during episodes with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.
+Instead of developing belief-contingent policies that are flexible across states, agents learn "do X" during episodes with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.
 
@@
 However, this approach consistently fails due to a fundamental constraint of neural network learning.
-When network parameters are continuously updated across episodes, action-value functions adapt to the most recent state, leading to policies that are only optimal for the last state encountered.
+When network parameters are continuously updated across episodes with fixed states, action-value functions adapt to the most recent state, leading to policies that are only optimal for the last state encountered.
 This phenomenon—known as \emph{catastrophic forgetting}—fundamentally constrains model evaluation for ex ante analysis.
@@
 This methodology provides a limited window into multi-agent learning patterns, allowing us to examine whether observed disparities represent structural features that persist across episodes rather than artifacts of specific agent characteristics.
+However, in addition to the fundamental limitations discussed above, it prevents the ability to isolate belief formation mechnanisms from network parameter updates.
 
